### 2018-11-14 scripts/ms_accessories.Rmd
many changes

---
title: "mssel_summarize_output"
author: "Patrick Monnahan"
date: "10/25/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
msr = read.table("~/Documents/Research/PloidySim/mssel_out_R3.txt",head=T)
msr$s = as.factor(msr$s)
msr %<>% mutate(Alt=ifelse(str_detect(substr(subrep,2,9), "Alt"), "Alt", "Org"))
msr['ALTPloidy'] = paste(msr$ploidy, msr$Alt)
msr$ALTPloidy = as.factor(msr$ALTPloidy)

msr["REP"] = paste(msr$s, msr$dom, msr$rep, msr$Alt)

```

## R Markdown

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r}

ggplot(msr, aes(x=bp.end, y = div2, color = as.factor(ploidy), linetype=as.factor(sel))) + geom_smooth() + facet_grid(~dom)

ggplot(msr[msr$dom=="additive" & msr$s!=0.001,], aes(x=bp.end, y = div2, color = as.factor(ALTPloidy), linetype = s)) + geom_smooth(method="loess",span=0.2, size=1, se=F) + xlab("Position") + scale_color_brewer(limits=c("2 Org", "2 Alt","4 Alt","4 Org"), labels = c("Dip/Dip", "Tet/Dip", "Dip/Tet","Tet/Tet"),palette = "RdBu") + guides(linetype=guide_legend(title="Sel. Coeff."), color = guide_legend(title="Traj/Params"))

ggplot(msr[msr$s!=0.001,], aes(x=bp.end, y = div2, color = as.factor(ALTPloidy), linetype = s)) + geom_smooth(method="loess",span=0.2, size=1, se=F) + xlab("Position") + scale_color_brewer(limits=c("2 Org", "2 Alt","4 Alt","4 Org"), labels = c("Dip/Dip", "Tet/Dip", "Dip/Tet","Tet/Tet"),palette = "RdBu") + facet_grid(~dom) + guides(linetype=guide_legend(title="Sel. Coeff."), color = guide_legend(title="Traj/Params")) + theme_bw() + ylab("Diversity")

```

Functions to generate allele frequency trajectory of beneficial alleles
```{r}

genoFreqs = function(freqs){
  AA = freqs ^ 2
  Aa = 2 * freqs * (1 - freqs)
  aa = (1 - freqs) ^ 2
  AAAA = freqs ^ 4
  AAAa = 4 * (freqs ^ 3) * (1 - freqs)
  AAaa = 6 * (freqs ^ 2) * (1 - freqs) ^ 2
  Aaaa = 4 * freqs * (1 - freqs) ^ 3
  aaaa = (1 - freqs) ^ 4
  dfreq = data.frame("p" = freqs, "AA" = AA, "Aa" = Aa, "aa" = aa, "Ploidy" = rep(2, length(freqs)))
  tfreq = data.frame("p" = freqs, "AAAA" = AAAA, "AAAa" = AAAa, "AAaa" = AAaa, "Aaaa" = Aaaa, "aaaa" = aaaa, "Ploidy" = rep(4, length(freqs)))
  DF = rbind(melt(dfreq, id.var = c("p", "Ploidy")), melt(tfreq, id.var = c("p", "Ploidy")))
  return(DF)
}

freqs = genoFreqs(seq(0,1,0.01))

ggplot(freqs, aes(x = p, y = value, color = as.factor(Ploidy), group = variable)) + geom_line() + scale_color_manual(name="Ploidy", values = c('red','blue')) + annotate("text", x = 0.25, y = 0.625, label="aa", color = "red") + annotate("text", x = 0.5, y = 0.55, label="Aa", color = "red") + annotate("text", x = 0.75, y = 0.625, label="AA", color = "red") + annotate("text", x = 0.085, y = 0.6, label="aaaa", color = "blue") + annotate("text", x = 0.085, y = 0.365, label="Aaaa", color = "blue") + annotate("text", x = 0.5, y = 0.395, label="AAaa", color = "blue") + annotate("text", x = 0.915, y = 0.365, label="AAAa", color = "blue") + annotate("text", x = 0.915, y = 0.6, label="AAAA", color = "blue") + ylab("Genotype Frequency") + xlab("Allele Frequency") + theme_bw()

dipTraj = function(s, h, start_freq, end_freq, max_gens){
  df = data.frame("s" = s, "h1" = h, "gen" = 0, "freq" = start_freq, "dp1" = 0, "dp2" = 0, "w.bar" = 0, "var.w" = 0, "w.bar.p" = 0, "h0" = NA, "h2" = NA, "ploidy" = as.factor(2))
  p = start_freq
  gen = 0
  fits = c(1 + s, 1 + (s * h), 1) / (1 + s)
  while (p < end_freq & gen < max_gens){
    q = 1 - p
    Gfreqs = c(p ^ 2, 2 * p * q, q ^ 2)
    num = (Gfreqs[1] * fits[1]) + (p * q * fits[2])
    w.bar.p = (p * fits[1]) + (q * fits[2])
    w.bar = sum(Gfreqs * fits)
    p_prime = num / w.bar
    dp1 = p_prime - p
    dp2 = (p * (w.bar.p - w.bar)) / w.bar
    p = p_prime
    var.w = sum((Gfreqs * (fits - w.bar) ^ 2) / length(Gfreqs))
    gen = gen + 1

    df = rbind(df, c(s, h, gen, p, dp1, dp2, w.bar, var.w, w.bar.p, NA, NA, 2))
  }
  return(df[-1,])
}

tetTraj = function(s, h2, h1, h0, start_freq, end_freq, max_gens){
  df = data.frame("s" = s, "h1" = h1, "gen" = 0, "freq" = start_freq, "dp1" = 0, "dp2" = 0, "w.bar" = 0, "var.w" = 0, "w.bar.p" = 0, "h0" = h0, "h2" = h2, "ploidy" = as.factor(4))
  p = start_freq
  gen = 0
  freq = c(p)
  fits = c(1 + s, 1 + (s * h0), 1 + (s * h1), 1 + (s * h2), 1) / (1 + s)
  while (p < end_freq & gen < max_gens){
    q = 1 - p
    Gfreqs = c(p ^ 4, 4 * p^3 * q, 6 * p^2 * q^2, 4 * p * q^3, q ^ 4)
    num = (Gfreqs[1] * fits[1]) + (3 * p ^ 3 * q * fits[2]) + (3 * p ^ 2 * q ^ 2 * fits[3]) + (p * q ^ 3 * fits[4])
    w.bar.p = ((p ^ 3) * fits[1]) + (3 * (p ^ 2) * q * fits[2]) + (3 * p * (q ^ 2) * fits[3]) + ((q ^ 3) * fits[4])
    w.bar = sum(Gfreqs * fits)
    p_prime = num / w.bar
    dp1 = p_prime - p
    dp2 = (p * (w.bar.p - w.bar)) / w.bar
    p = p_prime
    var.w = sum((Gfreqs * (fits - w.bar) ^ 2) / length(Gfreqs))
    gen = gen + 1
    df = rbind(df, c(s, h1, gen, p, dp1, dp2, w.bar, var.w, w.bar.p, h0, h2, 4))
  }
  return(df[-1,])
}

difTraj = function(s, start_freq, end_freq, N, ploidy, max_gens = 10000){
  df = data.frame("s" = s, "gen" = 0, "freq" = start_freq, "ploidy" = ploidy)
  p = start_freq
  gen = 0
  while (p < end_freq & gen < max_gens){
    pq = p * (1 - p)
    mux = 2 * N * s * pq / tanh(2 * N * s * p)
    t = 1 / (ploidy * 2 * N)
    varx = (pq * t) ^ 0.5
    p_prime = p + mux * t
    if (runif(1) >= 0.5){
      p_prime = p_prime + varx
    }
    else{
      p_prime = p_prime - varx
    }
    df = rbind(df, c(s, gen, p_prime, ploidy))
    print(c(p_prime, gen, mux, t, mux * t, varx))
    p = p_prime
    gen = gen + 1
  }
  return(df)
}

getFits = function(freqs, s, h0, h1, h2){
  df = data.frame("s" = s, "h1" = h1, "freq" = s, "w.bar" = 0, "var.w" = 0, "w.bar.p" = 0, "h0" = NA, "h2" = NA, "ploidy" = 2)
  for (i in 1:length(freqs)){
    p = freqs[i]
    q = 1 - p
    Tfits = c(1 + s, 1 + (s * h0), 1 + (s * h1), 1 + (s * h2), 1) / (1 + s)
    TGfreqs = c(p ^ 4, 4 * p^3 * q, 6 * p^2 * q^2, 4 * p * q^3, q ^ 4)
    Tw.bar = sum(TGfreqs * Tfits)
    Dfits = c(1 + s, 1 + (s * h1), 1) / (1 + s)
    DGfreqs = c(p ^ 2, 2 * p * q, q ^ 2)
    Dw.bar = sum(DGfreqs * Dfits)
    Tvar.w = sum((TGfreqs * (Tfits - Tw.bar) ^ 2) / length(TGfreqs))
    Dvar.w = sum((DGfreqs * (Dfits - Dw.bar) ^ 2) / length(DGfreqs))
    Dw.bar.p = (p * Dfits[1]) + (q * Dfits[2])
    Tw.bar.p = ((p ^ 3) * Tfits[1]) + (3 * (p ^ 2) * q * Tfits[2]) + (3 * p * (q ^ 2) * Tfits[3]) + ((q ^ 3) * Tfits[4])
    df = rbind(df, c(s, h1, p, Dw.bar, Dvar.w, Dw.bar.p, NA, NA, 2))
    df = rbind(df, c(s, h1, p, Tw.bar, Tvar.w, Tw.bar.p, h0, h2, 4))
  }
  return(df[-1,])
}

s = c(0.1, 0.01, 0.001)
h1 = c(0.5, 0, 1)
h0 = c(0.75, 0, 1)
h2 = c(0.25, 0, 1)

simTraj = function(s, h0, h1, h2, start_freq, end_freq, maxGen){
  traj = data.frame()
  for (i in 1:length(s)){
    for (j in 1:length(h1)){
      print(paste("Starting; s =", s[i], ", h =", h1[j]))
      jj = dipTraj(s[i], h1[j], start_freq, end_freq, maxGen)
      kk = tetTraj(s[i], h2[j], h1[j], h0[j], start_freq, end_freq, maxGen)
      traj = rbind(traj, jj)
      traj = rbind(traj, kk)
    }
  }
  return(traj)
}

traj = simTraj(s, h0, h1, h2, 0.05, 1.0, 9999)

ggplot(traj, aes(x=gen, y=freq, linetype=as.factor(s), color=ploidy)) + geom_line()+facet_grid(~h1,scales="free_x") + scale_color_discrete()

ggplot(traj[traj$s==0.1,], aes(x=gen, y=freq, linetype=as.factor(s), color=ploidy)) + geom_line() + scale_color_discrete()

ggplot(fits[fits$s==0.1,], aes(x=freq, y=var.w, color = as.factor(ploidy), linetype=as.factor(h1))) + geom_line() + scale_color_manual(name="Ploidy",values=c("red","blue")) + scale_linetype_discrete(name="Dominance", labels=c("Recessive","Additive","Dominant")) + xlab("Allele Frequency") + ylab("Variance in Fitness") + theme_bw()

ggplot(fits[fits$s==0.1,], aes(x=freq, y=w.bar, color = as.factor(ploidy), linetype=as.factor(h1))) + geom_line() + scale_color_manual(name="Ploidy",values=c("red","blue")) + scale_linetype_discrete(name="Dominance", labels=c("Recessive","Additive","Dominant")) + xlab("Allele Frequency") + ylab("Mean Fitness") + theme_bw()

```

```{r}

traj_file = "/Users/pmonnahan/Documents/Research/PloidySim/mssel_output/mssel_input/traj_p4_s0.001_N10000_recessive_rep4-4Alt.txt"

msselRun = function(N, n, traj_file, L = 1000000, mu = 1e-8, r = 1e-8, ploidy = 2, numWindows = 200, slideRate = 0.5, selPos = 0.5, selPop = 2, ms = "/Users/pmonnahan/Documents/Research/code/dmc/mssel_modified/mssel", ms_summarize = "/Users/pmonnahan/Documents/Research/PloidySim/scripts/ms_summarize.R"){

  p = ploidy

  out1 = str_replace(traj_file, ".txt", ".ms.out")
  out2 = str_replace(traj_file, ".txt", ".R.out")

  theta = N * p * mu * L 
  rho = N * p * r * L
  mig_str = "2 0 40 40 0 -ej 0.2825 2 1"

  args1 = paste((2 * p * n), 1, n * p, n * p, traj_file, L * selPos, "-r", rho, L, "-t", theta, "-I", mig_str)

  args2 = paste(out1, out2, L, numWindows, slideRate, Npops, selPop, n * p, n * p)

  system2(ms, args1, stdout = out1)

  system2(ms_summarize, args2)

  new_dat = read.table(out2)

  #change names
  return(new_dat)

}

dat = rbind(dat, new_dat)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

### 2018-11-14 scripts/ms_summarize.R

@@ -41,13 +41,23 @@ if (length(args)==0) {
   stop("At least one argument must be supplied (input file).n", call.=FALSE)
 } 
 
+in_file = args[1]
 out_file = args[2]
 Nsites = as.numeric(args[3])
-winSize = as.numeric(args[4])
+numWindows = as.numeric(args[4])
 slideRate = as.numeric(args[5])
 Npops = as.numeric(args[6])
 selPop = as.numeric(args[7])
 samp_sizes = as.numeric(c(args[8:length(args)]))
+
+in_file = "/Users/pmonnahan/Documents/Research/PloidySim/mssel_out_p2.0_s0.1_N1000000_additive_rep0Alt.txt"
+out_file = str_replace(in_file,"txt",".out")
+Nsites = 1000000
+numWindows = 20
+slideRate = 0.5
+Npops = 2
+selPop = 2
+samp_sizes = as.numeric(c(20,20))
 
 # Necessary Functions
 read.ms.output <- function( txt=NA, file.ms.output=NA,MSMS=FALSE) {
@@ -140,7 +150,8 @@ makePops <- function(sampSize_list){
   return(popList)
 }
 
-makePop.df=function(inp,Nsites,positions,selPop){
+## PROBLEM IS THAT EACH REP HAS A DIFFERENT NUMBER OF SITES.  USING ONE WINDOW SIZE RESULTS IN REPS WITH DIFFERENT NUMBER OF WINDOWS
+makePop.df=function(inp,Nsites,positions,selPop, numWindows){
   DF = data.frame()
   
   for (i in 1:length(inp@populations)){
@@ -148,18 +159,30 @@ makePop.df=function(inp,Nsites,positions,selPop){
     df$snp.start=as.numeric(str_split_fixed(rownames(df)," ",4)[,2])
     df$snp.end=as.numeric(str_split_fixed(str_split_fixed(rownames(df)," ",4)[,4]," ",2)[,1])
     df$rep=str_split_fixed(str_split_fixed(rownames(df),"_",3)[,3], "[.]",2)[,1]
-    
+
+    # df %<>% add_count(rep)
+    # df %>% mutate(winSize = round(length(positions[[1]]) / numWindows, digits = -1))
+    # 
+    # winSize = round(length(positions[[1]]) / numWindows, digits = -1)
+    # 
     df1=as.data.frame(get.linkage(inp)[[i]])
[…]

### 2018-11-14 scripts/mssel_wrapper.py

@@ -36,9 +36,9 @@ def makeFileNames(outdir, p, s, Ne, dom, rep):
 	return([traj_file, outfile, sumout])
 
 def make2popCmds(mssel_path, n_anc, n_der, p, num_reps, traj_file, selection_spot, rho, n_sites, theta, fuseTime, ms_out, Rscript_path, Rout, num_wind, slide_rate):
-	msCmd = f"{mssel_path} { (n_anc + n_der) * p } {num_reps} {n_anc * p} {n_der * p} {traj_file} {selection_spot} -r {rho} {n_sites} -t {theta} -I 2 0 {n_der * p} {n_anc * p} 0 -ej {fuseTime} 2 1 > {ms_out}"
+	msCmd = f"{mssel_path} { (n_anc + n_der) * p } {num_reps} {n_anc * p} {n_der * p} {traj_file} {selection_spot} -r {rho * p} {n_sites} -t {theta * p} -I 2 0 {n_der * p} {n_anc * p} 0 -ej {fuseTime} 2 1 > {ms_out}"
 	rCmd = f"{Rscript_path} {ms_out} {Rout.replace('.txt', '.tmp.txt')} {n_sites} {num_wind} {slide_rate} 2 1 {n_anc * p} {n_der * p}"
-	awkCmd = f"awk '{{printf \" {p} {rep} {s} {N} {dom} {n_sites} {theta} {rho} {Ne} %s {n_anc} {n_der} \\n\", $0}}\' {Rout.replace('.txt', '.tmp.txt')} > {Rout}"
+	awkCmd = f"awk '{{printf \" {p} {rep} {s} {N} {dom} {n_sites} {theta * p} {rho * p} {Ne} %s {n_anc} {n_der} \\n\", $0}}\' {Rout.replace('.txt', '.tmp.txt')} > {Rout}"
 	return([msCmd, rCmd, awkCmd])
 
 # Specify arguments to be read from the command line
@@ -47,7 +47,7 @@ parser.add_argument('-t', type=str, metavar='trajectory_file', required=True, he
 parser.add_argument('-o', type=str, metavar='output_directory', required=True, help='Full path to output directory.')
 parser.add_argument('-ms', type=str, metavar='mssel_path', default="/Users/pmonnahan/Documents/Research/code/dmc/mssel_modified/mssel", required=False, help='Full path to mssel executable')
[…]

### 2018-12-26 scripts/PloidySelection_Figs.Rmd
cluster runs and figs in markdown

---
title: "PloidySelection_Figs"
author: "Patrick Monnahan"
date: "10/25/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
library(assertthat)
library(tidyverse)
library(PopGenome)
library(stringr)
library(data.table)
library(gridExtra)

```

HW Genotype frequencies for diploids and tetraploids
```{r}
# Generate HW genotype frequencies for dips and tets
genoFreqs = function(freqs){
  AA = freqs ^ 2
  Aa = 2 * freqs * (1 - freqs)
  aa = (1 - freqs) ^ 2
  AAAA = freqs ^ 4
  AAAa = 4 * (freqs ^ 3) * (1 - freqs)
  AAaa = 6 * (freqs ^ 2) * (1 - freqs) ^ 2
  Aaaa = 4 * freqs * (1 - freqs) ^ 3
  aaaa = (1 - freqs) ^ 4
  dfreq = data.frame("p" = freqs, "AA" = AA, "Aa" = Aa, "aa" = aa, "Ploidy" = rep(2, length(freqs)))
  tfreq = data.frame("p" = freqs, "AAAA" = AAAA, "AAAa" = AAAa, "AAaa" = AAaa, "Aaaa" = Aaaa, "aaaa" = aaaa, "Ploidy" = rep(4, length(freqs)))
  DF = rbind(melt(dfreq, id.var = c("p", "Ploidy")), melt(tfreq, id.var = c("p", "Ploidy")))
  return(DF)
}

# Calculate diploid/tetraploid genotype frequencies across entire range of allele frequency values
freqs = genoFreqs(seq(0,1,0.01))

# Plot HW genotype frequencies
ggplot(freqs, aes(x = p, y = value, color = as.factor(Ploidy), group = variable)) + geom_line() + scale_color_manual(name="Ploidy", values = c('red','blue')) + annotate("text", x = 0.25, y = 0.625, label="aa", color = "red") + annotate("text", x = 0.5, y = 0.55, label="Aa", color = "red") + annotate("text", x = 0.75, y = 0.625, label="AA", color = "red") + annotate("text", x = 0.085, y = 0.6, label="aaaa", color = "blue") + annotate("text", x = 0.085, y = 0.365, label="Aaaa", color = "blue") + annotate("text", x = 0.5, y = 0.395, label="AAaa", color = "blue") + annotate("text", x = 0.915, y = 0.365, label="AAAa", color = "blue") + annotate("text", x = 0.915, y = 0.6, label="AAAA", color = "blue") + ylab("Genotype Frequency") + xlab("Allele Frequency") + theme_bw()
```

Dominance functions
```{r}
getDomCoefs = function(dominance, ploidy = 100){
  if (dominance == 0){
    coeffs = rep(0, ploidy - 1)
  }
  else if (dominance == 1){
    coeffs = rep(1, ploidy - 1)
  }
  else {
    dom = (1 - dominance) - 0.5
    dom = abs((dom * 10 + sign(dom)) ^ sign(dom))
    coeffs = (seq(1, ploidy - 1) / ploidy) ^ dom
  }
  return(coeffs)
}

doms = c(seq(0,1, 0.1))
Doms = as.data.frame(sapply(doms, getDomCoefs))
Doms = rbind(c(0,0,0,0,0,0,0), Doms, c(1,1,1,1,1,1,1))
colnames(Doms) = doms
Doms = cbind(Doms, data.frame("i/k"=seq(0,100) / 100))
mDoms = melt(Doms, id.var = "i.k")
ggplot(mDoms, aes(x = i.k, y = value, color = variable)) + geom_line() + scale_color_discrete(name = "Dominance\nScalar") + theme_bw() + xlab("i / k") + ylab("Dominance Coefficient")
```

Allele frequency trajectories plot (dips and tets)
```{r}
# Generate allele frequency trajectory based on deterministic recursion equations   
getTraj = function(s, dom, ploidy, start_freq, N = -9, end_freq = 0.99, maxGens = 9999, maxTries = 10){
  dom_coeffs = getDomCoefs(dom, ploidy)
  attempts = 0
  gen = 0
  p = start_freq
  k = ploidy
  while (attempts <= maxTries & p < end_freq & gen <= maxGens){
    df = data.frame("s" = s, "dom" = dom, "gen" = 0, "freq" = start_freq, "dp1" = 0, "w.bar" = 0, "ploidy" = ploidy)
    p = start_freq
    dp1 = 0
    gen = 0
    het_fits = 1 + dom_coeffs * s
    fits = c(1, het_fits, 1 + s) / (1 + s)
    while (p < end_freq & p > 0 & gen <= maxGens){
      q = 1 - p
      i = seq(0, k)
      Num = sum(choose(k, i) * ((k - i) / k) * (p ^ (k - i)) * (q ^ i) * rev(fits))
      Den = sum(choose(k, i) * (p ^ (k - i)) * (q ^ i) * rev(fits))
      p_prime = Num / Den
      if (N != -9){
        p_prime = sum(rbinom(N, k, p_prime)) / (k * N) 
      }
      df = rbind(df, c(s, dom, gen, p, dp1, Den, k))
      dp1 = p_prime - p
      p = p_prime
      gen = gen + 1
    }
    df = rbind(df, c(s, dom, gen, p, dp1, Den, k))
    attempts = attempts + 1
  }
  if (attempts > maxTries & nrow(df) <= maxGens){
    print(paste("Beneficial allele was lost due to drift for", maxTries, "consecutive attempts"))
  }
  if (nrow(df) > maxGens){
    print(paste("Beneficial allele did not fix before the maximum number of generations (", maxGens, ")."))
  }
  return(df[-1,])
}

#E.g
traj1 = rbind(getTraj(0.1, 0, 2, 0.05), getTraj(0.1, 0, 4, 0.05))
traj1 = rbind(traj1, getTraj(0.1, 0.5, 2, 0.05))
traj1 = rbind(traj1, getTraj(0.1, 0.5, 4, 0.05))
traj1 = rbind(traj1, getTraj(0.1, 1, 2, 0.05))
traj1 = rbind(traj1, getTraj(0.1, 1, 4, 0.05))

ggplot(traj1, aes(x=gen, y=freq, linetype=as.factor(dom), color=as.factor(ploidy))) + geom_line() + scale_color_manual(name="Ploidy",values=c('red','blue')) + scale_linetype_discrete(name="Dominance", labels=c("Recessive","Additive","Dominant")) + xlim(0,300) + theme_bw() + xlab("Generation") + ylab("Allele Frequency")

```

Allele frequency trajectories for additive allele with arbitrary ploidy
```{r}
s = 0.1
doms = c(0, 0.1, 0.3, 0.5, 0.7, 0.9, 1)
ploidies = c(2, 4, 6, 8)
traj2 = data.frame()
for (i in 1:length(doms)){
  for (j in 1:length(ploidies)){
    traj2 = rbind(traj2, getTraj(s, doms[i], ploidies[j], 0.05))
  }
}

ggplot(traj2, aes(x=gen/100, y=freq, color=as.factor(ploidy))) + geom_line() + scale_color_manual(name="Ploidy",values=c('red','blue','green','purple')) + theme_bw() + xlab("Generation (100's)") + ylab("Allele Frequency") + facet_grid(~dom, scales="free_x")
```

Mean and Variance in fitness
```{r}
# Generate fitness stats as a function of allele frequency
getFits = function(freqs, s, h1, h, h3){
  df = data.frame("s" = s, "h" = h, "freq" = s, "w.bar" = 0, "var.w" = 0, "w.bar.p" = 0, "h1" = NA, "h3" = NA, "ploidy" = 2)
  assert_that(length(h1) == length(h))
  assert_that(length(h) == length(h3))
  for (j in 1:length(s)){
    for(k in 1:length(h)){
    for (i in 1:length(freqs)){
      p = freqs[i]
      q = 1 - p
      Tfits = c(1 + s[j], 1 + (s[j] * h3[k]), 1 + (s[j] * h[k]), 1 + (s[j] * h1[k]), 1) / (1 + s[j])
      TGfreqs = c(p ^ 4, 4 * p^3 * q, 6 * p^2 * q^2, 4 * p * q^3, q ^ 4)
      Tw.bar = sum(TGfreqs * Tfits)
      Dfits = c(1 + s[j], 1 + (s[j] * h[k]), 1) / (1 + s[j])
      DGfreqs = c(p ^ 2, 2 * p * q, q ^ 2)
      Dw.bar = sum(DGfreqs * Dfits)
      Tvar.w = sum((TGfreqs * (Tfits - Tw.bar) ^ 2) / length(TGfreqs))
      Dvar.w = sum((DGfreqs * (Dfits - Dw.bar) ^ 2) / length(DGfreqs))
      Dw.bar.p = (p * Dfits[1]) + (q * Dfits[2])
      Tw.bar.p = ((p ^ 3) * Tfits[1]) + (3 * (p ^ 2) * q * Tfits[2]) + (3 * p * (q ^ 2) * Tfits[3]) + ((q ^ 3) * Tfits[4])
      df = rbind(df, c(s[j], h[k], p, Dw.bar, Dvar.w, Dw.bar.p, NA, NA, 2))
      df = rbind(df, c(s[j], h[k], p, Tw.bar, Tvar.w, Tw.bar.p, h1[k], h3[k], 4))
    }
    }
  }
  return(df[-1,])
}

fits = getFits(seq(0, 1, 0.01), c(0.1, 0.01, 0.001), c(0.25, 1, 0), c(0.5, 1, 0), c(0.75, 1, 0))
# Plot mean fitness 
mean_fit = ggplot(fits[fits$s==0.1,], aes(x=freq, y=w.bar, color = as.factor(ploidy), linetype=as.factor(h))) + geom_line() + scale_color_manual(name="Ploidy",values=c("red","blue")) + scale_linetype_discrete(name="Dominance", labels=c("Recessive","Additive","Dominant")) + xlab("Allele Frequency") + ylab("Mean Fitness") + theme_bw()

var_fit = ggplot(fits[fits$s==0.1,], aes(x=freq, y=var.w, color = as.factor(ploidy), linetype=as.factor(h))) + geom_line() + scale_color_manual(name="Ploidy",values=c("red","blue")) + scale_linetype_discrete(name="Dominance", labels=c("Recessive","Additive","Dominant")) + xlab("Allele Frequency") + ylab("Variance in Fitness") + theme_bw()

grid.arrange(mean_fit, var_fit)
```

Plot fixation probabilities as a function of ploidy
```{r}
#Fixation probs of diploids as function of N
getFix = function(p, s, N, c){
  num = 1 - exp(-2*c*N*s*p)
  den = 1 - exp(-2*c*N*s)
  return(num / den)
}

p = c(0.0001, 0.001, 0.01, 0.05, 0.1)
N = c(10, 100, 1000, 10000)
s = c(0.001, 0.01, 0.1)
c = c(2, 4, 6, 8)

params = expand.grid(p = p, s = s, N = N, ploidy = c)

params %<>% mutate(fixprob = pmap(list(p, s, N, ploidy), getFix))

params = data.frame("p" = c(0.0001, 0.001, 0.0))
fix = getFix(seq())

```

```{r}
# Function to loop over all possible combinations of s and h.
simTraj = function(s = c(0.1, 0.01, 0.001), h2 = c(0.25, 0, 1), h1 = c(0.5, 0, 1), h0 = c(0.75, 0, 1), start_freq =  0.05, end_freq = 1.0, maxGen = 9999){
  traj = data.frame()
  for (i in 1:length(s)){
    for (j in 1:length(h1)){
      print(paste("Starting; s =", s[i], ", h =", h1[j]))
      jj = dipTraj(s[i], h1[j], start_freq, end_freq, maxGen)
      kk = tetTraj(s[i], h2[j], h1[j], h0[j], start_freq, end_freq, maxGen)
      traj = rbind(traj, jj)
      traj = rbind(traj, kk)
    }
  }
  return(traj)
}

# Other plots

ggplot(traj, aes(x=gen, y=freq, linetype=as.factor(s), color=ploidy)) + geom_line()+facet_grid(~h1,scales="free_x") + scale_color_discrete()

ggplot(traj[traj$s==0.1,], aes(x=gen, y=var.w, linetype=as.factor(h1), color=ploidy)) + geom_line() + scale_color_manual(name="Ploidy",values=c("red","blue")) + scale_linetype_discrete(name="Dominance", labels=c("Recessive","Additive","Dominant")) + xlab("Generation") + ylab("Variance in Fitness") + theme_bw() + scale_x_log10()

ggplot(traj[traj$s==0.1,], aes(x=gen, y=w.bar, linetype=as.factor(h1), color=ploidy)) + geom_line() + scale_color_manual(name="Ploidy",values=c("red","blue")) + scale_linetype_discrete(name="Dominance", labels=c("Recessive","Additive","Dominant")) + xlab("Generation") + ylab("Mean Fitness") + theme_bw() + scale_x_log10()

ggplot(traj[traj$s==0.1,], aes(x=gen, y=freq, linetype=as.factor(s), color=ploidy)) + geom_line() + scale_color_manual(name="Ploidy",values=c("red","blue")) + scale_linetype_discrete(name="Dominance", labels=c("Recessive","Additive","Dominant")) + ylab("Allele Frequency") + xlab("Generation") + theme_bw()

ggplot(fits[fits$s==0.1,], aes(x=freq, y=var.w, color = as.factor(ploidy), linetype=as.factor(h1))) + geom_line() + scale_color_manual(name="Ploidy",values=c("red","blue")) + scale_linetype_discrete(name="Dominance", labels=c("Recessive","Additive","Dominant")) + xlab("Allele Frequency") + ylab("Variance in Fitness") + theme_bw()

ggplot(fits[fits$s==0.1,], aes(x=freq, y=w.bar, color = as.factor(ploidy), linetype=as.factor(h1))) + geom_line() + scale_color_manual(name="Ploidy",values=c("red","blue")) + scale_linetype_discrete(name="Dominance", labels=c("Recessive","Additive","Dominant")) + xlab("Allele Frequency") + ylab("Mean Fitness") + theme_bw()

```

OLD or incomplete ideas
```{r}

# Attempting to implement the diffusion approximations for dips and tets...currently not working
difTraj = function(s, start_freq, end_freq, N, ploidy, max_gens = 10000){
  df = data.frame("s" = s, "gen" = 0, "freq" = start_freq, "ploidy" = ploidy)
  p = start_freq
  gen = 0
  while (p < end_freq & gen < max_gens){
    pq = p * (1 - p)
    mux = 2 * N * s * pq / tanh(2 * N * s * p)
    t = 1 / (ploidy * 2 * N)
    varx = (pq * t) ^ 0.5
    p_prime = p + mux * t
    if (runif(1) >= 0.5){
      p_prime = p_prime + varx
    }
    else{
      p_prime = p_prime - varx
    }
    df = rbind(df, c(s, gen, p_prime, ploidy))
    print(c(p_prime, gen, mux, t, mux * t, varx))
    p = p_prime
    gen = gen + 1
  }
  return(df)
}

#Functions to run mssell
traj_file = "/Users/pmonnahan/Documents/Research/PloidySim/mssel_output/mssel_input/traj_p4_s0.001_N10000_recessive_rep4-4Alt.txt"
traj_file = "/Users/pmonnahan/Documents/Research/PloidySim/testing.txt"

msselRun = function(N, n, traj_file, L = 1000000, mu = 1e-8, r = 1e-8, ploidy = 2, numWindows = 200, slideRate = 0.5, selPos = 0.5, selPop = 2, ms = "/Users/pmonnahan/Documents/Research/code/dmc/mssel_modified/mssel", ms_summarize = "/Users/pmonnahan/Documents/Research/PloidySim/scripts/ms_summarize.R"){ 
  options(scipen=999)
  p = ploidy

  out1 = str_replace(traj_file, ".txt", ".ms.out")
  out2 = str_replace(traj_file, ".txt", ".R.out")

  theta = N * p * mu * L 
  rho = N * p * r * L
  mig_str = "2 0 40 40 0 -ej 0.2825 2 1"

  args1 = paste((2 * p * n), 1, n * p, n * p, traj_file, L * selPos, "-r", rho, L, "-t", theta, "-I", mig_str)

  args2 = paste(out1, out2, L, numWindows, slideRate, Npops, selPop, n * p, n * p)
  print(args1)
  print(args2)
  system2(ms, args1, stdout = out1)

  system2(ms_summarize, args2)

  new_dat = read.table(out2)

  #change names
  return(new_dat)

}

dat = rbind(dat, new_dat)

## Stochastic simulation of selection for a beneficial allele
PloidyForSim = function(ploidy,  N, s, h, start_freq, end_freq, maxGen, maxTries){

  assert_that(ploidy - length(h) == 1)
  attempts = 0

  #Sample individuals to reproduce
  # taken from https://stats.stackexchange.com/questions/67911/how-to-sample-from-a-discrete-distribution
  sampleDist = function(PLOIDY, n, genoFreqs) { 
    sample(x = seq(0, PLOIDY), n, replace = T, prob = genoFreqs)
  }

  #Initalize population
  fits = sort( c(1, 1 + h * s, 1 + s) / (1 + s))
  Pop = rbinom(n = N, size = ploidy, prob = start_freq)
  p = sum(Pop) / (ploidy * N)
  freqs = c(p)

  while(p < end_freq & length(freqs) < maxGen & attempts < maxTries){
    #Retry if stochastic loss of beneficial allele in previous generation
    if ( p == 0 ){
      Pop = rbinom(n = N, size = ploidy, prob = start_freq)
      p = sum(Pop) / (ploidy * N)
      freqs = c(p)
      attempts = attempts + 1
    }

    geno_freq = c( table(factor(Pop, levels = as.character(seq(0, ploidy)))) / N )
    g_prime = ( fits * geno_freq ) / sum(fits * geno_freq) 
    # Make individuals for next generation
    p1 = sampleDist(length(g_prime) - 1, N, g_prime)
    p2 = sampleDist(length(g_prime) - 1, N, g_prime)
    Pop = c()
    for (i in 1:N){
      g1 = sample(c(rep(0, ploidy - p1[i]), rep(1, p1[i])), ploidy / 2, replace = F)
      g2 = sample(c(rep(0, ploidy - p2[i]), rep(1, p2[i])), ploidy / 2, replace = F)
      Pop = c(Pop, sum(g1) + sum(g2))
    }
    p = sum(Pop) / (ploidy * N)
    print(p)
    freqs = c(freqs, p)
  }
  return(freqs)
}

writeTraj = function(file, traj, numPops, selPops, timeScale, trajName = "rep1"){
  gen = seq(1, length(traj) + 1) / timeScale
  traj = rev(traj)
  traj = c(traj, 0)
  anc_traj = rep(0, length(traj))
  fileConn = file(file)
  # writeLines(c(paste("ntraj:", "1"), paste("npop:", numPops), "", paste("n:", length(traj), trajName), paste(gen, traj, anc_traj), sep="\t"), fileConn)
  writeLines(c(paste("ntraj:", "1"), paste("npop:", numPops), paste("n:", length(traj), trajName)), con = fileConn)

  dat = data.frame("gen"=gen, "traj"=traj, "anc"=anc_traj)
  print(dat)
  write.table(dat, file, quote=F, col.names = F, row.names = F, sep="\t", append=T)
  close(fileConn)
}
```

### 2018-12-26 scripts/PloidyHitch.R

@@ -1,0 +1,366 @@
+#title: "PloidyHitch.R"
+#author: "Patrick Monnahan"
+#date: "11/23/2018"
+
+
+# Load required packages
+library(assertthat)
+library(dplyr)
+library(tidyr)
+library(PopGenome)
+library(stringr)
+library(data.table)
+library(foreach)
+library(doParallel)
+library(magrittr)
+library(parallel)
+
+# Read in arguments
+args = commandArgs(trailingOnly=TRUE)
+
+# test if there is at least one argument: if not, return an error
+if (length(args)==0) {
+  stop("At least one argument must be supplied (input file).n", call.=FALSE)
+} 
+
+outdir = args[1]
+path_to_mssel = args[2]
+num_cores = detectCores()
+
+cl <- makeCluster(num_cores - 1) # Do we need to leave one core to handle the results that are being returned??
+registerDoParallel(cl)
+
+##### BEGIN: Set parameter values to explore #####
+Ploidy = c(2, 4, 6, 8)
+pop_size = c(1000, 10000, 100000) # Keep this value above 100 and below 1000000 (computation time will increase with increasing pop_size)
+selection_coeff = c(0.1, 0.01, 0.001) # Keep this between 0 and 1
+dominance = c(0, 0.1, 0.4, 0.5, 0.6, 0.9, 1) #
+seq_len = 1000000 # Length of sequence that we will simulate with mssel.  Increasing this value will increase computation time.
+mutation_rate = c(1e-8, 1e-7) # per-base mutation rate; mu
+recomb_rate = c(1e-8, 1e-7) # per-base recombination rate; r
+sampGen = c(1, 100, 1000, 10000)
+fuseTime = c(1, 100, 1000, 10000)
+samp_num = 10 # number of individuals to sample
+num_reps = 5
+
+##### END: Set parameter values to explore #####
+
+####### Begin: Define Functions ##########
+
+# Retrieves dominance coefficients given ploidy and a single dominance scalar
+getDomCoefs = function(dom_scalar, ploidy = 100){
+  if (dom_scalar == 0){
+    coeffs = rep(0, ploidy - 1)
+  }
+  else if (dom_scalar == 1){
+    coeffs = rep(1, ploidy - 1)
+  }
+  else {
+    dom = (1 - dom_scalar) - 0.5
[…]

### 2018-12-26 scripts/ms_summarize.R

@@ -50,17 +50,17 @@ Npops = as.numeric(args[6])
 selPop = as.numeric(args[7])
 samp_sizes = as.numeric(c(args[8:length(args)]))
 
-in_file = "/Users/pmonnahan/Documents/Research/PloidySim/mssel_out_p2.0_s0.1_N1000000_additive_rep0Alt.txt"
-out_file = str_replace(in_file,"txt",".out")
-Nsites = 1000000
-numWindows = 20
-slideRate = 0.5
-Npops = 2
-selPop = 2
-samp_sizes = as.numeric(c(20,20))
+# in_file = "/Users/pmonnahan/Documents/Research/PloidySim/mssel_out_p2.0_s0.1_N1000000_additive_rep0Alt.txt"
+# out_file = str_replace(in_file,"txt",".out")
+# Nsites = 1000000
+# numWindows = 20
+# slideRate = 0.5
+# Npops = 2
+# selPop = 2
+# samp_sizes = as.numeric(c(20,20))
 
 # Necessary Functions
-read.ms.output <- function( txt=NA, file.ms.output=NA,MSMS=FALSE) {
+read.ms.output2 <- function( txt=NA, file.ms.output=NA,MSMS=FALSE) {
   
   if( !is.na(file.ms.output) ) txt <- scan(file=file.ms.output,
                                            what=character(0), sep="\n", quiet=TRUE)
@@ -150,8 +150,7 @@ makePops <- function(sampSize_list){
   return(popList)
 }
 
-## PROBLEM IS THAT EACH REP HAS A DIFFERENT NUMBER OF SITES.  USING ONE WINDOW SIZE RESULTS IN REPS WITH DIFFERENT NUMBER OF WINDOWS
-makePop.df=function(inp,Nsites,positions,selPop, numWindows){
+munge = function(inp,Nsites,positions,selPop, numWindows){
   DF = data.frame()
   
   for (i in 1:length(inp@populations)){
@@ -159,12 +158,7 @@ makePop.df=function(inp,Nsites,positions,selPop, numWindows){
     df$snp.start=as.numeric(str_split_fixed(rownames(df)," ",4)[,2])
     df$snp.end=as.numeric(str_split_fixed(str_split_fixed(rownames(df)," ",4)[,4]," ",2)[,1])
     df$rep=str_split_fixed(str_split_fixed(rownames(df),"_",3)[,3], "[.]",2)[,1]
-
-    # df %<>% add_count(rep)
[…]

### 2018-12-27 scripts/PloidySelection_Figs.Rmd
Some figure additions

@@
 library(assertthat)
-library(tidyverse)
+library(dplyr)
+library(purrr)
+library(tidyr)
+library(ggplot2)
 library(PopGenome)
@@
 library(gridExtra)
-
+library(magrittr)
 ```
@@
 Allele frequency trajectories plot (dips and tets)
-```{r}
+```{r, echo = FALSE}
 # Generate allele frequency trajectory based on deterministic recursion equations   
@@
 Allele frequency trajectories for additive allele with arbitrary ploidy
-```{r}
+```{r, echo = FALSE}
 s = 0.1
@@
 
-ggplot(traj2, aes(x=gen/100, y=freq, color=as.factor(ploidy))) + geom_line() + scale_color_manual(name="Ploidy",values=c('red','blue','green','purple')) + theme_bw() + xlab("Generation (100's)") + ylab("Allele Frequency") + facet_grid(~dom, scales="free_x")
+ggplot(traj2, aes(x=gen/1000, y=freq, color=as.factor(ploidy))) + geom_line() + scale_color_manual(name="Ploidy",values=c('red','blue','green','purple')) + theme_bw() + xlab("Generation (1k)") + ylab("Allele Frequency") + facet_wrap(~dom, scales="free_x", nrow = 2)
 ```
@@
 #Fixation probs of diploids as function of N
-getFix = function(p, s, N, c){
+getFix = function(s, N, c){
+  p = 1 / (N * c)
   num = 1 - exp(-2*c*N*s*p)
   den = 1 - exp(-2*c*N*s)
-  return(num / den)
+  return(as.numeric(num / den))
 }
 
-p = c(0.0001, 0.001, 0.01, 0.05, 0.1)
-N = c(10, 100, 1000, 10000)
-s = c(0.001, 0.01, 0.1)
+N = c(10, 20, 50, 100, 500, 1000)
+s = c(0.001)
 c = c(2, 4, 6, 8)
 
-params = expand.grid(p = p, s = s, N = N, ploidy = c)
+params = expand.grid(s = s, N = N, ploidy = c)
 
-params %<>% mutate(fixprob = pmap(list(p, s, N, ploidy), getFix))
+params %<>% mutate(fixprob = pmap(list(s, N, ploidy), getFix)) %>% unnest()
 
-params = data.frame("p" = c(0.0001, 0.001, 0.0))
-fix = getFix(seq())
-
+ggplot(params, aes(y = fixprob, x = N, color = as.factor(ploidy))) + geom_line() + geom_hline(yintercept = 2*s, linetype='dashed') + scale_x_log10() + xlab("Population Size") + ylab("Fixation Probability") + scale_color_discrete(name="Ploidy")
 ```
 
+OLD
 ```{r}
-# Function to loop over all possible combinations of s and h.
-simTraj = function(s = c(0.1, 0.01, 0.001), h2 = c(0.25, 0, 1), h1 = c(0.5, 0, 1), h0 = c(0.75, 0, 1), start_freq =  0.05, end_freq = 1.0, maxGen = 9999){
-  traj = data.frame()
-  for (i in 1:length(s)){
-    for (j in 1:length(h1)){
-      print(paste("Starting; s =", s[i], ", h =", h1[j]))
-      jj = dipTraj(s[i], h1[j], start_freq, end_freq, maxGen)
-      kk = tetTraj(s[i], h2[j], h1[j], h0[j], start_freq, end_freq, maxGen)
-      traj = rbind(traj, jj)
-      traj = rbind(traj, kk)
-    }
-  }
-  return(traj)
-}
-
-# Other plots
-
-ggplot(traj, aes(x=gen, y=freq, linetype=as.factor(s), color=ploidy)) + geom_line()+facet_grid(~h1,scales="free_x") + scale_color_discrete()
-
-ggplot(traj[traj$s==0.1,], aes(x=gen, y=var.w, linetype=as.factor(h1), color=ploidy)) + geom_line() + scale_color_manual(name="Ploidy",values=c("red","blue")) + scale_linetype_discrete(name="Dominance", labels=c("Recessive","Additive","Dominant")) + xlab("Generation") + ylab("Variance in Fitness") + theme_bw() + scale_x_log10()
-
-ggplot(traj[traj$s==0.1,], aes(x=gen, y=w.bar, linetype=as.factor(h1), color=ploidy)) + geom_line() + scale_color_manual(name="Ploidy",values=c("red","blue")) + scale_linetype_discrete(name="Dominance", labels=c("Recessive","Additive","Dominant")) + xlab("Generation") + ylab("Mean Fitness") + theme_bw() + scale_x_log10()
-
-ggplot(traj[traj$s==0.1,], aes(x=gen, y=freq, linetype=as.factor(s), color=ploidy)) + geom_line() + scale_color_manual(name="Ploidy",values=c("red","blue")) + scale_linetype_discrete(name="Dominance", labels=c("Recessive","Additive","Dominant")) + ylab("Allele Frequency") + xlab("Generation") + theme_bw()
-
-ggplot(fits[fits$s==0.1,], aes(x=freq, y=var.w, color = as.factor(ploidy), linetype=as.factor(h1))) + geom_line() + scale_color_manual(name="Ploidy",values=c("red","blue")) + scale_linetype_discrete(name="Dominance", labels=c("Recessive","Additive","Dominant")) + xlab("Allele Frequency") + ylab("Variance in Fitness") + theme_bw()
-
-ggplot(fits[fits$s==0.1,], aes(x=freq, y=w.bar, color = as.factor(ploidy), linetype=as.factor(h1))) + geom_line() + scale_color_manual(name="Ploidy",values=c("red","blue")) + scale_linetype_discrete(name="Dominance", labels=c("Recessive","Additive","Dominant")) + xlab("Allele Frequency") + ylab("Mean Fitness") + theme_bw()
+# # Function to loop over all possible combinations of s and h.
+# simTraj = function(s = c(0.1, 0.01, 0.001), h2 = c(0.25, 0, 1), h1 = c(0.5, 0, 1), h0 = c(0.75, 0, 1), start_freq =  0.05, end_freq = 1.0, maxGen = 9999){
+#   traj = data.frame()
+#   for (i in 1:length(s)){
+#     for (j in 1:length(h1)){
+#       print(paste("Starting; s =", s[i], ", h =", h1[j]))
+#       jj = dipTraj(s[i], h1[j], start_freq, end_freq, maxGen)
+#       kk = tetTraj(s[i], h2[j], h1[j], h0[j], start_freq, end_freq, maxGen)
+#       traj = rbind(traj, jj)
+#       traj = rbind(traj, kk)
+#     }
+#   }
+#   return(traj)
+# }
+# 
+# # Other plots
+# 
+# ggplot(traj, aes(x=gen, y=freq, linetype=as.factor(s), color=ploidy)) + geom_line()+facet_grid(~h1,scales="free_x") + scale_color_discrete()
+# 
+# ggplot(traj[traj$s==0.1,], aes(x=gen, y=var.w, linetype=as.factor(h1), color=ploidy)) + geom_line() + scale_color_manual(name="Ploidy",values=c("red","blue")) + scale_linetype_discrete(name="Dominance", labels=c("Recessive","Additive","Dominant")) + xlab("Generation") + ylab("Variance in Fitness") + theme_bw() + scale_x_log10()
+# 
+# ggplot(traj[traj$s==0.1,], aes(x=gen, y=w.bar, linetype=as.factor(h1), color=ploidy)) + geom_line() + scale_color_manual(name="Ploidy",values=c("red","blue")) + scale_linetype_discrete(name="Dominance", labels=c("Recessive","Additive","Dominant")) + xlab("Generation") + ylab("Mean Fitness") + theme_bw() + scale_x_log10()
+# 
+# ggplot(traj[traj$s==0.1,], aes(x=gen, y=freq, linetype=as.factor(s), color=ploidy)) + geom_line() + scale_color_manual(name="Ploidy",values=c("red","blue")) + scale_linetype_discrete(name="Dominance", labels=c("Recessive","Additive","Dominant")) + ylab("Allele Frequency") + xlab("Generation") + theme_bw()
+# 
+# ggplot(fits[fits$s==0.1,], aes(x=freq, y=var.w, color = as.factor(ploidy), linetype=as.factor(h1))) + geom_line() + scale_color_manual(name="Ploidy",values=c("red","blue")) + scale_linetype_discrete(name="Dominance", labels=c("Recessive","Additive","Dominant")) + xlab("Allele Frequency") + ylab("Variance in Fitness") + theme_bw()
+# 
+# ggplot(fits[fits$s==0.1,], aes(x=freq, y=w.bar, color = as.factor(ploidy), linetype=as.factor(h1))) + geom_line() + scale_color_manual(name="Ploidy",values=c("red","blue")) + scale_linetype_discrete(name="Dominance", labels=c("Recessive","Additive","Dominant")) + xlab("Allele Frequency") + ylab("Mean Fitness") + theme_bw()
 
@@
 # Attempting to implement the diffusion approximations for dips and tets...currently not working
-difTraj = function(s, start_freq, end_freq, N, ploidy, max_gens = 10000){
-  df = data.frame("s" = s, "gen" = 0, "freq" = start_freq, "ploidy" = ploidy)
-  p = start_freq
-  gen = 0
-  while (p < end_freq & gen < max_gens){
-    pq = p * (1 - p)
-    mux = 2 * N * s * pq / tanh(2 * N * s * p)
-    t = 1 / (ploidy * 2 * N)
-    varx = (pq * t) ^ 0.5
-    p_prime = p + mux * t
-    if (runif(1) >= 0.5){
-      p_prime = p_prime + varx
-    }
-    else{
-      p_prime = p_prime - varx
-    }
-    df = rbind(df, c(s, gen, p_prime, ploidy))
-    print(c(p_prime, gen, mux, t, mux * t, varx))
-    p = p_prime
-    gen = gen + 1
-  }
-  return(df)
-}
-
-#Functions to run mssell
-traj_file = "/Users/pmonnahan/Documents/Research/PloidySim/mssel_output/mssel_input/traj_p4_s0.001_N10000_recessive_rep4-4Alt.txt"
-traj_file = "/Users/pmonnahan/Documents/Research/PloidySim/testing.txt"
-
-msselRun = function(N, n, traj_file, L = 1000000, mu = 1e-8, r = 1e-8, ploidy = 2, numWindows = 200, slideRate = 0.5, selPos = 0.5, selPop = 2, ms = "/Users/pmonnahan/Documents/Research/code/dmc/mssel_modified/mssel", ms_summarize = "/Users/pmonnahan/Documents/Research/PloidySim/scripts/ms_summarize.R"){
-  options(scipen=999)
-  p = ploidy
-
-  out1 = str_replace(traj_file, ".txt", ".ms.out")
-  out2 = str_replace(traj_file, ".txt", ".R.out")
-
-  theta = N * p * mu * L 
-  rho = N * p * r * L
-  mig_str = "2 0 40 40 0 -ej 0.2825 2 1"
-
-  args1 = paste((2 * p * n), 1, n * p, n * p, traj_file, L * selPos, "-r", rho, L, "-t", theta, "-I", mig_str)
-
-  args2 = paste(out1, out2, L, numWindows, slideRate, Npops, selPop, n * p, n * p)
-  print(args1)
-  print(args2)
-  system2(ms, args1, stdout = out1)
-
-  system2(ms_summarize, args2)
-
-  new_dat = read.table(out2)
-
-  #change names
-  return(new_dat)
-
-}
-
-dat = rbind(dat, new_dat)
-
-## Stochastic simulation of selection for a beneficial allele
-PloidyForSim = function(ploidy,  N, s, h, start_freq, end_freq, maxGen, maxTries){
-
-  assert_that(ploidy - length(h) == 1)
-  attempts = 0
-
-  #Sample individuals to reproduce
-  # taken from https://stats.stackexchange.com/questions/67911/how-to-sample-from-a-discrete-distribution
-  sampleDist = function(PLOIDY, n, genoFreqs) { 
-    sample(x = seq(0, PLOIDY), n, replace = T, prob = genoFreqs)
-  }
-
-  #Initalize population
-  fits = sort( c(1, 1 + h * s, 1 + s) / (1 + s))
-  Pop = rbinom(n = N, size = ploidy, prob = start_freq)
-  p = sum(Pop) / (ploidy * N)
-  freqs = c(p)
-
-  while(p < end_freq & length(freqs) < maxGen & attempts < maxTries){
-    #Retry if stochastic loss of beneficial allele in previous generation
-    if ( p == 0 ){
-      Pop = rbinom(n = N, size = ploidy, prob = start_freq)
-      p = sum(Pop) / (ploidy * N)
-      freqs = c(p)
-      attempts = attempts + 1
-    }
-
-    geno_freq = c( table(factor(Pop, levels = as.character(seq(0, ploidy)))) / N )
-    g_prime = ( fits * geno_freq ) / sum(fits * geno_freq) 
-    # Make individuals for next generation
-    p1 = sampleDist(length(g_prime) - 1, N, g_prime)
-    p2 = sampleDist(length(g_prime) - 1, N, g_prime)
-    Pop = c()
-    for (i in 1:N){
-      g1 = sample(c(rep(0, ploidy - p1[i]), rep(1, p1[i])), ploidy / 2, replace = F)
-      g2 = sample(c(rep(0, ploidy - p2[i]), rep(1, p2[i])), ploidy / 2, replace = F)
-      Pop = c(Pop, sum(g1) + sum(g2))
-    }
-    p = sum(Pop) / (ploidy * N)
-    print(p)
-    freqs = c(freqs, p)
-  }
-  return(freqs)
-}
-
-writeTraj = function(file, traj, numPops, selPops, timeScale, trajName = "rep1"){
-  gen = seq(1, length(traj) + 1) / timeScale
-  traj = rev(traj)
-  traj = c(traj, 0)
-  anc_traj = rep(0, length(traj))
-  fileConn = file(file)
-  # writeLines(c(paste("ntraj:", "1"), paste("npop:", numPops), "", paste("n:", length(traj), trajName), paste(gen, traj, anc_traj), sep="\t"), fileConn)
-  writeLines(c(paste("ntraj:", "1"), paste("npop:", numPops), paste("n:", length(traj), trajName)), con = fileConn)
-
-  dat = data.frame("gen"=gen, "traj"=traj, "anc"=anc_traj)
-  print(dat)
-  write.table(dat, file, quote=F, col.names = F, row.names = F, sep="\t", append=T)
-  close(fileConn)
-}
+# difTraj = function(s, start_freq, end_freq, N, ploidy, max_gens = 10000){
+#   df = data.frame("s" = s, "gen" = 0, "freq" = start_freq, "ploidy" = ploidy)
+#   p = start_freq
+#   gen = 0
+#   while (p < end_freq & gen < max_gens){
+#     pq = p * (1 - p)
+#     mux = 2 * N * s * pq / tanh(2 * N * s * p)
+#     t = 1 / (ploidy * 2 * N)
+#     varx = (pq * t) ^ 0.5
+#     p_prime = p + mux * t
+#     if (runif(1) >= 0.5){
+#       p_prime = p_prime + varx
+#     }
+#     else{
+#       p_prime = p_prime - varx
+#     }
+#     df = rbind(df, c(s, gen, p_prime, ploidy))
+#     print(c(p_prime, gen, mux, t, mux * t, varx))
+#     p = p_prime
+#     gen = gen + 1
+#   }
+#   return(df)
+# }
+# 
+# #Functions to run mssell
+# traj_file = "/Users/pmonnahan/Documents/Research/PloidySim/mssel_output/mssel_input/traj_p4_s0.001_N10000_recessive_rep4-4Alt.txt"
+# traj_file = "/Users/pmonnahan/Documents/Research/PloidySim/testing.txt"
+# 
+# msselRun = function(N, n, traj_file, L = 1000000, mu = 1e-8, r = 1e-8, ploidy = 2, numWindows = 200, slideRate = 0.5, selPos = 0.5, selPop = 2, ms = "/Users/pmonnahan/Documents/Research/code/dmc/mssel_modified/mssel", ms_summarize = "/Users/pmonnahan/Documents/Research/PloidySim/scripts/ms_summarize.R"){
+#   options(scipen=999)
+#   p = ploidy
+#   
+#   out1 = str_replace(traj_file, ".txt", ".ms.out")
+#   out2 = str_replace(traj_file, ".txt", ".R.out")
+#   
+#   theta = N * p * mu * L 
+#   rho = N * p * r * L
+#   mig_str = "2 0 40 40 0 -ej 0.2825 2 1"
+#   
+#   args1 = paste((2 * p * n), 1, n * p, n * p, traj_file, L * selPos, "-r", rho, L, "-t", theta, "-I", mig_str)
+#   
+#   args2 = paste(out1, out2, L, numWindows, slideRate, Npops, selPop, n * p, n * p)
+#   print(args1)
+#   print(args2)
+#   system2(ms, args1, stdout = out1)
+# 
+#   system2(ms_summarize, args2)
+#   
+#   new_dat = read.table(out2)
+#   
+#   #change names
+#   return(new_dat)
+#   
+# }
+# 
+# dat = rbind(dat, new_dat)
+# 
+# ## Stochastic simulation of selection for a beneficial allele
+# PloidyForSim = function(ploidy,  N, s, h, start_freq, end_freq, maxGen, maxTries){
+#   
+#   assert_that(ploidy - length(h) == 1)
+#   attempts = 0
+#   
+#   #Sample individuals to reproduce
+#   # taken from https://stats.stackexchange.com/questions/67911/how-to-sample-from-a-discrete-distribution
+#   sampleDist = function(PLOIDY, n, genoFreqs) { 
+#     sample(x = seq(0, PLOIDY), n, replace = T, prob = genoFreqs)
+#   }
+#   
+#   #Initalize population
+#   fits = sort( c(1, 1 + h * s, 1 + s) / (1 + s))
+#   Pop = rbinom(n = N, size = ploidy, prob = start_freq)
+#   p = sum(Pop) / (ploidy * N)
+#   freqs = c(p)
+#   
+#   while(p < end_freq & length(freqs) < maxGen & attempts < maxTries){
+#     #Retry if stochastic loss of beneficial allele in previous generation
+#     if ( p == 0 ){
+#       Pop = rbinom(n = N, size = ploidy, prob = start_freq)
+#       p = sum(Pop) / (ploidy * N)
+#       freqs = c(p)
+#       attempts = attempts + 1
+#     }
+#     
+#     geno_freq = c( table(factor(Pop, levels = as.character(seq(0, ploidy)))) / N )
+#     g_prime = ( fits * geno_freq ) / sum(fits * geno_freq) 
+#     # Make individuals for next generation
+#     p1 = sampleDist(length(g_prime) - 1, N, g_prime)
+#     p2 = sampleDist(length(g_prime) - 1, N, g_prime)
+#     Pop = c()
+#     for (i in 1:N){
+#       g1 = sample(c(rep(0, ploidy - p1[i]), rep(1, p1[i])), ploidy / 2, replace = F)
+#       g2 = sample(c(rep(0, ploidy - p2[i]), rep(1, p2[i])), ploidy / 2, replace = F)
+#       Pop = c(Pop, sum(g1) + sum(g2))
+#     }
+#     p = sum(Pop) / (ploidy * N)
+#     print(p)
+#     freqs = c(freqs, p)
+#   }
+#   return(freqs)
+# }
+# 
+# writeTraj = function(file, traj, numPops, selPops, timeScale, trajName = "rep1"){
+#   gen = seq(1, length(traj) + 1) / timeScale
+#   traj = rev(traj)
+#   traj = c(traj, 0)
+#   anc_traj = rep(0, length(traj))
+#   fileConn = file(file)
+#   # writeLines(c(paste("ntraj:", "1"), paste("npop:", numPops), "", paste("n:", length(traj), trajName), paste(gen, traj, anc_traj), sep="\t"), fileConn)
+#   writeLines(c(paste("ntraj:", "1"), paste("npop:", numPops), paste("n:", length(traj), trajName)), con = fileConn)
+#   
+#   dat = data.frame("gen"=gen, "traj"=traj, "anc"=anc_traj)
+#   print(dat)
+#   write.table(dat, file, quote=F, col.names = F, row.names = F, sep="\t", append=T)
+#   close(fileConn)
+# }
 ```

### 2019-04-04 analysis/mssel_analysis.Rmd
stuck on XPEHH results

---
title: "Mssel_analysis"
author: "Patrick Monnahan"
date: "12/27/2018"
output: html_document
---

## Load packages and import data
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(assertthat)
library(ggplot2)
library(dplyr)
library(tidyr)
library(PopGenome)
library(stringr)
library(data.table)
library(magrittr)
library(wrapr)

ms2 = read.table("~/Documents/Research/PloidySim/data/mssel_out_2-24-19_fin.txt", head = T)

#Group windows into larger sets
ms2 %<>% mutate(ints = as.numeric(as.character(cut(bp.start, breaks = 50, labels = seq(1,50)))))

```

#Background

## Dominance scalar
This plot shows the dominance value of each genotype (given by within individual allele frequency) as a funciton of the dominance scalar
```{r}
getDomCoefs = function(dominance, ploidy = 100){
  if (dominance == 0){
    coeffs = rep(0, ploidy - 1)
  }
  else if (dominance == 1){
    coeffs = rep(1, ploidy - 1)
  }
  else {
    dom = (1 - dominance) - 0.5
    dom = abs((dom * 10 + sign(dom)) ^ sign(dom))
    coeffs = (seq(1, ploidy - 1) / ploidy) ^ dom
  }
  return(coeffs)
}

doms = c(seq(0,1, 0.1))
Doms = as.data.frame(sapply(doms, getDomCoefs))
Doms = rbind(c(0,0,0,0,0,0,0), Doms, c(1,1,1,1,1,1,1))
colnames(Doms) = doms
Doms = cbind(Doms, data.frame("i/k"=seq(0,100) / 100))
mDoms = melt(Doms, id.var = "i.k")
ggplot(mDoms, aes(x = i.k, y = value, color = variable)) + geom_line() + scale_color_discrete(name = "Dominance\nScalar") + theme_bw() + xlab("i / k") + ylab("Dominance Coefficient")
```

## Allele frequency trajectories based on deterministic recursion equations
```{r}
#Function creates trajectories
getTraj = function(s, dom, ploidy, start_freq, N = -9, end_freq = 0.99, maxGens = 9999, maxTries = 10){
  dom_coeffs = getDomCoefs(dom, ploidy)
  attempts = 0
  p = start_freq
  k = ploidy
  gen = 0
  while (attempts <= maxTries & p < end_freq & gen <= maxGens){
    df = data.frame("s" = s, "dom" = dom, "gen" = 0, "freq" = start_freq, "dp1" = 0, "w.bar" = 0, "ploidy" = ploidy)
    p = start_freq
    dp1 = 0
    gen = 0
    het_fits = 1 + dom_coeffs * s
    fits = c(1, het_fits, 1 + s) / (1 + s)
    while (p < end_freq & p > 0 & gen <= maxGens){
      q = 1 - p
      i = seq(0, k)
      Num = sum(choose(k, i) * ((k - i) / k) * (p ^ (k - i)) * (q ^ i) * rev(fits))
      Den = sum(choose(k, i) * (p ^ (k - i)) * (q ^ i) * rev(fits))
      p_prime = Num / Den
      if (N != -9){
        p_prime = sum(rbinom(N, k, p_prime)) / (k * N) 
      }
      df = rbind(df, c(s, dom, gen, p, dp1, Den, k))
      dp1 = p_prime - p
      p = p_prime
      gen = gen + 1
    }
    df = rbind(df, c(s, dom, gen, p, dp1, Den, k))
    attempts = attempts + 1
  }
  if (attempts > maxTries & nrow(df) <= maxGens){
    print(paste("Beneficial allele was lost due to drift for", maxTries, "consecutive attempts"))
  }
  if (nrow(df) > maxGens){
    print(paste("Beneficial allele did not fix before the maximum number of generations (", maxGens, ")."))
  }
  return(df[-1,])
}

# Param set to create trajectories for
params = data.frame("s" = rep(0.1,9), "dom" = c(rep(0.5,3), rep(0,3), rep(1,3)), "ploidy" = rep(c(2,4,8),3), "start" = rep(0.05, 9))

# Create trajectories
dat1 = foreach(i = 1:nrow(params), .combine=rbind) %do% {
  getTraj(params[i,]$s, params[i,]$dom, params[i,]$ploidy, params[i,]$start)
}

#plot
ggplot(dat1, aes(x=gen, y=freq, linetype=as.factor(dom), color=as.factor(ploidy))) + geom_line() + scale_color_discrete(name="Ploidy") + scale_linetype_discrete(name="Dominance Scalar", labels=c("0.1", "0.5", "0.9")) + xlim(0,300) + theme_bw() + xlab("Generation") + ylab("Allele Frequency")
```

## Fitness values as a function of frequency
```{r}
getFits = function(s, dom, ploidy){
  dom_coeffs = getDomCoefs(dom, ploidy)
  k = ploidy
  dat = foreach(i = 1:51, .combine=rbind) %do% {
    p = seq(0,1,1/50)[i]
    q = 1 - p
    het_fits = 1 + dom_coeffs * s
    fits = c(1, het_fits, 1 + s) / (1 + s)
    i = seq(0, k)
    freqs = choose(k, i) * (p ^ (k - i)) * (q ^ i)
    w.bar = sum(freqs * rev(fits))
    var.w = sum((freqs * (rev(fits) - w.bar) ^ 2) / length(freqs))
    data.frame('s' = s, 'dom' = dom, 'ploidy' = ploidy, 'freq' = p, 'w.bar' = w.bar, 'var.w' = var.w)
  }
  return(dat)
}

dat2 = foreach(i = 1:nrow(params), .combine=rbind) %do% {
  getFits(params[i,]$s, params[i,]$dom, params[i,]$ploidy)
}

ggplot(dat2, aes(x=freq, y=var.w, color = as.factor(ploidy), linetype=as.factor(dom))) + geom_line() + scale_color_discrete(name="Ploidy") + scale_linetype_discrete(name="Dominance", labels=c("0.1","0.5","0.9")) + xlab("Allele Frequency") + ylab("Variance in Fitness") + theme_bw()

ggplot(dat2, aes(x=freq, y=w.bar, color = as.factor(ploidy), linetype=as.factor(dom))) + geom_line() + scale_color_discrete(name="Ploidy") + scale_linetype_discrete(name="Dominance", labels=c("0.1","0.5","0.9")) + xlab("Allele Frequency") + ylab("Mean Fitness") + theme_bw()
```

## Variable key
N = Population size
s = selection coefficient; difference in fitness between alternative homozygotes
dom = dominance scalar; Run below chunk for meaning
recomb = per-base mutation rate
mu = per-base mutation rate.  Theta is ploidy x mu x N (x sequence length which is 1Mb)
sim_ploidy = ploidy used for mssel simulation.  Value used in calculating theta above
traj_ploidy = ploidy used to generate sweep trajectory.  see getTraj() function in PloidyHitch.R
sampGen = number of generations passed since selection ends (i.e. fixation of beneficial allele)
fuseGen = number of generations prior to start of sweep that the two populations fused.

## Summary of depth and breadth of peaks
Controlling for number of chromosomes in the population (i.e. Simulation Ploidy), higher ploidies have a shallower dip, due to the slowed rate of fixation of the sweeping allele. 
Similarly, the dips in diversity are narrower in higher ploidies for same reason as before. 
```{r}
MS2.a = ms2 %>% group_by(s, dom, recomb, N, mu, sim_ploidy, traj_ploidy, sampGen, fuseGen, rep) %>% summarize(depth = (mean(Pi.2,na.rm=T) - min(Pi.1)) / mean(Pi.2,na.rm=T))

MS2.a %>% filter(fuseGen == 1 & mu==1e-08 & N == 10000 & recomb=="1e-08" & s =="0.01") %>% ggplot(., aes(y=-(log(depth)), fill = as.factor(traj_ploidy), x = as.factor(sim_ploidy))) + geom_boxplot() + ylab(expression(paste("Dip Depth = min(", pi[1], ") / ",pi[2],sep = ""))) + facet_grid(~sampGen) + scale_y_log10() + scale_fill_discrete(name = "Trajectory\nPloidy") + xlab("Simulation Ploidy") + theme_bw()

MS2.b = ms2 %>% group_by(s, dom, recomb, N, mu, sim_ploidy, traj_ploidy, sampGen, fuseGen, rep, ints) %>% summarize(lessWind = ifelse(mean(Pi.1, na.rm=T) < (mean(Pi.2, na.rm=T) / 2),1,0))

MS2.c = MS2.b %>% group_by(s, dom, recomb, N, mu, sim_ploidy, traj_ploidy, sampGen, fuseGen, rep) %>% summarize(breadth = sum(lessWind) * 20000)

MS2.c %>% filter(fuseGen == 1 & mu==1e-08 & N == 10000 & recomb=="1e-08" & s =="0.01") %>% ggplot(., aes(y=breadth/1000, fill = as.factor(traj_ploidy), x = as.factor(sim_ploidy))) + geom_boxplot(notch=T) + ylab(expression(paste("Dip Breadth = Length (kb) of which ", pi[1], " < (",pi[2], " / 2)",sep = ""))) + facet_grid(~sampGen, labeller = label_both) + scale_fill_discrete(name = "Trajectory\nPloidy") + xlab("Simulation Ploidy") + theme_bw()

MS2.c %>% filter(fuseGen == 1 & mu==1e-08 & N == 10000 & recomb=="1e-08" & s =="0.01") %>% ggplot(., aes(y=breadth/1000, fill = as.factor(sampGen), x = as.factor(sim_ploidy))) + geom_boxplot(notch=T) + ylab(expression(paste("Dip Breadth = Length (1 kb) of which ", pi[1], " < (",pi[2], " / 2)",sep = ""))) + scale_y_log10() + scale_fill_discrete(name = "Generations prior\nto fixation") + xlab("Simulation Ploidy") + theme_bw()

# # Look for proportional difference in breadth/depth within a simul
# MS2.a %>% filter(fuseGen == 1 & mu==1e-08 & traj_ploidy == 4 & N == 10000 & recomb=="1e-08" & s =="0.01") %>% ggplot(., aes(y=depth, fill = as.factor(sampGen), x = as.factor(sim_ploidy))) + geom_boxplot(notch=T) + ylab(expression(paste("Dip Breadth = Length of which ", pi[1], " < (",pi[2], " / 2)",sep = "")))+ scale_fill_discrete(name = "Trajectory\nPloidy") + xlab("Simulation Ploidy") + theme_bw()
```

## Combined effects of factor of two and trajectory
Higher ploidies result in deeper and broader dips in diversity relative to diploids.  The effect of recombination rate is not striking.
```{r}
ms2 %>% filter(dom %in% c("0.1","0.9","0.5") & fuseGen == 1 & sampGen ==1 & mu==1e-08 & N == 10000 & sim_ploidy == traj_ploidy) %>% ggplot(., aes(y=Pi.1 * 100, color = as.factor(traj_ploidy), x = mid/100000)) + geom_smooth(method="loess", size =0.5, span=0.1, se=F) + scale_x_continuous(breaks=c(1,5,9)) + scale_y_continuous(breaks=c(0.05,0.15)) + xlab("Position (100 kb)") + ylab("Diversity (%)") + scale_color_discrete(name="Ploidy") + facet_grid(vars(recomb,s), vars(dom),labeller = label_both) + theme_bw()
```

## Trajectory effect
Here, we are keeping fixed the ploidy specified for the coalescent simulations (fixed at 8 in this example), and we are varying the ploidy under which the sweep trajectories are simulated.  For some parameter sets, higher ploidies and thus slower sweeps results in a visible difference in terms of the reduction of diversity at and around the beneficial allele.  The effect is more pronounced for weaker selection and for partial dominance/recessivity.  The breadth of the dips is also notably lesser for higher ploidies.  Thus, if chromosome number in a population is held constant, higher ploidies exhibit reduced signals associated with selective sweeps.
```{r}
ms2 %>% filter(dom %in% c("0.1","0.9","0.5") & N == 10000 & fuseGen == 1 & sampGen ==1 & mu==1e-08 & sim_ploidy == 8) %>% ggplot(., aes(y=Pi.1 * 100, color = as.factor(traj_ploidy), x = mid/100000)) + geom_smooth(method="loess", size =0.5, span=0.1, se=F) + scale_x_continuous(breaks=c(1,5,9)) + xlab("Position (100 kb)") + ylab("Diversity (%)") + scale_color_discrete(name="Trajectory\nPloidy") + facet_grid(vars(s, recomb), vars(dom),labeller = label_both, scales = "free_y") + theme_bw()
```

## Factor of 2 effect
This is the complement to the previous figure.  We use the same sweep trajectory, but we vary the ploidy specified for the coalescent simulation.  
```{r}

ms2 %>% filter(dom %in% c("0.1","0.9","0.5") & fuseGen == 1 & sampGen ==1 & mu==1e-08 & N == 10000 & traj_ploidy == 4) %>% ggplot(., aes(y=Pi.1 * 100, color = as.factor(sim_ploidy), x = mid/100000)) + geom_smooth(method="loess", size =0.5, span=0.1, se=F) + scale_x_continuous(breaks=c(1,5,9)) + scale_y_continuous(breaks=c(0.05,0.15)) + xlab("Position (100 kb)") + ylab("Diversity (%)") + scale_color_discrete(name="Simulation\nPloidy") + facet_grid(vars(recomb,s), vars(dom),labeller = label_both) + theme_bw()

```

## Effect of sample generation on Taj D.  Polyploids recover new mutations more quickly, but they take longer to drift to higher frequencies.  ThetaW goes up but ThetaPi lags...
```{r}
ms2 %>% filter(dom %in% c("0.1","0.9","0.5") & s==0.01 & fuseGen == 1 & mu==1e-08 & N == 10000 & sim_ploidy == traj_ploidy & recomb == 1e-08) %>% ggplot(., aes(y=Tajima.D_1, color = as.factor(sim_ploidy), x = mid/100000)) + geom_smooth(method="loess", size =0.5, span=0.1, se=F) + scale_x_continuous(breaks=c(1,5,9)) + xlab("Position (100 kb)") + ylab("Tajima's D") + scale_color_discrete(name="Ploidy") + facet_grid(vars(sampGen), vars(dom),labeller = label_both) + theme_bw()

ms2 %>% filter(dom == "0.5" & s==0.01 & fuseGen == 1 & mu==1e-08 & N == 10000 & recomb == 1e-08) %>% ggplot(., aes(y=Tajima.D_1, color = as.factor(sim_ploidy), x = mid/100000)) + geom_smooth(method="loess", size =0.5, span=0.1, se=F) + scale_x_continuous(breaks=c(1,5,9)) + xlab("Position (100 kb)") + ylab("Tajima's D") + scale_color_discrete(name="Ploidy") + facet_grid(vars(sampGen), vars(traj_ploidy),labeller = label_both) + theme_bw()
```

## Effect of sample generation on Fst.  
Neutral divergence in allele frequencies increases Fst more quickly in lower ploidies, thus erasing 'outlier' signal due to sweep
```{r}
ms2 %>% filter(dom %in% c("0.1","0.9","0.5") & s==0.01 & fuseGen == 1 & mu==1e-08 & N == 10000 & sim_ploidy == traj_ploidy & recomb == 1e-08) %>% ggplot(., aes(y=fst, color = as.factor(sim_ploidy), x = mid/100000)) + geom_smooth(method="loess", size =0.5, span=0.1, se=F) + scale_x_continuous(breaks=c(1,5,9)) + xlab("Position (100 kb)") + ylab("Fst") + scale_color_discrete(name="Ploidy") + facet_grid(vars(sampGen), vars(dom),labeller = label_both) + theme_bw()
```

##Analysis of rehh calculations
###Import Data
```{r}
traj.ehh = read.csv("~/Documents/Research/PloidySim/rehh/rehh_calcs_sp2_se0.01.csv")
fact.ehh = read.csv("~/Documents/Research/PloidySim/rehh/rehh_calcs_do0.5_fG1_DS.csv")
```

###Trajectory effect on xp-ehh (colors) 
```{r}
traj.ehh %>% filter(fuseGen=="fG1" & sampGen=="sG1" & recomb == "re1e-08" & dom=="do0.5" & N=="NN10000") %>% ggplot(.,aes(x=POSITION / 100000,y=xpehh.p,color=traj_ploidy)) + geom_smooth(method="loess", span=0.1, se = F) + scale_color_discrete(name="Trajectory\nPloidy", breaks=c("tp2","tp4","tp8"), labels=c("2","4","8")) + xlab("Position (100 kb)") + ylab(expression("-log"[10]*"(p-value)")) + theme_bw()

# fact.ehh %>% filter(sim_ploidy=="sp8" & fuseGen=="fG1" & sampGen=="sG1" & recomb == "re1e-08" & dom=="do0.5" & N=="NN10000") %>% ggplot(.,aes(x=POSITION / 100000,y=xpehh.p,color=traj_ploidy)) + geom_smooth(method="loess", span=0.1, se = F) + scale_color_discrete(name="Trajectory\nPloidy", breaks=c("tp2","tp4","tp8"), labels=c("2","4","8")) + xlab("Position (100 kb)") + ylab(expression("-log"[10]*"(p-value)")) + theme_bw()
```

###Factor of two effect on xp-ehh for different trajectory ploidies
That is, trajectory ploidy is constant within each panel, while simulation ploidy is varied.  Higher diversity in higher ploidies produces stronger signal due to greater deviation from baseline genomic diversity.

Something strange here though...why is p value always highest when tp=sp?
Maybe look at density of NA along chromosomes?
```{r}
# fact.ehh %>% filter(traj_ploidy == "tp4" & fuseGen=="fG1" & dom=="do0.5" & N=="NN10000" & recomb=="re1e-08" & sampGen=="sG1") %>% ggplot(.,aes(x=cut_interval(x=POSITION, n=50),y=xpehh.p,fill=sim_ploidy)) + geom_boxplot() + facet_grid(cols = vars(sampGen))

fact.ehh %>% filter(s == "se0.01" & fuseGen=="fG1" & recomb == "re1e-08" & dom=="do0.5" & N=="NN10000") %>% ggplot(.,aes(x=POSITION / 100000, y=nocalc, color=sim_ploidy)) + geom_smooth(method="loess", span=0.1, se = F) + scale_color_discrete(name="Simulation\nPloidy", breaks=c("sp2","sp4","sp8"), labels=c("2","4","8"))  + facet_grid(cols = vars(traj_ploidy), rows = vars(sampGen))  + xlab("Position (100 kb)") + ylab(expression("-log"[10]*"(p-value)")) + theme_bw()

```

###Effect of sample generation for each ploidy.  Does signal decay faster in higher or lower ploidies?
```{r}
fact.ehh %>% filter(s == "se0.01" & fuseGen=="fG1" & dom=="do0.5" & N=="NN10000" & recomb=="re1e-08") %>% ggplot(.,aes(x=POSITION,y=xpehh.p,color=sim_ploidy)) + geom_smooth() + facet_grid(rows = vars(traj_ploidy), cols = vars(sampGen))
```

# Less interesting analyses

## Effect of sample generation
Sample generation is the number of generations following a sweep at which sampling occurs
```{r} 
ms2 %>% filter(dom %in% c("0.1","0.9","0.5") & s==0.01 & fuseGen == 1 & mu==1e-08 & N == 10000 & recomb == 5e-08 & sim_ploidy == traj_ploidy) %>% ggplot(., aes(y=Pi.1 * 100, color = as.factor(sim_ploidy), x = mid/100000)) + geom_smooth(method="loess", size =0.5, span=0.1, se=F) + scale_x_continuous(breaks=c(1,5,9)) + scale_y_continuous(breaks=c(0.05,0.15)) + xlab("Position (100 kb)") + ylab("Diversity (%)") + scale_color_discrete(name="Simulation\nPloidy") + facet_grid(vars(sampGen), vars(dom),labeller = label_both) + theme_bw()
```

## Effect of population size
Nothing really interesting here...Smaller population size seems noisier as expected
```{r}
ms2 %>% filter(dom %in% c("0.1","0.9","0.5") & recomb=="1e-08" & fuseGen == 1 & sampGen ==1 & mu==1e-08 & sim_ploidy == traj_ploidy) %>% ggplot(., aes(y=Pi.1 * 100, color = as.factor(traj_ploidy), x = mid/100000)) + geom_smooth(method="loess", size =0.5, span=0.1, se=F) + scale_x_continuous(breaks=c(1,5,9)) + xlab("Position (100 kb)") + ylab("Diversity (%)") + scale_color_discrete(name="Ploidy") + facet_grid(vars(s, N), vars(dom),labeller = label_both, scales = "free_y") + theme_bw()
```

### 2019-04-04 scripts/PloidyHitch.R
forgot to add

@@ -5,6 +5,7 @@
 
 # Load required packages
 library(assertthat)
+library(plyr)
 library(dplyr)
 library(tidyr)
 library(PopGenome)
@@ -13,6 +14,8 @@ library(data.table)
 library(magrittr)
 library(doParallel)
 library(parallel)
+library(inline)
+library(wrapr)
 
 # Read in arguments
 args = commandArgs(trailingOnly=TRUE)
@@ -25,35 +28,185 @@ if (length(args)==0) {
 outdir = args[1]
 outfile = args[2]
 path_to_mssel = args[3]
-dom_idx = args[4]
-num_tries = args[5]
+dom_idx = as.numeric(args[4])
+num_tries = as.numeric(args[5])
 current_df = args[6] # file containing data of most current df of results.  used to keep track of how many reps we've done of each param set
-num_cores = detectCores()
+recomb_rate = as.numeric(args[7]) # per-base recombination rate; r
+num_reps = as.numeric(args[8])
+num_cores = detectCores() - 2
 
-cl <- makeCluster(num_cores - 1) # Do we need to leave one core to handle the results that are being returned??
-registerDoParallel(cl)
+#make tmpdir
+tmpdir = paste(outdir,"/tmp", round(runif(1, 5000,1000000000)), sep="")
+dir.create(tmpdir, showWarnings = FALSE)
+setwd(tmpdir)
+
+# cl <- makeCluster(num_cores) # Do we need to leave one core to handle the results that are being returned??
+# registerDoParallel(cl)
 
 ##### BEGIN: Set parameter values to explore #####
 Ploidy = c(2, 4, 8)
 pop_size = c(1000, 10000) # Keep this value above 100 and below 1000000 (computation time will increase with increasing pop_size)
-selection_coeff = c(0.1, 0.01, 0.001) # Keep this between 0 and 1
+selection_coeff = c(0.1, 0.01) # Keep this between 0 and 1
 
 dominance = c(0.1, 0.4, 0.5, 0.6, 0.9, 1, 0) #
 dominance = dominance[dom_idx]
 
 seq_len = 1000000 # Length of sequence that we will simulate with mssel.  Increasing this value will increase computation time.
-mutation_rate = c(1e-8, 1e-7) # per-base mutation rate; mu
[…]

### 2019-04-04 scripts/calcREHH.R

@@ -14,6 +14,7 @@ args = commandArgs(trailingOnly=TRUE)
 
 ms_outdir_path = args[1]
 outfile = args[2]
+downsample = 20
 files <- list.files(path = ms_outdir_path, pattern = "*.out", full.names=TRUE, recursive=FALSE)
 
 num_cores=4
@@ -224,7 +225,7 @@ parse_ms <- function(x, include_seeds=FALSE) {
   out
 }
 
-RE.input = function(ms_file, jit_amt = 1){
+RE.input = function(ms_file, num_chrom, jit_amt = 1){
   bb = read_lines(ms_file)
   aa = bb %>% parse_ms()
   haps = as.numeric(str_split(bb[1]," ")[[1]][2])
@@ -234,8 +235,8 @@ RE.input = function(ms_file, jit_amt = 1){
   hap_file2 = str_replace(ms_file,"[.]out",".hap2") #population 2 - nonsweep
   map_file = str_replace(ms_file,"[.]out",".map")
   
-  write.table(aa$gametes[[1]][1:(haps/2),1:aa$segsites] + 1, hap_file1, col.names = F)
-  write.table(aa$gametes[[1]][((haps/2) + 1):haps,1:aa$segsites] + 1, hap_file2, col.names = F)
+  write.table(aa$gametes[[1]][sample(1:(haps/2), num_chrom),1:aa$segsites] + 1, hap_file1, col.names = F)
+  write.table(aa$gametes[[1]][sample(((haps/2) + 1):haps, num_chrom),1:aa$segsites] + 1, hap_file2, col.names = F)
   
   write.table(data.frame("snp" = seq(1,aa$segsites), "chr" = rep("1",aa$segsites), "pos" = sort(ceiling(jitter(aa$positions[[1]] * L, amount = jit_amt))), "anc" = rep(1, aa$segsites), "der" = rep(2, aa$segsites)), map_file, col.names = F, row.names = F)
   return(c(hap_file1, hap_file2, map_file))
@@ -336,7 +337,7 @@ dat = foreach(i = 1:(length(files)), .combine=rbind,
         print(paste(i," of ",length(files),"; ", round(i/length(files)*100, 2), "% complete", sep = ''))
         params = str_split(basename(files[i]),"_")[[1]]
         paths = tryCatch({
-            RE.input(files[i])
+            RE.input(files[i], downsample)
           },
           error = function(e){
             message("Error: RE.input")
[…]

### 2019-04-05 analysis/mssel_analysis.Rmd
push summary

@@
 output: html_document
+toc: true
+toc_depth: 3
+toc_float: true
 ---
@@
 ## Load packages and import data
-```{r setup, include=FALSE}
+```{r setup, message=F}
 knitr::opts_chunk$set(echo = TRUE)
@@
 library(wrapr)
+library(foreach)
 
@@
 
-#Background
+---
 
-## Dominance scalar
-This plot shows the dominance value of each genotype (given by within individual allele frequency) as a funciton of the dominance scalar
-```{r}
+# Background {.tabset}
+
+## Dominance
+
+This plot shows the dominance value of each genotype (given by within individual allele frequency) as a function of the dominance scalar.
+The purpose was to write a function that would take a single dominance value that could be specified for any ploidy and return a comparable set of dominance coefficients for heterozygous genotypes.
+
+```{r, echo=T,message=F}
 getDomCoefs = function(dominance, ploidy = 100){
@@
 ggplot(mDoms, aes(x = i.k, y = value, color = variable)) + geom_line() + scale_color_discrete(name = "Dominance\nScalar") + theme_bw() + xlab("i / k") + ylab("Dominance Coefficient")
+
+# Example
+
+# dominance=c(seq(0.1,0.9,0.1))
+# > dominance
+# [1] 0.1 0.2 0.3 0.4 0.5 0.6 0.7 0.8 0.9
+
+# Centers around 0.5 (additivity)
+# dom = (1 - dominance) - 0.5
+# > dom
+# [1]  0.4  0.3  0.2  0.1  0.0 -0.1 -0.2 -0.3 -0.4
+
+# dom1 = abs((dom * 10 + sign(dom)) ^ sign(dom))
+# > dom1
+# [1] 5.0000000 4.0000000 3.0000000 2.0000000 1.0000000 0.5000000 0.3333333 0.2500000 0.2000000
+
+# > getDomCoefs(dominance = 0.2, ploidy = 4)
+# [1] 0.00390625 0.06250000 0.31640625
+# > getDomCoefs(dominance = 0.5, ploidy = 4)
+# [1] 0.25 0.50 0.75
+
 ```
 
-## Allele frequency trajectories based on deterministic recursion equations
-```{r}
+## Sweep trajectories
+
+These plots show a primary motivating result for this study, in that higher ploidies show increased fixation times of sweeping beneficial alleles regardless of the dominance scenario being evaluated.
+
+```{r, echo=T,message=F}
 #Function creates trajectories
@@
 
-## Fitness values as a function of frequency
-```{r}
+## Fitness
+
+First plot shows reason why allele frequency change is faster in lower ploidies; increased variance in fitness at any given frequency.
+The second plot just shows mean fitness as a function of allele frequency and is not terribly interesting.
+```{r, echo=T,message=F}
 getFits = function(s, dom, ploidy){
@@
 
-## Variable key
-N = Population size
-s = selection coefficient; difference in fitness between alternative homozygotes
-dom = dominance scalar; Run below chunk for meaning
-recomb = per-base mutation rate
-mu = per-base mutation rate.  Theta is ploidy x mu x N (x sequence length which is 1Mb)
-sim_ploidy = ploidy used for mssel simulation.  Value used in calculating theta above
-traj_ploidy = ploidy used to generate sweep trajectory.  see getTraj() function in PloidyHitch.R
-sampGen = number of generations passed since selection ends (i.e. fixation of beneficial allele)
-fuseGen = number of generations prior to start of sweep that the two populations fused.
+---
 
-## Summary of depth and breadth of peaks
+# mssel analysis
+
+### Variable key
+* N = Population size
+
+* s = selection coefficient; difference in fitness between alternative homozygotes
+
+* dom = dominance scalar; a single value that determines the dominance coefficients of heterozygous genotypes for an arbitrary ploidy
+
+* recomb = per-base recombination rate
+
+* mu = per-base mutation rate.  Theta is ploidy x mu x N (x sequence length which is 1Mb)
+
+* sim_ploidy = **Simulation Ploidy**; ploidy used for mssel simulation.  Value used in calculating theta above
+
+* traj_ploidy = **Trajectory Ploidy**; ploidy used to generate sweep trajectory.  see getTraj() function in PloidyHitch.R
+
+* sampGen = sampling generation; number of generations passed since selection ends (i.e. fixation of beneficial allele)
+
+* fuseGen = fuse generation; number of generations prior to start of sweep that the two populations fused.
+
+**Simulation Ploidy** and **Trajectory Ploidy** are the two focal variables.
+The former refers to the ploidy value used to scale population parameters when running mssel.
+For example, theta = 2(N)(mu)(sim_ploidy).
+The latter refers to the ploidy used for simulating the sweep trajectory, which is subsequently passed to mssel.
+
+## Summary of depth and breadth of peaks {.tabset}
 Controlling for number of chromosomes in the population (i.e. Simulation Ploidy), higher ploidies have a shallower dip, due to the slowed rate of fixation of the sweeping allele. 
 Similarly, the dips in diversity are narrower in higher ploidies for same reason as before.
-```{r}
+
+### Depth
+```{r, echo=T,message=F}
 MS2.a = ms2 %>% group_by(s, dom, recomb, N, mu, sim_ploidy, traj_ploidy, sampGen, fuseGen, rep) %>% summarize(depth = (mean(Pi.2,na.rm=T) - min(Pi.1)) / mean(Pi.2,na.rm=T))
@@
 MS2.a %>% filter(fuseGen == 1 & mu==1e-08 & N == 10000 & recomb=="1e-08" & s =="0.01") %>% ggplot(., aes(y=-(log(depth)), fill = as.factor(traj_ploidy), x = as.factor(sim_ploidy))) + geom_boxplot() + ylab(expression(paste("Dip Depth = min(", pi[1], ") / ",pi[2],sep = ""))) + facet_grid(~sampGen) + scale_y_log10() + scale_fill_discrete(name = "Trajectory\nPloidy") + xlab("Simulation Ploidy") + theme_bw()
+```
 
+### Breadth
+```{r, echo=T,message=F}
 MS2.b = ms2 %>% group_by(s, dom, recomb, N, mu, sim_ploidy, traj_ploidy, sampGen, fuseGen, rep, ints) %>% summarize(lessWind = ifelse(mean(Pi.1, na.rm=T) < (mean(Pi.2, na.rm=T) / 2),1,0))
@@
 
-MS2.c %>% filter(fuseGen == 1 & mu==1e-08 & N == 10000 & recomb=="1e-08" & s =="0.01") %>% ggplot(., aes(y=breadth/1000, fill = as.factor(traj_ploidy), x = as.factor(sim_ploidy))) + geom_boxplot(notch=T) + ylab(expression(paste("Dip Breadth = Length (kb) of which ", pi[1], " < (",pi[2], " / 2)",sep = ""))) + facet_grid(~sampGen, labeller = label_both) + scale_fill_discrete(name = "Trajectory\nPloidy") + xlab("Simulation Ploidy") + theme_bw()
-
-MS2.c %>% filter(fuseGen == 1 & mu==1e-08 & N == 10000 & recomb=="1e-08" & s =="0.01") %>% ggplot(., aes(y=breadth/1000, fill = as.factor(sampGen), x = as.factor(sim_ploidy))) + geom_boxplot(notch=T) + ylab(expression(paste("Dip Breadth = Length (1 kb) of which ", pi[1], " < (",pi[2], " / 2)",sep = ""))) + scale_y_log10() + scale_fill_discrete(name = "Generations prior\nto fixation") + xlab("Simulation Ploidy") + theme_bw()
-
-# # Look for proportional difference in breadth/depth within a simul
-# MS2.a %>% filter(fuseGen == 1 & mu==1e-08 & traj_ploidy == 4 & N == 10000 & recomb=="1e-08" & s =="0.01") %>% ggplot(., aes(y=depth, fill = as.factor(sampGen), x = as.factor(sim_ploidy))) + geom_boxplot(notch=T) + ylab(expression(paste("Dip Breadth = Length of which ", pi[1], " < (",pi[2], " / 2)",sep = "")))+ scale_fill_discrete(name = "Trajectory\nPloidy") + xlab("Simulation Ploidy") + theme_bw()
+MS2.c %>% filter(fuseGen == 1 & mu==1e-08 & N == 10000 & recomb=="1e-08" & s =="0.01" & sampGen == 1) %>% ggplot(., aes(y=breadth/1000, fill = as.factor(traj_ploidy), x = as.factor(sim_ploidy))) + geom_boxplot(notch=T) + ylab(expression(paste("Dip Breadth = Length (kb) of which ", pi[1], " < (",pi[2], " / 2)",sep = ""))) + scale_fill_discrete(name = "Trajectory\nPloidy") + xlab("Simulation Ploidy") + theme_bw()
 ```
 
-## Combined effects of factor of two and trajectory
-Higher ploidies result in deeper and broader dips in diversity relative to diploids.  The effect of recombination rate is not striking.
-```{r}
-ms2 %>% filter(dom %in% c("0.1","0.9","0.5") & fuseGen == 1 & sampGen ==1 & mu==1e-08 & N == 10000 & sim_ploidy == traj_ploidy) %>% ggplot(., aes(y=Pi.1 * 100, color = as.factor(traj_ploidy), x = mid/100000)) + geom_smooth(method="loess", size =0.5, span=0.1, se=F) + scale_x_continuous(breaks=c(1,5,9)) + scale_y_continuous(breaks=c(0.05,0.15)) + xlab("Position (100 kb)") + ylab("Diversity (%)") + scale_color_discrete(name="Ploidy") + facet_grid(vars(recomb,s), vars(dom),labeller = label_both) + theme_bw()
+### Decay
+Does breadth of peak decay more quickly for a given simulation ploidy
+
+```{r, echo=T,message=F}
+MS2.c %>% filter(fuseGen == 1 & mu==1e-08 & N == 10000 & recomb=="1e-08" & s =="0.01") %>% ggplot(., aes(y=breadth/1000, fill = as.factor(sampGen), x = as.factor(sim_ploidy))) + geom_boxplot(notch=T) + ylab(expression(paste("Dip Breadth = Length (1 kb) of which ", pi[1], " < (",pi[2], " / 2)",sep = ""))) + scale_y_log10() + scale_fill_discrete(name = "Generations prior\nto fixation") + xlab("Simulation Ploidy") + theme_bw()
 ```
+
+# Diversity plots {.tabset}
 
@@
 Thus, if chromosome number in a population is held constant, higher ploidies exhibit reduced signals associated with selective sweeps.
-```{r}
+
+```{r, echo=T,message=F}
 ms2 %>% filter(dom %in% c("0.1","0.9","0.5") & N == 10000 & fuseGen == 1 & sampGen ==1 & mu==1e-08 & sim_ploidy == 8) %>% ggplot(., aes(y=Pi.1 * 100, color = as.factor(traj_ploidy), x = mid/100000)) + geom_smooth(method="loess", size =0.5, span=0.1, se=F) + scale_x_continuous(breaks=c(1,5,9)) + xlab("Position (100 kb)") + ylab("Diversity (%)") + scale_color_discrete(name="Trajectory\nPloidy") + facet_grid(vars(s, recomb), vars(dom),labeller = label_both, scales = "free_y") + theme_bw()
@@
 
-## Factor of 2 effect
+## Factor-of-2 effect
 This is the complement to the previous figure.  We use the same sweep trajectory, but we vary the ploidy specified for the coalescent simulation.  
-```{r}
+```{r, echo=T,message=F}
 
@@
 
-## Effect of sample generation on Taj D.  Polyploids recover new mutations more quickly, but they take longer to drift to higher frequencies.  ThetaW goes up but ThetaPi lags...
-```{r}
-ms2 %>% filter(dom %in% c("0.1","0.9","0.5") & s==0.01 & fuseGen == 1 & mu==1e-08 & N == 10000 & sim_ploidy == traj_ploidy & recomb == 1e-08) %>% ggplot(., aes(y=Tajima.D_1, color = as.factor(sim_ploidy), x = mid/100000)) + geom_smooth(method="loess", size =0.5, span=0.1, se=F) + scale_x_continuous(breaks=c(1,5,9)) + xlab("Position (100 kb)") + ylab("Tajima's D") + scale_color_discrete(name="Ploidy") + facet_grid(vars(sampGen), vars(dom),labeller = label_both) + theme_bw()
+## Combined effects
+Higher ploidies result in deeper and broader dips in diversity relative to diploids.  The effect of recombination rate is not striking.
+```{r, echo=T,message=F}
+ms2 %>% filter(dom %in% c("0.1","0.9","0.5") & fuseGen == 1 & sampGen ==1 & mu==1e-08 & N == 10000 & sim_ploidy == traj_ploidy) %>% ggplot(., aes(y=Pi.1 * 100, color = as.factor(traj_ploidy), x = mid/100000)) + geom_smooth(method="loess", size =0.5, span=0.1, se=F) + scale_x_continuous(breaks=c(1,5,9)) + scale_y_continuous(breaks=c(0.05,0.15)) + xlab("Position (100 kb)") + ylab("Diversity (%)") + scale_color_discrete(name="Ploidy") + facet_grid(vars(recomb,s), vars(dom),labeller = label_both) + theme_bw()
+```
+
+# Effect of trajectory ploidy, simulation ploidy, and sample generation on classic selection metrics {.tabset}
+
+## Tajima's D
+
+Polyploids recover new mutations more quickly, but they take longer to drift to higher frequencies.  ThetaW goes up but ThetaPi lags...
+```{r, echoe=F}
+# ms2 %>% filter(dom %in% c("0.1","0.9","0.5") & s==0.01 & fuseGen == 1 & mu==1e-08 & N == 10000 & sim_ploidy == traj_ploidy & recomb == 1e-08) %>% ggplot(., aes(y=Tajima.D_1, color = as.factor(sim_ploidy), x = mid/100000)) + geom_smooth(method="loess", size =0.5, span=0.1, se=F) + scale_x_continuous(breaks=c(1,5,9)) + xlab("Position (100 kb)") + ylab("Tajima's D") + scale_color_discrete(name="Ploidy") + facet_grid(vars(sampGen), vars(dom),labeller = label_both) + theme_bw()
 
@@
 
-## Effect of sample generation on Fst.  
+## Fst
+
 Neutral divergence in allele frequencies increases Fst more quickly in lower ploidies, thus erasing 'outlier' signal due to sweep
-```{r}
+```{r, echo=T,message=F}
 ms2 %>% filter(dom %in% c("0.1","0.9","0.5") & s==0.01 & fuseGen == 1 & mu==1e-08 & N == 10000 & sim_ploidy == traj_ploidy & recomb == 1e-08) %>% ggplot(., aes(y=fst, color = as.factor(sim_ploidy), x = mid/100000)) + geom_smooth(method="loess", size =0.5, span=0.1, se=F) + scale_x_continuous(breaks=c(1,5,9)) + xlab("Position (100 kb)") + ylab("Fst") + scale_color_discrete(name="Ploidy") + facet_grid(vars(sampGen), vars(dom),labeller = label_both) + theme_bw()
@@
 
-##Analysis of rehh calculations
-###Import Data
+---
+
+# Analysis of rehh calculations
+
+This R package calculates EHH (Extended Haplotype Homozygosity) and related metrics, which can be used to detect a selective sweep.  I'm showing results for the XP-EHH, the cross-populatin EHH.
+
+[Link to Article](https://www.nature.com/articles/nature06250)
+
+### Import Data
 ```{r}
@@
 
-###Trajectory effect on xp-ehh (colors) 
-```{r}
+## Trajectory effect
+
+Faster sweeps in the lower ploidies results in stronger signals of selection.
+```{r, echo=T,message=F}
 traj.ehh %>% filter(fuseGen=="fG1" & sampGen=="sG1" & recomb == "re1e-08" & dom=="do0.5" & N=="NN10000") %>% ggplot(.,aes(x=POSITION / 100000,y=xpehh.p,color=traj_ploidy)) + geom_smooth(method="loess", span=0.1, se = F) + scale_color_discrete(name="Trajectory\nPloidy", breaks=c("tp2","tp4","tp8"), labels=c("2","4","8")) + xlab("Position (100 kb)") + ylab(expression("-log"[10]*"(p-value)")) + theme_bw()
-
-# fact.ehh %>% filter(sim_ploidy=="sp8" & fuseGen=="fG1" & sampGen=="sG1" & recomb == "re1e-08" & dom=="do0.5" & N=="NN10000") %>% ggplot(.,aes(x=POSITION / 100000,y=xpehh.p,color=traj_ploidy)) + geom_smooth(method="loess", span=0.1, se = F) + scale_color_discrete(name="Trajectory\nPloidy", breaks=c("tp2","tp4","tp8"), labels=c("2","4","8")) + xlab("Position (100 kb)") + ylab(expression("-log"[10]*"(p-value)")) + theme_bw()
 ```
 
-###Factor of two effect on xp-ehh for different trajectory ploidies
-That is, trajectory ploidy is constant within each panel, while simulation ploidy is varied.
+## Factor-of-two effect
+
+Trajectory ploidy is constant within each panel, while simulation ploidy is varied.
 Higher diversity in higher ploidies produces stronger signal due to greater deviation from baseline genomic diversity.
@@
 Maybe look at density of NA along chromosomes?
-```{r}
-# fact.ehh %>% filter(traj_ploidy == "tp4" & fuseGen=="fG1" & dom=="do0.5" & N=="NN10000" & recomb=="re1e-08" & sampGen=="sG1") %>% ggplot(.,aes(x=cut_interval(x=POSITION, n=50),y=xpehh.p,fill=sim_ploidy)) + geom_boxplot() + facet_grid(cols = vars(sampGen))
-
-fact.ehh %>% filter(s == "se0.01" & fuseGen=="fG1" & recomb == "re1e-08" & dom=="do0.5" & N=="NN10000") %>% ggplot(.,aes(x=POSITION / 100000, y=nocalc, color=sim_ploidy)) + geom_smooth(method="loess", span=0.1, se = F) + scale_color_discrete(name="Simulation\nPloidy", breaks=c("sp2","sp4","sp8"), labels=c("2","4","8"))  + facet_grid(cols = vars(traj_ploidy), rows = vars(sampGen))  + xlab("Position (100 kb)") + ylab(expression("-log"[10]*"(p-value)")) + theme_bw()
-
+```{r, echo=T,message=F}
+fact.ehh %>% filter(s == "se0.01" & fuseGen=="fG1" & recomb == "re1e-08" & dom=="do0.5" & N=="NN10000") %>% ggplot(.,aes(x=POSITION / 100000, y=xpehh.p, color=sim_ploidy)) + geom_smooth(method="loess", span=0.1, se = F) + scale_color_discrete(name="Simulation\nPloidy", breaks=c("sp2","sp4","sp8"), labels=c("2","4","8"))  + facet_grid(cols = vars(traj_ploidy), rows = vars(sampGen))  + xlab("Position (100 kb)") + ylab(expression("-log"[10]*"(p-value)")) + theme_bw()
 ```
 
-###Effect of sample generation for each ploidy.  Does signal decay faster in higher or lower ploidies?
+## Sample generation effect
+
+Does signal decay faster in higher or lower ploidies?
+Answer seems to be that decay is faster in lower ploidies.  Drift is faster in lower ploidies, which is primary mechanism that erases signal of selection.  
 ```{r}
@@
 
+---
+
 # Less interesting analyses
 
-## Effect of sample generation
+### Effect of sample generation
 Sample generation is the number of generations following a sweep at which sampling occurs
@@
 
-## Effect of population size
+### Effect of population size
 Nothing really interesting here...Smaller population size seems noisier as expected
@@
 ```
+
+### Other plots
+```{r}
+fact.ehh %>% filter(traj_ploidy == "tp4" & fuseGen=="fG1" & dom=="do0.5" & N=="NN10000" & recomb=="re1e-08" & sampGen=="sG1") %>% ggplot(.,aes(x=cut_interval(x=POSITION, n=50),y=xpehh.p,fill=sim_ploidy)) + geom_boxplot() + facet_grid(cols = vars(sampGen))
+
+# # Look for proportional difference in breadth/depth within a simul
+MS2.a %>% filter(fuseGen == 1 & mu==1e-08 & traj_ploidy == 4 & N == 10000 & recomb=="1e-08" & s =="0.01") %>% ggplot(., aes(y=depth, fill = as.factor(sampGen), x = as.factor(sim_ploidy))) + geom_boxplot(notch=T) + ylab(expression(paste("Dip Breadth = Length of which ", pi[1], " < (",pi[2], " / 2)",sep = "")))+ scale_fill_discrete(name = "Trajectory\nPloidy") + xlab("Simulation Ploidy") + theme_bw()
+
+fact.ehh %>% filter(sim_ploidy=="sp8" & fuseGen=="fG1" & sampGen=="sG1" & recomb == "re1e-08" & dom=="do0.5" & N=="NN10000") %>% ggplot(.,aes(x=POSITION / 100000,y=xpehh.p,color=traj_ploidy)) + geom_smooth(method="loess", span=0.1, se = F) + scale_color_discrete(name="Trajectory\nPloidy", breaks=c("tp2","tp4","tp8"), labels=c("2","4","8")) + xlab("Position (100 kb)") + ylab(expression("-log"[10]*"(p-value)")) + theme_bw()
+```

### 2019-06-10 analysis/EvolTalk.Rmd
Talk Prep Figures

---
title: "R Notebook"
output: html_notebook
---

```{r}
library(assertthat)
library(ggplot2)
library(dplyr)
library(tidyr)
library(PopGenome)
library(stringr)
library(data.table)
library(magrittr)
library(wrapr)
library(foreach)
library(IDPmisc)

map <- purrr::map

ms = read.table("~/Documents/Research/PloidySim/data/mssel_out_2-24-19_fin.txt", head = T)

#Group windows into larger sets
ms %<>% mutate(driftGen = 0)

ms2 = read.table("~/Documents/Research/PloidySim/data/mssel_out_highRe_drift_4-30-19.txt", head = T)

#NEED TO ADD this data
ms3 = read.table("~/Documents/Research/PloidySim/data/mssel_out_5-10-19.txt", head = T)
ms3 %<>% filter(sim_ploidy!=1)

ms = rbind(ms,ms2)

ms %<>% mutate(ints = as.numeric(as.character(cut(bp.start, breaks = 50, labels = seq(1,50)))))
ms3 %<>% mutate(ints = as.numeric(as.character(cut(bp.start, breaks = 50, labels = seq(1,50)))))

ms = rbind(ms, ms3)

ms %>% filter(traj_ploidy==sim_ploidy & sampGen == "1" & s == 0.01 & dom == "0.5" & N == 10000 & sim_ploidy == 2) %>% ggplot(., aes(y=Pi.1 * 100, x = mid/100000)) + geom_smooth(method="loess", size =0.5, span=0.1, se=F, color = "black", fullrange=T) + geom_hline(yintercept = 0.051, linetype="dashed") + scale_x_continuous(expand = c(0,0), breaks=c(1,5,9), limits = c(0.2,9.8)) + coord_cartesian(ylim = c(0, 0.055), xlim = c(0.2, 9.8)) + xlab("Position (100 kb)") + ylab("Diversity (%)") + theme_bw() + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18),axis.text.x=element_text(size=16),axis.title.x=element_text(size=18),legend.text = element_text(size=16), legend.title = element_text(size=18))

MS2.a = ms %>% group_by(s, dom, recomb, N, mu, sim_ploidy, traj_ploidy, sampGen, fuseGen, rep, driftGen) %>% summarize(depth.pi = mean(Pi.2,na.rm=T) - min(Pi.1), min.pi = min(Pi.1, na.rm=T), max.taj = abs(min(Tajima.D_1, na.rm = T)), height.fst = max(fst, na.rm = T) - mean(fst, na.rm = T))

MS2.b = ms %>% group_by(s, dom, recomb, N, mu, sim_ploidy, traj_ploidy, sampGen, fuseGen, driftGen, rep, ints) %>% summarize(lessWind.pi = ifelse(mean(Pi.1, na.rm=T) < (mean(Pi.2, na.rm=T) / 2),1,0), lessWind.taj = ifelse(mean(Tajima.D_1, na.rm=T) < -1, 1, 0))

MS2.c = MS2.b %>% group_by(s, dom, recomb, N, mu, sim_ploidy, traj_ploidy, sampGen, fuseGen, driftGen, rep) %>% summarize(breadth.pi = sum(lessWind.pi) * 20000, breadth.taj = sum(lessWind.taj) * 20000)

MS2.f = merge(MS2.a, MS2.c, by = c("s", "dom", "recomb", "N", "mu", "sim_ploidy", "traj_ploidy", "sampGen", "fuseGen", "driftGen", "rep"))

MS2.f %<>% mutate(same_ploidy = ifelse(sim_ploidy==traj_ploidy, "yellow", "black"))

MS2.f %>% filter(sim_ploidy == traj_ploidy & mu==1e-08 & N == 10000 & s =="0.01" & driftGen %in% c(0,1) & sampGen == 1 & dom %in% c(0.1, 0.5, 0.9)) %>% mutate(Dom = factor(case_when(dom == 0.1 ~ "Partial Recessivity", dom == 0.5 ~ "Additivity", dom == 0.9 ~ "Partial Dominance"), levels = c("Partial Recessivity", "Additivity", "Partial Dominance")), Height = (log(min.pi, 10)), Breadth = breadth.pi/100000, Depth = depth.pi) %>% select(Dom, traj_ploidy, Depth, Breadth) %>% melt(., id.var = c("Dom", "traj_ploidy")) %>% ggplot(., aes(y = value, fill = as.factor(Dom), x = as.factor(traj_ploidy))) + geom_boxplot(outlier.shape = NA) + scale_fill_discrete(name = "Dominance") + facet_wrap(~variable, scales = "free_y") + ylab("") + xlab("Ploidy") + theme_bw() + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18),axis.text.x=element_text(size=16),axis.title.x=element_text(size=18),legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16))

#Ploidy
MS2.f %>% filter(sim_ploidy == traj_ploidy & mu==1e-08 & N == 10000 & s =="0.01" & driftGen %in% c(0,1) & sampGen == 1 & dom %in% c(0.1, 0.5, 0.9)) %>% mutate(Dom = factor(case_when(dom == 0.1 ~ "Partial Recessivity", dom == 0.5 ~ "Additivity", dom == 0.9 ~ "Partial Dominance"), levels = c("Partial Recessivity", "Additivity", "Partial Dominance")), Height = (log(min.pi, 10)), Breadth = breadth.pi/100000, Depth = depth.pi) %>% select(Dom, traj_ploidy, Depth, Breadth, Height) %>% melt(., id.var = c("Dom", "traj_ploidy")) %>% ggplot(., aes(y = value, fill = as.factor(Dom), x = as.factor(traj_ploidy))) + geom_boxplot(outlier.shape = NA) + scale_fill_manual(name = "Dominance", values=wes_palette("Royal1")) + facet_wrap(~variable, scales = "free_y") + ylab("") + xlab("Ploidy") + theme_bw() + theme(axis.text.y=element_blank(), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18),legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16), axis.ticks.y = element_blank())

#disentangling
MS2.f %>% filter(mu==1e-08 & N == 10000 & s =="0.01" & driftGen %in% c(0,1) & sampGen == 1 & dom %in% c(0.5)) %>% mutate(Height = (log(min.pi, 10)), Breadth = breadth.pi/100000, Depth = depth.pi) %>% select(sim_ploidy, traj_ploidy, Depth, Breadth, Height, same_ploidy) %>% melt(., id.var = c("sim_ploidy", "traj_ploidy", "same_ploidy")) %>% ggplot(., aes(y = value, fill = as.factor(traj_ploidy), x = as.factor(sim_ploidy), color = same_ploidy)) + geom_boxplot(outlier.shape = NA) + scale_fill_discrete(name = "Trajectory Ploidy") + scale_color_manual(guide=F, values = c("black", "red")) + facet_wrap(~variable, scales = "free_y") + ylab("") + xlab("Coalescent Ploidy") + theme_bw() + theme(axis.text.y=element_blank(), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18), legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16), axis.ticks.y = element_blank())

#drift
MS2.f %>% filter(mu==1e-08 & N == 10000 & s =="0.01" & driftGen %in% c(0) & sampGen == 1 & dom %in% c(0.5)) %>% mutate(Height = (log(min.pi, 10)), Breadth = breadth.pi/100000, Depth = depth.pi) %>% select(sim_ploidy, traj_ploidy, driftGen, Depth, Breadth, Height, same_ploidy) %>% melt(., id.var = c("sim_ploidy", "traj_ploidy", "driftGen", "same_ploidy")) %>% ggplot(., aes(y = value, fill = as.factor(traj_ploidy), x = as.factor(sim_ploidy), color = same_ploidy)) + geom_boxplot(outlier.shape = NA) + scale_color_manual(guide=F, values = c("black", "red")) + scale_fill_discrete(name = "Trajectory Ploidy") + facet_wrap(~variable, scales = "free_y") + ylab("") + xlab("Coalescent Ploidy") + theme_bw() + theme(axis.text.y=element_blank(), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18), legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16), axis.ticks.y = element_blank())

MS2.f %>% filter(mu==1e-08 & N == 10000 & s =="0.01" & driftGen %in% c(10000) & sampGen == 1 & dom %in% c(0.5)) %>% mutate(Height = (log(min.pi, 10)), Breadth = breadth.pi/100000, Depth = depth.pi) %>% select(sim_ploidy, traj_ploidy, driftGen, Depth, Breadth, Height, same_ploidy) %>% melt(., id.var = c("sim_ploidy", "traj_ploidy", "driftGen", "same_ploidy")) %>% ggplot(., aes(y = value, fill = as.factor(traj_ploidy), x = as.factor(sim_ploidy), color = same_ploidy)) + scale_color_manual(guide=F, values = c("black", "red")) + geom_boxplot(outlier.shape = NA) + scale_fill_discrete(name = "Trajectory Ploidy") + facet_wrap(~variable, scales = "free_y") + ylab("") + xlab("Coalescent Ploidy") + theme_bw() + theme(axis.text.y=element_blank(), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18), legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16), axis.ticks.y = element_blank())

#sampGen
MS2.f %>% filter(mu==1e-08 & N == 10000 & s =="0.1" & driftGen %in% c(0,1) & sampGen == 1 & dom %in% c(0.5)) %>% mutate(Breadth = breadth.taj/100000, "Minimum Tajima's D" = depth.taj) %>% select(sim_ploidy, traj_ploidy, `Minimum Tajima's D`, Breadth, same_ploidy) %>% melt(., id.var = c("sim_ploidy", "traj_ploidy", "same_ploidy")) %>% ggplot(., aes(y = value, fill = as.factor(traj_ploidy), x = as.factor(sim_ploidy), color = same_ploidy)) + geom_boxplot(outlier.shape = NA) + scale_fill_discrete(name = "Trajectory Ploidy") + scale_color_manual(guide=F, values = c("black", "red")) + facet_wrap(~variable, scales = "free_y") + ylab("") + xlab("Coalescent Ploidy") + theme_bw() + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18), legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16))

MS2.f %>% filter(mu==1e-08 & N == 10000 & s =="0.1" & driftGen %in% c(0,1) & sampGen == 10000 & dom %in% c(0.5)) %>% mutate(Breadth = breadth.taj/100000, "Minimum Tajima's D" = max.taj) %>% select(sim_ploidy, traj_ploidy, `Minimum Tajima's D`, Breadth, same_ploidy) %>% melt(., id.var = c("sim_ploidy", "traj_ploidy", "same_ploidy")) %>% ggplot(., aes(y = value, fill = as.factor(traj_ploidy), x = as.factor(sim_ploidy), color = same_ploidy)) + geom_boxplot(outlier.shape = NA) + scale_fill_discrete(name = "Trajectory Ploidy") + scale_color_manual(guide=F, values = c("black", "red")) + facet_wrap(~variable, scales = "free_y") + ylab("") + xlab("Coalescent Ploidy") + theme_bw() + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18), legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16))

MS2.f %>% filter(sampGen!="1000" & mu==1e-08 & N == 10000 & s =="0.1" & driftGen %in% c(0,1) & dom %in% c(0.5)) %>% mutate(Breadth = breadth.taj/100000, "Minimum Tajima's D" = max.taj) %>% select(sampGen, sim_ploidy, traj_ploidy, `Minimum Tajima's D`, Breadth, same_ploidy) %>% melt(., id.var = c("sim_ploidy", "traj_ploidy", "same_ploidy", "sampGen"))  %>% filter(variable == "Breadth") %>% ggplot(., aes(y = value, fill = as.factor(traj_ploidy), x = as.factor(sim_ploidy), color = same_ploidy)) + geom_boxplot(outlier.shape = NA) + scale_fill_discrete(name = "Trajectory Ploidy") + scale_color_manual(guide=F, values = c("black", "red")) + facet_wrap(~sampGen) + ylab("Breadth of dip (100kb)") + xlab("Coalescent Ploidy") + theme_bw() + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18), legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16))

MS2.f %>% filter(sampGen!="1000" & mu==1e-08 & N == 10000 & s =="0.1" & driftGen %in% c(0,1) & dom %in% c(0.5)) %>% mutate(Breadth = breadth.taj/100000, "Minimum Tajima's D" = max.taj) %>% select(sampGen, sim_ploidy, traj_ploidy, `Minimum Tajima's D`, Breadth, same_ploidy) %>% melt(., id.var = c("sim_ploidy", "traj_ploidy", "same_ploidy", "sampGen"))  %>% filter(variable == "Minimum Tajima's D") %>% ggplot(., aes(y = value, fill = as.factor(traj_ploidy), x = as.factor(sim_ploidy), color = same_ploidy)) + geom_boxplot(outlier.shape = NA) + scale_fill_discrete(name = "Trajectory Ploidy") + scale_color_manual(guide=F, values = c("black", "red")) + facet_wrap(~sampGen) + ylab("Minimum Tajima's D") + xlab("Coalescent Ploidy") + theme_bw() + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18), legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16))

#Fst
MS2.f %>% filter(mu==1e-08 & N == 10000 & s =="0.1" & driftGen %in% c(0,1) & sampGen == 1 & dom %in% c(0.5)) %>% mutate(Breadth = breadth.taj/100000, "Minimum Tajima's D" = max.taj, "Fst Height" = height.fst) %>% select(sim_ploidy, traj_ploidy, `Minimum Tajima's D`, Breadth, `Fst Height`, same_ploidy) %>% melt(., id.var = c("sim_ploidy", "traj_ploidy", "same_ploidy")) %>% ggplot(., aes(y = value, fill = as.factor(traj_ploidy), x = as.factor(sim_ploidy), color = same_ploidy)) + geom_boxplot(outlier.shape = NA) + scale_fill_discrete(name = "Trajectory Ploidy") + scale_color_manual(guide=F, values = c("black", "red")) + facet_wrap(~variable, scales = "free_y") + ylab("") + xlab("Coalescent Ploidy") + theme_bw() + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18), legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16))

getDims = function(dat, y.metric = "fst", offset = 100000){
  # dat = data.frame("mid" = mid, "fst" = febugst)
  peak = tryCatch({
    peaks(dat$mid, abs(dat[y.metric])) %>% filter(x > 500000 - offset & x < 500000 + offset & w > 0) %>% filter(w == max(w)) %>% summarize(height = max(y), width = max(w))}
    , error = function(e){
      return(data.frame("height" = -9, "width" = -9))
    })
  return(peak)
}

# getDims = function(dat, y.metric = "fst", offset = 100000){
#   # dat = data.frame("mid" = mid, "fst" = febugst)
#   peak = tryCatch({
#     peaks(dat$mid, abs(dat[y.metric])) %>% filter(x > 500000 - offset & x < 500000 + offset & w > 0) %>% summarize(height = median(y), width = median(w))}
#     , error = function(e){
#       return(data.frame("height" = -9, "width" = -9))
#     })
#   return(peak)
# }

ee = ms %>% filter(fuseGen==1 & driftGen %in% c(1,0,10000) & dom == 0.5 & sampGen %in% c(1,10000)) %>% nest(-c(s, dom, recomb, N, mu, sim_ploidy, traj_ploidy, sampGen, fuseGen, rep, driftGen)) %>% mutate(height.taj = map(data, ~getDims(., y.metric = "Tajima.D_1")$height), width.taj = map(data, ~getDims(., y.metric = "Tajima.D_1")$width), height.fst = map(data, ~getDims(.)$height), width.fst = map(data, ~getDims(.)$width), height.h = map(data, ~getDims(., y.metric = "Fay.Wu.H_1")$height), width.h = map(data, ~getDims(., y.metric = "Fay.Wu.H_1")$width), height.e = map(data, ~getDims(., y.metric = "Zeng.E_1")$height), width.e = map(data, ~getDims(., y.metric = "Zeng.E_1")$width),) %>% select(-data) %>% unnest()

ee %>% filter(sampGen == "1" & s == "0.01" & fuseGen=="1" & recomb == "5e-08" & dom=="0.5" & N=="10000" & driftGen == 0 & width.fst < 60000) %>% mutate("Magnitude" = height.fst, "Breadth" = width.fst / 10000, same_ploidy = ifelse(sim_ploidy == traj_ploidy, 1, 0)) %>% select(sim_ploidy, traj_ploidy, same_ploidy, Magnitude, Breadth) %>% melt(., id.var = c("sim_ploidy", "traj_ploidy", "same_ploidy")) %>% mutate("Fst" = variable) %>% filter(value != -9) %>% ggplot(., aes(y = value, fill = as.factor(traj_ploidy), x = as.factor(sim_ploidy), color = as.factor(same_ploidy))) + geom_boxplot(outlier.shape = NA) + scale_fill_discrete(name = "Trajectory Ploidy", labels = c("2", "4", "8")) + scale_color_manual(guide=F, values = c("black","red")) + facet_wrap(~Fst, scales = "free_y", labeller = label_both) + ylab("") + xlab("Coalescent Ploidy") + theme_bw() + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18), legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16))

ee %>% filter(sampGen == "1" & s == "0.01" & fuseGen=="1" & recomb == "5e-08" & dom=="0.5" & N=="10000" & driftGen == 0 & width.taj < 100000) %>% mutate("Magnitude" = height.taj, "Breadth" = width.taj / 10000, same_ploidy = ifelse(sim_ploidy == traj_ploidy, 1, 0)) %>% select(sim_ploidy, traj_ploidy, same_ploidy, Magnitude, Breadth) %>% melt(., id.var = c("sim_ploidy", "traj_ploidy", "same_ploidy")) %>% mutate("TajD" = variable) %>% filter(value != -9) %>% ggplot(., aes(y = value, fill = as.factor(traj_ploidy), x = as.factor(sim_ploidy), color = as.factor(same_ploidy))) + geom_boxplot(outlier.shape = NA) + scale_fill_discrete(name = "Trajectory Ploidy", labels = c("2", "4", "8")) + scale_color_manual(guide=F, values = c("black","red")) + facet_wrap(~TajD, scales = "free_y", labeller = label_both) + ylab("") + xlab("Coalescent Ploidy") + theme_bw() + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18), legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16))

ee %>% filter(sampGen == "1" & s == "0.01" & fuseGen=="1" & recomb == "5e-08" & dom=="0.5" & N=="10000" & driftGen == 0) %>% mutate("Magnitude" = height.h, "Breadth" = width.h / 10000, same_ploidy = ifelse(sim_ploidy == traj_ploidy, 1, 0)) %>% select(sim_ploidy, traj_ploidy, same_ploidy, Magnitude, Breadth) %>% melt(., id.var = c("sim_ploidy", "traj_ploidy", "same_ploidy")) %>% mutate("Fay & Wu's H" = variable) %>% filter(value != -9) %>% ggplot(., aes(y = value, fill = as.factor(traj_ploidy), x = as.factor(sim_ploidy), color = as.factor(same_ploidy))) + geom_boxplot(outlier.shape = NA) + scale_fill_discrete(name = "Trajectory Ploidy", labels = c("2", "4", "8")) + scale_color_manual(guide=F, values = c("black","red")) + facet_wrap(~`Fay & Wu's H`, scales = "free_y", labeller = label_both) + ylab("") + xlab("Coalescent Ploidy") + theme_bw() + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18), legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16))

ee %>% filter(sampGen == "1" & s == "0.01" & fuseGen=="1" & recomb == "5e-08" & dom=="0.5" & N=="10000" & driftGen == 0) %>% mutate("Magnitude" = height.e, "Breadth" = width.e / 10000, same_ploidy = ifelse(sim_ploidy == traj_ploidy, 1, 0)) %>% select(sim_ploidy, traj_ploidy, same_ploidy, Magnitude, Breadth) %>% melt(., id.var = c("sim_ploidy", "traj_ploidy", "same_ploidy")) %>% mutate("Zeng's E" = variable) %>% filter(value != -9) %>% ggplot(., aes(y = value, fill = as.factor(traj_ploidy), x = as.factor(sim_ploidy), color = as.factor(same_ploidy))) + geom_boxplot(outlier.shape = NA) + scale_fill_discrete(name = "Trajectory Ploidy", labels = c("2", "4", "8")) + scale_color_manual(guide=F, values = c("black","red")) + facet_wrap(~`Zeng's E`, scales = "free_y", labeller = label_both) + ylab("") + xlab("Coalescent Ploidy") + theme_bw() + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18), legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16))

ee %>% filter(sampGen == "10000" & s == "0.01" & fuseGen=="1" & recomb == "5e-08" & dom=="0.5" & N=="10000" & driftGen == 0 & width.fst < 60000) %>% mutate("Magnitude" = height.fst, "Breadth" = width.fst / 10000, same_ploidy = ifelse(sim_ploidy == traj_ploidy, 1, 0)) %>% select(sim_ploidy, traj_ploidy, same_ploidy, Magnitude, Breadth) %>% melt(., id.var = c("sim_ploidy", "traj_ploidy", "same_ploidy")) %>% mutate("Fst" = variable) %>% filter(value != -9) %>% ggplot(., aes(y = value, fill = as.factor(traj_ploidy), x = as.factor(sim_ploidy), color = as.factor(same_ploidy))) + geom_boxplot(outlier.shape = NA) + scale_fill_discrete(name = "Trajectory Ploidy", labels = c("2", "4", "8")) + scale_color_manual(guide=F, values = c("black","red")) + facet_wrap(~Fst, scales = "free_y", labeller = label_both) + ylab("") + xlab("Coalescent Ploidy") + theme_bw() + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18), legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16))

ee %>% filter(sampGen == "10000" & s == "0.01" & fuseGen=="1" & recomb == "5e-08" & dom=="0.5" & N=="10000" & driftGen == 0 & width.taj < 100000) %>% mutate("Magnitude" = height.taj, "Breadth" = width.taj / 10000, same_ploidy = ifelse(sim_ploidy == traj_ploidy, 1, 0)) %>% select(sim_ploidy, traj_ploidy, same_ploidy, Magnitude, Breadth) %>% melt(., id.var = c("sim_ploidy", "traj_ploidy", "same_ploidy")) %>% mutate("TajD" = variable) %>% filter(value != -9) %>% ggplot(., aes(y = value, fill = as.factor(traj_ploidy), x = as.factor(sim_ploidy), color = as.factor(same_ploidy))) + geom_boxplot(outlier.shape = NA) + scale_fill_discrete(name = "Trajectory Ploidy", labels = c("2", "4", "8")) + scale_color_manual(guide=F, values = c("black","red")) + facet_wrap(~TajD, scales = "free_y", labeller = label_both) + ylab("") + xlab("Coalescent Ploidy") + theme_bw() + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18), legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16))

ee %>% filter(traj_ploidy == sim_ploidy & s == "0.01" & fuseGen=="1" & recomb == "5e-08" & dom=="0.5" & N=="10000" & driftGen == 0 & width.taj < 100000) %>% mutate("Magnitude" = height.taj, "Breadth" = width.taj / 10000, same_ploidy = ifelse(sim_ploidy == traj_ploidy, 1, 0)) %>% select(sim_ploidy, sampGen, Magnitude, Breadth) %>% melt(., id.var = c("sim_ploidy", "sampGen")) %>% mutate("TajD" = variable) %>% filter(value != -9) %>% ggplot(., aes(y = value, fill = as.factor(sampGen), x = as.factor(sim_ploidy))) + geom_boxplot(outlier.shape = NA) + scale_fill_discrete(name = "Generations since\nFixation") + ylab("") + xlab("Coalescent Ploidy") + facet_wrap(~TajD, labeller = label_both, scales = "free_y") +theme_bw() + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18), legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16))

ee %>% filter(traj_ploidy == sim_ploidy & s == "0.01" & fuseGen=="1" & recomb == "5e-08" & dom=="0.5" & N=="10000" & driftGen == 0 & width.fst < 100000) %>% mutate("Magnitude" = height.fst, "Breadth" = width.fst / 10000, same_ploidy = ifelse(sim_ploidy == traj_ploidy, 1, 0)) %>% select(sim_ploidy, sampGen, Magnitude, Breadth) %>% melt(., id.var = c("sim_ploidy", "sampGen")) %>% mutate("Fst" = variable) %>% filter(value != -9) %>% ggplot(., aes(y = value, fill = as.factor(sampGen), x = as.factor(sim_ploidy))) + geom_boxplot(outlier.shape = NA) + scale_fill_discrete(name = "Generations since\nFixation") + ylab("") + xlab("Coalescent Ploidy") + facet_wrap(~Fst, labeller = label_both, scales = "free_y") +theme_bw() + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18), legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16))

ee %>% filter(traj_ploidy == sim_ploidy & s == "0.01" & fuseGen=="1" & recomb == "5e-08" & dom=="0.5" & N=="10000" & driftGen == 0 & width.taj < 100000) %>% mutate("Magnitude" = height.h, "Breadth" = width.h / 10000, same_ploidy = ifelse(sim_ploidy == traj_ploidy, 1, 0)) %>% select(sim_ploidy, sampGen, Magnitude, Breadth) %>% melt(., id.var = c("sim_ploidy", "sampGen")) %>% mutate("Fay & Wu's H" = variable) %>% filter(value != -9) %>% ggplot(., aes(y = value, fill = as.factor(sampGen), x = as.factor(sim_ploidy))) + geom_boxplot(outlier.shape = NA) + scale_fill_discrete(name = "Generations since\nFixation") + ylab("") + xlab("Coalescent Ploidy") + facet_wrap(~`Fay & Wu's H`, labeller = label_both, scales = "free_y") +theme_bw() + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18), legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16))

ee %>% filter(traj_ploidy == sim_ploidy & s == "0.01" & fuseGen=="1" & recomb == "5e-08" & dom=="0.5" & N=="10000" & driftGen == 0 & width.fst < 100000) %>% mutate("Magnitude" = height.e, "Breadth" = width.e / 10000, same_ploidy = ifelse(sim_ploidy == traj_ploidy, 1, 0)) %>% select(sim_ploidy, sampGen, Magnitude, Breadth) %>% melt(., id.var = c("sim_ploidy", "sampGen")) %>% mutate("Zeng's E" = variable) %>% filter(value != -9) %>% ggplot(., aes(y = value, fill = as.factor(sampGen), x = as.factor(sim_ploidy))) + geom_boxplot(outlier.shape = NA) + scale_fill_discrete(name = "Generations since\nFixation") + ylab("") + xlab("Coalescent Ploidy") + facet_wrap(~`Zeng's E`, labeller = label_both, scales = "free_y") +theme_bw() + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18), legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16))

fact.ehh = read.csv("~/Documents/Research/PloidySim/rehh/rehh_calcs_do0.5_fG1_DS_fmted.csv")

cc = fact.ehh %>% filter(!is.na(xpehh.p) & sampGen!=1000) %>% mutate(mid = POSITION) %>% nest(-c(s, dom, recomb, N, mu, sim_ploidy, traj_ploidy, sampGen, fuseGen, rep)) %>% mutate(height.xp = map(data, ~getDims(., y.metric = "XPEHH")$height), width.xp = map(data, ~getDims(., y.metric = "XPEHH")$width), height.xp.p = map(data, ~getDims(., y.metric = "xpehh.p")$height), width.xp.p = map(data, ~getDims(., y.metric = "xpehh.p")$width)) %>% select(-data) %>% unnest()

cc %>% filter(N == "10000" & s =="0.01" & sampGen == "1") %>% select(sim_ploidy, traj_ploidy, height.xp, width.xp, height.xp.p, width.xp.p) %>% melt(., id.var = c("sim_ploidy", "traj_ploidy")) %>% ggplot(., aes(y = value, fill = as.factor(traj_ploidy), x = as.factor(sim_ploidy))) + geom_boxplot(outlier.shape = NA) + scale_fill_discrete(name = "Trajectory Ploidy") + facet_wrap(~variable, scales = "free_y") + ylab("") + xlab("Coalescent Ploidy") + theme_bw() + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18), legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16))

fact.ehh %>% filter(s == "0.01" & recomb == "re1e-08" & dom=="0.5" & N=="10000" & sampGen == "1") %>% ggplot(.,aes(x=POSITION / 100000, y=xpehh.p, color=sim_ploidy)) + geom_smooth(method="loess", span=0.1, se = F) + scale_color_discrete(name="Trajectory\nPloidy") + facet_grid(~sim_ploidy) + xlab("Position (100 kb)") + ylab(expression("-log"[10]*"(p-value)")) + theme_bw()
```

```{r}
genoFreqs = function(freqs){
  AA = freqs ^ 2
  Aa = 2 * freqs * (1 - freqs)
  aa = (1 - freqs) ^ 2
  AAAA = freqs ^ 4
  AAAa = 4 * (freqs ^ 3) * (1 - freqs)
  AAaa = 6 * (freqs ^ 2) * (1 - freqs) ^ 2
  Aaaa = 4 * freqs * (1 - freqs) ^ 3
  aaaa = (1 - freqs) ^ 4
  dfreq = data.frame("p" = freqs, "AA" = AA, "Aa" = Aa, "aa" = aa, "Ploidy" = rep(2, length(freqs)))
  tfreq = data.frame("p" = freqs, "AAAA" = AAAA, "AAAa" = AAAa, "AAaa" = AAaa, "Aaaa" = Aaaa, "aaaa" = aaaa, "Ploidy" = rep(4, length(freqs)))
  DF = rbind(melt(dfreq, id.var = c("p", "Ploidy")), melt(tfreq, id.var = c("p", "Ploidy")))
  return(DF)
}

# Calculate diploid/tetraploid genotype frequencies across entire range of allele frequency values
freqs = genoFreqs(seq(0,1,0.01))

ggplot(freqs, aes(x = p, y = value, color = as.factor(Ploidy), group = variable)) + geom_line() + scale_color_manual(name="Ploidy", values = c("#F8766D", "#00BA38")) + annotate("text", x = 0.28, y = 0.625, label="aa", color = "#F8766D", size = 6) + annotate("text", x = 0.5, y = 0.55, label="Aa", color = "#F8766D", size = 6) + annotate("text", x = 0.72, y = 0.625, label="AA", color = "#F8766D", size = 6) + annotate("text", x = 0.055, y = 0.6, label="aaaa", color = "#00BA38", size = 6) + annotate("text", x = 0.055, y = 0.365, label="Aaaa", color = "#00BA38", size = 6) + annotate("text", x = 0.5, y = 0.415, label="AAaa", color = "#00BA38", size = 6) + annotate("text", x = 0.955, y = 0.365, label="AAAa", color = "#00BA38", size = 6) + annotate("text", x = 0.955, y = 0.6, label="AAAA", color = "#00BA38", size = 6) + ylab("Genotype Frequency") + xlab("Allele Frequency") + theme_bw() + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18),axis.text.x=element_text(size=16),axis.title.x=element_text(size=18),legend.text = element_text(size=16), legend.title = element_text(size=18))

freqs %>% filter(Ploidy == 2) %>% ggplot(., aes(x = p, y = value, color = "#F8766D", group = variable)) + geom_line() + scale_color_manual(name="Ploidy", values = c("#F8766D"), label = "2") + annotate("text", x = 0.28, y = 0.625, label="aa", color = "#F8766D", size = 6) + annotate("text", x = 0.5, y = 0.55, label="Aa", color = "#F8766D", size = 6) + annotate("text", x = 0.72, y = 0.625, label="AA", color = "#F8766D", size = 6) + ylab("Genotype Frequency") + xlab("Allele Frequency") + theme_bw() + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18),axis.text.x=element_text(size=16),axis.title.x=element_text(size=18),legend.text = element_text(size=16), legend.title = element_text(size=18))

ggplot(freqs, aes(x = p, y = value, color = as.factor(Ploidy), group = variable)) + geom_line() + scale_color_manual(name="Ploidy", values = c("#F8766D", "#00BA38")) + annotate("text", x = 0.28, y = 0.625, label="aa", color = "#F8766D", size = 6) + annotate("text", x = 0.5, y = 0.55, label="Aa", color = "#F8766D", size = 6) + annotate("text", x = 0.72, y = 0.625, label="AA", color = "#F8766D", size = 6) + annotate("text", x = 0.055, y = 0.6, label="aaaa", color = "#00BA38", size = 6) + annotate("text", x = 0.055, y = 0.365, label="Aaaa", color = "#00BA38", size = 6) + annotate("text", x = 0.5, y = 0.415, label="AAaa", color = "#00BA38", size = 6) + annotate("text", x = 0.955, y = 0.365, label="AAAa", color = "#00BA38", size = 6) + annotate("text", x = 0.955, y = 0.6, label="AAAA", color = "#00BA38", size = 6) + ylab("Genotype Frequency") + xlab("Allele Frequency") + theme_bw() + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18),axis.text.x=element_text(size=16),axis.title.x=element_text(size=18),legend.text = element_text(size=16), legend.title = element_text(size=18))
```

```{r}

getFits = function(freqs, s, h1, h, h3){
  df = data.frame("s" = s, "h" = h, "freq" = s, "w.bar" = 0, "var.w" = 0, "w.bar.p" = 0, "h1" = NA, "h3" = NA, "ploidy" = 2)
  assert_that(length(h1) == length(h))
  assert_that(length(h) == length(h3))
  for (j in 1:length(s)){
    for(k in 1:length(h)){
    for (i in 1:length(freqs)){
      p = freqs[i]
      q = 1 - p
      Tfits = c(1 + s[j], 1 + (s[j] * h3[k]), 1 + (s[j] * h[k]), 1 + (s[j] * h1[k]), 1) / (1 + s[j])
      TGfreqs = c(p ^ 4, 4 * p^3 * q, 6 * p^2 * q^2, 4 * p * q^3, q ^ 4)
      Tw.bar = sum(TGfreqs * Tfits)
      Dfits = c(1 + s[j], 1 + (s[j] * h[k]), 1) / (1 + s[j])
      DGfreqs = c(p ^ 2, 2 * p * q, q ^ 2)
      Dw.bar = sum(DGfreqs * Dfits)
      Tvar.w = sum((TGfreqs * (Tfits - Tw.bar) ^ 2) / length(TGfreqs))
      Dvar.w = sum((DGfreqs * (Dfits - Dw.bar) ^ 2) / length(DGfreqs))
      Dw.bar.p = (p * Dfits[1]) + (q * Dfits[2])
      Tw.bar.p = ((p ^ 3) * Tfits[1]) + (3 * (p ^ 2) * q * Tfits[2]) + (3 * p * (q ^ 2) * Tfits[3]) + ((q ^ 3) * Tfits[4])
      df = rbind(df, c(s[j], h[k], p, Dw.bar, Dvar.w, Dw.bar.p, NA, NA, 2))
      df = rbind(df, c(s[j], h[k], p, Tw.bar, Tvar.w, Tw.bar.p, h1[k], h3[k], 4))
    }
    }
  }
  return(df[-1,])
}

fits = getFits(seq(0,1,0.01), 0.1, 0.25, 0.5, 0.75)
fits = rbind(fits, getFits(seq(0,1,0.01), 0.1, 1, 1, 1))
fits = rbind(fits, getFits(seq(0,1,0.01), 0.1, 0, 0, 0))

fits %>% filter(s == 0.1) %>% ggplot(., aes(x=freq, y=var.w, linetype=as.factor(h), color=as.factor(ploidy))) + geom_line() + scale_color_manual(name="Ploidy", values = c("#F8766D", "#00BA38")) + scale_linetype_discrete(name="Dominance", labels=c("Recessive","Additive","Dominant")) + xlab("Allele Frequency") + ylab("Variance in Fitness") + theme_bw() + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18),axis.text.x=element_text(size=16),axis.title.x=element_text(size=18),legend.text = element_text(size=16), legend.title = element_text(size=18))

fits %>% filter(s == 0.1, h == 0.5, ploidy == 2) %>% ggplot(., aes(x=freq, y=var.w, color=as.factor(ploidy))) + geom_line() + scale_color_manual(name="Ploidy", values = c("#F8766D", "#00BA38")) + xlab("Allele Frequency") + ylab("Variance in Fitness\n") + theme_bw() + theme(axis.text.y=element_blank(), axis.title.y=element_text(size=18),axis.text.x=element_text(size=16),axis.title.x=element_text(size=18),legend.text = element_text(size=16), legend.title = element_text(size=18))

fits %>% filter(s == 0.1, h == 0.5) %>% ggplot(., aes(x=freq, y=var.w, color=as.factor(ploidy))) + geom_line() + scale_color_manual(name="Ploidy", values = c("#F8766D", "#00BA38")) + xlab("Allele Frequency") + ylab("Variance in Fitness\n") + theme_bw() + theme(axis.text.y=element_blank(), axis.title.y=element_text(size=18),axis.text.x=element_text(size=16),axis.title.x=element_text(size=18),legend.text = element_text(size=16), legend.title = element_text(size=18))

```

```{r, echo=T,message=F}
getDomCoefs = function(dominance, ploidy = 100){
  if (dominance == 0){
    coeffs = rep(0, ploidy - 1)
  }
  else if (dominance == 1){
    coeffs = rep(1, ploidy - 1)
  }
  else {
    dom = (1 - dominance) - 0.5
    dom = abs((dom * 10 + sign(dom)) ^ sign(dom))
    coeffs = (seq(1, ploidy - 1) / ploidy) ^ dom
  }
  return(coeffs)
}

doms = c(seq(0,1, 0.1))
Doms = as.data.frame(sapply(doms, getDomCoefs))
Doms = rbind(c(0,0,0,0,0,0,0), Doms, c(1,1,1,1,1,1,1))
colnames(Doms) = doms
Doms = cbind(Doms, data.frame("i/k"=seq(0,100) / 100))
mDoms = melt(Doms, id.var = "i.k")
ggplot(mDoms, aes(x = i.k, y = value, color = variable)) + geom_line() + scale_color_discrete(name = "Dominance\nScalar") + theme_bw() + xlab("i / k") + ylab("Dominance Coefficient")

mDoms %>% filter(variable %in% c("0.1", "0.5", "0.9")) %>% ggplot(., aes(x = i.k, y = value, linetype = variable)) + geom_line() + scale_color_discrete(name = "Dominance", breaks = c("0.1", "0.5", "0.9"), labels = c("Partial\nRecessivity\n", "Additive\n", "Partial\nDominance")) + theme_bw() + xlab("Individual allele frequency of beneficial allele") + ylab("Dominance Coefficient")

mDoms$variable = factor(mDoms$variable, levels(mDoms$variable)[c(rev(seq(1,11)))])
ALL$Call=factor(ALL$Call,levels(ALL$Call)[c(2,1,3)])

#Color
mDoms %>% filter(variable %in% c("0.1", "0.5", "0.9")) %>% ggplot(., aes(x = i.k, y = value, color = variable)) + geom_line(size = 1.2) + scale_color_manual(name = "Dominance", breaks = c("0.9", "0.5", "0.1"), labels = c("Partial\nDominance", "Additive", "Partial\nRecessivity\n"), values = c("#E6A0C4", "#C6CDF7", "#D8A499")) + theme_bw() + xlab("Individual allele frequency of beneficial allele") + ylab("Dominance Coefficient") + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18),axis.text.x=element_text(size=16),axis.title.x=element_text(size=18),legend.text = element_text(size=16), legend.title = element_text(size=18))

#Linetype
mDoms %>% filter(variable %in% c("0.1", "0.5", "0.9")) %>% ggplot(., aes(x = i.k, y = value, linetype = variable)) + geom_line() + scale_linetype_manual(name = "Dominance", breaks = c("0.1", "0.5", "0.9"), labels = c("Partial\nRecessivity\n", "Additive\n", "Partial\nDominance"), values = c("dashed", "solid","dotdash")) + theme_bw() + xlab("Individual allele frequency of beneficial allele") + ylab("Dominance Coefficient") + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18),axis.text.x=element_text(size=16),axis.title.x=element_text(size=18),legend.text = element_text(size=16), legend.title = element_text(size=18))
# Example

# dominance=c(seq(0.1,0.9,0.1))
# > dominance
# [1] 0.1 0.2 0.3 0.4 0.5 0.6 0.7 0.8 0.9

# Centers around 0.5 (additivity)
# dom = (1 - dominance) - 0.5
# > dom
# [1]  0.4  0.3  0.2  0.1  0.0 -0.1 -0.2 -0.3 -0.4

# dom1 = abs((dom * 10 + sign(dom)) ^ sign(dom))
# > dom1
# [1] 5.0000000 4.0000000 3.0000000 2.0000000 1.0000000 0.5000000 0.3333333 0.2500000 0.2000000

# > getDomCoefs(dominance = 0.2, ploidy = 4)
# [1] 0.00390625 0.06250000 0.31640625
# > getDomCoefs(dominance = 0.5, ploidy = 4)
# [1] 0.25 0.50 0.75

```

```{r}
getTraj = function(s, dom, ploidy, start_freq, N = -9, end_freq = 0.99, maxGens = 9999, maxTries = 10){
  dom_coeffs = getDomCoefs(dom, ploidy)
  attempts = 0
  p = start_freq
  k = ploidy
  gen = 0
  while (attempts <= maxTries & p < end_freq & gen <= maxGens){
    df = data.frame("s" = s, "dom" = dom, "gen" = 0, "freq" = start_freq, "dp1" = 0, "w.bar" = 0, "ploidy" = ploidy)
    p = start_freq
    dp1 = 0
    gen = 0
    het_fits = 1 + dom_coeffs * s
    fits = c(1, het_fits, 1 + s) / (1 + s)
    while (p < end_freq & p > 0 & gen <= maxGens){
      q = 1 - p
      i = seq(0, k)
      Num = sum(choose(k, i) * ((k - i) / k) * (p ^ (k - i)) * (q ^ i) * rev(fits))
      Den = sum(choose(k, i) * (p ^ (k - i)) * (q ^ i) * rev(fits))
      p_prime = Num / Den
      if (N != -9){
        p_prime = sum(rbinom(N, k, p_prime)) / (k * N) 
      }
      df = rbind(df, c(s, dom, gen, p, dp1, Den, k))
      dp1 = p_prime - p
      p = p_prime
      gen = gen + 1
    }
    df = rbind(df, c(s, dom, gen, p, dp1, Den, k))
    attempts = attempts + 1
  }
  if (attempts > maxTries & nrow(df) <= maxGens){
    print(paste("Beneficial allele was lost due to drift for", maxTries, "consecutive attempts"))
  }
  if (nrow(df) > maxGens){
    print(paste("Beneficial allele did not fix before the maximum number of generations (", maxGens, ")."))
  }
  return(df[-1,])
}

# Param set to create trajectories for
params = data.frame("s" = rep(0.1,9), "dom" = c(rep(0.5,3), rep(0.1,3), rep(0.9,3)), "ploidy" = rep(c(2,4,8),3), "start" = rep(0.05, 9))

# Create trajectories
dat1 = foreach(i = 1:nrow(params), .combine=rbind) %do% {
  getTraj(params[i,]$s, params[i,]$dom, params[i,]$ploidy, params[i,]$start)
}

params2 = data.frame("s" = c(rep(0.01,3), rep(0.005,3)), "dom" = c(rep(0.5,6)), "ploidy" = rep(c(2,4,8),2), "start" = rep(0.05, 6))

# Create trajectories
dat2 = foreach(i = 1:nrow(params2), .combine=rbind) %do% {
  getTraj(params2[i,]$s, params2[i,]$dom, params2[i,]$ploidy, params2[i,]$start)
}

dat1$dom = factor(dat1$dom, levels(dat1$dom)[c(3,2,1)])
#plot
ggplot(dat1, aes(x=gen, y=freq, linetype=as.factor(dom), color=as.factor(ploidy))) + geom_line() + scale_color_discrete(name="Ploidy") + scale_linetype_discrete(name="Dominance Scalar", labels=c("0.1", "0.5", "0.9")) + xlim(0,300) + theme_bw() + xlab("Generation") + ylab("Allele Frequency")

#ALL
dat1 %>% filter(ploidy %in% c(2, 4, 8) & dom %in% c(0.1, 0.5, 0.9)) %>% 
ggplot(., aes(x=gen, y=freq, linetype=as.factor(dom), color=as.factor(ploidy))) + geom_line() + scale_color_manual(name = "Ploidy", values = c("#F8766D", "#00BA38", "#619CFF")) + scale_linetype_manual(name = "Dominance", labels=c("Partial\nRecessivity\n", "Additivity", "Partial\nDominance")) + xlim(0,300) + theme_bw() + xlab("Generation") + ylab("Allele Frequency") + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18),axis.text.x=element_text(size=16),axis.title.x=element_text(size=18),legend.text = element_text(size=16), legend.title = element_text(size=18))

#Additive Series
dat1 %>% filter(ploidy %in% c(2) & dom %in% c(0.5)) %>% 
ggplot(., aes(x=gen, y=freq, linetype=as.factor(dom), color=as.factor(ploidy))) + geom_line() + scale_color_manual(name = "Ploidy", values = c("#F8766D", "#00BA38", "#619CFF")) + scale_linetype_manual(name = "Dominance", breaks = c("0.5"), labels = c("Additive"), values = c("solid")) + xlim(0,300) + theme_bw() + xlab("Generation") + ylab("Allele Frequency") + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18),axis.text.x=element_text(size=16),axis.title.x=element_text(size=18),legend.text = element_text(size=16), legend.title = element_text(size=18)) + guides(color = guide_legend(order=1), linetype = guide_legend(order=2))

dat1 %>% filter(ploidy %in% c(2, 4) & dom %in% c(0.5)) %>% 
ggplot(., aes(x=gen, y=freq, linetype=as.factor(dom), color=as.factor(ploidy))) + geom_line() + scale_linetype_manual(name = "Dominance", breaks = c("0.5"), labels = c("Additive"), values = c("solid")) + scale_color_manual(name = "Ploidy", values = c("#F8766D", "#00BA38", "#619CFF")) + xlim(0,300) + theme_bw() + xlab("Generation") + ylab("Allele Frequency") + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18),axis.text.x=element_text(size=16),axis.title.x=element_text(size=18),legend.text = element_text(size=16), legend.title = element_text(size=18)) + guides(color = guide_legend(order=1), linetype = guide_legend(order=2))

dat1 %>% filter(ploidy %in% c(2, 4, 8) & dom %in% c(0.5)) %>% 
ggplot(., aes(x=gen, y=freq, linetype=as.factor(dom), color=as.factor(ploidy))) + geom_line() + scale_linetype_manual(name = "Dominance", breaks = c("0.5"), labels = c("Additive"), values = c("solid")) + scale_color_manual(name = "Ploidy", values = c("#F8766D", "#00BA38", "#619CFF")) + xlim(0,300) + theme_bw() + xlab("Generation") + ylab("Allele Frequency") + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18),axis.text.x=element_text(size=16),axis.title.x=element_text(size=18),legend.text = element_text(size=16), legend.title = element_text(size=18)) + guides(color = guide_legend(order=1), linetype = guide_legend(order=2))

# Additive plus dominant
dat1 %>% filter(ploidy %in% c(2) & dom %in% c(0.5, 0.9)) %>% 
ggplot(., aes(x=gen, y=freq, linetype=as.factor(dom), color=as.factor(ploidy))) + geom_line() + scale_color_manual(name = "Ploidy", values = c("#F8766D", "#00BA38", "#619CFF")) + scale_linetype_manual(name = "Dominance", breaks = c("0.5", "0.9"), labels = c("Additive", "\nPartial\nDominance"), values = c("dashed","solid")) + xlim(0,300) + theme_bw() + xlab("Generation") + ylab("Allele Frequency") + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18),axis.text.x=element_text(size=16),axis.title.x=element_text(size=18),legend.text = element_text(size=16), legend.title = element_text(size=18)) + guides(color = guide_legend(order=1), linetype = guide_legend(order=2))

dat1 %>% filter(ploidy %in% c(2, 4) & dom %in% c(0.5, 0.9)) %>% 
ggplot(., aes(x=gen, y=freq, linetype=as.factor(dom), color=as.factor(ploidy))) + geom_line() + scale_linetype_manual(name = "Dominance", breaks = c("0.5", "0.9"), labels = c("Additive", "\nPartial\nDominance"), values = c("dashed","solid")) + scale_color_manual(name = "Ploidy", values = c("#F8766D", "#00BA38", "#619CFF")) + xlim(0,300) + theme_bw() + xlab("Generation") + ylab("Allele Frequency") + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18),axis.text.x=element_text(size=16),axis.title.x=element_text(size=18),legend.text = element_text(size=16), legend.title = element_text(size=18)) + guides(color = guide_legend(order=1), linetype = guide_legend(order=2))

dat1 %>% filter(ploidy %in% c(2, 4, 8) & dom %in% c(0.5, 0.9)) %>% 
ggplot(., aes(x=gen, y=freq, linetype=as.factor(dom), color=as.factor(ploidy))) + geom_line() + scale_linetype_manual(name = "Dominance", breaks = c("0.5", "0.9"), labels = c("Additive", "\nPartial\nDominance"), values = c("dashed","solid")) + scale_color_manual(name = "Ploidy", values = c("#F8766D", "#00BA38", "#619CFF")) + xlim(0,300) + theme_bw() + xlab("Generation") + ylab("Allele Frequency") + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18),axis.text.x=element_text(size=16),axis.title.x=element_text(size=18),legend.text = element_text(size=16), legend.title = element_text(size=18)) + guides(color = guide_legend(order=1), linetype = guide_legend(order=2))

# All Series
dat1 %>% filter(ploidy %in% c(2) & dom %in% c(0.5, 0.9, 0.1)) %>% 
ggplot(., aes(x=gen, y=freq, linetype=as.factor(dom), color=as.factor(ploidy))) + geom_line() + scale_color_manual(name = "Ploidy", values = c("#F8766D", "#00BA38", "#619CFF")) + scale_linetype_manual(name = "Dominance", breaks = c("0.1", "0.5", "0.9"), labels = c("Partial\nRecessivity\n", "Additive", "\nPartial\nDominance"), values = c("dashed", "solid","dotdash")) + xlim(0,300) + theme_bw() + xlab("Generation") + ylab("Allele Frequency") + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18),axis.text.x=element_text(size=16),axis.title.x=element_text(size=18),legend.text = element_text(size=16), legend.title = element_text(size=18)) + guides(color = guide_legend(order=1), linetype = guide_legend(order=2))

dat1 %>% filter(ploidy %in% c(2, 4) & dom %in% c(0.5, 0.9, 0.1)) %>% 
ggplot(., aes(x=gen, y=freq, linetype=as.factor(dom), color=as.factor(ploidy))) + geom_line() + scale_linetype_manual(name = "Dominance", breaks = c("0.1", "0.5", "0.9"), labels = c("Partial\nRecessivity\n", "Additive", "\nPartial\nDominance"), values = c("dashed", "solid","dotdash")) + scale_color_manual(name = "Ploidy", values = c("#F8766D", "#00BA38", "#619CFF")) + xlim(0,300) + theme_bw() + xlab("Generation") + ylab("Allele Frequency") + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18),axis.text.x=element_text(size=16),axis.title.x=element_text(size=18),legend.text = element_text(size=16), legend.title = element_text(size=18)) + guides(color = guide_legend(order=1), linetype = guide_legend(order=2))

dat1 %>% filter(ploidy %in% c(2, 4, 8) & dom %in% c(0.5, 0.9, 0.1)) %>% 
ggplot(., aes(x=gen, y=freq, linetype=as.factor(dom), color=as.factor(ploidy))) + geom_line() + scale_linetype_manual(name = "Dominance", breaks = c("0.1", "0.5", "0.9"), labels = c("Partial\nRecessivity\n", "Additive", "\nPartial\nDominance"), values = c("dashed", "solid","dotdash")) + scale_color_manual(name = "Ploidy", values = c("#F8766D", "#00BA38", "#619CFF")) + xlim(0,300) + theme_bw() + xlab("Generation") + ylab("Allele Frequency") + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18),axis.text.x=element_text(size=16),axis.title.x=element_text(size=18),legend.text = element_text(size=16), legend.title = element_text(size=18)) + guides(color = guide_legend(order=1), linetype = guide_legend(order=2))
```

```{r}
dat = read.table("~/Documents/Research/PloidySim/data/drift_start_freqs.txt", head = T)

dat %>% filter(N == 1000) %>% mutate("Drift Generations" = ends, "Pop. Size" = N) %>% ggplot(., aes(fill = as.factor(ploidy), x = start_freq, y = ..scaled..)) + geom_density(alpha=0.5) + facet_grid(cols = vars(`Drift Generations`)) + ylab("") + xlab("Frequency") + ggtitle("Allele frequency distribution of new mutations \nsurviving after drifting for X generations") + scale_fill_discrete(name = "Ploidy") + theme_bw() + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18),axis.text.x=element_text(size=16),axis.title.x=element_text(size=18),legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=14), plot.title = element_text(size = 18), panel.spacing = unit(2, "lines"))
```

### 2019-06-10 analysis/mssel_analysis.Rmd
Talk Prep Figures

@@
 library(foreach)
+library(purrr)
 
-ms2 = read.table("~/Documents/Research/PloidySim/data/mssel_out_2-24-19_fin.txt", head = T)
+ms = read.table("~/Documents/Research/PloidySim/data/mssel_out_2-24-19_fin.txt", head = T)
 
 #Group windows into larger sets
-ms2 %<>% mutate(ints = as.numeric(as.character(cut(bp.start, breaks = 50, labels = seq(1,50)))))
+ms %<>% mutate(driftGen = 0)
+
+ms2 = read.table("~/Documents/Research/PloidySim/data/mssel_out_highRe_drift_4-30-19.txt", head = T)
+
+#NEED TO ADD this data
+ms3 = read.table("~/Documents/Research/PloidySim/data/mssel_out_5-10-19.txt", head = T)
+ms3 %<>% filter(sim_ploidy!=1)
+
+ms = rbind(ms,ms2)
+
+ms %<>% mutate(ints = as.numeric(as.character(cut(bp.start, breaks = 50, labels = seq(1,50)))))
+ms3 %<>% mutate(ints = as.numeric(as.character(cut(bp.start, breaks = 50, labels = seq(1,50)))))
+
+ms = rbind(ms, ms3)
 
@@
 
+mDoms %>% filter(variable %in% c("0.1", "0.5", "0.9")) %>% ggplot(., aes(x = i.k, y = value, linetype = variable)) + geom_line() + scale_color_discrete(name = "Dominance", breaks = c("0.1", "0.5", "0.9"), labels = c("Partial\nRecessivity\n", "Additive\n", "Partial\nDominance")) + theme_bw() + xlab("Individual allele frequency of beneficial allele") + ylab("Dominance Coefficient")
+
+mDoms$variable = factor(mDoms$variable, levels(mDoms$variable)[c(rev(seq(1,11)))])
+ALL$Call=factor(ALL$Call,levels(ALL$Call)[c(2,1,3)])
+
+#Color
+mDoms %>% filter(variable %in% c("0.1", "0.5", "0.9")) %>% ggplot(., aes(x = i.k, y = value, color = variable)) + geom_line(size = 1.2) + scale_color_manual(name = "Dominance", breaks = c("0.9", "0.5", "0.1"), labels = c("Partial\nDominance", "Additive", "Partial\nRecessivity\n"), values = c("#E6A0C4", "#C6CDF7", "#D8A499")) + theme_bw() + xlab("Individual allele frequency of beneficial allele") + ylab("Dominance Coefficient") + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18),axis.text.x=element_text(size=16),axis.title.x=element_text(size=18),legend.text = element_text(size=16), legend.title = element_text(size=18))
+
+#Linetype
+mDoms %>% filter(variable %in% c("0.1", "0.5", "0.9")) %>% ggplot(., aes(x = i.k, y = value, linetype = variable)) + geom_line() + scale_linetype_manual(name = "Dominance", breaks = c("0.1", "0.5", "0.9"), labels = c("Partial\nRecessivity\n", "Additive\n", "Partial\nDominance"), values = c("dashed", "solid","dotdash")) + theme_bw() + xlab("Individual allele frequency of beneficial allele") + ylab("Dominance Coefficient") + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18),axis.text.x=element_text(size=16),axis.title.x=element_text(size=18),legend.text = element_text(size=16), legend.title = element_text(size=18))
 # Example
@@
 # Param set to create trajectories for
-params = data.frame("s" = rep(0.1,9), "dom" = c(rep(0.5,3), rep(0,3), rep(1,3)), "ploidy" = rep(c(2,4,8),3), "start" = rep(0.05, 9))
+params = data.frame("s" = rep(0.1,9), "dom" = c(rep(0.5,3), rep(0.1,3), rep(0.9,3)), "ploidy" = rep(c(2,4,8),3), "start" = rep(0.05, 9))
 
@@
 
+dat1$dom = factor(dat1$dom, levels(dat1$dom)[c(3,2,1)])
 #plot
 ggplot(dat1, aes(x=gen, y=freq, linetype=as.factor(dom), color=as.factor(ploidy))) + geom_line() + scale_color_discrete(name="Ploidy") + scale_linetype_discrete(name="Dominance Scalar", labels=c("0.1", "0.5", "0.9")) + xlim(0,300) + theme_bw() + xlab("Generation") + ylab("Allele Frequency")
+
+#ALL
+dat1 %>% filter(ploidy %in% c(2, 4, 8) & dom %in% c(0.1, 0.5, 0.9)) %>% 
+ggplot(., aes(x=gen, y=freq, linetype=as.factor(dom), color=as.factor(ploidy))) + geom_line() + scale_color_manual(name = "Ploidy", values = c("#F8766D", "#00BA38", "#619CFF")) + scale_linetype_manual(name = "Dominance", labels=c("Partial\nRecessivity\n", "Additivity", "Partial\nDominance")) + xlim(0,300) + theme_bw() + xlab("Generation") + ylab("Allele Frequency") + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18),axis.text.x=element_text(size=16),axis.title.x=element_text(size=18),legend.text = element_text(size=16), legend.title = element_text(size=18))
+
 ```
@@
 
-## Summary of depth and breadth of peaks {.tabset}
+## Summary of depth and breadth of dips in diversity {.tabset}
 Controlling for number of chromosomes in the population (i.e. Simulation Ploidy), higher ploidies have a shallower dip, due to the slowed rate of fixation of the sweeping allele. 
@@
 ```{r, echo=T,message=F}
-MS2.a = ms2 %>% group_by(s, dom, recomb, N, mu, sim_ploidy, traj_ploidy, sampGen, fuseGen, rep) %>% summarize(depth = (mean(Pi.2,na.rm=T) - min(Pi.1)) / mean(Pi.2,na.rm=T))
+MS2.a = ms %>% group_by(s, dom, recomb, N, mu, sim_ploidy, traj_ploidy, sampGen, fuseGen, rep, driftGen) %>% summarize(depth = (mean(Pi.2,na.rm=T) - (mean(Pi.2,na.rm=T) - min(Pi.1))) / mean(Pi.2,na.rm=T), min = min(Pi.1, na.rm=T))
 
-MS2.a %>% filter(fuseGen == 1 & mu==1e-08 & N == 10000 & recomb=="1e-08" & s =="0.01") %>% ggplot(., aes(y=-(log(depth)), fill = as.factor(traj_ploidy), x = as.factor(sim_ploidy))) + geom_boxplot() + ylab(expression(paste("Dip Depth = min(", pi[1], ") / ",pi[2],sep = ""))) + facet_grid(~sampGen) + scale_y_log10() + scale_fill_discrete(name = "Trajectory\nPloidy") + xlab("Simulation Ploidy") + theme_bw()
+MS2.a %>% filter(fuseGen == 1 & mu==1e-08 & N == 10000 & recomb=="1e-08" & s =="0.01") %>% ggplot(., aes(y=-(log(depth)), fill = as.factor(traj_ploidy), x = as.factor(sim_ploidy))) + geom_boxplot() + ylab(expression(paste("Dip Depth = [", bar(pi[2])," - (", bar(pi[2]), " - min(", pi[1], ")] / ", bar(pi[2]),sep = ""))) + facet_grid(rows= vars(sampGen), cols = vars(driftGen)) + scale_y_log10() + scale_fill_discrete(name = "Trajectory\nPloidy") + xlab("Simulation Ploidy") + theme_bw()
+
+MS2.a %>% filter(fuseGen == 1 & mu==1e-08 & N == 10000 & recomb=="1e-08" & s =="0.01") %>% ggplot(., aes(y=-(log(min)), fill = as.factor(traj_ploidy), x = as.factor(sim_ploidy))) + geom_boxplot() + ylab(expression(paste("Dip Depth = [", bar(pi[2])," - (", bar(pi[2]), " - min(", pi[1], ")] / ", bar(pi[2]),sep = ""))) + facet_grid(rows= vars(sampGen), cols = vars(driftGen)) + scale_y_log10() + scale_fill_discrete(name = "Trajectory\nPloidy") + xlab("Simulation Ploidy") + theme_bw()
 ```
@@
 ```{r, echo=T,message=F}
-MS2.b = ms2 %>% group_by(s, dom, recomb, N, mu, sim_ploidy, traj_ploidy, sampGen, fuseGen, rep, ints) %>% summarize(lessWind = ifelse(mean(Pi.1, na.rm=T) < (mean(Pi.2, na.rm=T) / 2),1,0))
+MS2.b = ms %>% group_by(s, dom, recomb, N, mu, sim_ploidy, traj_ploidy, sampGen, fuseGen, driftGen, rep, ints) %>% summarize(lessWind = ifelse(mean(Pi.1, na.rm=T) < (mean(Pi.2, na.rm=T) / 2),1,0))
 
-MS2.c = MS2.b %>% group_by(s, dom, recomb, N, mu, sim_ploidy, traj_ploidy, sampGen, fuseGen, rep) %>% summarize(breadth = sum(lessWind) * 20000)
+MS2.c = MS2.b %>% group_by(s, dom, recomb, N, mu, sim_ploidy, traj_ploidy, sampGen, fuseGen, driftGen, rep) %>% summarize(breadth = sum(lessWind) * 20000)
 
@@
 MS2.c %>% filter(fuseGen == 1 & mu==1e-08 & N == 10000 & recomb=="1e-08" & s =="0.01") %>% ggplot(., aes(y=breadth/1000, fill = as.factor(sampGen), x = as.factor(sim_ploidy))) + geom_boxplot(notch=T) + ylab(expression(paste("Dip Breadth = Length (1 kb) of which ", pi[1], " < (",pi[2], " / 2)",sep = ""))) + scale_y_log10() + scale_fill_discrete(name = "Generations prior\nto fixation") + xlab("Simulation Ploidy") + theme_bw()
+```
+
+### Drift
+What happens if we let the beneficial allele drift neutrally for some number of generations prior to the start of selection
+
+The allele is introduced at frequency 1/(C * N), where C is ploidy.
+It then drifts for a specified number of generations as if it is in a population of size (C * N).
+After this generation, selection starts.
+So, a trajectory ploidy of 2 means that drift and selection are occuring as if this was a diploid population.
+
+Since drift happens more quickly in lower ploidies, the alleles that are not lost after X generations tend to be at higher frequency in lower ploidies.
+As selection takes off, these higher starting frequencies result in higher diversity following the sweep.
+Although the faster selection in lower ploidies promotes stronger signals of sweeps, the higher starting frequencies due to drift effectively erases or reverses the effect of ploidy on selection.
+```{r}
+sf = read.table("~/Documents/Research/PloidySim/data/drift_start_freqs.txt", header = T)
+
+sf %>% mutate("Drift Generations" = ends, "Pop.
+Size" = N) %>% ggplot(., aes(fill = as.factor(ploidy), x = start_freq, y = ..scaled..)) + geom_density(alpha=0.5) + facet_grid(rows=vars(`Drift Generations`), cols = vars(`Pop.
+Size`), labeller = label_both, scales = "free_y") + ylab("") + xlab("Frequency") + ggtitle("Allele frequency distribution of new mutations \nsurviving after drifting for X generations") + scale_fill_discrete(name = "Ploidy") + theme_bw()
+
+MS3.d = ms3 %>% group_by(s, dom, recomb, N, mu, sim_ploidy, traj_ploidy, sampGen, fuseGen, rep, driftGen) %>% summarize(depth = (mean(Pi.2,na.rm=T) - (mean(Pi.2,na.rm=T) - min(Pi.1))) / mean(Pi.2,na.rm=T))
+
+MS3.d %>% filter(sampGen == 1 & fuseGen == 1 & mu==1e-08 & N == 10000 & recomb=="5e-08" & dom == 0.5) %>% ggplot(., aes(y=-(log(depth)), fill = as.factor(traj_ploidy), x = as.factor(sim_ploidy))) + geom_boxplot() + ylab(expression(paste("Dip Depth = [", bar(pi[2])," - (", bar(pi[2]), " - min(", pi[1], ")] / ", bar(pi[2]),sep = ""))) + facet_grid(cols = vars(driftGen), rows = vars(s), labeller = label_both) + scale_y_log10() + scale_fill_discrete(name = "Trajectory\nPloidy") + xlab("Simulation Ploidy") + theme_bw()
+
+MS3.b = ms3 %>% group_by(s, dom, recomb, N, mu, sim_ploidy, traj_ploidy, sampGen, fuseGen, rep, driftGen, ints) %>% summarize(lessWind = ifelse(mean(Pi.1, na.rm=T) < (mean(Pi.2, na.rm=T) / 2),1,0))
+
+MS3.c = MS3.b %>% group_by(s, dom, recomb, N, mu, sim_ploidy, traj_ploidy, sampGen, fuseGen, driftGen, rep) %>% summarize(breadth = sum(lessWind) * 20000)
+
+MS3.c %>% filter(sampGen == 1 & fuseGen == 1 & mu==1e-08 & N == 10000 & recomb=="1e-08" & dom == 0.5 & sampGen == 1) %>% ggplot(., aes(y=breadth/1000, fill = as.factor(traj_ploidy), x = as.factor(sim_ploidy))) + geom_boxplot() + facet_grid(cols = vars(driftGen), rows = vars(s), labeller = label_both, scales = "free_y") + ylab(expression(paste("Dip Breadth = Length (kb) of which ", pi[1], " < (",pi[2], " / 2)",sep = ""))) + scale_fill_discrete(name = "Trajectory\nPloidy") + xlab("Simulation Ploidy") + theme_bw()
 ```
@@
 ```{r, echo=T,message=F}
-ms2 %>% filter(dom %in% c("0.1","0.9","0.5") & N == 10000 & fuseGen == 1 & sampGen ==1 & mu==1e-08 & sim_ploidy == 8) %>% ggplot(., aes(y=Pi.1 * 100, color = as.factor(traj_ploidy), x = mid/100000)) + geom_smooth(method="loess", size =0.5, span=0.1, se=F) + scale_x_continuous(breaks=c(1,5,9)) + xlab("Position (100 kb)") + ylab("Diversity (%)") + scale_color_discrete(name="Trajectory\nPloidy") + facet_grid(vars(s, recomb), vars(dom),labeller = label_both, scales = "free_y") + theme_bw()
+ms2 %>% filter(dom %in% c("0.1","0.9","0.5") & N == 10000 & fuseGen == 1 & sampGen ==1 & mu==1e-08 & sim_ploidy == 4) %>% ggplot(., aes(y=Pi.1 * 100, color = as.factor(traj_ploidy), x = mid/100000)) + geom_smooth(method="loess", size =0.5, span=0.1, se=F) + scale_x_continuous(breaks=c(1,5,9)) + xlab("Position (100 kb)") + ylab("Diversity (%)") + scale_color_discrete(name="Trajectory\nPloidy") + facet_grid(vars(s, recomb), vars(dom),labeller = label_both, scales = "free_y") + theme_bw()
 ```
@@
 
-ms2 %>% filter(dom == "0.5" & s==0.01 & fuseGen == 1 & mu==1e-08 & N == 10000 & recomb == 1e-08) %>% ggplot(., aes(y=Tajima.D_1, color = as.factor(sim_ploidy), x = mid/100000)) + geom_smooth(method="loess", size =0.5, span=0.1, se=F) + scale_x_continuous(breaks=c(1,5,9)) + xlab("Position (100 kb)") + ylab("Tajima's D") + scale_color_discrete(name="Ploidy") + facet_grid(vars(sampGen), vars(traj_ploidy),labeller = label_both) + theme_bw()
+ms2 %>% filter(dom == "0.5" & s==0.01 & fuseGen == 1 & mu==1e-08 & N == 10000 & recomb == 5e-08) %>% ggplot(., aes(y=Tajima.D_1, color = as.factor(sim_ploidy), x = mid/100000)) + geom_smooth(method="loess", size =0.5, span=0.1, se=F) + scale_x_continuous(breaks=c(1,5,9)) + xlab("Position (100 kb)") + ylab("Tajima's D") + scale_color_discrete(name="Ploidy") + facet_grid(vars(sampGen), vars(traj_ploidy),labeller = label_both) + theme_bw()
 ```
@@
 ```{r, echo=T,message=F}
-ms2 %>% filter(dom %in% c("0.1","0.9","0.5") & s==0.01 & fuseGen == 1 & mu==1e-08 & N == 10000 & sim_ploidy == traj_ploidy & recomb == 1e-08) %>% ggplot(., aes(y=fst, color = as.factor(sim_ploidy), x = mid/100000)) + geom_smooth(method="loess", size =0.5, span=0.1, se=F) + scale_x_continuous(breaks=c(1,5,9)) + xlab("Position (100 kb)") + ylab("Fst") + scale_color_discrete(name="Ploidy") + facet_grid(vars(sampGen), vars(dom),labeller = label_both) + theme_bw()
+ms %>% filter(dom %in% c("0.1","0.9","0.5") & s==0.01 & fuseGen == 1 & mu==1e-08 & N == 10000 & sim_ploidy == traj_ploidy & recomb == 5e-08 & driftGen == 0) %>% ggplot(., aes(y=fst, color = as.factor(sim_ploidy), x = mid/100000)) + geom_smooth(method="loess", size =0.5, span=0.1, se=F) + scale_x_continuous(breaks=c(1,5,9)) + xlab("Position (100 kb)") + ylab("Fst") + scale_color_discrete(name="Ploidy") + facet_grid(vars(sampGen), vars(dom),labeller = label_both) + theme_bw()
 ```
@@
 ---
+# Evolution figures
+```{r}
+#Dominance curves
+mDoms %>% filter(variable %in% c("0.1", "0.5", "0.9")) %>% ggplot(., aes(x = i.k, y = value, linetype = variable)) + geom_line() + scale_linetype_manual(name = "Dominance", breaks = c("0.1", "0.5", "0.9"), labels = c("Partial\nRecessivity\n", "Additive\n", "Partial\nDominance"), values = c("dashed", "solid","dotdash")) + theme_bw() + xlab("Individual allele frequency of beneficial allele") + ylab("Dominance Coefficient") + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18),axis.text.x=element_text(size=16),axis.title.x=element_text(size=18),legend.text = element_text(size=16), legend.title = element_text(size=18))
 
-# Analysis of rehh calculations
+#Basic chromosome diversity plot
+ms %>% filter(traj_ploidy==sim_ploidy & sampGen == "1" & s == 0.01 & dom == "0.5") %>% ggplot(., aes(y=Pi.1 * 100, color = as.factor(sim_ploidy), x = mid/100000)) + geom_smooth(method="loess", size =0.5, span=0.1, se=F) + scale_x_continuous(breaks=c(1,5,9)) + xlab("Position (100 kb)") + ylab("Diversity (%)") + scale_color_discrete(name="Ploidy") + theme_bw() + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18),axis.text.x=element_text(size=16),axis.title.x=element_text(size=18),legend.text = element_text(size=16), legend.title = element_text(size=18)) + ylim(0, 0.2)
+```
 
-This R package calculates EHH (Extended Haplotype Homozygosity) and related metrics, which can be used to detect a selective sweep.  I'm showing results for the XP-EHH, the cross-populatin EHH.
-
-[Link to Article](https://www.nature.com/articles/nature06250)
-
-### Import Data
+ # Analysis of rehh calculations    This R package calculates EHH
+(Extended Haplotype Homozygosity) and related metrics, which can be used to
+detect a selective sweep.  I'm showing results for the XP-EHH, the
+cross-populatin EHH.   [Link to
+Article](https://www.nature.com/articles/nature06250)   ### Import Data
 ```{r} 
 traj.ehh = read.csv("~/Documents/Research/PloidySim/rehh/rehh_calcs_sp2_se0.01.csv") 
-fact.ehh = read.csv("~/Documents/Research/PloidySim/rehh/rehh_calcs_do0.5_fG1_DS.csv")
+fact.ehh = read.csv("~/Documents/Research/PloidySim/rehh/rehh_calcs_do0.5_fG1_DS_fmted.csv") 
 ```
 
-## Trajectory effect
-
-Faster sweeps in the lower ploidies results in stronger signals of selection.
+## Trajectory effect   Faster sweeps in the lower ploidies results in stronger signals of selection.   
 ```{r, echo=T,message=F}   
-traj.ehh %>% filter(fuseGen=="fG1" & sampGen=="sG1" & recomb == "re1e-08" & dom=="do0.5" & N=="NN10000") %>% ggplot(.,aes(x=POSITION / 100000,y=xpehh.p,color=traj_ploidy)) + geom_smooth(method="loess", span=0.1, se = F) + scale_color_discrete(name="Trajectory\nPloidy", breaks=c("tp2","tp4","tp8"), labels=c("2","4","8")) + xlab("Position (100 kb)") + ylab(expression("-log"[10]*"(p-value)")) + theme_bw()
+traj.ehh %>% filter(fuseGen=="fG1" & sampGen=="sG1" &
+recomb == "re1e-08" & dom=="do0.5" & N=="NN10000") %>% ggplot(.,aes(x=POSITION /
+100000,y=xpehh.p,color=traj_ploidy)) + geom_smooth(method="loess", span=0.1, se
+= F) + scale_color_discrete(name="Trajectory\nPloidy",
+breaks=c("tp2","tp4","tp8"), labels=c("2","4","8")) + xlab("Position (100 kb)")
++ ylab(expression("-log"[10]*"(p-value)")) + theme_bw()
 ```
 
-## Factor-of-two effect
-
-Trajectory ploidy is constant within each panel, while simulation ploidy is varied.
+# Factor-of-two effect   Trajectory ploidy is constant within each panel, while simulation ploidy is varied.
 Higher diversity in higher ploidies produces stronger signal due to greater deviation from baseline genomic diversity.
-
 Something strange here though...why is p value always highest when tp=sp?
 Maybe look at density of NA along chromosomes?
+
 ```{r, echo=T,message=F}   
-fact.ehh %>% filter(s == "se0.01" & fuseGen=="fG1" & recomb == "re1e-08" & dom=="do0.5" & N=="NN10000") %>% ggplot(.,aes(x=POSITION / 100000, y=xpehh.p, color=sim_ploidy)) + geom_smooth(method="loess", span=0.1, se = F) + scale_color_discrete(name="Simulation\nPloidy", breaks=c("sp2","sp4","sp8"), labels=c("2","4","8"))  + facet_grid(cols = vars(traj_ploidy), rows = vars(sampGen))  + xlab("Position (100 kb)") + ylab(expression("-log"[10]*"(p-value)")) + theme_bw()
+fact.ehh %>% filter(s == "se0.01" & fuseGen=="fG1" &
+recomb == "re1e-08" & dom=="do0.5" & N=="NN10000") %>% ggplot(.,aes(x=POSITION /
+100000, y=xpehh.p, color=sim_ploidy)) + geom_smooth(method="loess", span=0.1, se
+= F) + scale_color_discrete(name="Simulation\nPloidy", breaks=c("sp2","sp4","sp8"), labels=c("2","4","8"))  + facet_grid(cols = vars(traj_ploidy), rows = vars(sampGen))  + xlab("Position (100 kb)") + ylab(expression("-log"[10]*"(p-value)")) + theme_bw()
 ```
 
-## Sample generation effect
-
-Does signal decay faster in higher or lower ploidies?
-Answer seems to be that decay is faster in lower ploidies.  Drift is faster in lower ploidies, which is primary mechanism that erases signal of selection.  
+## Sample generation effect   Does signal decay faster in higher or lower
+ploidies?   Answer seems to be that decay is faster in lower ploidies.
+Drift is faster in lower ploidies, which is primary mechanism that erases signal
+of selection.     
 ```{r}   
-fact.ehh %>% filter(s == "se0.01" & fuseGen=="fG1" & dom=="do0.5" & N=="NN10000" & recomb=="re1e-08") %>% ggplot(.,aes(x=POSITION,y=xpehh.p,color=sim_ploidy)) + geom_smooth() + facet_grid(rows = vars(traj_ploidy), cols = vars(sampGen))
+fact.ehh %>% filter(s == "se0.01" &
+fuseGen=="fG1" & dom=="do0.5" & N=="NN10000" & recomb=="re1e-08") %>%
+ggplot(.,aes(x=POSITION,y=xpehh.p,color=sim_ploidy)) + geom_smooth() +
+facet_grid(rows = vars(traj_ploidy), cols = vars(sampGen))   
 ```
 
----
-
-# Less interesting analyses
-
-### Effect of sample generation
-Sample generation is the number of generations following a sweep at which sampling occurs
+---   # Less interesting analyses   
+### Effect of sample
+generation   Sample generation is the number of generations following a
+sweep at which sampling occurs   
 ```{r}    
-ms2 %>% filter(dom %in% c("0.1","0.9","0.5") & s==0.01 & fuseGen == 1 & mu==1e-08 & N == 10000 & recomb == 5e-08 & sim_ploidy == traj_ploidy) %>% ggplot(., aes(y=Pi.1 * 100, color = as.factor(sim_ploidy), x = mid/100000)) + geom_smooth(method="loess", size =0.5, span=0.1, se=F) + scale_x_continuous(breaks=c(1,5,9)) + scale_y_continuous(breaks=c(0.05,0.15)) + xlab("Position (100 kb)") + ylab("Diversity (%)") + scale_color_discrete(name="Simulation\nPloidy") + facet_grid(vars(sampGen), vars(dom),labeller = label_both) + theme_bw()
+ms2 %>% filter(dom %in%
+c("0.1","0.9","0.5") & s==0.01 & fuseGen == 1 & mu==1e-08 & N == 10000 & recomb
+== 5e-08 & sim_ploidy == traj_ploidy) %>% ggplot(., aes(y=Pi.1 * 100, color =
+as.factor(sim_ploidy), x = mid/100000)) + geom_smooth(method="loess", size =0.5,
+span=0.1, se=F) + scale_x_continuous(breaks=c(1,5,9)) +
+scale_y_continuous(breaks=c(0.05,0.15)) + xlab("Position (100 kb)") +
+ylab("Diversity (%)") + scale_color_discrete(name="Simulation\nPloidy") +
+facet_grid(vars(sampGen), vars(dom),labeller = label_both) + theme_bw()  
 ```
 
-### Effect of population size
-Nothing really interesting here...Smaller population size seems noisier as expected
+### Effect of population size   Nothing really interesting
+here...Smaller population size seems noisier as expected   
 ```{r}
-ms2 %>% filter(dom %in% c("0.1","0.9","0.5") & recomb=="1e-08" & fuseGen == 1 & sampGen ==1 & mu==1e-08 & sim_ploidy == traj_ploidy) %>% ggplot(., aes(y=Pi.1 * 100, color = as.factor(traj_ploidy), x = mid/100000)) + geom_smooth(method="loess", size =0.5, span=0.1, se=F) + scale_x_continuous(breaks=c(1,5,9)) + xlab("Position (100 kb)") + ylab("Diversity (%)") + scale_color_discrete(name="Ploidy") + facet_grid(vars(s, N), vars(dom),labeller = label_both, scales = "free_y") + theme_bw()
+ ms2 %>% filter(dom %in% c("0.1","0.9","0.5") & recomb=="1e-08" & fuseGen ==
+1 & sampGen ==1 & mu==1e-08 & sim_ploidy == traj_ploidy) %>% ggplot(.,
+aes(y=Pi.1 * 100, color = as.factor(traj_ploidy), x = mid/100000)) +
+geom_smooth(method="loess", size =0.5, span=0.1, se=F) +
+scale_x_continuous(breaks=c(1,5,9)) + xlab("Position (100 kb)") +
+ylab("Diversity (%)") + scale_color_discrete(name="Ploidy") + facet_grid(vars(s,
+N), vars(dom),labeller = label_both, scales = "free_y") + theme_bw()  
 ``` 
-
   ### Other plots   
-```{r}
-fact.ehh %>% filter(traj_ploidy == "tp4" & fuseGen=="fG1" & dom=="do0.5" & N=="NN10000" & recomb=="re1e-08" & sampGen=="sG1") %>% ggplot(.,aes(x=cut_interval(x=POSITION, n=50),y=xpehh.p,fill=sim_ploidy)) + geom_boxplot() + facet_grid(cols = vars(sampGen))
-
-# # Look for proportional difference in breadth/depth within a simul
-MS2.a %>% filter(fuseGen == 1 & mu==1e-08 & traj_ploidy == 4 & N == 10000 & recomb=="1e-08" & s =="0.01") %>% ggplot(., aes(y=depth, fill = as.factor(sampGen), x = as.factor(sim_ploidy))) + geom_boxplot(notch=T) + ylab(expression(paste("Dip Breadth = Length of which ", pi[1], " < (",pi[2], " / 2)",sep = "")))+ scale_fill_discrete(name = "Trajectory\nPloidy") + xlab("Simulation Ploidy") + theme_bw()
-
-fact.ehh %>% filter(sim_ploidy=="sp8" & fuseGen=="fG1" & sampGen=="sG1" & recomb == "re1e-08" & dom=="do0.5" & N=="NN10000") %>% ggplot(.,aes(x=POSITION / 100000,y=xpehh.p,color=traj_ploidy)) + geom_smooth(method="loess", span=0.1, se = F) + scale_color_discrete(name="Trajectory\nPloidy", breaks=c("tp2","tp4","tp8"), labels=c("2","4","8")) + xlab("Position (100 kb)") + ylab(expression("-log"[10]*"(p-value)")) + theme_bw()
-```
+```{r}   fact.ehh %>%
+filter(traj_ploidy == "tp4" & fuseGen=="fG1" & dom=="do0.5" & N=="NN10000" &
+recomb=="re1e-08" & sampGen=="sG1") %>% ggplot(.,aes(x=cut_interval(x=POSITION,
+n=50),y=xpehh.p,fill=sim_ploidy)) + geom_boxplot() + facet_grid(cols =
+vars(sampGen))   # # Look for proportional difference in breadth/depth
+within a simul   MS2.a %>% filter(fuseGen == 1 & mu==1e-08 & traj_ploidy
+== 4 & N == 10000 & recomb=="1e-08" & s =="0.01") %>% ggplot(., aes(y=depth,
+fill = as.factor(sampGen), x = as.factor(sim_ploidy))) + geom_boxplot(notch=T) +
+ylab(expression(paste("Dip Breadth = Length of which ", pi[1], " < (",pi[2], " /
+2)",sep = "")))+ scale_fill_discrete(name = "Trajectory\nPloidy") +
+xlab("Simulation Ploidy") + theme_bw()   fact.ehh %>%
+filter(sim_ploidy=="sp8" & fuseGen=="fG1" & sampGen=="sG1" & recomb == "re1e-08"
+& dom=="do0.5" & N=="NN10000") %>% ggplot(.,aes(x=POSITION /
+100000,y=xpehh.p,color=traj_ploidy)) + geom_smooth(method="loess", span=0.1, se
+= F) + scale_color_discrete(name="Trajectory\nPloidy",
+breaks=c("tp2","tp4","tp8"), labels=c("2","4","8")) + xlab("Position (100 kb)")
++ ylab(expression("-log"[10]*"(p-value)")) + theme_bw()   ```  
+```{r}   diffusionDensity = function(start_freq, N, ploidy, t){  
+x = seq(0, 1, 0.01)     d = N * ploidy     p = start_freq  
+dens = (6 * p * (1 - p) * exp(-t/d)) + (30 * p * (1 - p) * (1 - 2*p) * (1 - 2 *
+x ) * exp((-3*t)/d))     return(data.frame("dens" = dens, x = x)) 
+ }   aa = diffusionDensity(1/4000, 1000, 4, 1000)   aa %<>%
+mutate(ul = x, ll = lag(x), height = (lag(dens) + dens) / 2, width = ul - ll,
+area = height * width) %>% filter(area > 0) %>% select(-x) %>% mutate(prob =
+area / sum(area))   dfreq = sample(aa$ul, 1, replace = T, prob = aa$prob)
+  Drift = function(N, ploidy, end, tries){     drift = function(N,
+ploidy, end, tries){       C = N * ploidy # # of chromosomes   p =
+0 # Current frequency       traj = c(1/C)       while(p == 0){ 
+       p = rbinom(1, C, (1 / C)) / (C) # Draw # of mutant alleles for next
+generation and divive by C to get freq       }       t = 1 
+     traj = c(traj, p)       while(p != 0 & p != 1 & t < end){ # Loop
+till absorption or beginning of selection         p = rbinom(1, C, p) / C
+        t = t + 1         traj = c(traj, p)       } 
+     return(traj)     }     tt = 1     traj = drift(N,
+ploidy, end)     while(tt < tries & (traj[length(traj)] == 0 |
+traj[length(traj)] == 1)){       traj = drift(N, ploidy, end)  
+}     return(traj)   }   ```

### 2019-07-18 analysis/EvolTalk.Rmd
about to do some major reorganization

@@
 library(IDPmisc)
+library(wesanderson)
 
@@
 
-MS2.f %>% filter(sim_ploidy == traj_ploidy & mu==1e-08 & N == 10000 & s =="0.01" & driftGen %in% c(0,1) & sampGen == 1 & dom %in% c(0.1, 0.5, 0.9)) %>% mutate(Dom = factor(case_when(dom == 0.1 ~ "Partial Recessivity", dom == 0.5 ~ "Additivity", dom == 0.9 ~ "Partial Dominance"), levels = c("Partial Recessivity", "Additivity", "Partial Dominance")), Height = (log(min.pi, 10)), Breadth = breadth.pi/100000, Depth = depth.pi) %>% select(Dom, traj_ploidy, Depth, Breadth) %>% melt(., id.var = c("Dom", "traj_ploidy")) %>% ggplot(., aes(y = value, fill = as.factor(Dom), x = as.factor(traj_ploidy))) + geom_boxplot(outlier.shape = NA) + scale_fill_discrete(name = "Dominance") + facet_wrap(~variable, scales = "free_y") + ylab("") + xlab("Ploidy") + theme_bw() + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18),axis.text.x=element_text(size=16),axis.title.x=element_text(size=18),legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16))
+MS2.f %>% filter(sim_ploidy == traj_ploidy & mu==1e-08 & N == 10000 & s =="0.01" & driftGen %in% c(0,1) & sampGen == 1 & dom %in% c(0.1, 0.5, 0.9)) %>% mutate(Dom = factor(case_when(dom == 0.1 ~ "Partial Recessivity", dom == 0.5 ~ "Additivity", dom == 0.9 ~ "Partial Dominance"), levels = c("Partial Recessivity", "Additivity", "Partial Dominance")), Height = (log(min.pi, 10)), Breadth = breadth.pi/10000, Magnitude = depth.pi) %>% select(Dom, traj_ploidy, Magnitude, Breadth) %>% melt(., id.var = c("Dom", "traj_ploidy")) %>% ggplot(., aes(y = value, fill = as.factor(Dom), x = as.factor(traj_ploidy))) + geom_boxplot(outlier.shape = NA) + scale_fill_discrete(name = "Dominance") + facet_wrap(~variable, scales = "free_y") + ylab("") + xlab("Ploidy") + theme_bw() + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18),axis.text.x=element_text(size=16),axis.title.x=element_text(size=18),legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16))
 
 #Ploidy
-MS2.f %>% filter(sim_ploidy == traj_ploidy & mu==1e-08 & N == 10000 & s =="0.01" & driftGen %in% c(0,1) & sampGen == 1 & dom %in% c(0.1, 0.5, 0.9)) %>% mutate(Dom = factor(case_when(dom == 0.1 ~ "Partial Recessivity", dom == 0.5 ~ "Additivity", dom == 0.9 ~ "Partial Dominance"), levels = c("Partial Recessivity", "Additivity", "Partial Dominance")), Height = (log(min.pi, 10)), Breadth = breadth.pi/100000, Depth = depth.pi) %>% select(Dom, traj_ploidy, Depth, Breadth, Height) %>% melt(., id.var = c("Dom", "traj_ploidy")) %>% ggplot(., aes(y = value, fill = as.factor(Dom), x = as.factor(traj_ploidy))) + geom_boxplot(outlier.shape = NA) + scale_fill_manual(name = "Dominance", values=wes_palette("Royal1")) + facet_wrap(~variable, scales = "free_y") + ylab("") + xlab("Ploidy") + theme_bw() + theme(axis.text.y=element_blank(), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18),legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16), axis.ticks.y = element_blank())
+MS2.f %>% filter(sim_ploidy == traj_ploidy & mu==1e-08 & N == 10000 & s =="0.01" & driftGen %in% c(0,1) & sampGen == 1 & dom %in% c(0.1, 0.5, 0.9)) %>% mutate(Dom = factor(case_when(dom == 0.1 ~ "Partial Recessivity", dom == 0.5 ~ "Additivity", dom == 0.9 ~ "Partial Dominance"), levels = c("Partial Recessivity", "Additivity", "Partial Dominance")), Height = (log(min.pi, 10)), Breadth = breadth.pi/10000, Magnitude = depth.pi, Size = breadth.pi * depth.pi) %>% select(Dom, traj_ploidy, Magnitude, Breadth, Size) %>% melt(., id.var = c("Dom", "traj_ploidy")) %>% ggplot(., aes(y = value, fill = as.factor(Dom), x = as.factor(traj_ploidy))) + geom_boxplot(outlier.shape = NA) + scale_fill_manual(name = "Dominance", values=wes_palette("Royal1")) + facet_wrap(~variable, scales = "free_y") + ylab("") + xlab("Ploidy") + theme_bw() + theme(axis.text.y=element_text(size = 16), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18),legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16))
+
+#Just additive
+MS2.f %>% filter(sim_ploidy == traj_ploidy & mu==1e-08 & N == 10000 & s =="0.01" & driftGen %in% c(0,1) & sampGen == 1 & dom %in% c(0.5)) %>% mutate(Dom = factor(case_when(dom == 0.1 ~ "Partial Recessivity", dom == 0.5 ~ "Additivity", dom == 0.9 ~ "Partial Dominance"), levels = c("Partial Recessivity", "Additivity", "Partial Dominance")), Height = (log(min.pi, 10)), Breadth = breadth.pi/10000, Magnitude = depth.pi) %>% select(Dom, traj_ploidy, Magnitude, Breadth) %>% melt(., id.var = c("Dom", "traj_ploidy")) %>% ggplot(., aes(y = value, fill = as.factor(traj_ploidy), x = as.factor(traj_ploidy))) + geom_boxplot(outlier.shape = NA) + scale_fill_discrete(guide = F) + facet_wrap(~variable, scales = "free_y") + ylab("") + xlab("\n\n") + theme_bw() + theme(axis.text.y=element_text(size = 16), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18),legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16))
 
 #disentangling
-MS2.f %>% filter(mu==1e-08 & N == 10000 & s =="0.01" & driftGen %in% c(0,1) & sampGen == 1 & dom %in% c(0.5)) %>% mutate(Height = (log(min.pi, 10)), Breadth = breadth.pi/100000, Depth = depth.pi) %>% select(sim_ploidy, traj_ploidy, Depth, Breadth, Height, same_ploidy) %>% melt(., id.var = c("sim_ploidy", "traj_ploidy", "same_ploidy")) %>% ggplot(., aes(y = value, fill = as.factor(traj_ploidy), x = as.factor(sim_ploidy), color = same_ploidy)) + geom_boxplot(outlier.shape = NA) + scale_fill_discrete(name = "Trajectory Ploidy") + scale_color_manual(guide=F, values = c("black", "red")) + facet_wrap(~variable, scales = "free_y") + ylab("") + xlab("Coalescent Ploidy") + theme_bw() + theme(axis.text.y=element_blank(), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18), legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16), axis.ticks.y = element_blank())
+MS2.f %>% filter(mu==1e-08 & N == 10000 & s =="0.01" & driftGen %in% c(0,1) & sampGen == 1 & dom %in% c(0.5)) %>% mutate(Height = (log(min.pi, 10)), Breadth = breadth.pi/10000, Magnitude = depth.pi) %>% select(sim_ploidy, traj_ploidy, Magnitude, Breadth, same_ploidy) %>% melt(., id.var = c("sim_ploidy", "traj_ploidy", "same_ploidy")) %>% ggplot(., aes(y = value, fill = as.factor(traj_ploidy), x = as.factor(sim_ploidy), color = same_ploidy)) + geom_boxplot(outlier.shape = NA) + scale_fill_manual(name = "Trajectory Ploidy", values = wes_palette("Moonrise2")) + scale_color_manual(guide=F, values = c("black", "red")) + facet_wrap(~variable, scales = "free_y") + ylab("") + xlab("\n\n") + theme_bw() + theme(axis.text.y=element_text(size = 16), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18), legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16))
 
 #drift
-MS2.f %>% filter(mu==1e-08 & N == 10000 & s =="0.01" & driftGen %in% c(0) & sampGen == 1 & dom %in% c(0.5)) %>% mutate(Height = (log(min.pi, 10)), Breadth = breadth.pi/100000, Depth = depth.pi) %>% select(sim_ploidy, traj_ploidy, driftGen, Depth, Breadth, Height, same_ploidy) %>% melt(., id.var = c("sim_ploidy", "traj_ploidy", "driftGen", "same_ploidy")) %>% ggplot(., aes(y = value, fill = as.factor(traj_ploidy), x = as.factor(sim_ploidy), color = same_ploidy)) + geom_boxplot(outlier.shape = NA) + scale_color_manual(guide=F, values = c("black", "red")) + scale_fill_discrete(name = "Trajectory Ploidy") + facet_wrap(~variable, scales = "free_y") + ylab("") + xlab("Coalescent Ploidy") + theme_bw() + theme(axis.text.y=element_blank(), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18), legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16), axis.ticks.y = element_blank())
+MS2.f %>% filter(mu==1e-08 & N == 10000 & s =="0.01" & driftGen %in% c(0) & sampGen == 1 & dom %in% c(0.5)) %>% mutate(Height = (log(min.pi, 10)), Breadth = breadth.pi/10000, Magnitude = depth.pi) %>% select(sim_ploidy, traj_ploidy, driftGen, Depth, Breadth, same_ploidy) %>% melt(., id.var = c("sim_ploidy", "traj_ploidy", "driftGen", "same_ploidy")) %>% ggplot(., aes(y = value, fill = as.factor(traj_ploidy), x = as.factor(sim_ploidy), color = same_ploidy)) + geom_boxplot(outlier.shape = NA) + scale_color_manual(guide=F, values = c("black", "red")) + scale_fill_manual(name = "Trajectory Ploidy", values = wes_palette("Moonrise2")) + facet_wrap(~variable, scales = "free_y") + ylab("") + xlab("") + theme_bw() + theme(axis.text.y=element_text(size = 16), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18), legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16))
 
-MS2.f %>% filter(mu==1e-08 & N == 10000 & s =="0.01" & driftGen %in% c(10000) & sampGen == 1 & dom %in% c(0.5)) %>% mutate(Height = (log(min.pi, 10)), Breadth = breadth.pi/100000, Depth = depth.pi) %>% select(sim_ploidy, traj_ploidy, driftGen, Depth, Breadth, Height, same_ploidy) %>% melt(., id.var = c("sim_ploidy", "traj_ploidy", "driftGen", "same_ploidy")) %>% ggplot(., aes(y = value, fill = as.factor(traj_ploidy), x = as.factor(sim_ploidy), color = same_ploidy)) + scale_color_manual(guide=F, values = c("black", "red")) + geom_boxplot(outlier.shape = NA) + scale_fill_discrete(name = "Trajectory Ploidy") + facet_wrap(~variable, scales = "free_y") + ylab("") + xlab("Coalescent Ploidy") + theme_bw() + theme(axis.text.y=element_blank(), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18), legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16), axis.ticks.y = element_blank())
+MS2.f %>% filter(mu==1e-08 & N == 10000 & s =="0.01" & driftGen %in% c(10000) & sampGen == 1 & dom %in% c(0.5)) %>% mutate(Height = (log(min.pi, 10)), Breadth = breadth.pi/10000, Depth = depth.pi) %>% select(sim_ploidy, traj_ploidy, driftGen, Depth, Breadth, same_ploidy) %>% melt(., id.var = c("sim_ploidy", "traj_ploidy", "driftGen", "same_ploidy")) %>% ggplot(., aes(y = value, fill = as.factor(traj_ploidy), x = as.factor(sim_ploidy), color = same_ploidy)) + scale_color_manual(guide=F, values = c("black", "red")) + geom_boxplot(outlier.shape = NA) + scale_fill_manual(name = "Trajectory Ploidy",values = wes_palette("Moonrise2")) + facet_wrap(~variable, scales = "free_y") + ylab("") + xlab("") + theme_bw() + theme(axis.text.y=element_text(size = 16), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18), legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16))
 
@@
 
-ee = ms %>% filter(fuseGen==1 & driftGen %in% c(1,0,10000) & dom == 0.5 & sampGen %in% c(1,10000)) %>% nest(-c(s, dom, recomb, N, mu, sim_ploidy, traj_ploidy, sampGen, fuseGen, rep, driftGen)) %>% mutate(height.taj = map(data, ~getDims(., y.metric = "Tajima.D_1")$height), width.taj = map(data, ~getDims(., y.metric = "Tajima.D_1")$width), height.fst = map(data, ~getDims(.)$height), width.fst = map(data, ~getDims(.)$width), height.h = map(data, ~getDims(., y.metric = "Fay.Wu.H_1")$height), width.h = map(data, ~getDims(., y.metric = "Fay.Wu.H_1")$width), height.e = map(data, ~getDims(., y.metric = "Zeng.E_1")$height), width.e = map(data, ~getDims(., y.metric = "Zeng.E_1")$width),) %>% select(-data) %>% unnest()
+getStat = function(dat, stat){return(median(unlist(dat[stat]), na.rm = T))}
 
-ee %>% filter(sampGen == "1" & s == "0.01" & fuseGen=="1" & recomb == "5e-08" & dom=="0.5" & N=="10000" & driftGen == 0 & width.fst < 60000) %>% mutate("Magnitude" = height.fst, "Breadth" = width.fst / 10000, same_ploidy = ifelse(sim_ploidy == traj_ploidy, 1, 0)) %>% select(sim_ploidy, traj_ploidy, same_ploidy, Magnitude, Breadth) %>% melt(., id.var = c("sim_ploidy", "traj_ploidy", "same_ploidy")) %>% mutate("Fst" = variable) %>% filter(value != -9) %>% ggplot(., aes(y = value, fill = as.factor(traj_ploidy), x = as.factor(sim_ploidy), color = as.factor(same_ploidy))) + geom_boxplot(outlier.shape = NA) + scale_fill_discrete(name = "Trajectory Ploidy", labels = c("2", "4", "8")) + scale_color_manual(guide=F, values = c("black","red")) + facet_wrap(~Fst, scales = "free_y", labeller = label_both) + ylab("") + xlab("Coalescent Ploidy") + theme_bw() + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18), legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16))
+ee = ms %>% filter(fuseGen==1 & driftGen %in% c(1,0,10000) & sampGen %in% c(1,1000,10000)) %>% nest(-c(s, dom, recomb, N, mu, sim_ploidy, traj_ploidy, sampGen, fuseGen, rep, driftGen)) %>% mutate(height.taj = map(data, ~getDims(., y.metric = "Tajima.D_1")$height), width.taj = map(data, ~getDims(., y.metric = "Tajima.D_1")$width), height.fst = map(data, ~getDims(.)$height), med.fst = map(data, ~getStat(., "fst")), width.fst = map(data, ~getDims(.)$width), height.h = map(data, ~getDims(., y.metric = "Fay.Wu.H_1")$height), width.h = map(data, ~getDims(., y.metric = "Fay.Wu.H_1")$width), height.e = map(data, ~getDims(., y.metric = "Zeng.E_1")$height), width.e = map(data, ~getDims(., y.metric = "Zeng.E_1")$width), height.dxy = map(data, ~getDims(., y.metric = "dxy.1.2")$height), width.dxy = map(data, ~getDims(., y.metric = "dxy.1.2")$width), med.dxy = map(data, ~getStat(., "dxy.1.2"))) %>% select(-data) %>% unnest()
 
-ee %>% filter(sampGen == "1" & s == "0.01" & fuseGen=="1" & recomb == "5e-08" & dom=="0.5" & N=="10000" & driftGen == 0 & width.taj < 100000) %>% mutate("Magnitude" = height.taj, "Breadth" = width.taj / 10000, same_ploidy = ifelse(sim_ploidy == traj_ploidy, 1, 0)) %>% select(sim_ploidy, traj_ploidy, same_ploidy, Magnitude, Breadth) %>% melt(., id.var = c("sim_ploidy", "traj_ploidy", "same_ploidy")) %>% mutate("TajD" = variable) %>% filter(value != -9) %>% ggplot(., aes(y = value, fill = as.factor(traj_ploidy), x = as.factor(sim_ploidy), color = as.factor(same_ploidy))) + geom_boxplot(outlier.shape = NA) + scale_fill_discrete(name = "Trajectory Ploidy", labels = c("2", "4", "8")) + scale_color_manual(guide=F, values = c("black","red")) + facet_wrap(~TajD, scales = "free_y", labeller = label_both) + ylab("") + xlab("Coalescent Ploidy") + theme_bw() + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18), legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16))
+#All metrics together for sampGen
+#Magnitude
 
-ee %>% filter(sampGen == "1" & s == "0.01" & fuseGen=="1" & recomb == "5e-08" & dom=="0.5" & N=="10000" & driftGen == 0) %>% mutate("Magnitude" = height.h, "Breadth" = width.h / 10000, same_ploidy = ifelse(sim_ploidy == traj_ploidy, 1, 0)) %>% select(sim_ploidy, traj_ploidy, same_ploidy, Magnitude, Breadth) %>% melt(., id.var = c("sim_ploidy", "traj_ploidy", "same_ploidy")) %>% mutate("Fay & Wu's H" = variable) %>% filter(value != -9) %>% ggplot(., aes(y = value, fill = as.factor(traj_ploidy), x = as.factor(sim_ploidy), color = as.factor(same_ploidy))) + geom_boxplot(outlier.shape = NA) + scale_fill_discrete(name = "Trajectory Ploidy", labels = c("2", "4", "8")) + scale_color_manual(guide=F, values = c("black","red")) + facet_wrap(~`Fay & Wu's H`, scales = "free_y", labeller = label_both) + ylab("") + xlab("Coalescent Ploidy") + theme_bw() + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18), legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16))
+dd = ms %>% filter(sim_ploidy == traj_ploidy & fuseGen==1 & s == "0.01" & recomb == "1e-08" & N=="10000" & driftGen == 0 & sampGen %in% c(1,1000,10000)) %>% nest(-c(s, dom, recomb, N, mu, sim_ploidy, traj_ploidy, sampGen, fuseGen, rep, driftGen)) %>% mutate(height.taj = map(data, ~getDims(., y.metric = "Tajima.D_1")$height), width.taj = map(data, ~getDims(., y.metric = "Tajima.D_1")$width), height.fst = map(data, ~getDims(.)$height), med.fst = map(data, ~getStat(., "fst")), width.fst = map(data, ~getDims(.)$width), height.h = map(data, ~getDims(., y.metric = "Fay.Wu.H_1")$height), width.h = map(data, ~getDims(., y.metric = "Fay.Wu.H_1")$width), height.e = map(data, ~getDims(., y.metric = "Zeng.E_1")$height), width.e = map(data, ~getDims(., y.metric = "Zeng.E_1")$width), height.dxy = map(data, ~getDims(., y.metric = "dxy.1.2")$height), width.dxy = map(data, ~getDims(., y.metric = "dxy.1.2")$width), med.dxy = map(data, ~getStat(., "dxy.1.2"))) %>% select(-data) %>% unnest()
 
-ee %>% filter(sampGen == "1" & s == "0.01" & fuseGen=="1" & recomb == "5e-08" & dom=="0.5" & N=="10000" & driftGen == 0) %>% mutate("Magnitude" = height.e, "Breadth" = width.e / 10000, same_ploidy = ifelse(sim_ploidy == traj_ploidy, 1, 0)) %>% select(sim_ploidy, traj_ploidy, same_ploidy, Magnitude, Breadth) %>% melt(., id.var = c("sim_ploidy", "traj_ploidy", "same_ploidy")) %>% mutate("Zeng's E" = variable) %>% filter(value != -9) %>% ggplot(., aes(y = value, fill = as.factor(traj_ploidy), x = as.factor(sim_ploidy), color = as.factor(same_ploidy))) + geom_boxplot(outlier.shape = NA) + scale_fill_discrete(name = "Trajectory Ploidy", labels = c("2", "4", "8")) + scale_color_manual(guide=F, values = c("black","red")) + facet_wrap(~`Zeng's E`, scales = "free_y", labeller = label_both) + ylab("") + xlab("Coalescent Ploidy") + theme_bw() + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18), legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16))
+dd = ms %>% filter(sim_ploidy == traj_ploidy & s == "0.01" & recomb == "5e-08" & N=="10000" & driftGen == 0 & sampGen %in% c(1,1000,10000)) %>% nest(-c(s, dom, recomb, N, mu, sim_ploidy, traj_ploidy, sampGen, fuseGen, rep, driftGen)) %>% mutate(height.taj = map(data, ~getDims(., y.metric = "Tajima.D_1")$height), width.taj = map(data, ~getDims(., y.metric = "Tajima.D_1")$width), height.fst = map(data, ~getDims(.)$height), med.fst = map(data, ~getStat(., "fst")), width.fst = map(data, ~getDims(.)$width), height.h = map(data, ~getDims(., y.metric = "Fay.Wu.H_1")$height), width.h = map(data, ~getDims(., y.metric = "Fay.Wu.H_1")$width), height.e = map(data, ~getDims(., y.metric = "Zeng.E_1")$height), width.e = map(data, ~getDims(., y.metric = "Zeng.E_1")$width), height.dxy = map(data, ~getDims(., y.metric = "dxy.1.2")$height), width.dxy = map(data, ~getDims(., y.metric = "dxy.1.2")$width), med.dxy = map(data, ~getStat(., "dxy.1.2"))) %>% select(-data) %>% unnest()
 
-ee %>% filter(sampGen == "10000" & s == "0.01" & fuseGen=="1" & recomb == "5e-08" & dom=="0.5" & N=="10000" & driftGen == 0 & width.fst < 60000) %>% mutate("Magnitude" = height.fst, "Breadth" = width.fst / 10000, same_ploidy = ifelse(sim_ploidy == traj_ploidy, 1, 0)) %>% select(sim_ploidy, traj_ploidy, same_ploidy, Magnitude, Breadth) %>% melt(., id.var = c("sim_ploidy", "traj_ploidy", "same_ploidy")) %>% mutate("Fst" = variable) %>% filter(value != -9) %>% ggplot(., aes(y = value, fill = as.factor(traj_ploidy), x = as.factor(sim_ploidy), color = as.factor(same_ploidy))) + geom_boxplot(outlier.shape = NA) + scale_fill_discrete(name = "Trajectory Ploidy", labels = c("2", "4", "8")) + scale_color_manual(guide=F, values = c("black","red")) + facet_wrap(~Fst, scales = "free_y", labeller = label_both) + ylab("") + xlab("Coalescent Ploidy") + theme_bw() + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18), legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16))
+#Winner
+dd %>% filter(dom == 0.5 & traj_ploidy == sim_ploidy & s == "0.01" & N=="10000" & driftGen == 0)  %>% mutate("TajD" = height.taj * width.taj / 2, "FayWuH" = height.h * width.h / 2, "ZengsE" = height.e * width.e / 2) %>% select(sim_ploidy, sampGen, TajD, FayWuH, ZengsE) %>% melt(., id.var = c("sim_ploidy", "sampGen")) %>% mutate("Magnitude" = variable) %>% filter(value != 40.5) %>% ggplot(., aes(y = value / 10000, fill = as.factor(sampGen), x = as.factor(sim_ploidy))) + geom_boxplot(outlier.shape = NA) + scale_fill_manual(name = "Generations\nsince Fixation", values = wes_palette("Royal2")) + ylim(0,7) + ylab("Peak Area") + xlab("Ploidy") + facet_wrap(~Magnitude) + theme_bw() + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18), legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16))
 
-ee %>% filter(sampGen == "10000" & s == "0.01" & fuseGen=="1" & recomb == "5e-08" & dom=="0.5" & N=="10000" & driftGen == 0 & width.taj < 100000) %>% mutate("Magnitude" = height.taj, "Breadth" = width.taj / 10000, same_ploidy = ifelse(sim_ploidy == traj_ploidy, 1, 0)) %>% select(sim_ploidy, traj_ploidy, same_ploidy, Magnitude, Breadth) %>% melt(., id.var = c("sim_ploidy", "traj_ploidy", "same_ploidy")) %>% mutate("TajD" = variable) %>% filter(value != -9) %>% ggplot(., aes(y = value, fill = as.factor(traj_ploidy), x = as.factor(sim_ploidy), color = as.factor(same_ploidy))) + geom_boxplot(outlier.shape = NA) + scale_fill_discrete(name = "Trajectory Ploidy", labels = c("2", "4", "8")) + scale_color_manual(guide=F, values = c("black","red")) + facet_wrap(~TajD, scales = "free_y", labeller = label_both) + ylab("") + xlab("Coalescent Ploidy") + theme_bw() + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18), legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16))
+dd.points = dd %>% filter(dom %in% c("0.1", "0.9") & traj_ploidy == sim_ploidy & s == "0.01" & recomb == "1e-08" & N=="10000" & driftGen == 0)  %>% mutate("TajD" = height.taj * width.taj / 2, "FayWuH" = height.h * width.h / 2, "ZengsE" = height.e * width.e / 2) %>% select(sim_ploidy, dom, sampGen, TajD, FayWuH, ZengsE) %>% melt(., id.var = c("sim_ploidy", "sampGen", "dom")) %>% mutate("Area" = variable) %>% filter(value != 40.5) %>% group_by(sim_ploidy, sampGen, dom, variable) %>% summarize(median = median(value))
 
-ee %>% filter(traj_ploidy == sim_ploidy & s == "0.01" & fuseGen=="1" & recomb == "5e-08" & dom=="0.5" & N=="10000" & driftGen == 0 & width.taj < 100000) %>% mutate("Magnitude" = height.taj, "Breadth" = width.taj / 10000, same_ploidy = ifelse(sim_ploidy == traj_ploidy, 1, 0)) %>% select(sim_ploidy, sampGen, Magnitude, Breadth) %>% melt(., id.var = c("sim_ploidy", "sampGen")) %>% mutate("TajD" = variable) %>% filter(value != -9) %>% ggplot(., aes(y = value, fill = as.factor(sampGen), x = as.factor(sim_ploidy))) + geom_boxplot(outlier.shape = NA) + scale_fill_discrete(name = "Generations since\nFixation") + ylab("") + xlab("Coalescent Ploidy") + facet_wrap(~TajD, labeller = label_both, scales = "free_y") +theme_bw() + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18), legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16))
+gg %>% filter(dom == 0.5 & traj_ploidy == sim_ploidy & s == "0.01" & recomb == "1e-08" & N=="10000" & driftGen == 0)  %>% mutate("Fst" = (height.fst - med.fst) * width.fst, "Dxy" = (height.dxy - med.dxy) * width.dxy, "XPEHH" = height.xp * width.xp) %>% select(sim_ploidy, sampGen, Fst, Dxy, XPEHH) %>% melt(., id.var = c("sim_ploidy", "sampGen")) %>% mutate("Magnitude" = variable) %>% filter(value != -9) %>% ggplot(., aes(y = value / 10000, fill = as.factor(sampGen), x = as.factor(sim_ploidy))) + geom_boxplot(outlier.shape = NA) + scale_fill_manual(name = "Generations\nsince Fixation", values = wes_palette("Royal2")) + ylab("Peak Size") + xlab("Ploidy") + facet_wrap(~Magnitude, scales = "free_y") +theme_bw() + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18), legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16))
 
-ee %>% filter(traj_ploidy == sim_ploidy & s == "0.01" & fuseGen=="1" & recomb == "5e-08" & dom=="0.5" & N=="10000" & driftGen == 0 & width.fst < 100000) %>% mutate("Magnitude" = height.fst, "Breadth" = width.fst / 10000, same_ploidy = ifelse(sim_ploidy == traj_ploidy, 1, 0)) %>% select(sim_ploidy, sampGen, Magnitude, Breadth) %>% melt(., id.var = c("sim_ploidy", "sampGen")) %>% mutate("Fst" = variable) %>% filter(value != -9) %>% ggplot(., aes(y = value, fill = as.factor(sampGen), x = as.factor(sim_ploidy))) + geom_boxplot(outlier.shape = NA) + scale_fill_discrete(name = "Generations since\nFixation") + ylab("") + xlab("Coalescent Ploidy") + facet_wrap(~Fst, labeller = label_both, scales = "free_y") +theme_bw() + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18), legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16))
+# dd %>% filter(traj_ploidy == sim_ploidy & s == "0.01" & recomb == "1e-08" & N=="10000" & driftGen == 0)  %>% mutate("TajD" = height.taj, "FayWuH" = height.h, "ZengsE" = height.e) %>% select(sim_ploidy, sampGen, TajD, FayWuH, ZengsE) %>% melt(., id.var = c("sim_ploidy", "sampGen")) %>% mutate("Magnitude" = variable) %>% filter(value != -9) %>% ggplot(., aes(y = value, fill = as.factor(sampGen), x = as.factor(sim_ploidy))) + geom_boxplot(outlier.shape = NA) + scale_fill_manual(name = "Generations since\nFixation", values = wes_palette("Royal2")) + ylab("") + xlab("Ploidy") + facet_wrap(~Magnitude, labeller = label_both, scales = "free_y") +theme_bw() + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18), legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16))
+# 
+# dd %>% filter(traj_ploidy == sim_ploidy & s == "0.01" & recomb == "1e-08" & N=="10000" & driftGen == 0)  %>% mutate("TajD" = width.taj, "FayWuH" = width.h, "ZengsE" = width.e) %>% select(sim_ploidy, sampGen, TajD, FayWuH, ZengsE) %>% melt(., id.var = c("sim_ploidy", "sampGen")) %>% mutate("Breadth" = variable) %>% filter(value != -9) %>% ggplot(., aes(y = value / 10000, fill = as.factor(sampGen), x = as.factor(sim_ploidy))) + geom_boxplot(outlier.shape = NA) + scale_fill_manual(name = "Generations since\nFixation", values = wes_palette("Royal2")) + ylab("") + xlab("Ploidy") + facet_wrap(~Breadth, labeller = label_both, scales = "free_y") +theme_bw() + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18), legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16))
 
-ee %>% filter(traj_ploidy == sim_ploidy & s == "0.01" & fuseGen=="1" & recomb == "5e-08" & dom=="0.5" & N=="10000" & driftGen == 0 & width.taj < 100000) %>% mutate("Magnitude" = height.h, "Breadth" = width.h / 10000, same_ploidy = ifelse(sim_ploidy == traj_ploidy, 1, 0)) %>% select(sim_ploidy, sampGen, Magnitude, Breadth) %>% melt(., id.var = c("sim_ploidy", "sampGen")) %>% mutate("Fay & Wu's H" = variable) %>% filter(value != -9) %>% ggplot(., aes(y = value, fill = as.factor(sampGen), x = as.factor(sim_ploidy))) + geom_boxplot(outlier.shape = NA) + scale_fill_discrete(name = "Generations since\nFixation") + ylab("") + xlab("Coalescent Ploidy") + facet_wrap(~`Fay & Wu's H`, labeller = label_both, scales = "free_y") +theme_bw() + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18), legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16))
+# gg %>% filter(dom == 0.5 & traj_ploidy == sim_ploidy & s == "0.01" & recomb == "1e-08" & N=="10000" & driftGen == 0)  %>% mutate("Fst" = height.fst - med.fst, "Dxy" = height.dxy - med.dxy, "XPEHH" = height.xp) %>% select(sim_ploidy, sampGen, Fst, Dxy, XPEHH) %>% melt(., id.var = c("sim_ploidy", "sampGen")) %>% mutate("Magnitude" = variable) %>% filter(value != -9) %>% ggplot(., aes(y = value, fill = as.factor(sampGen), x = as.factor(sim_ploidy))) + geom_boxplot(outlier.shape = NA) + scale_fill_manual(name = "Generations since\nFixation", values = wes_palette("Royal2")) + ylab("") + xlab("Ploidy") + facet_wrap(~Magnitude, labeller = label_both, scales = "free_y") +theme_bw() + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18), legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16))
+# 
+# gg %>% filter(dom == 0.5 & traj_ploidy == sim_ploidy & s == "0.01" & recomb == "1e-08" & N=="10000" & driftGen == 0)  %>% mutate("Fst" = width.fst, "Dxy" = width.dxy, "XPEHH" = width.xp) %>% select(sim_ploidy, sampGen, Fst, Dxy, XPEHH) %>% melt(., id.var = c("sim_ploidy", "sampGen")) %>% mutate("Breadth" = variable) %>% filter(value != -9) %>% ggplot(., aes(y = value / 10000, fill = as.factor(sampGen), x = as.factor(sim_ploidy))) + geom_boxplot(outlier.shape = NA) + scale_fill_manual(name = "Generations since\nFixation", values = wes_palette("Royal2")) + ylab("") + xlab("Ploidy") + facet_wrap(~Breadth, labeller = label_both, scales = "free_y") +theme_bw() + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18), legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16))
 
-ee %>% filter(traj_ploidy == sim_ploidy & s == "0.01" & fuseGen=="1" & recomb == "5e-08" & dom=="0.5" & N=="10000" & driftGen == 0 & width.fst < 100000) %>% mutate("Magnitude" = height.e, "Breadth" = width.e / 10000, same_ploidy = ifelse(sim_ploidy == traj_ploidy, 1, 0)) %>% select(sim_ploidy, sampGen, Magnitude, Breadth) %>% melt(., id.var = c("sim_ploidy", "sampGen")) %>% mutate("Zeng's E" = variable) %>% filter(value != -9) %>% ggplot(., aes(y = value, fill = as.factor(sampGen), x = as.factor(sim_ploidy))) + geom_boxplot(outlier.shape = NA) + scale_fill_discrete(name = "Generations since\nFixation") + ylab("") + xlab("Coalescent Ploidy") + facet_wrap(~`Zeng's E`, labeller = label_both, scales = "free_y") +theme_bw() + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18), legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16))
+#Dominance...change to do peak size instead.  Without 0's
+ee %>% filter(dom %in% c(0.1, 0.5, 0.9) & traj_ploidy == sim_ploidy & s == "0.01" & recomb == "1e-08" & N=="10000" & driftGen == 0 & sampGen == 1) %>% mutate(Dom = factor(case_when(dom == 0.1 ~ "Partial Recessivity", dom == 0.5 ~ "Additivity", dom == 0.9 ~ "Partial Dominance"), levels = c("Partial Recessivity", "Additivity", "Partial Dominance")), "TajD" = height.taj * width.taj / 2, "FayWuH" = height.h * width.h / 2, "ZengsE" = height.e * width.e / 2, same_ploidy = ifelse(sim_ploidy == traj_ploidy, 1, 0)) %>% select(sim_ploidy, Dom, TajD, FayWuH, ZengsE) %>% melt(., id.var = c("sim_ploidy", "Dom")) %>% mutate("PeakSize" = variable) %>% filter(value != 40.5) %>% ggplot(., aes(y = value / 10000, fill = as.factor(Dom), x = as.factor(sim_ploidy))) + geom_boxplot(outlier.shape = NA) + scale_fill_manual(name = "Dominance", values = wes_palette("Royal1")) + ylab("") + xlab("Ploidy") + facet_wrap(~PeakSize) +theme_bw() + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18), legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16))
+
+#With zeros
+ee %>% filter(dom %in% c(0.1, 0.5, 0.9) & traj_ploidy == sim_ploidy & s == "0.01" & recomb == "1e-08" & N=="10000" & driftGen == 0 & sampGen == 1) %>% mutate(Dom = factor(case_when(dom == 0.1 ~ "Partial Recessivity", dom == 0.5 ~ "Additivity", dom == 0.9 ~ "Partial Dominance"), levels = c("Partial Recessivity", "Additivity", "Partial Dominance")), "TajD" = height.taj * width.taj / 2, "FayWuH" = height.h * width.h / 2, "ZengsE" = height.e * width.e / 2, same_ploidy = ifelse(sim_ploidy == traj_ploidy, 1, 0)) %>% select(sim_ploidy, Dom, TajD, FayWuH, ZengsE) %>% melt(., id.var = c("sim_ploidy", "Dom")) %>% mutate("PeakSize" = variable) %>% filter(value != 40.5) %>% ggplot(., aes(y = value / 10000, fill = as.factor(Dom), x = as.factor(sim_ploidy))) + geom_boxplot(outlier.shape = NA) + scale_fill_manual(name = "Dominance", values = wes_palette("Royal1")) + ylab("") + xlab("Ploidy") + facet_wrap(~PeakSize) +theme_bw() + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18), legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16))
+
+# # ee %>% filter(dom %in% c(0.1, 0.5, 0.9) & traj_ploidy == sim_ploidy & s == "0.01" & recomb == "1e-08" & N=="10000" & driftGen == 0 & sampGen == 1) %>% mutate(Dom = factor(case_when(dom == 0.1 ~ "Partial Recessivity", dom == 0.5 ~ "Additivity", dom == 0.9 ~ "Partial Dominance"), levels = c("Partial Recessivity", "Additivity", "Partial Dominance")), "Magnitude" = height.taj, "Breadth" = width.taj / 10000, same_ploidy = ifelse(sim_ploidy == traj_ploidy, 1, 0)) %>% select(sim_ploidy, Dom, Magnitude, Breadth) %>% melt(., id.var = c("sim_ploidy", "Dom")) %>% mutate("TajD" = variable) %>% filter(value != -9) %>% ggplot(., aes(y = value, fill = as.factor(Dom), x = as.factor(sim_ploidy))) + geom_boxplot(outlier.shape = NA) + scale_fill_manual(name = "Dominance", values = wes_palette("Royal1")) + ylab("") + xlab("Ploidy") + facet_wrap(~TajD, labeller = label_both, scales = "free_y") +theme_bw() + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18), legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16))
+# # 
+# # ee %>% filter(dom %in% c(0.1, 0.5, 0.9) & traj_ploidy == sim_ploidy & s == "0.01" & fuseGen=="1" & recomb == "1e-08" & N=="10000" & driftGen == 0 & sampGen == 1) %>% mutate(Dom = factor(case_when(dom == 0.1 ~ "Partial Recessivity", dom == 0.5 ~ "Additivity", dom == 0.9 ~ "Partial Dominance"), levels = c("Partial Recessivity", "Additivity", "Partial Dominance")), "Magnitude" = height.h, "Breadth" = width.h / 10000, same_ploidy = ifelse(sim_ploidy == traj_ploidy, 1, 0)) %>% select(sim_ploidy, Dom, Magnitude, Breadth) %>% melt(., id.var = c("sim_ploidy", "Dom")) %>% mutate("FayWuH" = variable) %>% filter(value != -9) %>% ggplot(., aes(y = value, fill = as.factor(Dom), x = as.factor(sim_ploidy))) + geom_boxplot(outlier.shape = NA) + scale_fill_manual(name = "Dominance", values = wes_palette("Royal1")) + ylab("") + xlab("Ploidy") + facet_wrap(~FayWuH, labeller = label_both, scales = "free_y") +theme_bw() + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18), legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16))
+# 
+# 
+# ee %>% filter(dom %in% c(0.1, 0.5, 0.9) & traj_ploidy == sim_ploidy & s == "0.01" & recomb == "1e-08" & N=="10000" & driftGen == 0 & sampGen == 1) %>% mutate(Dom = factor(case_when(dom == 0.1 ~ "Partial Recessivity", dom == 0.5 ~ "Additivity", dom == 0.9 ~ "Partial Dominance"), levels = c("Partial Recessivity", "Additivity", "Partial Dominance")), "Magnitude" = height.e, "Breadth" = width.e / 10000, same_ploidy = ifelse(sim_ploidy == traj_ploidy, 1, 0)) %>% select(sim_ploidy, Dom, Magnitude, Breadth) %>% melt(., id.var = c("sim_ploidy", "Dom")) %>% mutate("ZengsE" = variable) %>% filter(value != -9) %>% ggplot(., aes(y = value, fill = as.factor(Dom), x = as.factor(sim_ploidy))) + geom_boxplot(outlier.shape = NA) + scale_fill_manual(name = "Dominance", values = wes_palette("Royal1")) + ylab("") + xlab("Ploidy") + facet_wrap(~ZengsE, labeller = label_both, scales = "free_y") +theme_bw() + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18), legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16))
+
+kk = merge(ee, ff, by = c("traj_ploidy", "sim_ploidy", "dom", "s", "N", "mu", "recomb", "sampGen", "fuseGen", "rep"))
+
+kk %>% filter(dom %in% c(0.1, 0.5, 0.9) & traj_ploidy == sim_ploidy & s == "0.01" & recomb == "1e-08" & N=="10000" & driftGen == 0 & sampGen == 1) %>% mutate(Dom = factor(case_when(dom == 0.1 ~ "Partial Recessivity", dom == 0.5 ~ "Additivity", dom == 0.9 ~ "Partial Dominance"), levels = c("Partial Recessivity", "Additivity", "Partial Dominance")), "Fst" = height.fst * width.fst / 2, "Dxy" = height.dxy * width.dxy / 2, "XPEHH" = height.xp * width.xp / 2, same_ploidy = ifelse(sim_ploidy == traj_ploidy, 1, 0)) %>% select(sim_ploidy, Dom, Fst, Dxy, XPEHH) %>% melt(., id.var = c("sim_ploidy", "Dom")) %>% mutate("PeakSize" = variable) %>% filter(value != -9) %>% ggplot(., aes(y = value / 10000, fill = as.factor(Dom), x = as.factor(sim_ploidy))) + geom_boxplot(outlier.shape = NA) + scale_fill_manual(name = "Dominance", values = wes_palette("Royal1")) + ylab("") + xlab("Ploidy") + facet_wrap(~PeakSize) +theme_bw() + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18), legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16))
+
+ee %>% filter(dom %in% c(0.1, 0.5, 0.9) & traj_ploidy == sim_ploidy & s == "0.01" & fuseGen=="1" & recomb == "1e-08" & N=="10000" & driftGen == 0 & sampGen == 1) %>% mutate(Dom = factor(case_when(dom == 0.1 ~ "Partial Recessivity", dom == 0.5 ~ "Additivity", dom == 0.9 ~ "Partial Dominance"), levels = c("Partial Recessivity", "Additivity", "Partial Dominance")), "Magnitude" = height.fst, "Breadth" = width.fst / 10000, same_ploidy = ifelse(sim_ploidy == traj_ploidy, 1, 0)) %>% select(sim_ploidy, Dom, Magnitude, Breadth) %>% melt(., id.var = c("sim_ploidy", "Dom")) %>% mutate("Fst" = variable) %>% filter(value != -9) %>% ggplot(., aes(y = value, fill = as.factor(Dom), x = as.factor(sim_ploidy))) + geom_boxplot(outlier.shape = NA) + scale_fill_manual(name = "Dominance", values = wes_palette("Royal1")) + ylab("") + xlab("Ploidy") + facet_wrap(~Fst, labeller = label_both, scales = "free_y") +theme_bw() + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18), legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16))
+
+ee %>% filter(dom %in% c(0.1, 0.5, 0.9) & traj_ploidy == sim_ploidy & s == "0.01" & fuseGen=="1" & recomb == "1e-08" & N=="10000" & driftGen == 0 & sampGen == 1) %>% mutate(Dom = factor(case_when(dom == 0.1 ~ "Partial Recessivity", dom == 0.5 ~ "Additivity", dom == 0.9 ~ "Partial Dominance"), levels = c("Partial Recessivity", "Additivity", "Partial Dominance")), "Magnitude" = height.dxy - med.dxy, "Breadth" = width.dxy / 10000, same_ploidy = ifelse(sim_ploidy == traj_ploidy, 1, 0)) %>% select(sim_ploidy, Dom, Magnitude, Breadth) %>% melt(., id.var = c("sim_ploidy", "Dom")) %>% mutate("Dxy" = variable) %>% filter(value != -9) %>% ggplot(., aes(y = value, fill = as.factor(Dom), x = as.factor(sim_ploidy))) + geom_boxplot(outlier.shape = NA) + scale_fill_manual(name = "Dominance", values = wes_palette("Royal1")) + ylab("") + xlab("Ploidy") + facet_wrap(~Dxy, labeller = label_both, scales = "free_y") +theme_bw() + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18), legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16))
 
 fact.ehh = read.csv("~/Documents/Research/PloidySim/rehh/rehh_calcs_do0.5_fG1_DS_fmted.csv") 
+dom.rehh = read.csv("~/Documents/Research/PloidySim/rehh/dom/rehh_dom.csv")
 
@@
 fact.ehh %>% filter(s == "0.01" & recomb == "re1e-08" & dom=="0.5" & N=="10000" & sampGen == "1") %>% ggplot(.,aes(x=POSITION / 100000, y=xpehh.p, color=sim_ploidy)) + geom_smooth(method="loess", span=0.1, se = F) + scale_color_discrete(name="Trajectory\nPloidy") + facet_grid(~sim_ploidy) + xlab("Position (100 kb)") + ylab(expression("-log"[10]*"(p-value)")) + theme_bw()
+
+ff = dom.rehh %>% filter(!is.na(xpehh.p) & sampGen!=1000) %>% mutate(mid = POSITION) %>% nest(-c(s, dom, recomb, N, mu, sim_ploidy, traj_ploidy, sampGen, fuseGen, rep)) %>% mutate(height.xp = map(data, ~getDims(., y.metric = "XPEHH")$height), width.xp = map(data, ~getDims(., y.metric = "XPEHH")$width), height.xp.p = map(data, ~getDims(., y.metric = "xpehh.p")$height), width.xp.p = map(data, ~getDims(., y.metric = "xpehh.p")$width)) %>% select(-data) %>% unnest()
+
+ff %>% filter(N == "NN10000" & s =="se0.01" & sampGen == "sG1") %>% select(sim_ploidy,  dom, height.xp, width.xp, height.xp.p, width.xp.p) %>% melt(., id.var = c("sim_ploidy", "dom")) %>% ggplot(., aes(y = value, fill = as.factor(dom), x = as.factor(sim_ploidy))) + geom_boxplot(outlier.shape = NA) + scale_fill_discrete(name = "Dominance") + facet_wrap(~variable, scales = "free_y") + ylab("") + xlab("") + theme_bw() + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18), legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16))
+
+ff %>% filter(N == "NN10000" & s =="se0.01" & sampGen == "sG1" & dom %in% c("do0.1", "do0.5", "do0.9") & recomb=="re1e-08" & mu == "mu1e-08") %>% mutate(Magnitude = height.xp, Breadth = width.xp / 10000) %>% select(sim_ploidy, dom, Magnitude, Breadth) %>% melt(., id.var = c("sim_ploidy", "dom")) %>% mutate(XPEHH = variable) %>% ggplot(., aes(y = value, fill = as.factor(dom), x = as.factor(sim_ploidy))) + geom_boxplot(outlier.shape = NA) + scale_fill_manual(name = "Dominance", breaks = c("do0.1", "do0.5", "do0.9"), labels = c("Partial Recessivity","Additivity", "Partial Dominance"), values = wes_palette("Royal1")) + facet_wrap(~XPEHH, scales = "free_y", labeller = label_both) + scale_x_discrete(breaks = c("sp2","sp4","sp8"), labels = c("2","4","8")) + ylab("") + xlab("") + theme_bw() + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18), legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16))
+
+#placehold
+# ff %<>% mutate(traj_ploidy = case_when(traj_ploidy == "tp2" ~ 2, traj_ploidy == "tp4" ~ 4, traj_ploidy == "tp8" ~ 8), sim_ploidy = case_when(sim_ploidy == "sp2" ~ 2, sim_ploidy == "sp4" ~ 4, sim_ploidy == "sp8" ~ 8), dom = case_when(dom == "do0.1" ~ 0.1, dom == "do0.5" ~ 0.5, dom == "do0.9" ~ 0.9), s = case_when(s == "se0.01" ~ 0.01, s == "se0.1" ~ 0.1, s == "se0.001" ~ 0.001), N = case_when(N == "NN1000" ~ 1000, N == "NN10000" ~ 10000), traj_ploidy = case_when(traj_ploidy == "tp2" ~ 2, traj_ploidy == "tp4" ~ 4, traj_ploidy == "tp8" ~ 8)
+
+ff %<>% mutate(traj_ploidy = as.numeric(str_replace(traj_ploidy, "tp","")), sim_ploidy = as.numeric(str_replace(sim_ploidy, "sp","")), dom = as.numeric(str_replace(dom, "do","")), s = as.numeric(str_replace(s, "se","")), N = as.numeric(str_replace(N, "NN","")), mu = as.numeric(str_replace(mu, "mu","")), recomb = as.numeric(str_replace(recomb, "re","")), sampGen = as.numeric(str_replace(sampGen, "sG","")), fuseGen = as.numeric(str_replace(fuseGen, "fG","")), rep = as.numeric(str_replace(rep, "rep", "")))
+
+gg = merge(dd, ff, by = c("traj_ploidy", "sim_ploidy", "dom", "s", "N", "mu", "recomb", "sampGen", "fuseGen", "rep"))
+
 ```
@@
 dat1 = foreach(i = 1:nrow(params), .combine=rbind) %do% {
-  getTraj(params[i,]$s, params[i,]$dom, params[i,]$ploidy, params[i,]$start)
+  getTraj(params[i,]$s, params[i,]$dom, params[i,]$ploidy, params[i,]$start, maxGens = 12000)
 }
 
-params2 = data.frame("s" = c(rep(0.01,3), rep(0.005,3)), "dom" = c(rep(0.5,6)), "ploidy" = rep(c(2,4,8),2), "start" = rep(0.05, 6))
+params2 = data.frame("s" = c(rep(c(rep(0.1,3), rep(0.05,3), rep(0.025,3)),2)), "dom" = c(rep(0.5,9), rep(0.9,9)), "ploidy" = rep(c(2,4,8),6), "start" = rep(0.05, 18))
 
@@
 
-dat1$dom = factor(dat1$dom, levels(dat1$dom)[c(3,2,1)])
+dat1$dom = factor(dat1$dom, levels(as.factor(dat1$dom))[c(3,2,1)])
 #plot
@@
 dat1 %>% filter(ploidy %in% c(2, 4, 8) & dom %in% c(0.1, 0.5, 0.9)) %>% 
-ggplot(., aes(x=gen, y=freq, linetype=as.factor(dom), color=as.factor(ploidy))) + geom_line() + scale_color_manual(name = "Ploidy", values = c("#F8766D", "#00BA38", "#619CFF")) + scale_linetype_manual(name = "Dominance", labels=c("Partial\nRecessivity\n", "Additivity", "Partial\nDominance")) + xlim(0,300) + theme_bw() + xlab("Generation") + ylab("Allele Frequency") + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18),axis.text.x=element_text(size=16),axis.title.x=element_text(size=18),legend.text = element_text(size=16), legend.title = element_text(size=18))
+ggplot(., aes(x=gen, y=freq, linetype=as.factor(dom), color=as.factor(ploidy))) + geom_line() + scale_color_manual(name = "Ploidy", values = wes_palette("Moonrise2")) + scale_linetype_manual(name = "Dominance", labels=c("Partial\nRecessivity\n", "Additivity", "Partial\nDominance")) + xlim(0,300) + theme_bw() + xlab("Generation") + ylab("Allele Frequency") + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18),axis.text.x=element_text(size=16),axis.title.x=element_text(size=18),legend.text = element_text(size=16), legend.title = element_text(size=18))
 
@@
 dat1 %>% filter(ploidy %in% c(2) & dom %in% c(0.5)) %>% 
-ggplot(., aes(x=gen, y=freq, linetype=as.factor(dom), color=as.factor(ploidy))) + geom_line() + scale_color_manual(name = "Ploidy", values = c("#F8766D", "#00BA38", "#619CFF")) + scale_linetype_manual(name = "Dominance", breaks = c("0.5"), labels = c("Additive"), values = c("solid")) + xlim(0,300) + theme_bw() + xlab("Generation") + ylab("Allele Frequency") + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18),axis.text.x=element_text(size=16),axis.title.x=element_text(size=18),legend.text = element_text(size=16), legend.title = element_text(size=18)) + guides(color = guide_legend(order=1), linetype = guide_legend(order=2))
+ggplot(., aes(x=gen, y=freq, linetype=as.factor(dom), color=as.factor(ploidy))) + geom_line() + scale_color_manual(name = "Ploidy", values = wes_palette("Moonrise2")) + scale_linetype_manual(name = "Dominance", breaks = c("0.5"), labels = c("Additive"), values = c("solid")) + xlim(0,300) + theme_bw() + xlab("Generation") + ylab("Allele Frequency") + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18),axis.text.x=element_text(size=16),axis.title.x=element_text(size=18),legend.text = element_text(size=16), legend.title = element_text(size=18)) + guides(color = guide_legend(order=1), linetype = guide_legend(order=2))
 
 dat1 %>% filter(ploidy %in% c(2, 4) & dom %in% c(0.5)) %>% 
-ggplot(., aes(x=gen, y=freq, linetype=as.factor(dom), color=as.factor(ploidy))) + geom_line() + scale_linetype_manual(name = "Dominance", breaks = c("0.5"), labels = c("Additive"), values = c("solid")) + scale_color_manual(name = "Ploidy", values = c("#F8766D", "#00BA38", "#619CFF")) + xlim(0,300) + theme_bw() + xlab("Generation") + ylab("Allele Frequency") + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18),axis.text.x=element_text(size=16),axis.title.x=element_text(size=18),legend.text = element_text(size=16), legend.title = element_text(size=18)) + guides(color = guide_legend(order=1), linetype = guide_legend(order=2))
+ggplot(., aes(x=gen, y=freq, linetype=as.factor(dom), color=as.factor(ploidy))) + geom_line() + scale_linetype_manual(name = "Dominance", breaks = c("0.5"), labels = c("Additive"), values = c("solid")) + scale_color_manual(name = "Ploidy", values = wes_palette("Moonrise2")) + xlim(0,300) + theme_bw() + xlab("Generation") + ylab("Allele Frequency") + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18),axis.text.x=element_text(size=16),axis.title.x=element_text(size=18),legend.text = element_text(size=16), legend.title = element_text(size=18)) + guides(color = guide_legend(order=1), linetype = guide_legend(order=2))
 
 dat1 %>% filter(ploidy %in% c(2, 4, 8) & dom %in% c(0.5)) %>% 
-ggplot(., aes(x=gen, y=freq, linetype=as.factor(dom), color=as.factor(ploidy))) + geom_line() + scale_linetype_manual(name = "Dominance", breaks = c("0.5"), labels = c("Additive"), values = c("solid")) + scale_color_manual(name = "Ploidy", values = c("#F8766D", "#00BA38", "#619CFF")) + xlim(0,300) + theme_bw() + xlab("Generation") + ylab("Allele Frequency") + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18),axis.text.x=element_text(size=16),axis.title.x=element_text(size=18),legend.text = element_text(size=16), legend.title = element_text(size=18)) + guides(color = guide_legend(order=1), linetype = guide_legend(order=2))
+ggplot(., aes(x=gen, y=freq, linetype=as.factor(dom), color=as.factor(ploidy))) + geom_line() + scale_linetype_manual(name = "Dominance", breaks = c("0.5"), labels = c("Additive"), values = c("solid")) + scale_color_manual(name = "Ploidy", values = wes_palette("Moonrise2")) + xlim(0,300) + theme_bw() + xlab("Generation") + ylab("Allele Frequency") + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18),axis.text.x=element_text(size=16),axis.title.x=element_text(size=18),legend.text = element_text(size=16), legend.title = element_text(size=18)) + guides(color = guide_legend(order=1), linetype = guide_legend(order=2))
 
@@
 dat1 %>% filter(ploidy %in% c(2) & dom %in% c(0.5, 0.9)) %>% 
-ggplot(., aes(x=gen, y=freq, linetype=as.factor(dom), color=as.factor(ploidy))) + geom_line() + scale_color_manual(name = "Ploidy", values = c("#F8766D", "#00BA38", "#619CFF")) + scale_linetype_manual(name = "Dominance", breaks = c("0.5", "0.9"), labels = c("Additive", "\nPartial\nDominance"), values = c("dashed","solid")) + xlim(0,300) + theme_bw() + xlab("Generation") + ylab("Allele Frequency") + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18),axis.text.x=element_text(size=16),axis.title.x=element_text(size=18),legend.text = element_text(size=16), legend.title = element_text(size=18)) + guides(color = guide_legend(order=1), linetype = guide_legend(order=2))
+ggplot(., aes(x=gen, y=freq, linetype=as.factor(dom), color=as.factor(ploidy))) + geom_line() + scale_color_manual(name = "Ploidy", values = wes_palette("Moonrise2")) + scale_linetype_manual(name = "Dominance", breaks = c("0.5", "0.9"), labels = c("Additive", "\nPartial\nDominance"), values = c("dashed","solid")) + xlim(0,300) + theme_bw() + xlab("Generation") + ylab("Allele Frequency") + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18),axis.text.x=element_text(size=16),axis.title.x=element_text(size=18),legend.text = element_text(size=16), legend.title = element_text(size=18)) + guides(color = guide_legend(order=1), linetype = guide_legend(order=2))
 
 dat1 %>% filter(ploidy %in% c(2, 4) & dom %in% c(0.5, 0.9)) %>% 
-ggplot(., aes(x=gen, y=freq, linetype=as.factor(dom), color=as.factor(ploidy))) + geom_line() + scale_linetype_manual(name = "Dominance", breaks = c("0.5", "0.9"), labels = c("Additive", "\nPartial\nDominance"), values = c("dashed","solid")) + scale_color_manual(name = "Ploidy", values = c("#F8766D", "#00BA38", "#619CFF")) + xlim(0,300) + theme_bw() + xlab("Generation") + ylab("Allele Frequency") + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18),axis.text.x=element_text(size=16),axis.title.x=element_text(size=18),legend.text = element_text(size=16), legend.title = element_text(size=18)) + guides(color = guide_legend(order=1), linetype = guide_legend(order=2))
+ggplot(., aes(x=gen, y=freq, linetype=as.factor(dom), color=as.factor(ploidy))) + geom_line() + scale_linetype_manual(name = "Dominance", breaks = c("0.5", "0.9"), labels = c("Additive", "\nPartial\nDominance"), values = c("dashed","solid")) + scale_color_manual(name = "Ploidy", values = wes_palette("Moonrise2")) + xlim(0,300) + theme_bw() + xlab("Generation") + ylab("Allele Frequency") + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18),axis.text.x=element_text(size=16),axis.title.x=element_text(size=18),legend.text = element_text(size=16), legend.title = element_text(size=18)) + guides(color = guide_legend(order=1), linetype = guide_legend(order=2))
 
 dat1 %>% filter(ploidy %in% c(2, 4, 8) & dom %in% c(0.5, 0.9)) %>% 
-ggplot(., aes(x=gen, y=freq, linetype=as.factor(dom), color=as.factor(ploidy))) + geom_line() + scale_linetype_manual(name = "Dominance", breaks = c("0.5", "0.9"), labels = c("Additive", "\nPartial\nDominance"), values = c("dashed","solid")) + scale_color_manual(name = "Ploidy", values = c("#F8766D", "#00BA38", "#619CFF")) + xlim(0,300) + theme_bw() + xlab("Generation") + ylab("Allele Frequency") + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18),axis.text.x=element_text(size=16),axis.title.x=element_text(size=18),legend.text = element_text(size=16), legend.title = element_text(size=18)) + guides(color = guide_legend(order=1), linetype = guide_legend(order=2))
+ggplot(., aes(x=gen, y=freq, linetype=as.factor(dom), color=as.factor(ploidy))) + geom_line() + scale_linetype_manual(name = "Dominance", breaks = c("0.5", "0.9"), labels = c("Additive", "\nPartial\nDominance"), values = c("dashed","solid")) + scale_color_manual(name = "Ploidy", values = wes_palette("Moonrise2")) + xlim(0,300) + theme_bw() + xlab("Generation") + ylab("Allele Frequency") + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18),axis.text.x=element_text(size=16),axis.title.x=element_text(size=18),legend.text = element_text(size=16), legend.title = element_text(size=18)) + guides(color = guide_legend(order=1), linetype = guide_legend(order=2))
 
 # All Series
-dat1 %>% filter(ploidy %in% c(2) & dom %in% c(0.5, 0.9, 0.1)) %>% 
-ggplot(., aes(x=gen, y=freq, linetype=as.factor(dom), color=as.factor(ploidy))) + geom_line() + scale_color_manual(name = "Ploidy", values = c("#F8766D", "#00BA38", "#619CFF")) + scale_linetype_manual(name = "Dominance", breaks = c("0.1", "0.5", "0.9"), labels = c("Partial\nRecessivity\n", "Additive", "\nPartial\nDominance"), values = c("dashed", "solid","dotdash")) + xlim(0,300) + theme_bw() + xlab("Generation") + ylab("Allele Frequency") + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18),axis.text.x=element_text(size=16),axis.title.x=element_text(size=18),legend.text = element_text(size=16), legend.title = element_text(size=18)) + guides(color = guide_legend(order=1), linetype = guide_legend(order=2))
+dat1 %>% filter(ploidy %in% c(2) & dom %in% c(0.5, 0.9, 0.1)) %>% ggplot(., aes(x=gen, y=freq, linetype=as.factor(dom), color=as.factor(ploidy))) + geom_line(size = 1) + scale_color_manual(name = "Ploidy", values = c("#F8766D", "#00BA38", "#619CFF")) + scale_linetype_manual(name = "Dominance", breaks = c("0.9", "0.5", "0.1"), labels = c("Partial\nDominance\n", "Additive", "\nPartial\nRecessivity"), values = c("dotted", "solid","dashed")) + xlim(0,300) + theme_bw() + xlab("Generation") + ylab("Allele Frequency") + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18),axis.text.x=element_text(size=16),axis.title.x=element_text(size=18),legend.text = element_text(size=16), legend.title = element_text(size=18)) + guides(color = guide_legend(order=1), linetype = guide_legend(order=2))
 
-dat1 %>% filter(ploidy %in% c(2, 4) & dom %in% c(0.5, 0.9, 0.1)) %>% 
-ggplot(., aes(x=gen, y=freq, linetype=as.factor(dom), color=as.factor(ploidy))) + geom_line() + scale_linetype_manual(name = "Dominance", breaks = c("0.1", "0.5", "0.9"), labels = c("Partial\nRecessivity\n", "Additive", "\nPartial\nDominance"), values = c("dashed", "solid","dotdash")) + scale_color_manual(name = "Ploidy", values = c("#F8766D", "#00BA38", "#619CFF")) + xlim(0,300) + theme_bw() + xlab("Generation") + ylab("Allele Frequency") + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18),axis.text.x=element_text(size=16),axis.title.x=element_text(size=18),legend.text = element_text(size=16), legend.title = element_text(size=18)) + guides(color = guide_legend(order=1), linetype = guide_legend(order=2))
+dat1 %>% filter(ploidy %in% c(2, 4, 8) & dom %in% c(0.9, 0.1) & mod(gen,10)==0) %>%
 
-dat1 %>% filter(ploidy %in% c(2, 4, 8) & dom %in% c(0.5, 0.9, 0.1)) %>% 
-ggplot(., aes(x=gen, y=freq, linetype=as.factor(dom), color=as.factor(ploidy))) + geom_line() + scale_linetype_manual(name = "Dominance", breaks = c("0.1", "0.5", "0.9"), labels = c("Partial\nRecessivity\n", "Additive", "\nPartial\nDominance"), values = c("dashed", "solid","dotdash")) + scale_color_manual(name = "Ploidy", values = c("#F8766D", "#00BA38", "#619CFF")) + xlim(0,300) + theme_bw() + xlab("Generation") + ylab("Allele Frequency") + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18),axis.text.x=element_text(size=16),axis.title.x=element_text(size=18),legend.text = element_text(size=16), legend.title = element_text(size=18)) + guides(color = guide_legend(order=1), linetype = guide_legend(order=2))
 ```
@@
 ```
+
+```{r}
+
+ee %>% filter(sampGen == "1" & s == "0.01" & fuseGen=="1" & recomb == "5e-08" & dom=="0.5" & N=="10000" & driftGen == 0 & width.fst < 60000) %>% mutate("Magnitude" = height.fst, "Breadth" = width.fst / 10000, same_ploidy = ifelse(sim_ploidy == traj_ploidy, 1, 0)) %>% select(sim_ploidy, traj_ploidy, same_ploidy, Magnitude, Breadth) %>% melt(., id.var = c("sim_ploidy", "traj_ploidy", "same_ploidy")) %>% mutate("Fst" = variable) %>% filter(value != -9) %>% ggplot(., aes(y = value, fill = as.factor(traj_ploidy), x = as.factor(sim_ploidy), color = as.factor(same_ploidy))) + geom_boxplot(outlier.shape = NA) + scale_fill_manual(name = "Trajectory Ploidy", labels = c("2", "4", "8"), values = wes_palette("Moonrise2")) + scale_color_manual(guide=F, values = c("black","red")) + facet_wrap(~Fst, scales = "free_y", labeller = label_both) + ylab("") + xlab("Coalescent Ploidy") + theme_bw() + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18), legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16))
+
+ee %>% filter(sampGen == "1" & s == "0.01" & fuseGen=="1" & recomb == "5e-08" & dom=="0.5" & N=="10000" & driftGen == 0 & width.taj < 100000) %>% mutate("Magnitude" = height.taj, "Breadth" = width.taj / 10000, same_ploidy = ifelse(sim_ploidy == traj_ploidy, 1, 0)) %>% select(sim_ploidy, traj_ploidy, same_ploidy, Magnitude, Breadth) %>% melt(., id.var = c("sim_ploidy", "traj_ploidy", "same_ploidy")) %>% mutate("TajD" = variable) %>% filter(value != -9) %>% ggplot(., aes(y = value, fill = as.factor(traj_ploidy), x = as.factor(sim_ploidy), color = as.factor(same_ploidy))) + geom_boxplot(outlier.shape = NA) + scale_fill_manual(name = "Trajectory Ploidy", labels = c("2", "4", "8"), values = wes_palette("Moonrise2")) + scale_color_manual(guide=F, values = c("black","red")) + facet_wrap(~TajD, scales = "free_y", labeller = label_both) + ylab("") + xlab("Coalescent Ploidy") + theme_bw() + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18), legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16))
+
+ee %>% filter(sampGen == "1" & s == "0.01" & fuseGen=="1" & recomb == "5e-08" & dom=="0.5" & N=="10000" & driftGen == 0) %>% mutate("Magnitude" = height.h, "Breadth" = width.h / 10000, same_ploidy = ifelse(sim_ploidy == traj_ploidy, 1, 0)) %>% select(sim_ploidy, traj_ploidy, same_ploidy, Magnitude, Breadth) %>% melt(., id.var = c("sim_ploidy", "traj_ploidy", "same_ploidy")) %>% mutate("Fay & Wu's H" = variable) %>% filter(value != -9) %>% ggplot(., aes(y = value, fill = as.factor(traj_ploidy), x = as.factor(sim_ploidy), color = as.factor(same_ploidy))) + geom_boxplot(outlier.shape = NA) + scale_fill_manual(name = "Trajectory Ploidy", labels = c("2", "4", "8"), values = wes_palette("Moonrise2")) + scale_color_manual(guide=F, values = c("black","red")) + facet_wrap(~`Fay & Wu's H`, scales = "free_y", labeller = label_both) + ylab("") + xlab("Coalescent Ploidy") + theme_bw() + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18), legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16))
+
+ee %>% filter(sampGen == "1" & s == "0.01" & fuseGen=="1" & recomb == "5e-08" & dom=="0.5" & N=="10000" & driftGen == 0) %>% mutate("Magnitude" = height.e, "Breadth" = width.e / 10000, same_ploidy = ifelse(sim_ploidy == traj_ploidy, 1, 0)) %>% select(sim_ploidy, traj_ploidy, same_ploidy, Magnitude, Breadth) %>% melt(., id.var = c("sim_ploidy", "traj_ploidy", "same_ploidy")) %>% mutate("Zeng's E" = variable) %>% filter(value != -9) %>% ggplot(., aes(y = value, fill = as.factor(traj_ploidy), x = as.factor(sim_ploidy), color = as.factor(same_ploidy))) + geom_boxplot(outlier.shape = NA) + scale_fill_manual(name = "Trajectory Ploidy", labels = c("2", "4", "8"), values = wes_palette("Moonrise2")) + scale_color_manual(guide=F, values = c("black","red")) + facet_wrap(~`Zeng's E`, scales = "free_y", labeller = label_both) + ylab("") + xlab("Coalescent Ploidy") + theme_bw() + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18), legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16))
+
+ee %>% filter(sampGen == "10000" & s == "0.01" & fuseGen=="1" & recomb == "5e-08" & dom=="0.5" & N=="10000" & driftGen == 0 & width.fst < 60000) %>% mutate("Magnitude" = height.fst, "Breadth" = width.fst / 10000, same_ploidy = ifelse(sim_ploidy == traj_ploidy, 1, 0)) %>% select(sim_ploidy, traj_ploidy, same_ploidy, Magnitude, Breadth) %>% melt(., id.var = c("sim_ploidy", "traj_ploidy", "same_ploidy")) %>% mutate("Fst" = variable) %>% filter(value != -9) %>% ggplot(., aes(y = value, fill = as.factor(traj_ploidy), x = as.factor(sim_ploidy), color = as.factor(same_ploidy))) + geom_boxplot(outlier.shape = NA) + scale_fill_manual(name = "Trajectory Ploidy", labels = c("2", "4", "8"), values = wes_palette("Moonrise2")) + scale_color_manual(guide=F, values = c("black","red")) + facet_wrap(~Fst, scales = "free_y", labeller = label_both) + ylab("") + xlab("Coalescent Ploidy") + theme_bw() + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18), legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16))
+
+ee %>% filter(sampGen == "10000" & s == "0.01" & fuseGen=="1" & recomb == "5e-08" & dom=="0.5" & N=="10000" & driftGen == 0 & width.taj < 100000) %>% mutate("Magnitude" = height.taj, "Breadth" = width.taj / 10000, same_ploidy = ifelse(sim_ploidy == traj_ploidy, 1, 0)) %>% select(sim_ploidy, traj_ploidy, same_ploidy, Magnitude, Breadth) %>% melt(., id.var = c("sim_ploidy", "traj_ploidy", "same_ploidy")) %>% mutate("TajD" = variable) %>% filter(value != -9) %>% ggplot(., aes(y = value, fill = as.factor(traj_ploidy), x = as.factor(sim_ploidy), color = as.factor(same_ploidy))) + geom_boxplot(outlier.shape = NA) + scale_fill_manual(name = "Trajectory Ploidy", labels = c("2", "4", "8"), values = wes_palette("Moonrise2")) + scale_color_manual(guide=F, values = c("black","red")) + facet_wrap(~TajD, scales = "free_y", labeller = label_both) + ylab("") + xlab("Coalescent Ploidy") + theme_bw() + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18), legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16))
+
+#Sample Generation
+ee %>% filter(traj_ploidy == sim_ploidy & s == "0.01" & recomb == "1e-08" & N=="10000" & driftGen == 0)  %>% mutate("Magnitude" = height.taj, "Breadth" = width.taj / 10000, same_ploidy = ifelse(sim_ploidy == traj_ploidy, 1, 0)) %>% select(sim_ploidy, sampGen, Magnitude, Breadth) %>% melt(., id.var = c("sim_ploidy", "sampGen")) %>% mutate("TajD" = variable) %>% filter(value != -9) %>% ggplot(., aes(y = value, fill = as.factor(sampGen), x = as.factor(sim_ploidy))) + geom_boxplot(outlier.shape = NA) + scale_fill_manual(name = "Generations since\nFixation", values = wes_palette("Royal2")) + ylab("") + xlab("Coalescent Ploidy") + facet_wrap(~TajD, labeller = label_both, scales = "free_y") +theme_bw() + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18), legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16))
+
+ee %>% filter(traj_ploidy == sim_ploidy & s == "0.01" & recomb == "1e-08" & N=="10000" & driftGen == 0)  %>% mutate("Magnitude" = height.fst, "Breadth" = width.fst / 10000, same_ploidy = ifelse(sim_ploidy == traj_ploidy, 1, 0)) %>% select(sim_ploidy, sampGen, Magnitude, Breadth) %>% melt(., id.var = c("sim_ploidy", "sampGen")) %>% mutate("Fst" = variable) %>% filter(value != -9) %>% ggplot(., aes(y = value, fill = as.factor(sampGen), x = as.factor(sim_ploidy))) + geom_boxplot(outlier.shape = NA) + scale_fill_manual(name = "Generations since\nFixation", values = wes_palette("Royal2")) + ylab("") + xlab("Coalescent Ploidy") + facet_wrap(~Fst, labeller = label_both, scales = "free_y") +theme_bw() + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18), legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16))
+
+ee %>% filter(traj_ploidy == sim_ploidy & s == "0.01" & recomb == "1e-08" & N=="10000" & driftGen == 0)  %>% mutate("Magnitude" = height.h, "Breadth" = width.h / 10000, same_ploidy = ifelse(sim_ploidy == traj_ploidy, 1, 0)) %>% select(sim_ploidy, sampGen, Magnitude, Breadth) %>% melt(., id.var = c("sim_ploidy", "sampGen")) %>% mutate("Fay & Wu's H" = variable) %>% filter(value != -9) %>% ggplot(., aes(y = value, fill = as.factor(sampGen), x = as.factor(sim_ploidy))) + geom_boxplot(outlier.shape = NA) + scale_fill_manual(name = "Generations since\nFixation", values = wes_palette("Royal2")) + ylab("") + xlab("Coalescent Ploidy") + facet_wrap(~`Fay & Wu's H`, labeller = label_both, scales = "free_y") +theme_bw() + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18), legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16))
+
+ee %>% filter(traj_ploidy == sim_ploidy & s == "0.01" & fuseGen=="1" & recomb == "5e-08" & dom=="0.5" & N=="10000" & driftGen == 0) %>% mutate("Magnitude" = height.e, "Breadth" = width.e / 10000, same_ploidy = ifelse(sim_ploidy == traj_ploidy, 1, 0)) %>% select(sim_ploidy, sampGen, Magnitude, Breadth) %>% melt(., id.var = c("sim_ploidy", "sampGen")) %>% mutate("Zeng's E" = variable) %>% filter(value != -9) %>% ggplot(., aes(y = value, fill = as.factor(sampGen), x = as.factor(sim_ploidy))) + geom_boxplot(outlier.shape = NA) + scale_fill_manual(name = "Generations since\nFixation", values = wes_palette("Royal2")) + ylab("") + xlab("Coalescent Ploidy") + facet_wrap(~`Zeng's E`, labeller = label_both, scales = "free_y") +theme_bw() + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18), legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16))
+```

### 2019-07-18 analysis/mssel_analysis.Rmd
about to do some major reorganization

@@
 library(purrr)
+library(IDPmisc)
 
@@
 ms = rbind(ms, ms3)
+
+ms4 = read.table("~/Documents/Research/PloidySim/data/mssel_d3_moreReps.txt", head = T)
+ms4 %<>% mutate(rep = rep + 20)
+ms4 %<>% mutate(ints = as.numeric(as.character(cut(bp.start, breaks = 50, labels = seq(1,50)))))
+
+ms = rbind(ms, ms4)
+
+ms4 = read.table("~/Documents/Research/PloidySim/data/mssel_d2_moreReps.txt", head = T)
+ms4 %<>% mutate(rep = rep + 40)
+ms4 %<>% mutate(ints = as.numeric(as.character(cut(bp.start, breaks = 50, labels = seq(1,50)))))
+ms = rbind(ms, ms4)
 
@@
 mDoms %>% filter(variable %in% c("0.1", "0.5", "0.9")) %>% ggplot(., aes(x = i.k, y = value, linetype = variable)) + geom_line() + scale_linetype_manual(name = "Dominance", breaks = c("0.1", "0.5", "0.9"), labels = c("Partial\nRecessivity\n", "Additive\n", "Partial\nDominance"), values = c("dashed", "solid","dotdash")) + theme_bw() + xlab("Individual allele frequency of beneficial allele") + ylab("Dominance Coefficient") + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18),axis.text.x=element_text(size=16),axis.title.x=element_text(size=18),legend.text = element_text(size=16), legend.title = element_text(size=18))
+
+mDoms %>% filter(variable %in% c("0.9", "0.6", "0.5", "0.4", "0.1")) %>% ggplot(., aes(x = i.k, y = value, color = variable)) + geom_line(size = 1.2) + scale_color_discrete(name = "Dominance\nScalar", breaks = c("0.9", "0.6", "0.5", "0.4", "0.1"), labels = c("0.4", "0.1", "0", "-0.1", "-0.4")) + theme_bw() + xlab("Individual allele frequency of beneficial allele") + ylab("Dominance Coefficient") + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18),axis.text.x=element_text(size=16),axis.title.x=element_text(size=18),legend.text = element_text(size=16), legend.title = element_text(size=18))
 # Example
@@
 # Param set to create trajectories for
-params = data.frame("s" = rep(0.1,9), "dom" = c(rep(0.5,3), rep(0.1,3), rep(0.9,3)), "ploidy" = rep(c(2,4,8),3), "start" = rep(0.05, 9))
+params = data.frame("s" = rep(0.1,9), "dom" = c(rep(1,3), rep(0.5,3), rep(0,3)), "ploidy" = rep(c(2,4,8),3), "start" = rep(0.05, 9))
 
@@
 
+dat1$dom = as.factor(dat1$dom)
 dat1$dom = factor(dat1$dom, levels(dat1$dom)[c(3,2,1)])
+
 #plot
@@
 
+dat1 %>% filter(ploidy %in% c(2, 4, 8) & dom %in% c(1, 0.5, 0)) %>% 
+ggplot(., aes(x=gen, y=freq, linetype=as.factor(dom), color=as.factor(ploidy))) + geom_line() + scale_color_manual(name = "Ploidy", values = c("#F8766D", "#00BA38", "#619CFF")) + scale_linetype_manual(name = "Dominance", labels=c("Dominant", "Additive", "Recessive")) + xlim(0,300) + theme_bw() + xlab("Generation") + ylab("Allele Frequency") + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18),axis.text.x=element_text(size=16),axis.title.x=element_text(size=18),legend.text = element_text(size=16), legend.title = element_text(size=18))
 ```
@@
 
-ggplot(dat2, aes(x=freq, y=var.w, color = as.factor(ploidy), linetype=as.factor(dom))) + geom_line() + scale_color_discrete(name="Ploidy") + scale_linetype_discrete(name="Dominance", labels=c("0.1","0.5","0.9")) + xlab("Allele Frequency") + ylab("Variance in Fitness") + theme_bw()
+dat2$dom = as.factor(dat2$dom)
+dat2$dom = factor(dat2$dom, levels(dat2$dom)[c(3,2,1)])
+
+#Figure 1 right
+ggplot(dat2, aes(x=freq, y=var.w, color = as.factor(ploidy), linetype=as.factor(dom))) + geom_line(size = 0.9) + scale_color_discrete(name="Ploidy") + scale_linetype_manual(name="Dominance", labels=c("Dominant","Additive","Recessive"), values = c("dashed", "solid", "dotted")) + xlab("Allele Frequency") + ylab("Variance in Fitness\n") + theme_bw() + theme(axis.text.y=element_blank(), axis.title.y=element_text(size=18),axis.text.x=element_text(size=16),axis.title.x=element_text(size=18),legend.text = element_text(size=16), legend.title = element_text(size=18))
 
@@
 ```{r, echo=T,message=F}
-MS2.a = ms %>% group_by(s, dom, recomb, N, mu, sim_ploidy, traj_ploidy, sampGen, fuseGen, rep, driftGen) %>% summarize(depth = (mean(Pi.2,na.rm=T) - (mean(Pi.2,na.rm=T) - min(Pi.1))) / mean(Pi.2,na.rm=T), min = min(Pi.1, na.rm=T))
+MS2.a = ms %>% group_by(s, dom, recomb, N, mu, sim_ploidy, traj_ploidy, sampGen, fuseGen, rep, driftGen) %>% summarize(depth.pi = mean(Pi.2,na.rm=T) - min(Pi.1), min.pi = min(Pi.1, na.rm=T), max.taj = abs(min(Tajima.D_1, na.rm = T)), height.fst = max(fst, na.rm = T) - mean(fst, na.rm = T))
 
-MS2.a %>% filter(fuseGen == 1 & mu==1e-08 & N == 10000 & recomb=="1e-08" & s =="0.01") %>% ggplot(., aes(y=-(log(depth)), fill = as.factor(traj_ploidy), x = as.factor(sim_ploidy))) + geom_boxplot() + ylab(expression(paste("Dip Depth = [", bar(pi[2])," - (", bar(pi[2]), " - min(", pi[1], ")] / ", bar(pi[2]),sep = ""))) + facet_grid(rows= vars(sampGen), cols = vars(driftGen)) + scale_y_log10() + scale_fill_discrete(name = "Trajectory\nPloidy") + xlab("Simulation Ploidy") + theme_bw()
+MS2.b = ms %>% group_by(s, dom, recomb, N, mu, sim_ploidy, traj_ploidy, sampGen, fuseGen, driftGen, rep, ints) %>% summarize(lessWind.pi = ifelse(mean(Pi.1, na.rm=T) < (mean(Pi.2, na.rm=T) / 2),1,0), lessWind.taj = ifelse(mean(Tajima.D_1, na.rm=T) < -1, 1, 0))
 
-MS2.a %>% filter(fuseGen == 1 & mu==1e-08 & N == 10000 & recomb=="1e-08" & s =="0.01") %>% ggplot(., aes(y=-(log(min)), fill = as.factor(traj_ploidy), x = as.factor(sim_ploidy))) + geom_boxplot() + ylab(expression(paste("Dip Depth = [", bar(pi[2])," - (", bar(pi[2]), " - min(", pi[1], ")] / ", bar(pi[2]),sep = ""))) + facet_grid(rows= vars(sampGen), cols = vars(driftGen)) + scale_y_log10() + scale_fill_discrete(name = "Trajectory\nPloidy") + xlab("Simulation Ploidy") + theme_bw()
+MS2.c = MS2.b %>% group_by(s, dom, recomb, N, mu, sim_ploidy, traj_ploidy, sampGen, fuseGen, driftGen, rep) %>% summarize(breadth.pi = sum(lessWind.pi) * 20000, breadth.taj = sum(lessWind.taj) * 20000)
+
+MS2.f = merge(MS2.a, MS2.c, by = c("s", "dom", "recomb", "N", "mu", "sim_ploidy", "traj_ploidy", "sampGen", "fuseGen", "driftGen", "rep"))
+
+MS2.f %<>% mutate(same_ploidy = ifelse(sim_ploidy==traj_ploidy, "yellow", "black"))
+
+MS2.f %>% filter(sim_ploidy == traj_ploidy & mu==1e-08 & N == 10000 & s =="0.01" & driftGen %in% c(0,1) & sampGen == 1 & dom %in% c(0.1, 0.5, 0.9)) %>% mutate(Dom = factor(case_when(dom == 0.1 ~ "Partial Recessivity", dom == 0.5 ~ "Additivity", dom == 0.9 ~ "Partial Dominance"), levels = c("Partial Recessivity", "Additivity", "Partial Dominance")), Height = (log(min.pi, 10)), Breadth = breadth.pi/10000, Magnitude = depth.pi, Size = breadth.pi * depth.pi) %>% select(Dom, traj_ploidy, Magnitude, Breadth, Size) %>% melt(., id.var = c("Dom", "traj_ploidy")) %>% ggplot(., aes(y = value, fill = as.factor(Dom), x = as.factor(traj_ploidy))) + geom_boxplot(outlier.shape = NA) + scale_fill_manual(name = "Dominance", values=wes_palette("Royal1")) + facet_wrap(~variable, scales = "free_y") + ylab("") + xlab("Ploidy") + theme_bw() + theme(axis.text.y=element_text(size = 16), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18),legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16))
+
+#disentangling
+MS2.f %>% filter(mu==1e-08 & N == 10000 & s =="0.01" & driftGen %in% c(0,1) & sampGen == 1 & dom %in% c(0.5)) %>% mutate(Height = (log(min.pi, 10)), Breadth = breadth.pi/10000, Magnitude = depth.pi) %>% select(sim_ploidy, traj_ploidy, Magnitude, Breadth, same_ploidy) %>% melt(., id.var = c("sim_ploidy", "traj_ploidy", "same_ploidy")) %>% ggplot(., aes(y = value, fill = as.factor(traj_ploidy), x = as.factor(sim_ploidy), color = same_ploidy)) + geom_boxplot(outlier.shape = NA) + scale_fill_manual(name = "Trajectory Ploidy", values = wes_palette("Moonrise2")) + scale_color_manual(guide=F, values = c("black", "red")) + facet_wrap(~variable, scales = "free_y") + ylab("") + xlab("\n\n") + theme_bw() + theme(axis.text.y=element_text(size = 16), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18), legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16))
+
+# New functions to summarize breadth/depth
+# getDims = function(dat, y.metric = "fst", offset = 100000){
+#   # dat = data.frame("mid" = mid, "fst" = febugst)
+#   peak = tryCatch({
+#     peaks(dat$mid, abs(dat[,y.metric])) %>% filter(x > 500000 - offset & x < 500000 + offset & w > 0) %>% filter(w == max(w)) %>% summarize(height = max(y), width = max(w))}
+#     , error = function(e){
+#       return(data.frame("height" = -9, "width" = -9))
+#     })
+#   return(peak$height * peak$width)
+# }
+
+getDims = function(dat, y.metric = "fst", offset = 100000){
+  # dat = data.frame("mid" = mid, "fst" = febugst)
+  peak = tryCatch({
+    auc(dat$mid, unlist(abs(dat[,y.metric])), from = 500000 - offset, to = 500000 + offset)}
+    , error = function(e){
+      return(-9)
+    })
+  return(peak)
+}
+
+getUnd = function(dat, y.metric = "fst", offset = 100000){
+  # dat = data.frame("mid" = mid, "fst" = febugst)
+  dat = dat %>% filter(mid > 500000 - offset & mid < 500000 + offset)
+  dat["stat"] = dat[, y.metric]
+  val = nrow(dat[dat$stat == "-Inf",])
+  return(val)
+}
+
+ms %>% filter(sampGen==1 & driftGen == 0 & fuseGen %in% c(1,1000,10000) & dom %in% c(0.1, 0.5, 0.9)) %>% group_by(s, dom, recomb, N, mu, sim_ploidy, traj_ploidy, sampGen, fuseGen, rep, driftGen) %>% mutate(Div = mean(Pi.2) - Pi.1, Tajima.D_1 = abs(Tajima.D_1)) %>% ungroup() %>% nest(-c(s, dom, recomb, N, mu, sim_ploidy, traj_ploidy, sampGen, fuseGen, rep, driftGen)) %>% mutate(und.taj = map(data, ~getUnd(., y.metric = "Tajima.D_1")), und.h = map(data, ~getUnd(., y.metric = "Fay.Wu.H_1")), und.e = map(data, ~getUnd(., y.metric = "Zeng.E_1"))) %>% select(-data) %>% unnest() %>% group_by(s, dom, recomb, N, sim_ploidy) %>% summarize(n = n(), unds.d = sum(und.taj), unds.h = sum(und.h), unds.e = sum(und.e))
+
+getStat = function(dat, stat, offset = 25000){
+  dat = dat %>% filter(mid > 500000 - offset & mid < 500000 + offset)
+  val = max(abs(unlist(dat[,stat])), na.rm = T)
+  return(val)
+  }
+
+dd = ms %>% filter(sim_ploidy == traj_ploidy & fuseGen==1 & s == "0.01" & recomb == "1e-08" & N=="10000" & driftGen == 0 & sampGen %in% c(1,1000,10000)) %>% nest(-c(s, dom, recomb, N, mu, sim_ploidy, traj_ploidy, sampGen, fuseGen, rep, driftGen)) %>% mutate(size.taj = map(data, ~getDims(., y.metric = "Tajima.D_1")), size.h = map(data, ~getDims(., y.metric = "Fay.Wu.H_1")), size.e = map(data, ~getDims(., y.metric = "Zeng.E_1")), size.fst = map(data, ~getDims(., y.metric = "fst")), size.dxy = map(data, ~getDims(., y.metric = "dxy.1.2")), med.d = map(data, ~getStat(., "Tajima.D_1")), med.e = map(data, ~getStat(., "Zeng.E_1")), med.h = map(data, ~getStat(., "Fay.Wu.H_1")), med.fst = map(data, ~getStat(., "fst")), med.dxy = map(data, ~getStat(., "dxy.1.2"))) %>% select(-data) %>% unnest()
+
+dd.points = dd %>% filter(dom %in% c("0.1", "0.9") & traj_ploidy == sim_ploidy & s == "0.01" & recomb == "1e-08" & N=="10000" & driftGen == 0)  %>% mutate("TajD" = size.taj, "FayWuH" = size.h, "ZengsE" = size.e) %>% select(sim_ploidy, dom, sampGen, TajD, FayWuH, ZengsE) %>% melt(., id.var = c("sim_ploidy", "sampGen", "dom")) %>% mutate("Area" = variable) %>% filter(value != 40.5) %>% group_by(sim_ploidy, sampGen, dom, variable) %>% summarize(median = median(value)) %>% mutate(Magnitude = variable)
+
+#sampGen effect
+# Peak Size
+dd %>% filter(dom == 0.5 & traj_ploidy == sim_ploidy & s == "0.01" & N=="10000" & driftGen == 0)  %>% mutate("TajD" = size.taj, "FayWuH" = size.h, "ZengsE" = size.e) %>% select(sim_ploidy, sampGen, TajD, FayWuH, ZengsE) %>% melt(., id.var = c("sim_ploidy", "sampGen")) %>% mutate("Magnitude" = variable) %>% filter(value != 40.5) %>% ggplot(., aes(y = value / 10000, fill = as.factor(sampGen), x = as.factor(sim_ploidy))) + geom_boxplot(outlier.shape = NA) + geom_point(data = dd.points, aes(x = as.factor(sim_ploidy), y = median / 10000, group = sampGen, shape = as.factor(dom)), position = position_dodge(width = 0.85)) + scale_fill_manual(name = "Generations\nsince Fixation", values = wes_palette("Royal2")) + ylab("Peak Area") + xlab("Ploidy") + facet_wrap(~Magnitude) + theme_bw() + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18), legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16))
+
+#Just magnitude
+dd %>% filter(dom == 0.5 & traj_ploidy == sim_ploidy & s == "0.01" & N=="10000" & driftGen == 0 & recomb == 1e-08 & sampGen != 1)  %>% mutate("TajD" = med.d, "FayWuH" = med.h, "ZengsE" = med.e) %>% select(sim_ploidy, sampGen, TajD, ZengsE) %>% melt(., id.var = c("sim_ploidy", "sampGen")) %>% mutate("Magnitude" = variable) %>% filter(value != 40.5) %>% ggplot(., aes(y = value, fill = as.factor(sampGen), x = as.factor(sim_ploidy))) + geom_boxplot(outlier.shape = NA) + scale_fill_manual(name = "Generations\nsince Fixation", values = wes_palette("Royal2")) + ylim(0,2) + ylab("Magnitude") + xlab("Ploidy") + facet_wrap(~Magnitude) + theme_bw() + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18), legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16))
+
+#Combined sample gen figures
+kkk = merge(dd, ff, by = c("traj_ploidy", "sim_ploidy", "dom", "s", "N", "mu", "recomb", "sampGen", "fuseGen", "rep"), all.x = T)
+
+kkk.1 = kkk %>% filter(dom == 0.5 & traj_ploidy == sim_ploidy & s == "0.01" & N=="10000" & driftGen == 0 & recomb == 1e-08)  %>% mutate("TajD" = med.d, "FayWuH" = med.h, "ZengsE" = med.e, "Fst" = med.fst, "Dxy" = med.dxy, "XPEHH" = med.xp, "Rsb" = med.rsb) %>% select(sim_ploidy, sampGen, TajD, ZengsE, FayWuH, Fst, Dxy, XPEHH, Rsb) %>% melt(., id.var = c("sim_ploidy", "sampGen")) %>% mutate(stat = "MaxValue")
+
+kkk.2 = kkk %>% filter(dom == 0.5 & traj_ploidy == sim_ploidy & s == "0.01" & N=="10000" & driftGen == 0 & recomb == 1e-08)  %>% mutate("TajD" = size.taj, "FayWuH" = size.h, "ZengsE" = size.e, "Fst" = size.fst, "Dxy" = size.dxy, "XPEHH" = size.xp, "Rsb" = size.rsb) %>% select(sim_ploidy, sampGen, TajD, ZengsE, FayWuH, Fst, Dxy, XPEHH, Rsb) %>% melt(., id.var = c("sim_ploidy", "sampGen")) %>% mutate(stat = "AUC")
+
+kkk.3 = rbind(kkk.1, kkk.2)
+
+scaleFUN <- function(x) sprintf("%.1f", x)
+
+kkk.3 %>% filter(variable != "Dxy" & stat == "AUC") %>% ggplot(., aes(y = value / 100000, fill = as.factor(sampGen), x = as.factor(sim_ploidy))) + geom_boxplot(outlier.shape = NA) + scale_fill_manual(name = "Generations\nsince Fixation", values = wes_palette("Royal2")) + scale_y_continuous(labels=scaleFUN) + ylab("Area Under Curve") + xlab("Ploidy") + facet_wrap(~variable, scales = "free", shrink = T, nrow = 1) + theme_bw() + theme(axis.text.y=element_text(size = 12), axis.title.y=element_text(size=16), axis.text.x=element_blank(), axis.title.x=element_blank(), legend.text = element_text(size=13), legend.title = element_text(size=14), strip.text = element_text(size=14))
+
+kkk.3 %>% filter(variable != "Dxy" & stat == "MaxValue") %>% ggplot(., aes(y = value, fill = as.factor(sampGen), x = as.factor(sim_ploidy))) + geom_boxplot(outlier.shape = NA) + scale_fill_manual(name = "Generations\nsince Fixation", values = wes_palette("Royal2")) + scale_y_continuous(labels=scaleFUN) + ylab("Max Value") + xlab("Ploidy") + facet_wrap(~variable, scales = "free", shrink = T, nrow = 1) + theme_bw() + theme(axis.text.y=element_text(size = 12), axis.title.y=element_text(size=16), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18), legend.text = element_text(size=13), legend.title = element_text(size=14), strip.background = element_blank(), strip.text.x = element_blank())
+
+dom.rehh = read.csv("~/Documents/Research/PloidySim/rehh/dom/rehh_dom.csv")
+
+ff = dom.rehh %>% filter(!is.na(xpehh.p) & sampGen!=1000) %>% mutate(mid = POSITION) %>% nest(-c(s, dom, recomb, N, mu, sim_ploidy, traj_ploidy, sampGen, fuseGen, rep)) %>% mutate(size.xp = map(data, ~getDims(., y.metric = "XPEHH")), size.xp.p = map(data, ~getDims(., y.metric = "xpehh.p")), med.xp = map(data, ~getStat(., "XPEHH")), med.xpp = map(data, ~log(getStat(., "xpehh.p"))), size.rsb = map(data, ~getDims(., y.metric = "Rsb")), size.rsb.p = map(data, ~getDims(., y.metric = "rsb.p")), med.rsb = map(data, ~getStat(., "Rsb")), med.rsb.p = map(data, ~log(getStat(., "rsb.p")))) %>% select(-data) %>% unnest()
+
+ff %<>% mutate(traj_ploidy = as.numeric(str_replace(traj_ploidy, "tp","")), sim_ploidy = as.numeric(str_replace(sim_ploidy, "sp","")), dom = as.numeric(str_replace(dom, "do","")), s = as.numeric(str_replace(s, "se","")), N = as.numeric(str_replace(N, "NN","")), mu = as.numeric(str_replace(mu, "mu","")), recomb = as.numeric(str_replace(recomb, "re","")), sampGen = as.numeric(str_replace(sampGen, "sG","")), fuseGen = as.numeric(str_replace(fuseGen, "fG","")), rep = as.numeric(str_replace(rep, "rep", "")))
+
+# ee = ms %>% filter(sampGen==1 & driftGen == 0 & fuseGen %in% c(1,1000,10000) & dom %in% c(0.1, 0.5, 0.9)) %>% nest(-c(s, dom, recomb, N, mu, sim_ploidy, traj_ploidy, sampGen, fuseGen, rep, driftGen)) %>% mutate(height.taj = map(data, ~getDims(., y.metric = "Tajima.D_1")$height), width.taj = map(data, ~getDims(., y.metric = "Tajima.D_1")$width), height.fst = map(data, ~getDims(.)$height), med.fst = map(data, ~getStat(., "fst")), width.fst = map(data, ~getDims(.)$width), height.h = map(data, ~getDims(., y.metric = "Fay.Wu.H_1")$height), width.h = map(data, ~getDims(., y.metric = "Fay.Wu.H_1")$width), height.e = map(data, ~getDims(., y.metric = "Zeng.E_1")$height), width.e = map(data, ~getDims(., y.metric = "Zeng.E_1")$width), height.dxy = map(data, ~getDims(., y.metric = "dxy.1.2")$height), width.dxy = map(data, ~getDims(., y.metric = "dxy.1.2")$width), med.dxy = map(data, ~getStat(., "dxy.1.2")), height.div = map(data, ~getDims(., y.metric = "Pi.2")$height), width.div = map(data, ~getDims(., y.metric = "Pi.2")$width), med.div = map(data, ~getStat(., "Pi.2"))) %>% select(-data) %>% unnest()
+
+ee = ms %>% filter(sampGen==1 & driftGen == 0 & fuseGen %in% c(1,1000,10000) & dom %in% c(0.1, 0.5, 0.9)) %>% group_by(s, dom, recomb, N, mu, sim_ploidy, traj_ploidy, sampGen, fuseGen, rep, driftGen) %>% mutate(Div = mean(Pi.2) - Pi.1, Tajima.D_1 = abs(Tajima.D_1)) %>% ungroup() %>% nest(-c(s, dom, recomb, N, mu, sim_ploidy, traj_ploidy, sampGen, fuseGen, rep, driftGen)) %>% mutate(size.div = map(data, ~getDims(., y.metric = "Div")), size.taj = map(data, ~getDims(., y.metric = "Tajima.D_1")), size.h = map(data, ~getDims(., y.metric = "Fay.Wu.H_1")), size.e = map(data, ~getDims(., y.metric = "Zeng.E_1")), size.fst = map(data, ~getDims(., y.metric = "fst")), size.dxy = map(data, ~getDims(., y.metric = "dxy.1.2")), med.d = map(data, ~getStat(., "Tajima.D_1")), med.e = map(data, ~getStat(., "Zeng.E_1")), med.h = map(data, ~getStat(., "Fay.Wu.H_1")), med.fst = map(data, ~getStat(., "fst")), med.dxy = map(data, ~getStat(., "dxy.1.2"))) %>% select(-data) %>% unnest()
+
+kk = merge(ee, ff, by = c("traj_ploidy", "sim_ploidy", "dom", "s", "N", "mu", "recomb", "sampGen", "fuseGen", "rep"), all.x = T)
+
+kk %>% filter(dom %in% c(0.1, 0.5, 0.9) & traj_ploidy == sim_ploidy & s == "0.01" & N=="10000" & driftGen == 0 & sampGen == 1 & recomb == 1e-08 & fuseGen == 1) %>% mutate("Diversity" = size.div, "TajD" = size.taj, "FayWuH" = size.h, "ZengsE" = size.e, "Fst" = size.fst, "Dxy" = size.dxy, "XPEHH" = size.xp, same_ploidy = ifelse(sim_ploidy == traj_ploidy, 1, 0)) %>% select(sim_ploidy, dom, Diversity, TajD, FayWuH, ZengsE, Fst, XPEHH) %>% melt(., id.var = c("sim_ploidy", "dom")) %>% mutate("PeakSize" = variable) %>% filter(value != -9) %>% ggplot(., aes(y = value / 10000, fill = as.factor(dom), x = as.factor(sim_ploidy))) + geom_boxplot(outlier.shape = NA) + scale_fill_manual(name = "Dominance", values = wes_palette("Royal1")) + ylab("") + xlab("Ploidy") + facet_wrap(~PeakSize, scales = "free_y") +theme_bw() + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18), legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16))
+
+kk.points = kk %>% filter(dom %in% c("0.1", "0.5", "0.9") & traj_ploidy == sim_ploidy & s == "0.01" & recomb == "1e-08" & N=="1000" & driftGen == 0 & sampGen == 1)  %>% mutate("TajD" = size.taj, "FayWuH" = size.h, "ZengsE" = size.e, "Fst" = size.fst, "XPEHH" = size.xp, "Diversity" = size.div * 10) %>% select(sim_ploidy, dom, TajD, FayWuH, ZengsE, Fst, XPEHH, Diversity) %>% melt(., id.var = c("sim_ploidy", "dom")) %>% mutate("PeakSize" = variable) %>% filter(value != 40.5) %>% group_by(sim_ploidy, dom, variable) %>% summarize(median = median(value)) %>% mutate(PeakSize = variable)
+
+#dominance figure
+kk %>% filter(dom %in% c(0.1, 0.5, 0.9) & traj_ploidy == sim_ploidy & s == "0.01" & N=="10000" & driftGen == 0 & sampGen == 1 & recomb == 1e-08 & fuseGen == 1) %>% mutate("Diversity" = size.div, "TajD" = size.taj, "FayWuH" = size.h, "ZengsE" = size.e, "Fst" = size.fst, "Dxy" = size.dxy, "XPEHH" = size.xp, same_ploidy = ifelse(sim_ploidy == traj_ploidy, 1, 0)) %>% select(sim_ploidy, dom, Diversity, TajD, FayWuH, ZengsE, Fst, XPEHH) %>% melt(., id.var = c("sim_ploidy", "dom")) %>% mutate("PeakSize" = variable) %>% filter(value != -9) %>% ggplot(., aes(y = value / 10000, fill = as.factor(dom), x = as.factor(sim_ploidy))) + geom_boxplot(outlier.shape = NA) + geom_point(data = kk.points, aes(y = median / 10000, x = as.factor(sim_ploidy)), position = position_dodge(width = 0.8), size = 2, shape = 4) + scale_fill_manual(name = "Dominance\nScalar", values = wes_palette("Royal1"), labels = c("-0.4 (Partial\nRecessive)", "\n0 (Additive)\n", "0.4 (Partial\nDominance)")) + ylab("Peak Area") + xlab("Ploidy") + facet_wrap(~PeakSize, scales = "free_y") +theme_bw() + theme(axis.text.y=element_blank(), axis.ticks.y = element_blank(), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=16), legend.text = element_text(size=14), legend.title = element_text(size=16), strip.text = element_text(size=16))
+
+#magnitude instead
+kk %>% filter(dom %in% c(0.1, 0.5, 0.9) & traj_ploidy == sim_ploidy & s == "0.01" & N=="10000" & driftGen == 0 & sampGen == 1 & recomb == 1e-08 & fuseGen == 1) %>% mutate("TajD" = med.d, "FayWuH" = med.h, "ZengsE" = med.e, "Fst" = med.fst, "Dxy" = med.dxy, "XPEHH" = med.xp, same_ploidy = ifelse(sim_ploidy == traj_ploidy, 1, 0)) %>% select(sim_ploidy, dom, TajD, FayWuH, ZengsE, Fst, Dxy, XPEHH) %>% melt(., id.var = c("sim_ploidy", "dom")) %>% mutate("PeakSize" = variable) %>% filter(value != -9) %>% ggplot(., aes(y = value, fill = as.factor(dom), x = as.factor(sim_ploidy))) + geom_boxplot(outlier.shape = NA) + scale_fill_manual(name = "Dominance", values = wes_palette("Royal1")) + ylab("") + xlab("Ploidy") + facet_wrap(~PeakSize, scales = "free_y") +theme_bw() + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18), legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16))
+
+#Just diversity for panel
+kk %>% filter(dom %in% c(0.1, 0.5, 0.9) & traj_ploidy == sim_ploidy & s == "0.01" & N=="10000" & driftGen == 0 & sampGen == 1 & recomb == 1e-08 & fuseGen == 1) %>% mutate("Diversity" = size.div, "TajD" = size.taj, "FayWuH" = size.h, "ZengsE" = size.e, "Fst" = size.fst, "Dxy" = size.dxy, "XPEHH" = size.xp, same_ploidy = ifelse(sim_ploidy == traj_ploidy, 1, 0)) %>% select(sim_ploidy, dom, Diversity) %>% melt(., id.var = c("sim_ploidy", "dom")) %>% mutate("PeakSize" = variable) %>% filter(value != -9) %>% ggplot(., aes(y = value, fill = as.factor(dom), x = as.factor(sim_ploidy))) + geom_boxplot(outlier.shape = NA) + geom_point(data = kk.points[kk.points$variable == "Diversity",], aes(y = median, x = as.factor(sim_ploidy)), position = position_dodge(width = 0.8), size = 2, shape = 4) + scale_fill_manual(name = "Dominance\nScalar", values = wes_palette("Royal1"), labels = c("-0.4 (Recessive)", "\n0 (Additive)\n", "0.4 (Dominant)")) + ylab("Peak Area") + xlab("Ploidy") + theme_bw() + theme(axis.text.y=element_text(size = 12), axis.title.y=element_text(size=14), axis.text.x=element_text(size=12), axis.title.x=element_text(size=14), legend.text = element_text(size=12), legend.title = element_text(size=14), strip.text = element_text(size=16))
 ```
@@
 MS2.c %>% filter(fuseGen == 1 & mu==1e-08 & N == 10000 & recomb=="1e-08" & s =="0.01" & sampGen == 1) %>% ggplot(., aes(y=breadth/1000, fill = as.factor(traj_ploidy), x = as.factor(sim_ploidy))) + geom_boxplot(notch=T) + ylab(expression(paste("Dip Breadth = Length (kb) of which ", pi[1], " < (",pi[2], " / 2)",sep = ""))) + scale_fill_discrete(name = "Trajectory\nPloidy") + xlab("Simulation Ploidy") + theme_bw()
+
+```
+
+### Dominance
+```{r}
+MS2.a = ms %>% group_by(s, dom, recomb, N, mu, sim_ploidy, traj_ploidy, sampGen, fuseGen, rep, driftGen) %>% summarize(depth.pi = mean(Pi.2,na.rm=T) - min(Pi.1), min.pi = min(Pi.1, na.rm=T), max.taj = abs(min(Tajima.D_1, na.rm = T)), height.fst = max(fst, na.rm = T) - mean(fst, na.rm = T))
+
+MS2.b = ms %>% group_by(s, dom, recomb, N, mu, sim_ploidy, traj_ploidy, sampGen, fuseGen, driftGen, rep, ints) %>% summarize(lessWind.pi = ifelse(mean(Pi.1, na.rm=T) < (mean(Pi.2, na.rm=T) / 2),1,0), lessWind.taj = ifelse(mean(Tajima.D_1, na.rm=T) < -1, 1, 0))
+
+MS2.c = MS2.b %>% group_by(s, dom, recomb, N, mu, sim_ploidy, traj_ploidy, sampGen, fuseGen, driftGen, rep) %>% summarize(breadth.pi = sum(lessWind.pi) * 20000, breadth.taj = sum(lessWind.taj) * 20000)
+
+MS2.f = merge(MS2.a, MS2.c, by = c("s", "dom", "recomb", "N", "mu", "sim_ploidy", "traj_ploidy", "sampGen", "fuseGen", "driftGen", "rep"))
+
+MS2.f %<>% mutate(same_ploidy = ifelse(sim_ploidy==traj_ploidy, "yellow", "black"))
+
+n1k = MS2.f %>% filter(sim_ploidy == traj_ploidy & s == 0.01 & mu==1e-08 & N == 1000 & driftGen %in% c(0,1) & sampGen == 1 & dom %in% c(0.1, 0.5, 0.9)) %>% mutate(Height = (log(min.pi, 10)), Breadth = breadth.pi, Magnitude = depth.pi, Area = breadth.pi * depth.pi / 2) %>% group_by(sim_ploidy, dom) %>% summarize(Breadth = median(Breadth), Magnitude = median(Magnitude), Area = median(Area))
+m.n1k = melt(n1k, id.var = c("sim_ploidy", "dom"))
+
+#Current dominance fig.  Includes median for N = 1000
+MS2.f %>% filter(sim_ploidy == traj_ploidy & mu==1e-08 & s == 0.01 & driftGen %in% c(0,1) & N == 10000 & sampGen == 1 & dom %in% c(0.1, 0.5, 0.9)) %>% mutate(Height = (log(min.pi, 10)), Breadth = breadth.pi/10000, Magnitude = depth.pi, Area = breadth.pi * depth.pi / 2) %>% select(recomb, dom, traj_ploidy, Area) %>% melt(., id.var = c("recomb", "dom", "traj_ploidy")) %>% ggplot(., aes(y = value, fill = as.factor(dom), x = as.factor(traj_ploidy))) + geom_boxplot(outlier.shape = NA) + geom_point(data = m.n1k[m.n1k$dom %in% c(0.1, 0.5, 0.9) & m.n1k$variable %in% c("Area"),], aes(y = value * 10, x = as.factor(sim_ploidy)), position = position_dodge(width = 0.8), size = 4, shape = 4) + scale_fill_manual(name = "Dominance\nScalar", values = wes_palette("Royal1")) + ylim(0,100) + ylab("Peak Area") + xlab("Ploidy") + theme_bw() + theme(axis.text.y=element_text(size = 16), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18),legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16))
+
 ```
@@
 ```{r, echo=T,message=F}
+#Single panel figure
+ms %>% filter(traj_ploidy==sim_ploidy & sampGen == "1" & s == 0.01 & dom == "0.5" & N == 10000) %>% ggplot(., aes(y=Pi.1 * 100, color = as.factor(sim_ploidy), x = mid/100000)) + geom_smooth(method="loess", size =0.5, span=0.1, se=F) + scale_x_continuous(breaks=c(1,5,9), limits = c(0.2,9.8)) + xlab("Position (100 kb)") + ylab("Diversity (%)") + scale_color_discrete(name="Ploidy") + theme_bw() + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18),axis.text.x=element_text(size=16),axis.title.x=element_text(size=18),legend.text = element_text(size=16), legend.title = element_text(size=18))
+
+#Faceted with s and recomb
 ms2 %>% filter(dom %in% c("0.1","0.9","0.5") & N == 10000 & fuseGen == 1 & sampGen ==1 & mu==1e-08 & sim_ploidy == 4) %>% ggplot(., aes(y=Pi.1 * 100, color = as.factor(traj_ploidy), x = mid/100000)) + geom_smooth(method="loess", size =0.5, span=0.1, se=F) + scale_x_continuous(breaks=c(1,5,9)) + xlab("Position (100 kb)") + ylab("Diversity (%)") + scale_color_discrete(name="Trajectory\nPloidy") + facet_grid(vars(s, recomb), vars(dom),labeller = label_both, scales = "free_y") + theme_bw()

### 2019-08-17 analysis/mssel_analysis.Rmd
drift script

@@
 
-## Load packages and import data
+## Load packages and import/generate data
 ```{r setup, message=F}
@@
 library(IDPmisc)
+library(MESS)
+library(wesanderson)
 
@@
 
-#NEED TO ADD this data
 ms3 = read.table("~/Documents/Research/PloidySim/data/mssel_out_5-10-19.txt", head = T)
@@
 ms = rbind(ms, ms4)
+
+#Same number of sampled haplotypes.  Is reduced variance in higher ploidies due to higher haplotype sample size.
+ds = read.table("~/Documents/Research/PloidySim/data/mssel_out_DS_7-31-19.txt", head = T)
+nds = read.table("~/Documents/Research/PloidySim/data/mssel_out_nDS_7-31-19.txt", head = T)
+nds.ehh = read.csv("~/Documents/Research/PloidySim/rehh/dom/rehh_csv")
+
+ds.files = c("~/Documents/Research/PloidySim/rehh/rehh_tp2_do0.5_1krep_DS.csv", "~/Documents/Research/PloidySim/rehh/rehh_tp4_do0.5_1krep_DS.csv", "~/Documents/Research/PloidySim/rehh/rehh_tp8_do0.5_1krep_DS.csv")
+nds.files = c("~/Documents/Research/PloidySim/rehh/rehh_tp2_do0.5_1krep_nDS.csv", "~/Documents/Research/PloidySim/rehh/rehh_tp4_do0.5_1krep_nDS.csv", "~/Documents/Research/PloidySim/rehh/rehh_tp8_do0.5_1krep_nDS.csv")
+
+ds %<>% select(-start_freq) %>% mutate(DS="yes")
+nds %<>% select(-start_freq) %>% mutate(DS="no")
+ms5 = rbind(ds, nds)
+
+wrapEHH = function(files){
+  all.sum = data.frame()
+  for(i in 1:length(files)){
+    print(files[i])
+    dat = read.csv(files[i])
+    dat.sum = dat %>% mutate(traj_ploidy = as.numeric(str_replace(traj_ploidy, "tp","")), sim_ploidy = as.numeric(str_replace(sim_ploidy, "sp","")), dom = as.numeric(str_replace(dom, "do","")), s = as.numeric(str_replace(s, "se","")), N = as.numeric(str_replace(N, "NN","")), mu = as.numeric(str_replace(mu, "mu","")), recomb = as.numeric(str_replace(recomb, "re","")), sampGen = as.numeric(str_replace(sampGen, "sG","")), fuseGen = as.numeric(str_replace(fuseGen, "fG","")), rep = as.numeric(str_replace(rep, "rep", ""))) %>% filter(!is.na(xpehh.p)) %>% mutate(mid = POSITION) %>% nest(-c(sim_ploidy, rep)) %>% mutate(size.xp = map(data, ~getDims(., y.metric = "XPEHH")), size.xp.p = map(data, ~getDims(., y.metric = "xpehh.p")), med.xp = map(data, ~getStat(., "XPEHH")), med.xpp = map(data, ~log(getStat(., "xpehh.p"))), size.rsb = map(data, ~getDims(., y.metric = "Rsb")), size.rsb.p = map(data, ~getDims(., y.metric = "rsb.p")), med.rsb = map(data, ~getStat(., "Rsb")), med.rsb.p = map(data, ~log(getStat(., "rsb.p")))) %>% select(-data) %>% unnest()
+    all.sum = rbind(all.sum, dat.sum)
+    remove(dat)
+  }
+  return(all.sum)
+}
+
+ds.ehh = wrapEHH(ds.files)
+nds.ehh = wrapEHH(nds.files)
+ds.ehh %<>% mutate(DS="yes")
+nds.ehh %<>% mutate(DS="no")
+
+CV <- function(data){(sd(data, na.rm=T)/(mean(data, na.rm=T)))*100}
+
+lCV <- function(data, N = 10000, n = 100){
+    aa = foreach(i = 1:N, .combine = rbind) %do% {
+      ndat = sample(data, n)
+      sd(ndat, na.rm=T)/(mean(ndat, na.rm=T))*100}
+    return(quantile(aa,0.05, na.rm=T))
+}
+
+uCV <- function(data, N = 10000, n = 100){
+    aa = foreach(i = 1:N, .combine = rbind) %do% {
+      ndat = sample(data, n)
+      sd(ndat, na.rm=T)/(mean(ndat, na.rm=T))*100}
+    return(quantile(aa,0.95, na.rm=T))
+}
+
+ds = ms5 %>% group_by(sim_ploidy, DS, rep) %>% mutate(Div = mean(Pi.2) - Pi.1, Tajima.D_1 = abs(Tajima.D_1)) %>% ungroup() %>% nest(-c(sim_ploidy, DS, rep)) %>% mutate(size.div = map(data, ~getDims(., y.metric = "Div")), size.taj = map(data, ~getDims(., y.metric = "Tajima.D_1")), size.h = map(data, ~getDims(., y.metric = "Fay.Wu.H_1")), size.e = map(data, ~getDims(., y.metric = "Zeng.E_1")), size.fst = map(data, ~getDims(., y.metric = "fst")), size.dxy = map(data, ~getDims(., y.metric = "dxy.1.2")), med.d = map(data, ~getStat(., "Tajima.D_1")), med.e = map(data, ~getStat(., "Zeng.E_1")), med.h = map(data, ~getStat(., "Fay.Wu.H_1")), med.fst = map(data, ~getStat(., "fst")), med.dxy = map(data, ~getStat(., "dxy.1.2"))) %>% select(-data) %>% unnest()
+
+ds %>% group_by(sim_ploidy, DS) %>% select(-rep) %>% summarize_all(sd) %>% gather(variable, value, -c(sim_ploidy, DS)) %>% ggplot(aes(x = as.factor(sim_ploidy), fill = as.factor(DS), y = value)) + geom_bar(stat = "identity", position = "dodge") + facet_wrap(~variable, scales = "free_y")
+
+ehh = rbind(nDS.ehh, DS.ehh)
+
+ms6 = merge(ds, ehh, by = c("sim_ploidy", "DS", "rep"), all = T)
+
+ms6 %>% group_by(sim_ploidy, DS) %>% select(-rep) %>% summarize_all(CV) %>% gather(variable, value, -c(sim_ploidy, DS)) %>% ggplot(aes(x = as.factor(sim_ploidy), fill = as.factor(DS), y = value)) + geom_bar(stat = "identity", position = "dodge") + facet_wrap(~variable, scales = "free_y")
+
+ms6 %>% group_by(sim_ploidy, DS) %>% select(-rep) %>% summarize_all(CV) %>% gather(variable, value, -c(sim_ploidy, DS)) %>% ggplot(aes(x = as.factor(sim_ploidy), fill = as.factor(DS), y = value)) + geom_bar(stat = "identity", position = "dodge") + facet_wrap(~variable, scales = "free_y")
+
+ms6.1 = ms6 %>% mutate("TajD" = med.d, "FayWuH" = med.h, "ZengsE" = med.e, "Fst" = med.fst, "Dxy" = med.dxy, "XPEHH" = med.xp, "Rsb" = med.rsb) %>% select(sim_ploidy, DS, TajD, ZengsE, FayWuH, Fst, Dxy, XPEHH, Rsb) %>% melt(., id.var = c("sim_ploidy", "DS")) %>% mutate(stat = "MaxValue")
+
+ms6.2 = ms6 %>% mutate("TajD" = size.taj, "FayWuH" = size.h, "ZengsE" = size.e, "Fst" = size.fst, "Dxy" = size.dxy, "XPEHH" = size.xp, "Rsb" = size.rsb) %>% select(sim_ploidy, DS, TajD, ZengsE, FayWuH, Fst, Dxy, XPEHH, Rsb) %>% melt(., id.var = c("sim_ploidy", "DS")) %>% mutate(stat = "AUC")
+
+ms6.3 = rbind(ms6.1, ms6.2)
+
+scaleFUN <- function(x) sprintf("%.1f", x)
+
+#Not interesting
+# ms6.3 %>% filter(stat == "AUC") %>% group_by(sim_ploidy, DS, variable) %>% summarize(CV = CV(value)) %>% ggplot(., aes(y = CV, fill = as.factor(DS), x = as.factor(sim_ploidy))) + geom_bar(stat="identity", position = position_dodge()) + scale_fill_discrete(name = "Sampling", labels=c("Equal Individuals", "Equal Alleles")) + scale_y_continuous(labels=scaleFUN) + ylab("Var[AUC]") + xlab("Ploidy") + facet_wrap(~variable, scales = "free", shrink = T, nrow = 1) + theme_bw() + theme(axis.text.y=element_blank(), axis.title.y=element_text(size=16), axis.text.x=element_blank(), axis.title.x=element_blank(), legend.text = element_text(size=13), legend.title = element_text(size=14), strip.text = element_text(size=14))
+
+MS6.1 = ms6 %>% mutate("TajD" = med.d, "FayWuH" = med.h, "ZengsE" = med.e, "Fst" = med.fst, "Dxy" = med.dxy, "XPEHH" = med.xp, "Rsb" = med.rsb) %>% select(sim_ploidy, DS, TajD, ZengsE, FayWuH, Fst, Dxy, XPEHH, Rsb) %>% group_by(sim_ploidy, DS) %>% summarize_all(c("CV", "lCV", "uCV"))
+
+MS6.1 %>% melt(., id.var = c("sim_ploidy", "DS")) %>% separate(variable, c("variable","XX"), "_") %>% spread(XX, value) %>% ggplot(., aes(y = CV, fill = as.factor(DS), x = as.factor(sim_ploidy))) + geom_bar(stat="identity", position = position_dodge()) + geom_errorbar(aes(ymin = lCV, ymax = uCV, width = 0.5), position = position_dodge(width = 0.9)) + scale_fill_discrete(name = "Sampling", labels=c("Equal Individuals", "Equal Alleles")) + scale_y_continuous(labels=scaleFUN) + ylab("Var[MaxValue]") + xlab("Ploidy") + facet_wrap(~variable, scales = "free", shrink = T, nrow = 1) + theme_bw() + theme(axis.text.y=element_blank(), axis.title.y=element_text(size=16), axis.text.x=element_text(size=14), axis.title.x=element_text(size=16), legend.text = element_text(size=13), legend.title = element_text(size=14), strip.text = element_text(size=14))
 
@@
 mDoms$variable = factor(mDoms$variable, levels(mDoms$variable)[c(rev(seq(1,11)))])
-ALL$Call=factor(ALL$Call,levels(ALL$Call)[c(2,1,3)])
 
@@
 dat1 = foreach(i = 1:nrow(params), .combine=rbind) %do% {
-  getTraj(params[i,]$s, params[i,]$dom, params[i,]$ploidy, params[i,]$start)
+  getTraj(params[i,]$s, params[i,]$dom, params[i,]$ploidy, params[i,]$start, maxGens = 999999)
 }
@@
 
-dat1 %>% filter(ploidy %in% c(2, 4, 8) & dom %in% c(1, 0.5, 0)) %>% 
-ggplot(., aes(x=gen, y=freq, linetype=as.factor(dom), color=as.factor(ploidy))) + geom_line() + scale_color_manual(name = "Ploidy", values = c("#F8766D", "#00BA38", "#619CFF")) + scale_linetype_manual(name = "Dominance", labels=c("Dominant", "Additive", "Recessive")) + xlim(0,300) + theme_bw() + xlab("Generation") + ylab("Allele Frequency") + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18),axis.text.x=element_text(size=16),axis.title.x=element_text(size=18),legend.text = element_text(size=16), legend.title = element_text(size=18))
+#All together
+dat1 %>% filter(ploidy %in% c(2, 4, 8) & dom %in% c(0, 0.5, 1)) %>% ggplot(., aes(x=gen, y=freq, linetype=as.factor(dom), color=as.factor(ploidy))) + geom_line(size = 1.2) + scale_color_manual(name = "Ploidy", values = c("#F8766D", "#00BA38", "#619CFF")) + scale_linetype_manual(name = "Dominance", labels=c("Dominant", "Additive", "Recessive"), values = c("dashed", "solid", "dotted")) + xlim(0,500) + theme_bw() + xlab("Generation") + ylab("Allele Frequency") + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18),axis.text.x=element_text(size=16),axis.title.x=element_text(size=18),legend.text = element_text(size=16), legend.title = element_text(size=18))
+
+#Additive and non-additive apart
+dat1 %>% filter(ploidy %in% c(2, 4, 8) & dom %in% c(0.5)) %>% ggplot(., aes(x=gen, y=freq, color=as.factor(ploidy))) + geom_line(size = 1.2) + scale_color_manual(name = "Ploidy", values = c("#F8766D", "#00BA38", "#619CFF")) + xlim(0,500) + theme_bw() + xlab("Generation") + ylab("Allele Frequency") + theme(axis.text.y=element_text(size=14), axis.title.y=element_text(size=16),axis.text.x=element_text(size=14),axis.title.x=element_text(size=16),legend.text = element_text(size=14), legend.title = element_text(size=16))
+
+dat1 %>% filter(ploidy %in% c(2, 4, 8) & dom %in% c(0, 1) & mod(gen,100)==0) %>% ggplot(., aes(x=gen, y=freq, linetype=as.factor(dom), color=as.factor(ploidy))) + geom_line(size = 1.2) + scale_color_manual(name = "Ploidy", values = c("#F8766D", "#00BA38", "#619CFF")) + scale_linetype_manual(name = "Dominance", labels=c("Dominant", "Recessive"), values = c("dashed", "dotted")) + scale_x_log10() + theme_bw() + xlab("Generation") + ylab("Allele Frequency") + theme(axis.text.y=element_text(size=14), axis.title.y=element_text(size=16),axis.text.x=element_text(size=14),axis.title.x=element_text(size=16),legend.text = element_text(size=14), legend.title = element_text(size=16))
+
+#Stochastic effect of population size on
+params = data.frame("s" = rep(0.1,12), "dom" = c(rep(0.1,4), rep(0.5,4), rep(0.9,4)), "ploidy" = rep(c(2,4), 6), "start" = rep(0.05, 12), "N" = rep(c(1000, 1000, 10000, 10000), 3))
+params %<>% dplyr::slice(rep(row_number(), 1000))
+# Create trajectories
+dat1 = foreach(i = 1:nrow(params), .combine=rbind) %do% {
+  print(params[i,])
+  dat = getTraj(params[i,]$s, params[i,]$dom, params[i,]$ploidy, params[i,]$start, N = params[i,]$N, maxGens = 9999999, maxTries = 9999999)
+  dat["N"] = params[i,]$N
+  dat[nrow(dat),]
+}
+
+dat1 %>%  mutate(Dom = factor(case_when(dom == 0.1 ~ "Partial Recessivity", dom == 0.5 ~ "Additivity", dom == 0.9 ~ "Partial Dominance"), levels = c("Partial Recessivity", "Additivity", "Partial Dominance"))) %>% ggplot(aes(y = log(gen), fill = as.factor(N), x = as.factor(ploidy))) + geom_boxplot() + facet_wrap(~Dom) + ylab("Log(Time to Fixation)") + xlab("Ploidy") + scale_fill_discrete(name = "Population Size")+ theme_bw() + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18),axis.text.x=element_text(size=16),axis.title.x=element_text(size=18),legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16))
 ```
@@
 
-kkk.3 %>% filter(variable != "Dxy" & stat == "AUC") %>% ggplot(., aes(y = value / 100000, fill = as.factor(sampGen), x = as.factor(sim_ploidy))) + geom_boxplot(outlier.shape = NA) + scale_fill_manual(name = "Generations\nsince Fixation", values = wes_palette("Royal2")) + scale_y_continuous(labels=scaleFUN) + ylab("Area Under Curve") + xlab("Ploidy") + facet_wrap(~variable, scales = "free", shrink = T, nrow = 1) + theme_bw() + theme(axis.text.y=element_text(size = 12), axis.title.y=element_text(size=16), axis.text.x=element_blank(), axis.title.x=element_blank(), legend.text = element_text(size=13), legend.title = element_text(size=14), strip.text = element_text(size=14))
+kkk.3 %>% filter(variable %in% c("sim_ploidy", "sampGen", "TajD", "Fst", "Rsb", "XPEHH") & stat == "AUC") %>% ggplot(., aes(y = value / 100000, fill = as.factor(sampGen), x = as.factor(sim_ploidy))) + geom_boxplot(outlier.shape = NA) + scale_fill_manual(name = "Generations\nsince Fixation", values = wes_palette("Royal2")) + scale_y_continuous(labels=scaleFUN) + ylab("Area Under Curve") + xlab("Ploidy") + facet_wrap(~variable, scales = "free", shrink = T, nrow = 1) + theme_bw() + theme(axis.text.y=element_text(size = 12), axis.title.y=element_text(size=16), axis.text.x=element_blank(), axis.title.x=element_blank(), legend.text = element_text(size=13), legend.title = element_text(size=14), strip.text = element_text(size=14))
 
-kkk.3 %>% filter(variable != "Dxy" & stat == "MaxValue") %>% ggplot(., aes(y = value, fill = as.factor(sampGen), x = as.factor(sim_ploidy))) + geom_boxplot(outlier.shape = NA) + scale_fill_manual(name = "Generations\nsince Fixation", values = wes_palette("Royal2")) + scale_y_continuous(labels=scaleFUN) + ylab("Max Value") + xlab("Ploidy") + facet_wrap(~variable, scales = "free", shrink = T, nrow = 1) + theme_bw() + theme(axis.text.y=element_text(size = 12), axis.title.y=element_text(size=16), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18), legend.text = element_text(size=13), legend.title = element_text(size=14), strip.background = element_blank(), strip.text.x = element_blank())
+kkk.3 %>% filter(variable %in% c("sim_ploidy", "sampGen", "TajD", "Fst", "Rsb", "XPEHH") & stat == "MaxValue") %>% ggplot(., aes(y = value, fill = as.factor(sampGen), x = as.factor(sim_ploidy))) + geom_boxplot(outlier.shape = NA) + scale_fill_manual(name = "Generations\nsince Fixation", values = wes_palette("Royal2")) + scale_y_continuous(labels=scaleFUN) + ylab("Max Value") + xlab("Ploidy") + facet_wrap(~variable, scales = "free", shrink = T, nrow = 1) + theme_bw() + theme(axis.text.y=element_text(size = 12), axis.title.y=element_text(size=16), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18), legend.text = element_text(size=13), legend.title = element_text(size=14), strip.background = element_blank(), strip.text.x = element_blank())
 
@@
 
-kk %>% filter(dom %in% c(0.1, 0.5, 0.9) & traj_ploidy == sim_ploidy & s == "0.01" & N=="10000" & driftGen == 0 & sampGen == 1 & recomb == 1e-08 & fuseGen == 1) %>% mutate("Diversity" = size.div, "TajD" = size.taj, "FayWuH" = size.h, "ZengsE" = size.e, "Fst" = size.fst, "Dxy" = size.dxy, "XPEHH" = size.xp, same_ploidy = ifelse(sim_ploidy == traj_ploidy, 1, 0)) %>% select(sim_ploidy, dom, Diversity, TajD, FayWuH, ZengsE, Fst, XPEHH) %>% melt(., id.var = c("sim_ploidy", "dom")) %>% mutate("PeakSize" = variable) %>% filter(value != -9) %>% ggplot(., aes(y = value / 10000, fill = as.factor(dom), x = as.factor(sim_ploidy))) + geom_boxplot(outlier.shape = NA) + scale_fill_manual(name = "Dominance", values = wes_palette("Royal1")) + ylab("") + xlab("Ploidy") + facet_wrap(~PeakSize, scales = "free_y") +theme_bw() + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18), legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16))
-
-kk.points = kk %>% filter(dom %in% c("0.1", "0.5", "0.9") & traj_ploidy == sim_ploidy & s == "0.01" & recomb == "1e-08" & N=="1000" & driftGen == 0 & sampGen == 1)  %>% mutate("TajD" = size.taj, "FayWuH" = size.h, "ZengsE" = size.e, "Fst" = size.fst, "XPEHH" = size.xp, "Diversity" = size.div * 10) %>% select(sim_ploidy, dom, TajD, FayWuH, ZengsE, Fst, XPEHH, Diversity) %>% melt(., id.var = c("sim_ploidy", "dom")) %>% mutate("PeakSize" = variable) %>% filter(value != 40.5) %>% group_by(sim_ploidy, dom, variable) %>% summarize(median = median(value)) %>% mutate(PeakSize = variable)
+kk.points = kk %>% filter(dom %in% c("0.1", "0.5", "0.9") & traj_ploidy == sim_ploidy & s == "0.01" & recomb == "1e-08" & N=="1000" & driftGen == 0 & sampGen == 1)  %>% mutate("TajD" = size.taj, "FayWuH" = size.h, "ZengsE" = size.e, "Fst" = size.fst, "XPEHH" = size.xp, "Diversity" = size.div * 10) %>% select(sim_ploidy, dom, TajD, FayWuH, ZengsE, Fst, XPEHH, Diversity) %>% melt(., id.var = c("sim_ploidy", "dom")) %>% mutate("PeakSize" = variable) %>% filter(value != -9) %>% group_by(sim_ploidy, dom, variable) %>% summarize(median = median(value)) %>% mutate(PeakSize = variable)
 
@@
 #magnitude instead
-kk %>% filter(dom %in% c(0.1, 0.5, 0.9) & traj_ploidy == sim_ploidy & s == "0.01" & N=="10000" & driftGen == 0 & sampGen == 1 & recomb == 1e-08 & fuseGen == 1) %>% mutate("TajD" = med.d, "FayWuH" = med.h, "ZengsE" = med.e, "Fst" = med.fst, "Dxy" = med.dxy, "XPEHH" = med.xp, same_ploidy = ifelse(sim_ploidy == traj_ploidy, 1, 0)) %>% select(sim_ploidy, dom, TajD, FayWuH, ZengsE, Fst, Dxy, XPEHH) %>% melt(., id.var = c("sim_ploidy", "dom")) %>% mutate("PeakSize" = variable) %>% filter(value != -9) %>% ggplot(., aes(y = value, fill = as.factor(dom), x = as.factor(sim_ploidy))) + geom_boxplot(outlier.shape = NA) + scale_fill_manual(name = "Dominance", values = wes_palette("Royal1")) + ylab("") + xlab("Ploidy") + facet_wrap(~PeakSize, scales = "free_y") +theme_bw() + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18), legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16))
+kk %>% filter(dom %in% c(0.1, 0.5, 0.9) & traj_ploidy == sim_ploidy & s == "0.01" & N=="10000" & driftGen == 0 & sampGen == 1 & recomb == 1e-08 & fuseGen == 1) %>% mutate("TajD" = med.d, "FayWuH" = med.h, "ZengsE" = med.e, "Fst" = med.fst, "Dxy" = med.dxy, "XPEHH" = med.xp, "Rsb" = med.rsb, same_ploidy = ifelse(sim_ploidy == traj_ploidy, 1, 0)) %>% select(sim_ploidy, dom, TajD, FayWuH, ZengsE, Fst, Dxy, XPEHH) %>% melt(., id.var = c("sim_ploidy", "dom")) %>% mutate("PeakSize" = variable) %>% filter(value != -9) %>% ggplot(., aes(y = value, fill = as.factor(dom), x = as.factor(sim_ploidy))) + geom_boxplot(outlier.shape = NA) + scale_fill_manual(name = "Dominance", values = wes_palette("Royal1")) + ylab("") + xlab("Ploidy") + facet_wrap(~PeakSize, scales = "free_y") +theme_bw() + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18), legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16))
 
@@
 kk %>% filter(dom %in% c(0.1, 0.5, 0.9) & traj_ploidy == sim_ploidy & s == "0.01" & N=="10000" & driftGen == 0 & sampGen == 1 & recomb == 1e-08 & fuseGen == 1) %>% mutate("Diversity" = size.div, "TajD" = size.taj, "FayWuH" = size.h, "ZengsE" = size.e, "Fst" = size.fst, "Dxy" = size.dxy, "XPEHH" = size.xp, same_ploidy = ifelse(sim_ploidy == traj_ploidy, 1, 0)) %>% select(sim_ploidy, dom, Diversity) %>% melt(., id.var = c("sim_ploidy", "dom")) %>% mutate("PeakSize" = variable) %>% filter(value != -9) %>% ggplot(., aes(y = value, fill = as.factor(dom), x = as.factor(sim_ploidy))) + geom_boxplot(outlier.shape = NA) + geom_point(data = kk.points[kk.points$variable == "Diversity",], aes(y = median, x = as.factor(sim_ploidy)), position = position_dodge(width = 0.8), size = 2, shape = 4) + scale_fill_manual(name = "Dominance\nScalar", values = wes_palette("Royal1"), labels = c("-0.4 (Recessive)", "\n0 (Additive)\n", "0.4 (Dominant)")) + ylab("Peak Area") + xlab("Ploidy") + theme_bw() + theme(axis.text.y=element_text(size = 12), axis.title.y=element_text(size=14), axis.text.x=element_text(size=12), axis.title.x=element_text(size=14), legend.text = element_text(size=12), legend.title = element_text(size=14), strip.text = element_text(size=16))
+
+#Without X's
+kk %>% filter(dom %in% c(0.1, 0.5, 0.9) & traj_ploidy == sim_ploidy & s == "0.01" & N=="10000" & driftGen == 0 & sampGen == 1 & recomb == 1e-08 & fuseGen == 1) %>% mutate("Diversity" = size.div, "TajD" = size.taj, "FayWuH" = size.h, "ZengsE" = size.e, "Fst" = size.fst, "Dxy" = size.dxy, "XPEHH" = size.xp, same_ploidy = ifelse(sim_ploidy == traj_ploidy, 1, 0)) %>% select(sim_ploidy, dom, Diversity) %>% melt(., id.var = c("sim_ploidy", "dom")) %>% mutate("PeakSize" = variable) %>% filter(value != -9) %>% ggplot(., aes(y = value, fill = as.factor(dom), x = as.factor(sim_ploidy))) + geom_boxplot(outlier.shape = NA) + scale_fill_manual(name = "Dominance\nScalar", values = wes_palette("Royal1"), labels = c("-0.4 (Recessive)", "\n0 (Additive)\n", "0.4 (Dominant)")) + ylab("Peak Area") + xlab("Ploidy") + theme_bw() + theme(axis.text.y=element_text(size = 12), axis.title.y=element_text(size=14), axis.text.x=element_text(size=12), axis.title.x=element_text(size=14), legend.text = element_text(size=12), legend.title = element_text(size=14), strip.text = element_text(size=16))
+
+kk %>% filter(dom %in% c(0.1, 0.5, 0.9) & traj_ploidy == sim_ploidy & s == "0.01" & N=="1000" & driftGen == 0 & sampGen == 1 & recomb == 1e-08 & fuseGen == 1) %>% mutate("Diversity" = size.div, "TajD" = size.taj, "FayWuH" = size.h, "ZengsE" = size.e, "Fst" = size.fst, "Dxy" = size.dxy, "XPEHH" = size.xp, same_ploidy = ifelse(sim_ploidy == traj_ploidy, 1, 0)) %>% select(sim_ploidy, dom, Diversity) %>% melt(., id.var = c("sim_ploidy", "dom")) %>% mutate("PeakSize" = variable) %>% filter(value != -9) %>% ggplot(., aes(y = value, fill = as.factor(dom), x = as.factor(sim_ploidy))) + geom_boxplot(outlier.shape = NA) + scale_fill_manual(name = "Dominance\nScalar", values = wes_palette("Royal1"), labels = c("-0.4 (Recessive)", "\n0 (Additive)\n", "0.4 (Dominant)")) + ylab("Peak Area") + xlab("Ploidy") + theme_bw() + theme(axis.text.y=element_text(size = 12), axis.title.y=element_text(size=14), axis.text.x=element_text(size=12), axis.title.x=element_text(size=14), legend.text = element_text(size=12), legend.title = element_text(size=14), strip.text = element_text(size=16))
 ```

### 2019-08-17 scripts/PloidyHitch.R

@@ -52,21 +52,27 @@ setwd(tmpdir)
 
 ##### BEGIN: Set parameter values to explore #####
 Ploidy = c(2, 4, 8)
-pop_size = c(1000, 10000) # Keep this value above 100 and below 1000000 (computation time will increase with increasing pop_size)
-selection_coeff = c(0.1, 0.01) # Keep this between 0 and 1
+pop_size = c(10000) # Keep this value above 100 and below 1000000 (computation time will increase with increasing pop_size)
+# selection_coeff = c(0.1, 0.01) # Keep this between 0 and 1
+selection_coeff = c(0.01) # Keep this between 0 and 1
 
-drift_gen = c(0, 1000, 10000)
+# drift_gen = c(0, 1000, 10000)
+drift_gen = c(0)
 
 dominance = c(0.1, 0.5, 0.9, 1, 0) #
 dominance = dominance[dom_idx]
 
 seq_len = 1000000 # Length of sequence that we will simulate with mssel.  Increasing this value will increase computation time.
 mutation_rate = c(1e-8) # per-base mutation rate; mu
-sampGen = c(1, 10000)
-fuseTime = c(1, 10000)
-samp_num = 10 # number of individuals to sample
+# sampGen = c(1, 10000)
+sampGen = c(1)
+fuseTime = c(1)
+samp_num = -9 # number of individuals to sample
+samp_alleles = 20
 max_gens = 9999
 end_freq = 0.99
+
+same_ploidy = TRUE #Set to TRUE if you want traj_ploidy == sim_ploidy
 
 ##### END: Set parameter values to explore #####
 
@@ -215,8 +221,8 @@ getDomCoefs = function(dom_scalar, ploidy = 100){
     coeffs = rep(1, ploidy - 1)
   }
   else {
-    dom = (1 - dom_scalar) - 0.5 
-    dom = abs((dom * 10 + sign(dom)) ^ sign(dom))
+    dom = 0.5 - dom_scalar # Center around additivity (0.5)
+    dom = abs((dom * 10) ^ sign(dom))
     coeffs = (seq(1, ploidy - 1) / ploidy) ^ dom
   }
   return(coeffs)
@@ -264,7 +270,7 @@ getTraj = function(s, dom_scalar, ploidy, start_freq, N = -9, end_freq = 0.99, m
 }
 
 Drift = function(N, ploidy, end, tries){
-  drift = function(N, ploidy, end, tries){
[…]

### 2019-08-17 scripts/calcREHH.R

@@ -355,7 +355,7 @@ dat = foreach(i = 1:(length(files)), .combine=rbind,
             })
         }
         if (!is.null(out)){
-          out %<>% mutate(traj_ploidy = params[1], sim_ploidy = params[2], dom = params[3], s = params[4], N = params[5], mu = params[6], recomb = params[7], sampGen = params[8], fuseGen = params[9], rep = params[10])
+          out %<>% mutate(traj_ploidy = params[1], sim_ploidy = params[2], dom = params[3], s = params[4], N = params[5], mu = params[6], recomb = params[7], sampGen = params[8], fuseGen = params[9], driftGen = params[10], rep = params[11])
           # file.remove(paths)
           out
         }  

### 2019-08-17 scripts/drift.py

@@ -1,0 +1,92 @@
+import pdb
+import random
+import argparse
+import numpy
+import copy
+
+def initialize(size, ploidy, freq):
+    pop = [[] for x in range(0, size)]
+    for i, ind in enumerate(pop):
+        for k in range(0,ploidy):
+            rx = random.random()
+            if rx < freq:
+                pop[i].append(1)
+            else:
+                pop[i].append(0)
+    return(pop)
+
+def drift(pop, numGens):
+    popSize = len(pop)
+    p = calcFreq(pop) 
+    F = []
+    for i in range(0,numGens):
+        if p > 0 and p < 1:
+            newpop = []
+            for j in range(0, popSize):
+                p1 = copy.deepcopy(random.choice(pop))
+                p2 = copy.deepcopy(random.choice(pop))
+
+                g1 = [p1.pop() for x in range(0, int(len(p1)/2))]
+                g2 = [p2.pop() for x in range(0, int(len(p2)/2))]
+
+                o1 = g1 + g2
+                newpop.append(o1)
+            p = calcFreq(newpop)
+            F.append(p)
+
+        # print(i, p)
+        pop = newpop
+        
+    return(pop, F)
+
+def calcFreq(pop):
+    M = 0
+    T = 0
+    for ind in pop:
+        M += sum(ind)
+        T += len(ind)
+    if T != 0: p = M / T
+    else: p = 0
+    return(p)
+
+if __name__ == "__main__":
+    parser = argparse.ArgumentParser()
+    parser.add_argument('-N', type=int, metavar='Population_Size', required=False, default=1000)
+    parser.add_argument('-p', type=float, metavar='start_freq', required=False, default=0.5)
+    parser.add_argument('-k', type=int, metavar='ploidy', required=False, default = 2)
+    parser.add_argument('-t', type=int, metavar='numGens', required=False, default=100)
+    parser.add_argument('-r', type=int, metavar='replicates', required=False, default = 1000)
+
+    # parser.add_argument('-r', action='store_true', help='restrictTo_mainChroms')
+
+    args = parser.parse_args()
+
+    start_freq = args.p
+    N = args.N
+    t = args.t 
+    k = args.k #ploidy
+    reps = args.r
+
+    for k in [2, 4, 8]:
+        freq_diffs = []
+        varps = []
+        for rep in range(0, reps):
+            pop = initialize(N, k, start_freq)
+            start_freq = calcFreq(pop)
[…]

### 2019-08-30 analysis/PaperFigures.Rmd
cleaned up script to reproduce figs

---
title: "Paper_Figures"
author: "Patrick Monnahan"
date: "8/27/2019"
output: html_document
---

## Load packages, import data, and define functions
```{r setup, message=F}
knitr::opts_chunk$set(echo = TRUE)
library(assertthat)
library(ggplot2)
library(dplyr)
library(tidyr)
library(PopGenome)
library(stringr)
library(data.table)
library(magrittr)
library(wrapr)
library(foreach)
library(purrr)
library(IDPmisc)
library(MESS)
library(wesanderson)

getFits = function(s, dom, ploidy){
  dom_coeffs = getDomCoefs(dom, ploidy)
  k = ploidy
  dat = foreach(i = 1:51, .combine=rbind) %do% {
    p = seq(0,1,1/50)[i]
    q = 1 - p
    het_fits = 1 + dom_coeffs * s
    fits = c(1, het_fits, 1 + s) / (1 + s)
    i = seq(0, k)
    freqs = choose(k, i) * (p ^ (k - i)) * (q ^ i)
    w.bar = sum(freqs * rev(fits))
    var.w = sum((freqs * (rev(fits) - w.bar) ^ 2) / length(freqs))
    data.frame('s' = s, 'dom' = dom, 'ploidy' = ploidy, 'freq' = p, 'w.bar' = w.bar, 'var.w' = var.w)
  }
  return(dat)
}

dipTraj=function(start_freq,s,h,stop_freq){
  h=1-h
  p=start_freq
  traj = c(p)
  fits = c(1.0-s, 1.0 - h*s, 1.0)
  while(p < stop_freq){
    g_freqs = c((1-p)^2, 2*p*(1 - p), p^2)
    tot_fit = sum(fits * g_freqs)
    p_fit = (g_freqs[3] * fits[3]) + 0.5*(g_freqs[2] * fits[2])
    p_prime = p_fit/tot_fit
    traj = c(traj,p_prime)
    p = p_prime
  }
  return(traj)
}

tetTraj=function(start_freq,s,h1,h2,h3,stop_freq){
  h1 = 1-h1
  h2 = 1-h2
  h3 = 1-h3
  p=start_freq
  traj = c(p)
  fits = c(1.0-s, 1.0 - h1*s, 1.0 - h2*s, 1.0 - h3*s, 1.0)
  while(p < stop_freq){
    g_freqs = c((1-p)^4, 4*p*(1 - p)^3, 6*p^2*(1 - p)^2, 4*p^3*(1 - p), p^4)
    tot_fit = sum(fits * g_freqs)
    p_fit = (g_freqs[5] * fits[5]) + 0.75*(g_freqs[4] * fits[4]) + 0.5*(g_freqs[3] * fits[3]) + 0.25*(g_freqs[2] * fits[2])
    p_prime = p_fit/tot_fit
    traj = c(traj,p_prime)
    p = p_prime
  }
  return(traj)
}

getDomCoefs = function(dominance, ploidy = 100){
  if (dominance == 0){
    coeffs = rep(0, ploidy - 1)
  }
  else if (dominance == 1){
    coeffs = rep(1, ploidy - 1)
  }
  else {
    dom = (1 - dominance) - 0.5
    dom = abs((dom * 10 + sign(dom)) ^ sign(dom))
    coeffs = (seq(1, ploidy - 1) / ploidy) ^ dom
  }
  return(coeffs)
}

getStat = function(dat, stat, offset = 25000){
  dat = dat %>% filter(mid > 500000 - offset & mid < 500000 + offset)
  val = max(abs(unlist(dat[,stat])), na.rm = T)
  return(val)
  }

getTraj = function(s, dom, ploidy, start_freq, N = -9, end_freq = 0.99, maxGens = 9999, maxTries = 10){
  dom_coeffs = getDomCoefs(dom, ploidy)
  attempts = 0
  p = start_freq
  k = ploidy
  gen = 0
  while (attempts <= maxTries & p < end_freq & gen <= maxGens){
    df = data.frame("s" = s, "dom" = dom, "gen" = 0, "freq" = start_freq, "dp1" = 0, "w.bar" = 0, "ploidy" = ploidy)
    p = start_freq
    dp1 = 0
    gen = 0
    het_fits = 1 + dom_coeffs * s
    fits = c(1, het_fits, 1 + s) / (1 + s)
    while (p < end_freq & p > 0 & gen <= maxGens){
      q = 1 - p
      i = seq(0, k)
      Num = sum(choose(k, i) * ((k - i) / k) * (p ^ (k - i)) * (q ^ i) * rev(fits))
      Den = sum(choose(k, i) * (p ^ (k - i)) * (q ^ i) * rev(fits))
      p_prime = Num / Den
      if (N != -9){
        p_prime = sum(rbinom(N, k, p_prime)) / (k * N) 
      }
      df = rbind(df, c(s, dom, gen, p, dp1, Den, k))
      dp1 = p_prime - p
      p = p_prime
      gen = gen + 1
    }
    df = rbind(df, c(s, dom, gen, p, dp1, Den, k))
    attempts = attempts + 1
  }
  if (attempts > maxTries & nrow(df) <= maxGens){
    print(paste("Beneficial allele was lost due to drift for", maxTries, "consecutive attempts"))
  }
  if (nrow(df) > maxGens){
    print(paste("Beneficial allele did not fix before the maximum number of generations (", maxGens, ")."))
  }
  return(df[-1,])
}

getDims = function(dat, y.metric = "fst", offset = 100000){
  # dat = data.frame("mid" = mid, "fst" = febugst)
  peak = tryCatch({
    auc(dat$mid, unlist(abs(dat[,y.metric])), from = 500000 - offset, to = 500000 + offset)}
    , error = function(e){
      return(-9)
    })
  return(peak)
}

getUnd = function(dat, y.metric = "fst", offset = 100000){
  # dat = data.frame("mid" = mid, "fst" = febugst)
  dat = dat %>% filter(mid > 500000 - offset & mid < 500000 + offset)
  dat["stat"] = dat[, y.metric]
  val1 = nrow(dat[dat$stat == "-Inf",])
  val2 = nrow(dat[is.na(dat$stat),])
  return(val1+val2)
}

getUnd.h = function(dat, y.metric = "fst", offset = 100000){
  # dat = data.frame("mid" = mid, "fst" = febugst)
  dat = dat %>% filter(POSITION > 500000 - offset & POSITION < 500000 + offset)
  dat["stat"] = dat[, y.metric]
  val1 = nrow(dat[dat$stat == "-Inf",])
  val2 = nrow(dat[is.na(dat$stat),])
  return(val1+val2)
}

wrapEHH = function(files){
  all.sum = data.frame()
  for(i in 1:length(files)){
    print(files[i])
    dat = read.csv(files[i])
    dat.sum = dat %>% mutate(traj_ploidy = as.numeric(str_replace(traj_ploidy, "tp","")), sim_ploidy = as.numeric(str_replace(sim_ploidy, "sp","")), dom = as.numeric(str_replace(dom, "do","")), s = as.numeric(str_replace(s, "se","")), N = as.numeric(str_replace(N, "NN","")), mu = as.numeric(str_replace(mu, "mu","")), recomb = as.numeric(str_replace(recomb, "re","")), sampGen = as.numeric(str_replace(sampGen, "sG","")), fuseGen = as.numeric(str_replace(fuseGen, "fG","")), rep = as.numeric(str_replace(rep, "rep", ""))) %>% filter(!is.na(xpehh.p)) %>% mutate(mid = POSITION) %>% nest(-c(sim_ploidy, rep)) %>% mutate(size.xp = map(data, ~getDims(., y.metric = "XPEHH")), size.xp.p = map(data, ~getDims(., y.metric = "xpehh.p")), med.xp = map(data, ~getStat(., "XPEHH")), med.xpp = map(data, ~log(getStat(., "xpehh.p"))), size.ihs = map(data, ~getDims(., y.metric = "iHS")), size.ihs.p = map(data, ~getDims(., y.metric = "ihs.p")), med.ihs = map(data, ~getStat(., "iHS")), med.ihs.p = map(data, ~log(getStat(., "ihs.p")))) %>% select(-data) %>% unnest()
    all.sum = rbind(all.sum, dat.sum)
    remove(dat)
  }
  return(all.sum)
}

CV <- function(data){
  data = data[is.finite(data)]
  return((sd(data, na.rm=T)/(mean(data, na.rm=T)))*100)
  }

lCV <- function(data, N = 10000, n = 100){
    aa = foreach(i = 1:N, .combine = rbind) %do% {
      ndat = sample(data, n)
      sd(ndat, na.rm=T)/(mean(ndat, na.rm=T))*100}
    return(quantile(aa,0.05, na.rm=T))
}

uCV <- function(data, N = 10000, n = 100){
    aa = foreach(i = 1:N, .combine = rbind) %do% {
      ndat = sample(data, n)
      sd(ndat, na.rm=T)/(mean(ndat, na.rm=T))*100}
    return(quantile(aa,0.95, na.rm=T))
}

#Load data
scaleFUN <- function(x) sprintf("%.1f", x)

pardir = "/Users/pmonnahan/bkup"
ms = read.table(paste(pardir, "/Documents/Research/PloidySim/data/mssel_out_8-27-19.txt", sep = ""), head = T)
ms %<>% mutate(ints = as.numeric(as.character(cut(bp.start, breaks = 50, labels = seq(1,50))))) # label (bin) windows into larger intervals

ms2 = ms %<>% filter(DS != "-9")
ms %<>% filter(DS == "-9")

ds.ehh.files = c(paste(pardir,"/Documents/Research/PloidySim/rehh/rehh_DS.csv", sep = ""))
nds.ehh.files = c(paste(pardir,"/Documents/Research/PloidySim/rehh/rehh_tp2_do0.5_nDS.csv", sep = ""))
traj=read.table("/Users/pmonnahan/bkup//Documents/Research/PloidySim/data/Ploidy_Forward_Sim_results.txt",head=T, sep=",")
rehh = read.csv("/Users/pmonnahan/bkup/Documents/Research/PloidySim/rehh/rehh_calcs_do0.5_fG1_nDS.csv")

ds.ehh = wrapEHH(ds.files)
nds.ehh = wrapEHH(nds.files)
ds.ehh %<>% mutate(DS="yes")
nds.ehh %<>% mutate(DS="no")
ehh = rbind(nds.ehh, ds.ehh)
remove(c(ds.ehh, nds.ehh))
```

# Background {.tabset}

## Sweep trajectories; Figure 1A.

These plots show a primary motivating result for this study, in that higher ploidies show increased fixation times of sweeping beneficial alleles regardless of the dominance scenario being evaluated.

```{r, echo=T,message=F}
#Function creates trajectories

# Param set to create trajectories for
params = data.frame("s" = rep(0.1,9), "dom" = c(rep(1,3), rep(0.5,3), rep(0,3)), "ploidy" = rep(c(2,4,8),3), "start" = rep(0.05, 9))

# Create trajectories
dat1 = foreach(i = 1:nrow(params), .combine=rbind) %do% {
  getTraj(params[i,]$s, params[i,]$dom, params[i,]$ploidy, params[i,]$start, maxGens = 999999)
}

dat1$dom = as.factor(dat1$dom)
dat1$dom = factor(dat1$dom, levels(dat1$dom)[c(3,2,1)])

#All together
dat1 %>% filter(ploidy %in% c(2, 4, 8) & dom %in% c(0, 0.5, 1)) %>% ggplot(., aes(x=gen, y=freq, linetype=as.factor(dom), color=as.factor(ploidy))) + geom_line(size = 1.2) + scale_color_manual(name = "Ploidy", values = c("#F8766D", "#00BA38", "#619CFF")) + scale_linetype_manual(name = "Dominance", labels=c("Dominant", "Additive", "Recessive"), values = c("dashed", "solid", "dotted")) + xlim(0,500) + theme_bw() + xlab("Generation") + ylab("Allele Frequency") + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18),axis.text.x=element_text(size=16),axis.title.x=element_text(size=18),legend.text = element_text(size=16), legend.title = element_text(size=18))

dat2 = foreach(i = 1:nrow(params), .combine=rbind) %do% {
  getFits(params[i,]$s, params[i,]$dom, params[i,]$ploidy)
}

dat2$dom = as.factor(dat2$dom)
dat2$dom = factor(dat2$dom, levels(dat2$dom)[c(3,2,1)])

#Figure 1A right
ggplot(dat2, aes(x=freq, y=var.w, color = as.factor(ploidy), linetype=as.factor(dom))) + geom_line(size = 0.9) + scale_color_discrete(name="Ploidy") + scale_linetype_manual(name="Dominance", labels=c("Dominant","Additive","Recessive"), values = c("dashed", "solid", "dotted")) + xlab("Allele Frequency") + ylab("Variance in Fitness\n") + theme_bw() + theme(axis.text.y=element_blank(), axis.title.y=element_text(size=18),axis.text.x=element_text(size=16),axis.title.x=element_text(size=18),legend.text = element_text(size=16), legend.title = element_text(size=18))

ggplot(dat2, aes(x=freq, y=w.bar, color = as.factor(ploidy), linetype=as.factor(dom))) + geom_line() + scale_color_discrete(name="Ploidy") + scale_linetype_discrete(name="Dominance", labels=c("0.1","0.5","0.9")) + xlab("Allele Frequency") + ylab("Mean Fitness") + theme_bw()
```

## Dominance; Figure 1B

This plot shows the dominance value of each genotype (given by within individual allele frequency) as a function of the dominance scalar.  The purpose was to write a function that would take a single dominance value that could be specified for any ploidy and return a comparable set of dominance coefficients for heterozygous genotypes.

```{r, echo=T,message=F}

doms = c(seq(0,1, 0.1))
Doms = as.data.frame(sapply(doms, getDomCoefs))
Doms = rbind(c(0,0,0,0,0,0,0), Doms, c(1,1,1,1,1,1,1))
colnames(Doms) = doms
Doms = cbind(Doms, data.frame("i/k"=seq(0,100) / 100))
mDoms = melt(Doms, id.var = "i.k")

mDoms$variable = factor(mDoms$variable, levels(mDoms$variable)[c(rev(seq(1,11)))])

mDoms %>% filter(variable %in% c("0.9", "0.6", "0.5", "0.4", "0.1")) %>% ggplot(., aes(x = i.k, y = value, color = variable)) + geom_line(size = 1.2) + scale_color_discrete(name = "Dominance\nScalar", breaks = c("0.9", "0.6", "0.5", "0.4", "0.1"), labels = c("0.4", "0.1", "0", "-0.1", "-0.4")) + theme_bw() + xlab("Individual allele frequency of beneficial allele") + ylab("Dominance Coefficient") + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18),axis.text.x=element_text(size=16),axis.title.x=element_text(size=18),legend.text = element_text(size=16), legend.title = element_text(size=18))
```

## Stochasticity in recessive trajectories; Figure 1C
```{r}
bbR=data.frame(traj=dipTraj(0.05,0.1,0,0.99))
bbR$gen=seq.int(nrow(bbR))
aaR=data.frame(traj=tetTraj(0.05,0.1,0,0,0,0.99))
aaR$gen=seq.int(nrow(aaR))

traj %>% filter(N %in% c(1000,10000) & s == 0.01 & dom == "recessive") %>% ggplot()+geom_line(data=traj[traj$dom == "recessive" & traj$s==0.1 & traj$ploidy==4 & traj$N %in% c(1000,10000),],aes(y=freq,x=gen,group=as.factor(rep)),color="blue",alpha=0.5)+geom_line(data=traj[traj$dom == "recessive" & traj$s==0.1 & traj$ploidy==2 & traj$N %in% c(1000,10000),],aes(y=freq,x=gen,group=as.factor(rep)),color="red",alpha=0.5)+geom_line(data=bbR,aes(y=traj,x=gen), linetype="dashed")+geom_line(data=aaR,aes(y=traj,x=gen))+facet_grid(~N,scales="free_x")+xlab("Generation")+ylab("Frequency")+theme(legend.title = element_text("Ploidy"))+scale_x_log10()
```

## Effect of population size on fixation time; Figure 1D
```{r, echo=T,message=F}
#Stochastic effect of population size on
params2 = data.frame("s" = rep(0.1,12), "dom" = c(rep(0.1,4), rep(0.5,4), rep(0.9,4)), "ploidy" = rep(c(2,4), 6), "start" = rep(0.05, 12), "N" = rep(c(1000, 1000, 10000, 10000), 3))
params2 %<>% dplyr::slice(rep(row_number(), 1000))
# Create trajectories
dat3 = foreach(i = 1:nrow(params2), .combine=rbind) %do% {
  print(params2[i,])
  dat = getTraj(params2[i,]$s, params2[i,]$dom, params2[i,]$ploidy, params2[i,]$start, N = params2[i,]$N, maxGens = 9999999, maxTries = 9999999)
  dat["N"] = params2[i,]$N
  dat[nrow(dat),]
}

dat3 %>%  mutate(Dom = factor(case_when(dom == 0.1 ~ "Partial\nRecessivity (H = -0.4)", dom == 0.5 ~ "Additivity (H = 0)", dom == 0.9 ~ "Partial\nDominance (H = 0.4)"), levels = c("Partial\nRecessivity (H = -0.4)", "Additivity (H = 0)", "Partial\nDominance (H = 0.4)"))) %>% ggplot(aes(y = log(gen), fill = as.factor(N), x = as.factor(ploidy))) + geom_boxplot(outlier.size = 0.5) + facet_wrap(~Dom) + ylab("Log(Time to Fixation)") + xlab("Ploidy") + scale_fill_discrete(name = "N")+ theme_bw() + theme(axis.text.y=element_text(size=14), axis.title.y=element_text(size=16),axis.text.x=element_text(size=14),axis.title.x=element_text(size=16),legend.text = element_text(size=14), legend.title = element_text(size=16), strip.text = element_text(size=12))

```

---

# mssel analysis

### Variable key
* N = Population size

* s = selection coefficient; difference in fitness between alternative homozygotes

* dom = dominance scalar; a single value that determines the dominance coefficients of heterozygous genotypes for an arbitrary ploidy

* recomb = per-base recombination rate

* mu = per-base mutation rate.  Theta is ploidy x mu x N (x sequence length which is 1Mb)

* sim_ploidy = **Simulation Ploidy**; ploidy used for mssel simulation.  Value used in calculating theta above

* traj_ploidy = **Trajectory Ploidy**; ploidy used to generate sweep trajectory.  see getTraj() function in PloidyHitch.R

* sampGen = sampling generation; number of generations passed since selection ends (i.e. fixation of beneficial allele)

* fuseGen = fuse generation; number of generations prior to start of sweep that the two populations fused.

**Simulation Ploidy** and **Trajectory Ploidy** are the two focal variables.  The former refers to the ploidy value used to scale population parameters when running mssel.  For example, theta = 2(N)(mu)(sim_ploidy).  The latter refers to the ploidy used for simulating the sweep trajectory, which is subsequently passed to mssel.

## Figure 2A.  
```{r, echo=T,message=F}
#Figure 2A Smoothed diversity versus position
ms %>% filter(traj_ploidy==sim_ploidy & sampGen == "1" & dom == "0.5" & N == 10000) %>% ggplot(., aes(y=Pi.1 * 100, color = as.factor(sim_ploidy), x = mid/100000, linetype = as.factor(s))) + geom_smooth(method="loess", size = 0.9, span=0.1, se=F) + scale_x_continuous(breaks=c(1,5,9), limits = c(0.2,9.8)) + xlab("Position (100 kb)") + ylab("Diversity (%)") + scale_linetype_discrete(name="Selection\nCoefficient") + scale_color_discrete(name="Ploidy") + theme_bw() + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18),axis.text.x=element_text(size=16),axis.title.x=element_text(size=18),legend.text = element_text(size=16), legend.title = element_text(size=18))
```

#Figure 2B
```{r}
MS2.a = ms %>% group_by(s, dom, recomb, N, mu, sim_ploidy, traj_ploidy, sampGen, fuseGen, rep, driftGen) %>% summarize(depth.pi = mean(Pi.2,na.rm=T) - min(Pi.1), min.pi = min(Pi.1, na.rm=T), max.taj = abs(min(Tajima.D_1, na.rm = T)), height.fst = max(fst, na.rm = T) - mean(fst, na.rm = T))

MS2.b = ms %>% group_by(s, dom, recomb, N, mu, sim_ploidy, traj_ploidy, sampGen, fuseGen, driftGen, rep, ints) %>% summarize(lessWind.pi = ifelse(mean(Pi.1, na.rm=T) < (mean(Pi.2, na.rm=T) / 2),1,0), lessWind.taj = ifelse(mean(Tajima.D_1, na.rm=T) < -1, 1, 0))

MS2.c = MS2.b %>% group_by(s, dom, recomb, N, mu, sim_ploidy, traj_ploidy, sampGen, fuseGen, driftGen, rep) %>% summarize(breadth.pi = sum(lessWind.pi) * 20000, breadth.taj = sum(lessWind.taj) * 20000)

MS2.f = merge(MS2.a, MS2.c, by = c("s", "dom", "recomb", "N", "mu", "sim_ploidy", "traj_ploidy", "sampGen", "fuseGen", "driftGen", "rep"))

MS2.f %<>% mutate(same_ploidy = ifelse(sim_ploidy==traj_ploidy, "yellow", "black"))

#disentangling
MS2.f %>% filter(mu==1e-08 & N == 10000 & s =="0.01" & driftGen %in% c(0,1) & sampGen == 1 & dom %in% c(0.5)) %>% mutate(Height = (log(min.pi, 10)), Breadth = breadth.pi/10000, Magnitude = depth.pi) %>% select(sim_ploidy, traj_ploidy, Magnitude, Breadth, same_ploidy) %>% melt(., id.var = c("sim_ploidy", "traj_ploidy", "same_ploidy")) %>% ggplot(., aes(y = value, fill = as.factor(traj_ploidy), x = as.factor(sim_ploidy), color = same_ploidy)) + geom_boxplot(outlier.shape = NA) + scale_fill_manual(name = "Trajectory Ploidy", values = wes_palette("Moonrise2")) + scale_color_manual(guide=F, values = c("black", "red")) + facet_wrap(~variable, scales = "free_y") + ylab("") + xlab("\n\n") + theme_bw() + theme(axis.text.y=element_text(size = 16), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18), legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16))
```

#Figure 2C
```{r}
ff = rehh %>% filter(!is.na(xpehh.p) & sampGen!=1000) %>% mutate(mid = POSITION) %>% nest(-c(s, dom, recomb, N, mu, sim_ploidy, traj_ploidy, sampGen, fuseGen, driftGen)) %>% mutate(size.xp = map(data, ~getDims(., y.metric = "XPEHH")), size.xp.p = map(data, ~getDims(., y.metric = "xpehh.p")), med.xp = map(data, ~getStat(., "XPEHH")), med.xpp = map(data, ~log(getStat(., "xpehh.p"))), size.ihs = map(data, ~getDims(., y.metric = "iHS")), size.ihs.p = map(data, ~getDims(., y.metric = "ihs.p")), med.ihs = map(data, ~getStat(., "iHS")), med.ihs.p = map(data, ~log(getStat(., "ihs.p"))), rep = driftGen) %>% select(-c(data, driftGen)) %>% unnest()

ff %<>% mutate(traj_ploidy = as.numeric(str_replace(traj_ploidy, "tp","")), sim_ploidy = as.numeric(str_replace(sim_ploidy, "sp","")), dom = as.numeric(str_replace(dom, "do","")), s = as.numeric(str_replace(s, "se","")), N = as.numeric(str_replace(N, "NN","")), mu = as.numeric(str_replace(mu, "mu","")), recomb = as.numeric(str_replace(recomb, "re","")), sampGen = as.numeric(str_replace(sampGen, "sG","")), fuseGen = as.numeric(str_replace(fuseGen, "fG","")), rep = as.numeric(str_replace(rep, "rep", "")))

ee = ms %>% filter(sampGen==1 & driftGen == 0 & fuseGen %in% c(1,1000,10000) & dom %in% c(0.1, 0.5, 0.9)) %>% group_by(s, dom, recomb, N, mu, sim_ploidy, traj_ploidy, sampGen, fuseGen, rep, driftGen) %>% mutate(Div = mean(Pi.2) - Pi.1, Tajima.D_1 = abs(Tajima.D_1)) %>% ungroup() %>% nest(-c(s, dom, recomb, N, mu, sim_ploidy, traj_ploidy, sampGen, fuseGen, rep, driftGen)) %>% mutate(size.div = map(data, ~getDims(., y.metric = "Div")), size.taj = map(data, ~getDims(., y.metric = "Tajima.D_1")), size.h = map(data, ~getDims(., y.metric = "Fay.Wu.H_1")), size.e = map(data, ~getDims(., y.metric = "Zeng.E_1")), size.fst = map(data, ~getDims(., y.metric = "fst")), size.dxy = map(data, ~getDims(., y.metric = "dxy.1.2")), med.d = map(data, ~getStat(., "Tajima.D_1")), med.e = map(data, ~getStat(., "Zeng.E_1")), med.h = map(data, ~getStat(., "Fay.Wu.H_1")), med.fst = map(data, ~getStat(., "fst")), med.dxy = map(data, ~getStat(., "dxy.1.2"))) %>% select(-data) %>% unnest()

kk = merge(ee, ff, by = c("traj_ploidy", "sim_ploidy", "dom", "s", "N", "mu", "recomb", "sampGen", "fuseGen", "rep"), all.x = T)

kk.points = kk %>% filter(dom %in% c("0.1", "0.5", "0.9") & traj_ploidy == sim_ploidy & s == "0.01" & recomb == "1e-08" & N=="1000" & driftGen == 0 & sampGen == 1)  %>% mutate("TajD" = size.taj, "FayWuH" = size.h, "ZengsE" = size.e, "Fst" = size.fst, "XPEHH" = size.xp, "Diversity" = size.div * 10) %>% select(sim_ploidy, dom, TajD, FayWuH, ZengsE, Fst, XPEHH, Diversity) %>% melt(., id.var = c("sim_ploidy", "dom")) %>% mutate("PeakSize" = variable) %>% filter(value != -9) %>% group_by(sim_ploidy, dom, variable) %>% summarize(median = median(value)) %>% mutate(PeakSize = variable)

#Just diversity for panel
kk %>% filter(dom %in% c(0.1, 0.5, 0.9) & traj_ploidy == sim_ploidy & s == "0.01" & N=="10000" & driftGen == 0 & sampGen == 1 & recomb == 1e-08 & fuseGen == 1) %>% mutate("Diversity" = size.div, same_ploidy = ifelse(sim_ploidy == traj_ploidy, 1, 0)) %>% select(sim_ploidy, dom, Diversity) %>% melt(., id.var = c("sim_ploidy", "dom")) %>% mutate("PeakSize" = variable) %>% filter(value != -9) %>% ggplot(., aes(y = value, fill = as.factor(dom), x = as.factor(sim_ploidy))) + geom_boxplot(outlier.shape = NA) + geom_point(data = kk.points[kk.points$variable == "Diversity",], aes(y = median, x = as.factor(sim_ploidy)), position = position_dodge(width = 0.8), size = 2, shape = 4) + scale_fill_manual(name = "Dominance\nScalar", values = wes_palette("Royal1"), labels = c("-0.4 (Recessive)", "\n0 (Additive)\n", "0.4 (Dominant)")) + ylab("Peak Area") + xlab("Ploidy") + theme_bw() + theme(axis.text.y=element_text(size = 12), axis.title.y=element_text(size=14), axis.text.x=element_text(size=12), axis.title.x=element_text(size=14), legend.text = element_text(size=12), legend.title = element_text(size=14), strip.text = element_text(size=16))

```

#Figure 2E
```{r}
ds = ms2 %>% group_by(sim_ploidy, DS, rep) %>% mutate(Div = mean(Pi.2) - Pi.1, Tajima.D_1 = abs(Tajima.D_1), Fst = scale(fst)) %>% ungroup() %>% nest(-c(sim_ploidy, DS, rep)) %>% mutate(size.div = map(data, ~getDims(., y.metric = "Div")), size.taj = map(data, ~getDims(., y.metric = "Tajima.D_1")), size.h = map(data, ~getDims(., y.metric = "Fay.Wu.H_1")), size.e = map(data, ~getDims(., y.metric = "Zeng.E_1")), size.fst = map(data, ~getDims(., y.metric = "Fst")), size.dxy = map(data, ~getDims(., y.metric = "dxy.1.2")), med.d = map(data, ~getStat(., "Tajima.D_1")), med.e = map(data, ~getStat(., "Zeng.E_1")), med.h = map(data, ~getStat(., "Fay.Wu.H_1")), med.fst = map(data, ~getStat(., "Fst")), med.dxy = map(data, ~getStat(., "dxy.1.2"))) %>% select(-data) %>% unnest()

ms2 = merge(ds, ehh, by = c("sim_ploidy", "DS", "rep"), all = T)

MS6.1 = ms2 %>% mutate("TajD" = med.d, "FayWuH" = med.h, "ZengsE" = med.e, "Fst" = med.fst, "Dxy" = med.dxy, "XPEHH" = med.xp, "iHS" = med.ihs) %>% select(sim_ploidy, DS, TajD, ZengsE, FayWuH, Fst, Dxy, XPEHH, iHS) %>% group_by(sim_ploidy, DS) %>% summarize_all(c("CV", "lCV", "uCV"))

MS6.1 %>% melt(., id.var = c("sim_ploidy", "DS")) %>% separate(variable, c("variable","XX"), "_") %>% spread(XX, value) %>% filter(variable %in% c("TajD", "Fst", "iHS", "XPEHH")) %>% mutate(Variable = factor(variable, levels=c("TajD", "Fst", "iHS", "XPEHH"))) %>% ggplot(., aes(y = CV, fill = as.factor(DS), x = as.factor(sim_ploidy))) + geom_bar(stat="identity", position = position_dodge()) + geom_errorbar(aes(ymin = lCV, ymax = uCV, width = 0.5), position = position_dodge(width = 0.9)) + scale_fill_discrete(name = "Sampling", labels=c("Equal Individuals", "Equal Alleles")) + scale_y_continuous(labels=scaleFUN) + ylab("CV[MaxValue]") + xlab("Ploidy") + facet_wrap(~Variable, scales = "free", shrink = T, nrow = 1) + theme_bw() + theme(axis.text.y=element_blank(), axis.title.y=element_text(size=16), axis.text.x=element_text(size=14), axis.title.x=element_text(size=16), legend.text = element_text(size=13), legend.title = element_text(size=14), strip.text = element_text(size=14))
```

#Figure 2D
```{r}
dd = ms %>% filter(sim_ploidy == traj_ploidy & fuseGen==1 & s == "0.01" & recomb == "1e-08" & N=="10000" & driftGen == 0 & sampGen %in% c(1,1000,10000)) %>% group_by(s, dom, recomb, N, mu, sim_ploidy, traj_ploidy, sampGen, fuseGen, rep, driftGen) %>% mutate(Fst = scale(fst)) %>% ungroup() %>% nest(-c(s, dom, recomb, N, mu, sim_ploidy, traj_ploidy, sampGen, fuseGen, rep, driftGen)) %>% mutate(size.taj = map(data, ~getDims(., y.metric = "Tajima.D_1")), size.h = map(data, ~getDims(., y.metric = "Fay.Wu.H_1")), size.e = map(data, ~getDims(., y.metric = "Zeng.E_1")), size.fst = map(data, ~getDims(., y.metric = "Fst")), size.dxy = map(data, ~getDims(., y.metric = "dxy.1.2")), med.d = map(data, ~getStat(., "Tajima.D_1")), med.e = map(data, ~getStat(., "Zeng.E_1")), med.h = map(data, ~getStat(., "Fay.Wu.H_1")), med.fst = map(data, ~getStat(., "Fst")), med.dxy = map(data, ~getStat(., "dxy.1.2"))) %>% select(-data) %>% unnest()

#Combined sample gen figures
kkk = merge(dd, ff, by = c("traj_ploidy", "sim_ploidy", "dom", "s", "N", "mu", "recomb", "sampGen", "fuseGen", "rep"), all = T)

kkk.1 = kkk %>% filter(dom == 0.5 & traj_ploidy == sim_ploidy & s == "0.01" & N=="10000" & driftGen == 0 & recomb == 1e-08)  %>% mutate("TajD" = med.d, "FayWuH" = med.h, "ZengsE" = med.e, "Fst" = med.fst, "Dxy" = med.dxy, "XPEHH" = med.xp, "iHS" = med.ihs) %>% select(sim_ploidy, sampGen, TajD, ZengsE, FayWuH, Fst, Dxy, XPEHH, iHS) %>% melt(., id.var = c("sim_ploidy", "sampGen")) %>% mutate(stat = "MaxValue")

kkk.med.points = kkk %>% filter(dom == 0.5 & traj_ploidy == sim_ploidy & s == "0.01" & N=="10000" & driftGen == 0 & recomb == 1e-08)  %>% mutate("TajD" = med.d, "FayWuH" = med.h, "ZengsE" = med.e, "Fst" = med.fst, "Dxy" = med.dxy, "XPEHH" = med.xp, "iHS" = med.ihs) %>% select(sim_ploidy, sampGen, TajD, ZengsE, FayWuH, Fst, Dxy, XPEHH, iHS) %>% melt(., id.var = c("sim_ploidy", "sampGen")) %>% mutate(stat = "MaxValue") %>% group_by(sim_ploidy, sampGen, variable) %>% summarize(value = median(value, na.rm=T))

kkk.2 = kkk %>% filter(dom == 0.5 & traj_ploidy == sim_ploidy & s == "0.01" & N=="10000" & driftGen == 0 & recomb == 1e-08)  %>% mutate("TajD" = size.taj, "FayWuH" = size.h, "ZengsE" = size.e, "Fst" = size.fst, "Dxy" = size.dxy, "XPEHH" = size.xp, "iHS" = size.ihs) %>% select(sim_ploidy, sampGen, TajD, ZengsE, FayWuH, Fst, Dxy, XPEHH, iHS) %>% melt(., id.var = c("sim_ploidy", "sampGen")) %>% mutate(stat = "AUC")

kkk.3 = rbind(kkk.1, kkk.2)

#Combined AUC and MaxValue
kkk.3 %>% filter(variable %in% c("sim_ploidy", "sampGen", "TajD", "Fst", "iHS", "XPEHH") & stat == "AUC") %>% mutate(variable = factor(variable, levels = c("TajD", "Fst", "iHS", "XPEHH"))) %>% ggplot(., aes(y = value / 100000, fill = as.factor(sampGen), x = as.factor(sim_ploidy))) + geom_boxplot(outlier.shape = NA) + geom_point(data = kkk.med.points[kkk.med.points$variable %in% c("TajD", "Fst", "iHS", "XPEHH"),], aes(y = value), shape = 4, position = position_dodge(width = 0.8)) + scale_fill_manual(name = "Generations\nsince Fixation", values = wes_palette("Royal2")) + scale_y_continuous(labels=scaleFUN) + ylab("Peak Size") + xlab("Ploidy") + facet_wrap(~variable, scales = "free", shrink = T, nrow = 1) + theme_bw() + theme(axis.text.y=element_text(size = 12), axis.title.y=element_text(size=16), axis.text.x=element_text(size=13), axis.title.x=element_text(size = 16), legend.text = element_text(size=13), legend.title = element_text(size=14), strip.text = element_text(size=14))
```

### 2019-10-12 analysis/PaperFigures.Rmd
resubmission changes

@@
 
+getStat = function(dat, stat, offset = 25000){
+  dat = dat %>% filter(mid > 500000 - offset & mid < 500000 + offset)
+  val = max(abs(unlist(dat[,stat])), na.rm = T)
+  return(val)
+  }
+
 wrapEHH = function(files){
@@
     dat = read.csv(files[i])
-    dat.sum = dat %>% mutate(traj_ploidy = as.numeric(str_replace(traj_ploidy, "tp","")), sim_ploidy = as.numeric(str_replace(sim_ploidy, "sp","")), dom = as.numeric(str_replace(dom, "do","")), s = as.numeric(str_replace(s, "se","")), N = as.numeric(str_replace(N, "NN","")), mu = as.numeric(str_replace(mu, "mu","")), recomb = as.numeric(str_replace(recomb, "re","")), sampGen = as.numeric(str_replace(sampGen, "sG","")), fuseGen = as.numeric(str_replace(fuseGen, "fG","")), rep = as.numeric(str_replace(rep, "rep", ""))) %>% filter(!is.na(xpehh.p)) %>% mutate(mid = POSITION) %>% nest(-c(sim_ploidy, rep)) %>% mutate(size.xp = map(data, ~getDims(., y.metric = "XPEHH")), size.xp.p = map(data, ~getDims(., y.metric = "xpehh.p")), med.xp = map(data, ~getStat(., "XPEHH")), med.xpp = map(data, ~log(getStat(., "xpehh.p"))), size.ihs = map(data, ~getDims(., y.metric = "iHS")), size.ihs.p = map(data, ~getDims(., y.metric = "ihs.p")), med.ihs = map(data, ~getStat(., "iHS")), med.ihs.p = map(data, ~log(getStat(., "ihs.p")))) %>% select(-data) %>% unnest()
+    dat.sum = dat %>% mutate(traj_ploidy = as.numeric(str_replace(traj_ploidy, "tp","")), sim_ploidy = as.numeric(str_replace(sim_ploidy, "sp","")), dom = as.numeric(str_replace(dom, "do","")), s = as.numeric(str_replace(s, "se","")), N = as.numeric(str_replace(N, "NN","")), mu = as.numeric(str_replace(mu, "mu","")), recomb = as.numeric(str_replace(recomb, "re","")), sampGen = as.numeric(str_replace(sampGen, "sG","")), fuseGen = as.numeric(str_replace(fuseGen, "fG","")), rep = as.numeric(str_replace(rep, "rep", ""))) %>% filter(!is.na(xpehh.p)) %>% mutate(mid = POSITION) %>% nest(-c(sim_ploidy, dom, rep)) %>% mutate(size.xp = map(data, ~getDims(., y.metric = "XPEHH")), size.xp.p = map(data, ~getDims(., y.metric = "xpehh.p")), med.xp = map(data, ~getStat(., "XPEHH")), med.xpp = map(data, ~log(getStat(., "xpehh.p"))), size.ihs = map(data, ~getDims(., y.metric = "IHS")), size.ihs.p = map(data, ~getDims(., y.metric = "ihs.p")), med.ihs = map(data, ~getStat(., "IHS")), med.ihs.p = map(data, ~log(getStat(., "ihs.p")))) %>% select(-data) %>% unnest()
     all.sum = rbind(all.sum, dat.sum)
@@
 
-pardir = "/Users/pmonnahan/bkup"
-ms = read.table(paste(pardir, "/Documents/Research/PloidySim/data/mssel_out_8-27-19.txt", sep = ""), head = T)
+# pardir = "/Users/..." #Directory where data files are located
+pardir = "~/Documents/Research/PloidySim/data/"
+ms = read.table(paste(pardir, "mssel_out_10-4-19.txt", sep = ""), head = T)
 ms %<>% mutate(ints = as.numeric(as.character(cut(bp.start, breaks = 50, labels = seq(1,50))))) # label (bin) windows into larger intervals
 
-ms2 = ms %<>% filter(DS != "-9")
+ms2 = ms %>% filter(DS != "-9")
 ms %<>% filter(DS == "-9")
 
-ds.ehh.files = c(paste(pardir,"/Documents/Research/PloidySim/rehh/rehh_DS.csv", sep = ""))
-nds.ehh.files = c(paste(pardir,"/Documents/Research/PloidySim/rehh/rehh_tp2_do0.5_nDS.csv", sep = ""))
-traj=read.table("/Users/pmonnahan/bkup//Documents/Research/PloidySim/data/Ploidy_Forward_Sim_results.txt",head=T, sep=",")
-rehh = read.csv("/Users/pmonnahan/bkup/Documents/Research/PloidySim/rehh/rehh_calcs_do0.5_fG1_nDS.csv")
+ds.ehh.files = c(paste(pardir,"rehh_DS.csv", sep = ""))
+nds.ehh.files = c(paste(pardir,"rehh_nDS.csv", sep = ""))
+traj=read.table(paste(pardir, "Ploidy_Forward_Sim_results.txt", sep = ""),head=T, sep=",")
 
-ds.ehh = wrapEHH(ds.files)
-nds.ehh = wrapEHH(nds.files)
+rehh = read.csv(paste(pardir, "rehh_calcs_do0.5_fG1_nDS.csv", sep=""))
+
+ds.ehh = wrapEHH(ds.ehh.files)
+nds.ehh = wrapEHH(nds.ehh.files)
 ds.ehh %<>% mutate(DS="yes")
@@
 ehh = rbind(nds.ehh, ds.ehh)
-remove(c(ds.ehh, nds.ehh))
+remove(ds.ehh)
+remove(nds.ehh)
 ```
-
-# Background {.tabset}
 
@@
 dat1 = foreach(i = 1:nrow(params), .combine=rbind) %do% {
-  getTraj(params[i,]$s, params[i,]$dom, params[i,]$ploidy, params[i,]$start, maxGens = 999999)
+  getTraj(params[i,]$s, params[i,]$dom, params[i,]$ploidy, params[i,]$start, maxGens = 99999, maxTries = 1)
 }
@@
 
-#All together
+#Figure 1A left
 dat1 %>% filter(ploidy %in% c(2, 4, 8) & dom %in% c(0, 0.5, 1)) %>% ggplot(., aes(x=gen, y=freq, linetype=as.factor(dom), color=as.factor(ploidy))) + geom_line(size = 1.2) + scale_color_manual(name = "Ploidy", values = c("#F8766D", "#00BA38", "#619CFF")) + scale_linetype_manual(name = "Dominance", labels=c("Dominant", "Additive", "Recessive"), values = c("dashed", "solid", "dotted")) + xlim(0,500) + theme_bw() + xlab("Generation") + ylab("Allele Frequency") + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18),axis.text.x=element_text(size=16),axis.title.x=element_text(size=18),legend.text = element_text(size=16), legend.title = element_text(size=18))
@@
 **Simulation Ploidy** and **Trajectory Ploidy** are the two focal variables.
-The former refers to the ploidy value used to scale population parameters when running mssel.
+The former refers to the ploidy value  %<>%  %>%used to scale population parameters when running mssel.
 For example, theta = 2(N)(mu)(sim_ploidy).
@@
 #disentangling
-MS2.f %>% filter(mu==1e-08 & N == 10000 & s =="0.01" & driftGen %in% c(0,1) & sampGen == 1 & dom %in% c(0.5)) %>% mutate(Height = (log(min.pi, 10)), Breadth = breadth.pi/10000, Magnitude = depth.pi) %>% select(sim_ploidy, traj_ploidy, Magnitude, Breadth, same_ploidy) %>% melt(., id.var = c("sim_ploidy", "traj_ploidy", "same_ploidy")) %>% ggplot(., aes(y = value, fill = as.factor(traj_ploidy), x = as.factor(sim_ploidy), color = same_ploidy)) + geom_boxplot(outlier.shape = NA) + scale_fill_manual(name = "Trajectory Ploidy", values = wes_palette("Moonrise2")) + scale_color_manual(guide=F, values = c("black", "red")) + facet_wrap(~variable, scales = "free_y") + ylab("") + xlab("\n\n") + theme_bw() + theme(axis.text.y=element_text(size = 16), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18), legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16))
+# MS2.f %>% filter(mu==1e-08 & N == 10000 & s =="0.01" & driftGen %in% c(0,1) & sampGen == 1 & dom %in% c(0.5)) %>% mutate(Height = (log(min.pi, 10)), Breadth = breadth.pi/10000, Magnitude = depth.pi) %>% select(sim_ploidy, traj_ploidy, Magnitude, Breadth, same_ploidy) %>% melt(., id.var = c("sim_ploidy", "traj_ploidy", "same_ploidy")) %>% ggplot(., aes(y = value, fill = as.factor(traj_ploidy), x = as.factor(sim_ploidy), color = same_ploidy)) + geom_boxplot(outlier.shape = NA) + scale_fill_manual(name = "Trajectory Ploidy", values = wes_palette("Moonrise2")) + scale_x_discrete(name = expression(paste(theta)), labels = c(expression(paste("4x10", "^-4")), expression(paste("8x10", "^-4")), expression(paste("16x10", "^-4")))) + scale_color_manual(guide=F, values = c("black", "red")) + facet_wrap(~variable, scales = "free_y") + ylab("") + xlab("\n\n") + theme_bw() + theme(axis.text.y=element_text(size = 16), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18), legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16))
+
+MS2.f %>% filter(mu==1e-08 & N == 10000 & s =="0.01" & driftGen %in% c(0,1) & sampGen == 1 & dom %in% c(0.5)) %>% mutate(Height = (log(min.pi, 10)), Breadth = breadth.pi/100000, Magnitude = depth.pi * 100) %>% select(sim_ploidy, traj_ploidy, Magnitude, Breadth, same_ploidy) %>% melt(., id.var = c("sim_ploidy", "traj_ploidy", "same_ploidy")) %>% ggplot(., aes(y = value, fill = as.factor(traj_ploidy), x = as.factor(sim_ploidy))) + geom_boxplot(outlier.shape = NA) + scale_fill_manual(name = "Sweep\nTrajectory", values = wes_palette("Moonrise2"), labels = c("Diploid", "Tetraploid", "Octaploid")) + scale_x_discrete(name = expression(paste(theta," = ", rho)), labels = c(expression(paste("4x10"^"-4")), expression(paste("8x10"^"-4")), expression(paste("16x10"^"-4")))) + scale_color_manual(guide=F, values = c("black", "red")) + facet_wrap(~variable, scales = "free_y") + ylab("") + xlab("\n\n") + theme_bw() + theme(axis.text.y=element_text(size = 14), axis.title.y=element_text(size=18), axis.text.x=element_text(size=14), axis.title.x=element_text(size=22), legend.text = element_text(size=12), legend.title = element_text(size=14), strip.text = element_text(size=14))
 ```
@@
 ```{r}
-ff = rehh %>% filter(!is.na(xpehh.p) & sampGen!=1000) %>% mutate(mid = POSITION) %>% nest(-c(s, dom, recomb, N, mu, sim_ploidy, traj_ploidy, sampGen, fuseGen, driftGen)) %>% mutate(size.xp = map(data, ~getDims(., y.metric = "XPEHH")), size.xp.p = map(data, ~getDims(., y.metric = "xpehh.p")), med.xp = map(data, ~getStat(., "XPEHH")), med.xpp = map(data, ~log(getStat(., "xpehh.p"))), size.ihs = map(data, ~getDims(., y.metric = "iHS")), size.ihs.p = map(data, ~getDims(., y.metric = "ihs.p")), med.ihs = map(data, ~getStat(., "iHS")), med.ihs.p = map(data, ~log(getStat(., "ihs.p"))), rep = driftGen) %>% select(-c(data, driftGen)) %>% unnest()
+ff = rehh %>% filter(!is.na(xpehh.p) & sampGen!=1000) %>% mutate(mid = POSITION) %>% nest(-c(s, dom, recomb, N, mu, sim_ploidy, traj_ploidy, sampGen, fuseGen, rep)) %>% mutate(size.xp = map(data, ~getDims(., y.metric = "XPEHH")), size.xp.p = map(data, ~getDims(., y.metric = "xpehh.p")), med.xp = map(data, ~getStat(., "XPEHH")), med.xpp = map(data, ~log(getStat(., "xpehh.p"))), size.ihs = map(data, ~getDims(., y.metric = "IHS")), size.ihs.p = map(data, ~getDims(., y.metric = "ihs.p")), med.ihs = map(data, ~getStat(., "IHS")), med.ihs.p = map(data, ~log(getStat(., "ihs.p")))) %>% select(-c(data)) %>% unnest()
 
@@
 #Just diversity for panel
-kk %>% filter(dom %in% c(0.1, 0.5, 0.9) & traj_ploidy == sim_ploidy & s == "0.01" & N=="10000" & driftGen == 0 & sampGen == 1 & recomb == 1e-08 & fuseGen == 1) %>% mutate("Diversity" = size.div, same_ploidy = ifelse(sim_ploidy == traj_ploidy, 1, 0)) %>% select(sim_ploidy, dom, Diversity) %>% melt(., id.var = c("sim_ploidy", "dom")) %>% mutate("PeakSize" = variable) %>% filter(value != -9) %>% ggplot(., aes(y = value, fill = as.factor(dom), x = as.factor(sim_ploidy))) + geom_boxplot(outlier.shape = NA) + geom_point(data = kk.points[kk.points$variable == "Diversity",], aes(y = median, x = as.factor(sim_ploidy)), position = position_dodge(width = 0.8), size = 2, shape = 4) + scale_fill_manual(name = "Dominance\nScalar", values = wes_palette("Royal1"), labels = c("-0.4 (Recessive)", "\n0 (Additive)\n", "0.4 (Dominant)")) + ylab("Peak Area") + xlab("Ploidy") + theme_bw() + theme(axis.text.y=element_text(size = 12), axis.title.y=element_text(size=14), axis.text.x=element_text(size=12), axis.title.x=element_text(size=14), legend.text = element_text(size=12), legend.title = element_text(size=14), strip.text = element_text(size=16))
+kk %>% filter(dom %in% c(0.1, 0.5, 0.9) & traj_ploidy == sim_ploidy & s == "0.1" & N=="10000" & driftGen == 0 & sampGen == 1 & recomb == 1e-08 & fuseGen == 1) %>% mutate("Diversity" = size.div, same_ploidy = ifelse(sim_ploidy == traj_ploidy, 1, 0)) %>% select(sim_ploidy, dom, Diversity) %>% melt(., id.var = c("sim_ploidy", "dom")) %>% mutate("PeakSize" = variable) %>% filter(value != -9) %>% ggplot(., aes(y = value, fill = as.factor(dom), x = as.factor(sim_ploidy))) + geom_boxplot(outlier.shape = NA) + geom_point(data = kk.points[kk.points$variable == "Diversity",], aes(y = median, x = as.factor(sim_ploidy)), position = position_dodge(width = 0.8), size = 2, shape = 23, color="cyan") + scale_fill_manual(name = "Dominance\nScalar", values = wes_palette("Royal1"), labels = c("-0.4 (Recessive)", "\n0 (Additive)\n", "0.4 (Dominant)")) + ylab("Peak Area") + xlab("Ploidy") + theme_bw() + theme(axis.text.y=element_text(size = 12), axis.title.y=element_text(size=14), axis.text.x=element_text(size=12), axis.title.x=element_text(size=14), legend.text = element_text(size=12), legend.title = element_text(size=14), strip.text = element_text(size=16))
 
-```
-
-#Figure 2E
-```{r}
-ds = ms2 %>% group_by(sim_ploidy, DS, rep) %>% mutate(Div = mean(Pi.2) - Pi.1, Tajima.D_1 = abs(Tajima.D_1), Fst = scale(fst)) %>% ungroup() %>% nest(-c(sim_ploidy, DS, rep)) %>% mutate(size.div = map(data, ~getDims(., y.metric = "Div")), size.taj = map(data, ~getDims(., y.metric = "Tajima.D_1")), size.h = map(data, ~getDims(., y.metric = "Fay.Wu.H_1")), size.e = map(data, ~getDims(., y.metric = "Zeng.E_1")), size.fst = map(data, ~getDims(., y.metric = "Fst")), size.dxy = map(data, ~getDims(., y.metric = "dxy.1.2")), med.d = map(data, ~getStat(., "Tajima.D_1")), med.e = map(data, ~getStat(., "Zeng.E_1")), med.h = map(data, ~getStat(., "Fay.Wu.H_1")), med.fst = map(data, ~getStat(., "Fst")), med.dxy = map(data, ~getStat(., "dxy.1.2"))) %>% select(-data) %>% unnest()
-
-ms2 = merge(ds, ehh, by = c("sim_ploidy", "DS", "rep"), all = T)
-
-MS6.1 = ms2 %>% mutate("TajD" = med.d, "FayWuH" = med.h, "ZengsE" = med.e, "Fst" = med.fst, "Dxy" = med.dxy, "XPEHH" = med.xp, "iHS" = med.ihs) %>% select(sim_ploidy, DS, TajD, ZengsE, FayWuH, Fst, Dxy, XPEHH, iHS) %>% group_by(sim_ploidy, DS) %>% summarize_all(c("CV", "lCV", "uCV"))
-
-MS6.1 %>% melt(., id.var = c("sim_ploidy", "DS")) %>% separate(variable, c("variable","XX"), "_") %>% spread(XX, value) %>% filter(variable %in% c("TajD", "Fst", "iHS", "XPEHH")) %>% mutate(Variable = factor(variable, levels=c("TajD", "Fst", "iHS", "XPEHH"))) %>% ggplot(., aes(y = CV, fill = as.factor(DS), x = as.factor(sim_ploidy))) + geom_bar(stat="identity", position = position_dodge()) + geom_errorbar(aes(ymin = lCV, ymax = uCV, width = 0.5), position = position_dodge(width = 0.9)) + scale_fill_discrete(name = "Sampling", labels=c("Equal Individuals", "Equal Alleles")) + scale_y_continuous(labels=scaleFUN) + ylab("CV[MaxValue]") + xlab("Ploidy") + facet_wrap(~Variable, scales = "free", shrink = T, nrow = 1) + theme_bw() + theme(axis.text.y=element_blank(), axis.title.y=element_text(size=16), axis.text.x=element_text(size=14), axis.title.x=element_text(size=16), legend.text = element_text(size=13), legend.title = element_text(size=14), strip.text = element_text(size=14))
 ```
@@
 #Combined AUC and MaxValue
-kkk.3 %>% filter(variable %in% c("sim_ploidy", "sampGen", "TajD", "Fst", "iHS", "XPEHH") & stat == "AUC") %>% mutate(variable = factor(variable, levels = c("TajD", "Fst", "iHS", "XPEHH"))) %>% ggplot(., aes(y = value / 100000, fill = as.factor(sampGen), x = as.factor(sim_ploidy))) + geom_boxplot(outlier.shape = NA) + geom_point(data = kkk.med.points[kkk.med.points$variable %in% c("TajD", "Fst", "iHS", "XPEHH"),], aes(y = value), shape = 4, position = position_dodge(width = 0.8)) + scale_fill_manual(name = "Generations\nsince Fixation", values = wes_palette("Royal2")) + scale_y_continuous(labels=scaleFUN) + ylab("Peak Size") + xlab("Ploidy") + facet_wrap(~variable, scales = "free", shrink = T, nrow = 1) + theme_bw() + theme(axis.text.y=element_text(size = 12), axis.title.y=element_text(size=16), axis.text.x=element_text(size=13), axis.title.x=element_text(size = 16), legend.text = element_text(size=13), legend.title = element_text(size=14), strip.text = element_text(size=14))
+kkk.3 %>% filter(variable %in% c("sim_ploidy", "sampGen", "TajD", "Fst", "iHS", "XPEHH") & stat == "AUC") %>% mutate(variable = factor(variable, levels = c("TajD", "Fst", "iHS", "XPEHH"))) %>% ggplot(., aes(y = value / 100000, fill = as.factor(sampGen), x = as.factor(sim_ploidy))) + geom_boxplot(outlier.shape = NA) + geom_point(data = kkk.med.points[kkk.med.points$variable %in% c("TajD", "Fst", "iHS", "XPEHH"),], aes(y = value), shape = 18, color = "blue", position = position_dodge(width = 0.75), show.legend = F, size=2.5)+ scale_fill_manual(name = "Generations\nsince Fixation", values = wes_palette("Royal2")) + scale_y_continuous(labels=scaleFUN) + ylab("Peak Area") + xlab("Ploidy") + facet_wrap(~variable, scales = "free", shrink = T, nrow = 1) + theme_bw() + theme(axis.text.y=element_text(size = 12), axis.title.y=element_text(size=16), axis.text.x=element_text(size=13), axis.title.x=element_text(size = 16), legend.text = element_text(size=13), legend.title = element_text(size=14), strip.text = element_text(size=14))
 ```
+
+#Figure 2E
+```{r}
+ds = ms2 %>% group_by(sim_ploidy, DS, rep, dom) %>% mutate(Div = mean(Pi.2) - Pi.1, Tajima.D_1 = abs(Tajima.D_1), Fst = scale(fst)) %>% ungroup() %>% nest(-c(sim_ploidy, dom, DS, rep)) %>% mutate(size.div = map(data, ~getDims(., y.metric = "Div")), size.taj = map(data, ~getDims(., y.metric = "Tajima.D_1")), size.h = map(data, ~getDims(., y.metric = "Fay.Wu.H_1")), size.e = map(data, ~getDims(., y.metric = "Zeng.E_1")), size.fst = map(data, ~getDims(., y.metric = "Fst")), size.dxy = map(data, ~getDims(., y.metric = "dxy.1.2")), med.d = map(data, ~getStat(., "Tajima.D_1")), med.e = map(data, ~getStat(., "Zeng.E_1")), med.h = map(data, ~getStat(., "Fay.Wu.H_1")), med.fst = map(data, ~getStat(., "Fst")), med.dxy = map(data, ~getStat(., "dxy.1.2"))) %>% select(-data) %>% unnest()
+
+ms2b = merge(ds, ehh, by = c("sim_ploidy", "dom", "DS", "rep"), all = T)
+
+MS6.1 = ms2b %>% mutate("TajD" = med.d, "FayWuH" = med.h, "ZengsE" = med.e, "Fst" = med.fst, "Dxy" = med.dxy, "XPEHH" = med.xp, "iHS" = med.ihs) %>% select(sim_ploidy, DS, TajD, ZengsE, FayWuH, Fst, Dxy, XPEHH, iHS) %>% group_by(sim_ploidy, DS) %>% summarize_all(c("CV", "lCV", "uCV"))
+
+MS6.1 %>% melt(., id.var = c("sim_ploidy", "DS")) %>% separate(variable, c("variable","XX"), "_") %>% spread(XX, value) %>% filter(variable %in% c("TajD", "Fst", "iHS", "XPEHH")) %>% mutate(Variable = factor(variable, levels=c("TajD", "Fst", "iHS", "XPEHH"))) %>% ggplot(., aes(y = CV, fill = as.factor(DS), x = as.factor(sim_ploidy))) + geom_bar(stat="identity", position = position_dodge()) + geom_errorbar(aes(ymin = lCV, ymax = uCV, width = 0.5), position = position_dodge(width = 0.9)) + scale_fill_discrete(name = "Sampling", labels=c("Equal Individuals", "Equal Alleles")) + scale_y_continuous(labels=scaleFUN) + ylab("CV[MaxValue]") + xlab("Ploidy") + facet_wrap(~Variable, scales = "free", shrink = T, nrow = 1) + theme_bw() + theme(axis.text.y=element_blank(), axis.title.y=element_text(size=16), axis.text.x=element_text(size=14), axis.title.x=element_text(size=16), legend.text = element_text(size=13), legend.title = element_text(size=14), strip.text = element_text(size=14))
+```
+
+Supp Fig 5
+```{r}
+
+rehh2 = read.csv(paste("~/Documents/Research/PloidySim/rehh/", "rehh_calcs_do0.1_do0.9_sG_nDS.csv", sep=""))
+
+rehh2 %<>% mutate(driftGen = 0) %>% select(-X)
+
+rehh3 = read.csv(paste("~/Documents/Research/PloidySim/rehh/", "rehh_calcs_do0.1_sG_mkup3.csv", sep=""))
+
+rehh3 %<>% mutate(driftGen = 0)
+
+rehh2 = rbind(rehh2,rehh3)
+
+ff2 = rehh2 %>% filter(!is.na(xpehh.p) & sampGen!=1000) %>% mutate(mid = POSITION) %>% nest(-c(s, dom, recomb, N, mu, sim_ploidy, traj_ploidy, sampGen, fuseGen, driftGen, rep)) %>% mutate(size.xp = map(data, ~getDims(., y.metric = "XPEHH")), size.xp.p = map(data, ~getDims(., y.metric = "xpehh.p")), med.xp = map(data, ~getStat(., "XPEHH")), med.xpp = map(data, ~log(getStat(., "xpehh.p"))), size.ihs = map(data, ~getDims(., y.metric = "IHS")), size.ihs.p = map(data, ~getDims(., y.metric = "ihs.p")), med.ihs = map(data, ~getStat(., "IHS")), med.ihs.p = map(data, ~log(getStat(., "ihs.p")))) %>% select(-c(data)) %>% unnest()
+
+ff2 %<>% mutate(traj_ploidy = as.numeric(str_replace(traj_ploidy, "tp","")), sim_ploidy = as.numeric(str_replace(sim_ploidy, "sp","")), dom = as.numeric(str_replace(dom, "do","")), s = as.numeric(str_replace(s, "se","")), N = as.numeric(str_replace(N, "NN","")), mu = as.numeric(str_replace(mu, "mu","")), recomb = as.numeric(str_replace(recomb, "re","")), sampGen = as.numeric(str_replace(sampGen, "sG","")), fuseGen = as.numeric(str_replace(fuseGen, "fG","")), rep = as.numeric(str_replace(rep, "rep", "")))
+
+kkk2 = merge(dd, ff2, by = c("traj_ploidy", "sim_ploidy", "dom", "s", "N", "mu", "recomb", "sampGen", "fuseGen", "rep", "driftGen"), all = T)
+
+#Recessive
+kkk.1b = kkk2 %>% filter(dom == 0.1 & traj_ploidy == sim_ploidy & s == "0.01" & N=="10000" & driftGen == 0 & recomb == 1e-08)  %>% mutate("TajD" = med.d, "FayWuH" = med.h, "ZengsE" = med.e, "Fst" = med.fst, "Dxy" = med.dxy, "XPEHH" = med.xp, "iHS" = med.ihs) %>% select(sim_ploidy, sampGen, TajD, ZengsE, FayWuH, Fst, Dxy, XPEHH, iHS) %>% melt(., id.var = c("sim_ploidy", "sampGen")) %>% mutate(stat = "MaxValue")
+
+kkk.med.points.b = kkk2 %>% filter(dom == 0.1 & traj_ploidy == sim_ploidy & s == "0.01" & N=="10000" & driftGen == 0 & recomb == 1e-08)  %>% mutate("TajD" = med.d, "FayWuH" = med.h, "ZengsE" = med.e, "Fst" = med.fst, "Dxy" = med.dxy, "XPEHH" = med.xp, "iHS" = med.ihs) %>% select(sim_ploidy, sampGen, TajD, ZengsE, FayWuH, Fst, Dxy, XPEHH, iHS) %>% melt(., id.var = c("sim_ploidy", "sampGen")) %>% mutate(stat = "MaxValue") %>% group_by(sim_ploidy, sampGen, variable) %>% summarize(value = median(value, na.rm=T))
+
+kkk.2b = kkk2 %>% filter(dom == 0.1 & traj_ploidy == sim_ploidy & s == "0.01" & N=="10000" & driftGen == 0 & recomb == 1e-08)  %>% mutate("TajD" = size.taj, "FayWuH" = size.h, "ZengsE" = size.e, "Fst" = size.fst, "Dxy" = size.dxy, "XPEHH" = size.xp, "iHS" = size.ihs) %>% select(sim_ploidy, sampGen, TajD, ZengsE, FayWuH, Fst, Dxy, XPEHH, iHS) %>% melt(., id.var = c("sim_ploidy", "sampGen")) %>% mutate(stat = "AUC")
+
+kkk.3b = rbind(kkk.1b, kkk.2b)
+
+#Combined AUC and MaxValue
+kkk.3b %>% filter(variable %in% c("sim_ploidy", "sampGen", "TajD", "Fst", "iHS", "XPEHH") & stat == "AUC") %>% mutate(variable = factor(variable, levels = c("TajD", "Fst", "iHS", "XPEHH"))) %>% ggplot(., aes(y = value / 100000, fill = as.factor(sampGen), x = as.factor(sim_ploidy))) + geom_boxplot(outlier.shape = NA) + geom_point(data = kkk.med.points.b[kkk.med.points.b$variable %in% c("TajD", "Fst", "iHS", "XPEHH"),], aes(y = value), shape = 18, color = "blue", position = position_dodge(width = 0.75), show.legend = F, size=2.5)+ scale_fill_manual(name = "Generations\nsince Fixation", values = wes_palette("Royal2")) + scale_y_continuous(labels=scaleFUN) + ylab("Peak Area") + xlab("Ploidy") + facet_wrap(~variable, scales = "free", shrink = T, nrow = 1) + theme_bw() + theme(axis.text.y=element_text(size = 12), axis.title.y=element_text(size=16), axis.text.x=element_text(size=13), axis.title.x=element_text(size = 16), legend.text = element_text(size=13), legend.title = element_text(size=14), strip.text = element_text(size=14))
+
+#Dominant
+kkk.1c = kkk2 %>% filter(dom == 0.9 & traj_ploidy == sim_ploidy & s == "0.01" & N=="10000" & driftGen == 0 & recomb == 1e-08)  %>% mutate("TajD" = med.d, "FayWuH" = med.h, "ZengsE" = med.e, "Fst" = med.fst, "Dxy" = med.dxy, "XPEHH" = med.xp, "iHS" = med.ihs) %>% select(sim_ploidy, sampGen, TajD, ZengsE, FayWuH, Fst, Dxy, XPEHH, iHS) %>% melt(., id.var = c("sim_ploidy", "sampGen")) %>% mutate(stat = "MaxValue")
+
+kkk.med.points.c = kkk2 %>% filter(dom == 0.9 & traj_ploidy == sim_ploidy & s == "0.01" & N=="10000" & driftGen == 0 & recomb == 1e-08)  %>% mutate("TajD" = med.d, "FayWuH" = med.h, "ZengsE" = med.e, "Fst" = med.fst, "Dxy" = med.dxy, "XPEHH" = med.xp, "iHS" = med.ihs) %>% select(sim_ploidy, sampGen, TajD, ZengsE, FayWuH, Fst, Dxy, XPEHH, iHS) %>% melt(., id.var = c("sim_ploidy", "sampGen")) %>% mutate(stat = "MaxValue") %>% group_by(sim_ploidy, sampGen, variable) %>% summarize(value = median(value, na.rm=T))
+
+kkk.2c = kkk2 %>% filter(dom == 0.9 & traj_ploidy == sim_ploidy & s == "0.01" & N=="10000" & driftGen == 0 & recomb == 1e-08)  %>% mutate("TajD" = size.taj, "FayWuH" = size.h, "ZengsE" = size.e, "Fst" = size.fst, "Dxy" = size.dxy, "XPEHH" = size.xp, "iHS" = size.ihs) %>% select(sim_ploidy, sampGen, TajD, ZengsE, FayWuH, Fst, Dxy, XPEHH, iHS) %>% melt(., id.var = c("sim_ploidy", "sampGen")) %>% mutate(stat = "AUC")
+
+kkk.3c = rbind(kkk.1c, kkk.2c)
+
+#Combined AUC and MaxValue
+kkk.3c %>% filter(variable %in% c("sim_ploidy", "sampGen", "TajD", "Fst", "iHS", "XPEHH") & stat == "AUC") %>% mutate(variable = factor(variable, levels = c("TajD", "Fst", "iHS", "XPEHH"))) %>% ggplot(., aes(y = value / 100000, fill = as.factor(sampGen), x = as.factor(sim_ploidy))) + geom_boxplot(outlier.shape = NA) + geom_point(data = kkk.med.points.c[kkk.med.points.c$variable %in% c("TajD", "Fst", "iHS", "XPEHH"),], aes(y = value), shape = 18, color = "blue", position = position_dodge(width = 0.75), show.legend = F, size=2.5)+ scale_fill_manual(name = "Generations\nsince Fixation", values = wes_palette("Royal2")) + scale_y_continuous(labels=scaleFUN) + ylab("Peak Area") + xlab("Ploidy") + facet_wrap(~variable, scales = "free", shrink = T, nrow = 1) + theme_bw() + theme(axis.text.y=element_text(size = 12), axis.title.y=element_text(size=16), axis.text.x=element_text(size=13), axis.title.x=element_text(size = 16), legend.text = element_text(size=13), legend.title = element_text(size=14), strip.text = element_text(size=14))
+```
+
+Supplemental Figure 
+```{r}
+
+lCV <- function(data, N = 1000, n = 50){
+    aa = foreach(i = 1:N, .combine = rbind) %do% {
+      ndat = sample(data, n)
+      sd(ndat, na.rm=T)/(mean(ndat, na.rm=T))*100}
+    return(quantile(aa,0.05, na.rm=T))
+}
+
+uCV <- function(data, N = 1000, n = 50){
+    aa = foreach(i = 1:N, .combine = rbind) %do% {
+      ndat = sample(data, n)
+      sd(ndat, na.rm=T)/(mean(ndat, na.rm=T))*100}
+    return(quantile(aa,0.95, na.rm=T))
+}
+
+pardir = "..." #Set directory housing data for SuppFig6
+ehh = read.csv(paste(pardir, "rehh_calcs_SuppFig6.csv", sep = ""))
+
+ds2 = ms2 %>% group_by(sim_ploidy, DS, rep, dom) %>% mutate(Div = mean(Pi.2) - Pi.1, Tajima.D_1 = abs(Tajima.D_1), Fst = scale(fst)) %>% ungroup() %>% nest(-c(sim_ploidy, dom, DS, rep)) %>% mutate(size.div = map(data, ~getDims(., y.metric = "Div")), size.taj = map(data, ~getDims(., y.metric = "Tajima.D_1")), size.h = map(data, ~getDims(., y.metric = "Fay.Wu.H_1")), size.e = map(data, ~getDims(., y.metric = "Zeng.E_1")), size.fst = map(data, ~getDims(., y.metric = "Fst")), size.dxy = map(data, ~getDims(., y.metric = "dxy.1.2")), med.d = map(data, ~getStat(., "Tajima.D_1")), med.e = map(data, ~getStat(., "Zeng.E_1")), med.h = map(data, ~getStat(., "Fay.Wu.H_1")), med.fst = map(data, ~getStat(., "Fst")), med.dxy = map(data, ~getStat(., "dxy.1.2"))) %>% select(-data) %>% unnest()
+
+ms3 = merge(ds2, ehh2, by = c("sim_ploidy", "DS", "rep", "dom"), all = T)
+
+MS6.1b = ms3 %>% filter(dom==0.9) %>%  mutate("TajD" = med.d, "FayWuH" = med.h, "ZengsE" = med.e, "Fst" = med.fst, "Dxy" = med.dxy, "XPEHH" = med.xp, "iHS" = med.ihs) %>% select(sim_ploidy, dom, DS, TajD, ZengsE, FayWuH, Fst, Dxy, XPEHH, iHS) %>% group_by(sim_ploidy, dom, DS) %>% summarize_all(c("CV", "lCV", "uCV"))
+
+MS6.1b = ms3 %>% mutate("TajD" = med.d, "FayWuH" = med.h, "ZengsE" = med.e, "Fst" = med.fst, "Dxy" = med.dxy, "XPEHH" = med.xp, "iHS" = med.ihs) %>% select(sim_ploidy, dom, DS, TajD, ZengsE, FayWuH, Fst, Dxy, XPEHH, iHS) %>% group_by(sim_ploidy, dom, DS) %>% summarize_all(c("CV", "lCV", "uCV"))
+
+MS6.1b %>% filter(dom==0.1) %>% melt(., id.var = c("sim_ploidy", "DS")) %>% separate(variable, c("variable","XX"), "_") %>% spread(XX, value) %>% filter(variable %in% c("TajD", "Fst", "iHS", "XPEHH")) %>% mutate(Variable = factor(variable, levels=c("TajD", "Fst", "iHS", "XPEHH"))) %>% ggplot(., aes(y = CV, fill = as.factor(DS), x = as.factor(sim_ploidy))) + geom_bar(stat="identity", position = position_dodge()) + geom_errorbar(aes(ymin = lCV, ymax = uCV, width = 0.5), position = position_dodge(width = 0.9)) + scale_fill_discrete(name = "Sampling", labels=c("Equal Individuals", "Equal Alleles")) + scale_y_continuous(labels=scaleFUN) + ylab("CV[MaxValue]") + xlab("Ploidy") + facet_wrap(~Variable, scales = "free", shrink = T, nrow = 1) + theme_bw() + theme(axis.text.y=element_blank(), axis.title.y=element_text(size=16), axis.text.x=element_text(size=14), axis.title.x=element_text(size=16), legend.text = element_text(size=13), legend.title = element_text(size=14), strip.text = element_text(size=14))
+MS6.1b %>% filter(dom==0.9) %>% melt(., id.var = c("sim_ploidy", "DS")) %>% separate(variable, c("variable","XX"), "_") %>% spread(XX, value) %>% filter(variable %in% c("TajD", "Fst", "iHS", "XPEHH")) %>% mutate(Variable = factor(variable, levels=c("TajD", "Fst", "iHS", "XPEHH"))) %>% ggplot(., aes(y = CV, fill = as.factor(DS), x = as.factor(sim_ploidy))) + geom_bar(stat="identity", position = position_dodge()) + geom_errorbar(aes(ymin = lCV, ymax = uCV, width = 0.5), position = position_dodge(width = 0.9)) + scale_fill_discrete(name = "Sampling", labels=c("Equal Individuals", "Equal Alleles")) + scale_y_continuous(labels=scaleFUN) + ylab("CV[MaxValue]") + xlab("Ploidy") + facet_wrap(~Variable, scales = "free", shrink = T, nrow = 1) + theme_bw() + theme(axis.text.y=element_blank(), axis.title.y=element_text(size=16), axis.text.x=element_text(size=14), axis.title.x=element_text(size=16), legend.text = element_text(size=13), legend.title = element_text(size=14), strip.text = element_text(size=14))
+```

### 2019-10-12 analysis/mssel_analysis.Rmd
resubmission changes

@@
 
-ms = read.table("~/Documents/Research/PloidySim/data/mssel_out_2-24-19_fin.txt", head = T)
+ms = read.table("/Users/pmonnahan/Documents/Research/PloidySim/data/mssel_out_2-24-19_fin.txt", head = T)
 
@@
 
-ms2 = read.table("~/Documents/Research/PloidySim/data/mssel_out_highRe_drift_4-30-19.txt", head = T)
+ms2 = read.table("/Users/pmonnahan/Documents/Research/PloidySim/data/mssel_out_highRe_drift_4-30-19.txt", head = T)
 
-ms3 = read.table("~/Documents/Research/PloidySim/data/mssel_out_5-10-19.txt", head = T)
+ms3 = read.table("/Users/pmonnahan/Documents/Research/PloidySim/data/mssel_out_5-10-19.txt", head = T)
 ms3 %<>% filter(sim_ploidy!=1)
@@
 
-ms4 = read.table("~/Documents/Research/PloidySim/data/mssel_d3_moreReps.txt", head = T)
+ms4 = read.table("/Users/pmonnahan/Documents/Research/PloidySim/data/mssel_d3_moreReps.txt", head = T)
+ms4 %<>% filter((s==0.1 | s==0.01))
 ms4 %<>% mutate(rep = rep + 20)
@@
 
+#THIS IS FUCKING THINGS UP!!
 ms = rbind(ms, ms4)
 
-ms4 = read.table("~/Documents/Research/PloidySim/data/mssel_d2_moreReps.txt", head = T)
+ms4 = read.table("/Users/pmonnahan/Documents/Research/PloidySim/data/mssel_d2_moreReps.txt", head = T)
 ms4 %<>% mutate(rep = rep + 40)
@@
 
-ds.files = c("~/Documents/Research/PloidySim/rehh/rehh_tp2_do0.5_1krep_DS.csv", "~/Documents/Research/PloidySim/rehh/rehh_tp4_do0.5_1krep_DS.csv", "~/Documents/Research/PloidySim/rehh/rehh_tp8_do0.5_1krep_DS.csv")
-nds.files = c("~/Documents/Research/PloidySim/rehh/rehh_tp2_do0.5_1krep_nDS.csv", "~/Documents/Research/PloidySim/rehh/rehh_tp4_do0.5_1krep_nDS.csv", "~/Documents/Research/PloidySim/rehh/rehh_tp8_do0.5_1krep_nDS.csv")
-
 ds %<>% select(-start_freq) %>% mutate(DS="yes")
@@
 ms5 = rbind(ds, nds)
+
+ds.files = c("~/Documents/Research/PloidySim/rehh/rehh_tp2_do0.5_1krep_DS.csv", "~/Documents/Research/PloidySim/rehh/rehh_tp4_do0.5_1krep_DS.csv", "~/Documents/Research/PloidySim/rehh/rehh_tp8_do0.5_1krep_DS.csv")
+nds.files = c("~/Documents/Research/PloidySim/rehh/rehh_tp2_do0.5_1krep_nDS.csv", "~/Documents/Research/PloidySim/rehh/rehh_tp4_do0.5_1krep_nDS.csv", "~/Documents/Research/PloidySim/rehh/rehh_tp8_do0.5_1krep_nDS.csv")
 
@@
     dat = read.csv(files[i])
-    dat.sum = dat %>% mutate(traj_ploidy = as.numeric(str_replace(traj_ploidy, "tp","")), sim_ploidy = as.numeric(str_replace(sim_ploidy, "sp","")), dom = as.numeric(str_replace(dom, "do","")), s = as.numeric(str_replace(s, "se","")), N = as.numeric(str_replace(N, "NN","")), mu = as.numeric(str_replace(mu, "mu","")), recomb = as.numeric(str_replace(recomb, "re","")), sampGen = as.numeric(str_replace(sampGen, "sG","")), fuseGen = as.numeric(str_replace(fuseGen, "fG","")), rep = as.numeric(str_replace(rep, "rep", ""))) %>% filter(!is.na(xpehh.p)) %>% mutate(mid = POSITION) %>% nest(-c(sim_ploidy, rep)) %>% mutate(size.xp = map(data, ~getDims(., y.metric = "XPEHH")), size.xp.p = map(data, ~getDims(., y.metric = "xpehh.p")), med.xp = map(data, ~getStat(., "XPEHH")), med.xpp = map(data, ~log(getStat(., "xpehh.p"))), size.rsb = map(data, ~getDims(., y.metric = "Rsb")), size.rsb.p = map(data, ~getDims(., y.metric = "rsb.p")), med.rsb = map(data, ~getStat(., "Rsb")), med.rsb.p = map(data, ~log(getStat(., "rsb.p")))) %>% select(-data) %>% unnest()
+    dat.sum = dat %>% mutate(traj_ploidy = as.numeric(str_replace(traj_ploidy, "tp","")), sim_ploidy = as.numeric(str_replace(sim_ploidy, "sp","")), dom = as.numeric(str_replace(dom, "do","")), s = as.numeric(str_replace(s, "se","")), N = as.numeric(str_replace(N, "NN","")), mu = as.numeric(str_replace(mu, "mu","")), recomb = as.numeric(str_replace(recomb, "re","")), sampGen = as.numeric(str_replace(sampGen, "sG","")), fuseGen = as.numeric(str_replace(fuseGen, "fG","")), rep = as.numeric(str_replace(rep, "rep", ""))) %>% filter(!is.na(xpehh.p)) %>% mutate(mid = POSITION) %>% nest(-c(sim_ploidy, rep)) %>% mutate(size.xp = map(data, ~getDims(., y.metric = "XPEHH")), size.xp.p = map(data, ~getDims(., y.metric = "xpehh.p")), med.xp = map(data, ~getStat(., "XPEHH")), med.xpp = map(data, ~log(getStat(., "xpehh.p"))), size.ihs = map(data, ~getDims(., y.metric = "iHS")), size.ihs.p = map(data, ~getDims(., y.metric = "ihs.p")), med.ihs = map(data, ~getStat(., "iHS")), med.ihs.p = map(data, ~log(getStat(., "ihs.p")))) %>% select(-data) %>% unnest()
     all.sum = rbind(all.sum, dat.sum)
@@
 
-CV <- function(data){(sd(data, na.rm=T)/(mean(data, na.rm=T)))*100}
+CV <- function(data){
+  data = data[is.finite(data)]
+  return((sd(data, na.rm=T)/(mean(data, na.rm=T)))*100)
+  }
 
@@
 
-ds = ms5 %>% group_by(sim_ploidy, DS, rep) %>% mutate(Div = mean(Pi.2) - Pi.1, Tajima.D_1 = abs(Tajima.D_1)) %>% ungroup() %>% nest(-c(sim_ploidy, DS, rep)) %>% mutate(size.div = map(data, ~getDims(., y.metric = "Div")), size.taj = map(data, ~getDims(., y.metric = "Tajima.D_1")), size.h = map(data, ~getDims(., y.metric = "Fay.Wu.H_1")), size.e = map(data, ~getDims(., y.metric = "Zeng.E_1")), size.fst = map(data, ~getDims(., y.metric = "fst")), size.dxy = map(data, ~getDims(., y.metric = "dxy.1.2")), med.d = map(data, ~getStat(., "Tajima.D_1")), med.e = map(data, ~getStat(., "Zeng.E_1")), med.h = map(data, ~getStat(., "Fay.Wu.H_1")), med.fst = map(data, ~getStat(., "fst")), med.dxy = map(data, ~getStat(., "dxy.1.2"))) %>% select(-data) %>% unnest()
+ds = ms5 %>% group_by(sim_ploidy, DS, rep) %>% mutate(Div = mean(Pi.2) - Pi.1, Tajima.D_1 = abs(Tajima.D_1), Fst = scale(fst)) %>% ungroup() %>% nest(-c(sim_ploidy, DS, rep)) %>% mutate(size.div = map(data, ~getDims(., y.metric = "Div")), size.taj = map(data, ~getDims(., y.metric = "Tajima.D_1")), size.h = map(data, ~getDims(., y.metric = "Fay.Wu.H_1")), size.e = map(data, ~getDims(., y.metric = "Zeng.E_1")), size.fst = map(data, ~getDims(., y.metric = "Fst")), size.dxy = map(data, ~getDims(., y.metric = "dxy.1.2")), med.d = map(data, ~getStat(., "Tajima.D_1")), med.e = map(data, ~getStat(., "Zeng.E_1")), med.h = map(data, ~getStat(., "Fay.Wu.H_1")), med.fst = map(data, ~getStat(., "Fst")), med.dxy = map(data, ~getStat(., "dxy.1.2"))) %>% select(-data) %>% unnest()
 
@@
 
-ehh = rbind(nDS.ehh, DS.ehh)
+ehh = rbind(nds.ehh, ds.ehh)
 
@@
 
-ms6.1 = ms6 %>% mutate("TajD" = med.d, "FayWuH" = med.h, "ZengsE" = med.e, "Fst" = med.fst, "Dxy" = med.dxy, "XPEHH" = med.xp, "Rsb" = med.rsb) %>% select(sim_ploidy, DS, TajD, ZengsE, FayWuH, Fst, Dxy, XPEHH, Rsb) %>% melt(., id.var = c("sim_ploidy", "DS")) %>% mutate(stat = "MaxValue")
+ms6.1 = ms6 %>% mutate("TajD" = med.d, "FayWuH" = med.h, "ZengsE" = med.e, "Fst" = med.fst, "Dxy" = med.dxy, "XPEHH" = med.xp, "Rsb" = med.rsb) %>% select(sim_ploidy, DS, TajD, ZengsE, FayWuH, Fst, Dxy, XPEHH, iHS) %>% melt(., id.var = c("sim_ploidy", "DS")) %>% mutate(stat = "MaxValue")
 
-ms6.2 = ms6 %>% mutate("TajD" = size.taj, "FayWuH" = size.h, "ZengsE" = size.e, "Fst" = size.fst, "Dxy" = size.dxy, "XPEHH" = size.xp, "Rsb" = size.rsb) %>% select(sim_ploidy, DS, TajD, ZengsE, FayWuH, Fst, Dxy, XPEHH, Rsb) %>% melt(., id.var = c("sim_ploidy", "DS")) %>% mutate(stat = "AUC")
+ms6.2 = ms6 %>% mutate("TajD" = size.taj, "FayWuH" = size.h, "ZengsE" = size.e, "Fst" = size.fst, "Dxy" = size.dxy, "XPEHH" = size.xp, "Rsb" = size.rsb) %>% select(sim_ploidy, DS, TajD, ZengsE, FayWuH, Fst, Dxy, XPEHH, iHS) %>% melt(., id.var = c("sim_ploidy", "DS")) %>% mutate(stat = "AUC")
 
@@
 
-MS6.1 = ms6 %>% mutate("TajD" = med.d, "FayWuH" = med.h, "ZengsE" = med.e, "Fst" = med.fst, "Dxy" = med.dxy, "XPEHH" = med.xp, "Rsb" = med.rsb) %>% select(sim_ploidy, DS, TajD, ZengsE, FayWuH, Fst, Dxy, XPEHH, Rsb) %>% group_by(sim_ploidy, DS) %>% summarize_all(c("CV", "lCV", "uCV"))
+MS6.1 = ms6 %>% mutate("TajD" = med.d, "FayWuH" = med.h, "ZengsE" = med.e, "Fst" = med.fst, "Dxy" = med.dxy, "XPEHH" = med.xp, "iHS" = med.ihs) %>% select(sim_ploidy, DS, TajD, ZengsE, FayWuH, Fst, Dxy, XPEHH, iHS) %>% group_by(sim_ploidy, DS) %>% summarize_all(c("CV", "lCV", "uCV"))
 
 MS6.1 %>% melt(., id.var = c("sim_ploidy", "DS")) %>% separate(variable, c("variable","XX"), "_") %>% spread(XX, value) %>% ggplot(., aes(y = CV, fill = as.factor(DS), x = as.factor(sim_ploidy))) + geom_bar(stat="identity", position = position_dodge()) + geom_errorbar(aes(ymin = lCV, ymax = uCV, width = 0.5), position = position_dodge(width = 0.9)) + scale_fill_discrete(name = "Sampling", labels=c("Equal Individuals", "Equal Alleles")) + scale_y_continuous(labels=scaleFUN) + ylab("Var[MaxValue]") + xlab("Ploidy") + facet_wrap(~variable, scales = "free", shrink = T, nrow = 1) + theme_bw() + theme(axis.text.y=element_blank(), axis.title.y=element_text(size=16), axis.text.x=element_text(size=14), axis.title.x=element_text(size=16), legend.text = element_text(size=13), legend.title = element_text(size=14), strip.text = element_text(size=14))
+
+MS6.1 %>% melt(., id.var = c("sim_ploidy", "DS")) %>% separate(variable, c("variable","XX"), "_") %>% spread(XX, value) %>% filter(variable %in% c("TajD", "Fst", "iHS", "XPEHH")) %>% mutate(Variable = factor(variable, levels=c("TajD", "Fst", "iHS", "XPEHH"))) %>% ggplot(., aes(y = CV, fill = as.factor(DS), x = as.factor(sim_ploidy))) + geom_bar(stat="identity", position = position_dodge()) + geom_errorbar(aes(ymin = lCV, ymax = uCV, width = 0.5), position = position_dodge(width = 0.9)) + scale_fill_discrete(name = "Sampling", labels=c("Equal Individuals", "Equal Alleles")) + scale_y_continuous(labels=scaleFUN) + ylab("CV[MaxValue]") + xlab("Ploidy") + facet_wrap(~Variable, scales = "free", shrink = T, nrow = 1) + theme_bw() + theme(axis.text.y=element_blank(), axis.title.y=element_text(size=16), axis.text.x=element_text(size=14), axis.title.x=element_text(size=16), legend.text = element_text(size=13), legend.title = element_text(size=14), strip.text = element_text(size=14))
 
@@
 ---
+```{r}
+traj=read.table("~/Documents/Research/PloidySim/data/Ploidy_Forward_Sim_results.txt",head=T, sep=",")
+traj2=read.table("~/Documents/Research/PloidySim/data/Ploidy_Forward_Sim_results_N1mil.txt",head=T, sep=",")
+
+dipTraj=function(start_freq,s,h,stop_freq){
+  h=1-h
+  p=start_freq
+  traj = c(p)
+  fits = c(1.0-s, 1.0 - h*s, 1.0)
+  while(p < stop_freq){
+    g_freqs = c((1-p)^2, 2*p*(1 - p), p^2)
+    tot_fit = sum(fits * g_freqs)
+    p_fit = (g_freqs[3] * fits[3]) + 0.5*(g_freqs[2] * fits[2])
+    p_prime = p_fit/tot_fit
+    traj = c(traj,p_prime)
+    p = p_prime
+  }
+  return(traj)
+}
+
+tetTraj=function(start_freq,s,h1,h2,h3,stop_freq){
+  h1 = 1-h1
+  h2 = 1-h2
+  h3 = 1-h3
+  p=start_freq
+  traj = c(p)
+  fits = c(1.0-s, 1.0 - h1*s, 1.0 - h2*s, 1.0 - h3*s, 1.0)
+  while(p < stop_freq){
+    g_freqs = c((1-p)^4, 4*p*(1 - p)^3, 6*p^2*(1 - p)^2, 4*p^3*(1 - p), p^4)
+    tot_fit = sum(fits * g_freqs)
+    p_fit = (g_freqs[5] * fits[5]) + 0.75*(g_freqs[4] * fits[4]) + 0.5*(g_freqs[3] * fits[3]) + 0.25*(g_freqs[2] * fits[2])
+    p_prime = p_fit/tot_fit
+    traj = c(traj,p_prime)
+    p = p_prime
+  }
+  return(traj)
+}
+
+bbR=data.frame(traj=dipTraj(0.05,0.1,0,0.99))
+bbR$gen=seq.int(nrow(bbR))
+aaR=data.frame(traj=tetTraj(0.05,0.1,0,0,0,0.99))
+aaR$gen=seq.int(nrow(aaR))
+
+#recessive
+ggplot(traj[traj$dom == "recessive" & traj$s==0.1,])+geom_line(data=traj[traj$dom == "recessive" & traj$s==0.1 & traj$ploidy==4,],aes(y=freq,x=gen,group=as.factor(rep)),color="blue",alpha=0.5)+geom_line(data=traj[traj$dom == "recessive" & traj$s==0.1 & traj$ploidy==2,],aes(y=freq,x=gen,group=as.factor(rep)),color="red",alpha=0.5)+geom_line(data=bbR,aes(y=traj,x=gen))+geom_line(data=aaR,aes(y=traj,x=gen))+facet_grid(~N,scales="free_x")+xlab("Generation")+ylab("Frequency")+theme(legend.title = element_text("Ploidy"))+scale_x_log10()
+
+traj %>% filter(N %in% c(1000,10000) & s == 0.01 & dom == "recessive") %>% ggplot()+geom_line(data=traj[traj$dom == "recessive" & traj$s==0.1 & traj$ploidy==4 & traj$N %in% c(1000,10000),],aes(y=freq,x=gen,group=as.factor(rep)),color="blue",alpha=0.5)+geom_line(data=traj[traj$dom == "recessive" & traj$s==0.1 & traj$ploidy==2 & traj$N %in% c(1000,10000),],aes(y=freq,x=gen,group=as.factor(rep)),color="red",alpha=0.5)+geom_line(data=bbR,aes(y=traj,x=gen), linetype="dashed")+geom_line(data=aaR,aes(y=traj,x=gen))+facet_grid(~N,scales="free_x")+xlab("Generation")+ylab("Frequency")+theme(legend.title = element_text("Ploidy"))+scale_x_log10()
+
+#dominant
+bbD=data.frame(traj=dipTraj(0.05,0.1,1,0.95))
+bbD$gen=seq.int(nrow(bbD))
+aaD=data.frame(traj=tetTraj(0.05,0.1,1,1,1,0.95))
+aaD$gen=seq.int(nrow(aaD))
+
+ggplot(traj[traj$dom == "dominant" & traj$s==0.1,])+geom_line(data=traj[traj$dom == "dominant" & traj$s==0.1 & traj$ploidy==4,],aes(y=freq,x=gen,group=as.factor(rep)),color="blue",alpha=0.5)+geom_line(data=traj[traj$dom == "dominant" & traj$s==0.1 & traj$ploidy==2,],aes(y=freq,x=gen,group=as.factor(rep)),color="red",alpha=0.5)+geom_line(data=bbD,aes(y=traj,x=gen))+geom_line(data=aaD,aes(y=traj,x=gen))+facet_grid(~N,scales="free_x")+xlab("Generation")+ylab("Frequency")+theme(legend.title = element_text("Ploidy"))+scale_x_log10()
+
+#additive
+ggplot(traj[traj$dom == "recessive" & traj$s==0.1,])+geom_line(data=traj[traj$dom == "recessive" & traj$s==0.1 & traj$ploidy==4,],aes(y=freq,x=gen,group=as.factor(rep)),color="blue",alpha=0.5)+geom_line(data=traj[traj$dom == "recessive" & traj$s==0.1 & traj$ploidy==2,],aes(y=freq,x=gen,group=as.factor(rep)),color="red",alpha=0.5)+geom_line(data=bbR,aes(y=traj,x=gen))+geom_line(data=aaR,aes(y=traj,x=gen))+facet_grid(~N,scales="free_x")+xlab("Generation")+ylab("Frequency")+theme(legend.title = element_text("Ploidy"))+scale_x_log10()
+
+params = data.frame("s" = rep(0.1,6), "dom" = c(rep(1,6)), "ploidy" = rep(c(2,4),3), "start" = rep(0.05, 6))
+params %<>% dplyr::slice(rep(row_number(), 100))
+# Create trajectories
+dat1 = foreach(i = 1:nrow(params), .combine=rbind) %do% {
+  print(i)
+  getTraj(params[i,]$s, params[i,]$dom, params[i,]$ploidy, params[i,]$start, maxGens = 999999, N = 1000000)
+}
+
+```
 
@@
 
+dat1 = read.csv("~/Documents/Research/PloidySim/data/fixationTimes_byN.csv")
+dat1 %>%  mutate(Dom = factor(case_when(dom == 0.1 ~ "Partial\nRecessivity (H = -0.4)", dom == 0.5 ~ "Additivity (H = 0)", dom == 0.9 ~ "Partial\nDominance (H = 0.4)"), levels = c("Partial\nRecessivity (H = -0.4)", "Additivity (H = 0)", "Partial\nDominance (H = 0.4)"))) %>% ggplot(aes(y = log(gen), fill = as.factor(N), x = as.factor(ploidy))) + geom_boxplot(outlier.size = 0.5) + facet_wrap(~Dom) + ylab("Log(Time to Fixation)") + xlab("Ploidy") + scale_fill_discrete(name = "N")+ theme_bw() + theme(axis.text.y=element_text(size=14), axis.title.y=element_text(size=16),axis.text.x=element_text(size=14),axis.title.x=element_text(size=16),legend.text = element_text(size=14), legend.title = element_text(size=16), strip.text = element_text(size=12))
+
 #Stochastic effect of population size on
@@
   dat["stat"] = dat[, y.metric]
-  val = nrow(dat[dat$stat == "-Inf",])
-  return(val)
+  val1 = nrow(dat[dat$stat == "-Inf",])
+  val2 = nrow(dat[is.na(dat$stat),])
+  return(val1+val2)
 }
 
-ms %>% filter(sampGen==1 & driftGen == 0 & fuseGen %in% c(1,1000,10000) & dom %in% c(0.1, 0.5, 0.9)) %>% group_by(s, dom, recomb, N, mu, sim_ploidy, traj_ploidy, sampGen, fuseGen, rep, driftGen) %>% mutate(Div = mean(Pi.2) - Pi.1, Tajima.D_1 = abs(Tajima.D_1)) %>% ungroup() %>% nest(-c(s, dom, recomb, N, mu, sim_ploidy, traj_ploidy, sampGen, fuseGen, rep, driftGen)) %>% mutate(und.taj = map(data, ~getUnd(., y.metric = "Tajima.D_1")), und.h = map(data, ~getUnd(., y.metric = "Fay.Wu.H_1")), und.e = map(data, ~getUnd(., y.metric = "Zeng.E_1"))) %>% select(-data) %>% unnest() %>% group_by(s, dom, recomb, N, sim_ploidy) %>% summarize(n = n(), unds.d = sum(und.taj), unds.h = sum(und.h), unds.e = sum(und.e))
+getUnd.h = function(dat, y.metric = "fst", offset = 100000){
+  # dat = data.frame("mid" = mid, "fst" = febugst)
+  dat = dat %>% filter(POSITION > 500000 - offset & POSITION < 500000 + offset)
+  dat["stat"] = dat[, y.metric]
+  val1 = nrow(dat[dat$stat == "-Inf",])
+  val2 = nrow(dat[is.na(dat$stat),])
+  return(val1+val2)
+}
+
+ms %>% filter(sampGen==1 & driftGen == 0 & fuseGen %in% c(1,1000,10000) & dom %in% c(0.1, 0.5, 0.9)) %>% group_by(s, dom, recomb, N, mu, sim_ploidy, traj_ploidy, sampGen, fuseGen, rep, driftGen) %>% mutate(Div = mean(Pi.2) - Pi.1, Tajima.D_1 = abs(Tajima.D_1)) %>% ungroup() %>% nest(-c(s, dom, recomb, N, mu, sim_ploidy, traj_ploidy, sampGen, fuseGen, rep, driftGen)) %>% mutate(und.taj = map(data, ~getUnd(., y.metric = "Tajima.D_1")), und.h = map(data, ~getUnd(., y.metric = "Fay.Wu.H_1")), und.e = map(data, ~getUnd(., y.metric = "Zeng.E_1")), und.ihs = map(data, ~getUnd(., y.metric = "iHS")), und.xp = map(data, ~getUnd(., y.metric = "XPEHH"))) %>% select(-data) %>% unnest() %>% group_by(s, dom, recomb, N, sim_ploidy) %>% summarize(n = n(), unds.d = sum(und.taj), unds.h = sum(und.h), unds.e = sum(und.e), unds.ihs = sum(und.ihs), unds.xp = sum(und.xp))
 
@@
 
-dd = ms %>% filter(sim_ploidy == traj_ploidy & fuseGen==1 & s == "0.01" & recomb == "1e-08" & N=="10000" & driftGen == 0 & sampGen %in% c(1,1000,10000)) %>% nest(-c(s, dom, recomb, N, mu, sim_ploidy, traj_ploidy, sampGen, fuseGen, rep, driftGen)) %>% mutate(size.taj = map(data, ~getDims(., y.metric = "Tajima.D_1")), size.h = map(data, ~getDims(., y.metric = "Fay.Wu.H_1")), size.e = map(data, ~getDims(., y.metric = "Zeng.E_1")), size.fst = map(data, ~getDims(., y.metric = "fst")), size.dxy = map(data, ~getDims(., y.metric = "dxy.1.2")), med.d = map(data, ~getStat(., "Tajima.D_1")), med.e = map(data, ~getStat(., "Zeng.E_1")), med.h = map(data, ~getStat(., "Fay.Wu.H_1")), med.fst = map(data, ~getStat(., "fst")), med.dxy = map(data, ~getStat(., "dxy.1.2"))) %>% select(-data) %>% unnest()
+dd = ms %>% filter(sim_ploidy == traj_ploidy & fuseGen==1 & s == "0.01" & recomb == "1e-08" & N=="10000" & driftGen == 0 & sampGen %in% c(1,1000,10000)) %>% group_by(s, dom, recomb, N, mu, sim_ploidy, traj_ploidy, sampGen, fuseGen, rep, driftGen) %>% mutate(Fst = scale(fst)) %>% ungroup() %>% nest(-c(s, dom, recomb, N, mu, sim_ploidy, traj_ploidy, sampGen, fuseGen, rep, driftGen)) %>% mutate(size.taj = map(data, ~getDims(., y.metric = "Tajima.D_1")), size.h = map(data, ~getDims(., y.metric = "Fay.Wu.H_1")), size.e = map(data, ~getDims(., y.metric = "Zeng.E_1")), size.fst = map(data, ~getDims(., y.metric = "Fst")), size.dxy = map(data, ~getDims(., y.metric = "dxy.1.2")), med.d = map(data, ~getStat(., "Tajima.D_1")), med.e = map(data, ~getStat(., "Zeng.E_1")), med.h = map(data, ~getStat(., "Fay.Wu.H_1")), med.fst = map(data, ~getStat(., "Fst")), med.dxy = map(data, ~getStat(., "dxy.1.2"))) %>% select(-data) %>% unnest()
 
-dd.points = dd %>% filter(dom %in% c("0.1", "0.9") & traj_ploidy == sim_ploidy & s == "0.01" & recomb == "1e-08" & N=="10000" & driftGen == 0)  %>% mutate("TajD" = size.taj, "FayWuH" = size.h, "ZengsE" = size.e) %>% select(sim_ploidy, dom, sampGen, TajD, FayWuH, ZengsE) %>% melt(., id.var = c("sim_ploidy", "sampGen", "dom")) %>% mutate("Area" = variable) %>% filter(value != 40.5) %>% group_by(sim_ploidy, sampGen, dom, variable) %>% summarize(median = median(value)) %>% mutate(Magnitude = variable)
+dd = ms %>% filter(sim_ploidy == traj_ploidy & fuseGen==1 & s == "0.01" & recomb == "1e-08" & N=="10000" & driftGen == 0 & sampGen %in% c(1,1000,10000)) %>% nest(-c(s, dom, recomb, N, mu, sim_ploidy, traj_ploidy, sampGen, fuseGen, rep, driftGen)) %>% mutate(size.taj = map(data, ~getDims(., y.metric = "Tajima.D_1")), size.h = map(data, ~getDims(., y.metric = "Fay.Wu.H_1")), size.e = map(data, ~getDims(., y.metric = "Zeng.E_1")), size.fst = map(data, ~getDims(., y.metric = "Fst")), size.dxy = map(data, ~getDims(., y.metric = "dxy.1.2")), med.d = map(data, ~getStat(., "Tajima.D_1")), med.e = map(data, ~getStat(., "Zeng.E_1")), med.h = map(data, ~getStat(., "Fay.Wu.H_1")), med.fst = map(data, ~getStat(., "Fst")), med.dxy = map(data, ~getStat(., "dxy.1.2"))) %>% select(-data) %>% unnest()
+
+dd.points.dom.size = dd %>% filter(dom %in% c("0.1", "0.9") & traj_ploidy == sim_ploidy & s == "0.01" & recomb == "1e-08" & N=="10000" & driftGen == 0)  %>% mutate("TajD" = size.taj, "FayWuH" = size.h, "ZengsE" = size.e) %>% select(sim_ploidy, dom, sampGen, TajD, FayWuH, ZengsE) %>% melt(., id.var = c("sim_ploidy", "sampGen", "dom")) %>% mutate("Area" = variable) %>% filter(value != 40.5) %>% group_by(sim_ploidy, sampGen, dom, variable) %>% summarize(median = median(value)) %>% mutate(Magnitude = variable)
+
+dd.points.size = dd %>% filter(dom == 0.5 & traj_ploidy == sim_ploidy & s == "0.01" & recomb == "1e-08" & N=="10000" & driftGen == 0)  %>% mutate("TajD" = size.taj, "FayWuH" = size.h, "ZengsE" = size.e) %>% select(sim_ploidy, dom, sampGen, TajD, FayWuH, ZengsE) %>% melt(., id.var = c("sim_ploidy", "sampGen", "dom")) %>% mutate("Area" = variable) %>% filter(value != 40.5) %>% group_by(sim_ploidy, sampGen, dom, variable) %>% summarize(median = median(value)) %>% mutate(Magnitude = variable)
 
@@
 #Combined sample gen figures
-kkk = merge(dd, ff, by = c("traj_ploidy", "sim_ploidy", "dom", "s", "N", "mu", "recomb", "sampGen", "fuseGen", "rep"), all.x = T)
+kkk = merge(dd, ff, by = c("traj_ploidy", "sim_ploidy", "dom", "s", "N", "mu", "recomb", "sampGen", "fuseGen", "rep"), all = T)
 
-kkk.1 = kkk %>% filter(dom == 0.5 & traj_ploidy == sim_ploidy & s == "0.01" & N=="10000" & driftGen == 0 & recomb == 1e-08)  %>% mutate("TajD" = med.d, "FayWuH" = med.h, "ZengsE" = med.e, "Fst" = med.fst, "Dxy" = med.dxy, "XPEHH" = med.xp, "Rsb" = med.rsb) %>% select(sim_ploidy, sampGen, TajD, ZengsE, FayWuH, Fst, Dxy, XPEHH, Rsb) %>% melt(., id.var = c("sim_ploidy", "sampGen")) %>% mutate(stat = "MaxValue")
+kkk.1 = kkk %>% filter(dom == 0.5 & traj_ploidy == sim_ploidy & s == "0.01" & N=="10000" & driftGen == 0 & recomb == 1e-08)  %>% mutate("TajD" = med.d, "FayWuH" = med.h, "ZengsE" = med.e, "Fst" = med.fst, "Dxy" = med.dxy, "XPEHH" = med.xp, "iHS" = med.ihs) %>% select(sim_ploidy, sampGen, TajD, ZengsE, FayWuH, Fst, Dxy, XPEHH, iHS) %>% melt(., id.var = c("sim_ploidy", "sampGen")) %>% mutate(stat = "MaxValue")
 
-kkk.2 = kkk %>% filter(dom == 0.5 & traj_ploidy == sim_ploidy & s == "0.01" & N=="10000" & driftGen == 0 & recomb == 1e-08)  %>% mutate("TajD" = size.taj, "FayWuH" = size.h, "ZengsE" = size.e, "Fst" = size.fst, "Dxy" = size.dxy, "XPEHH" = size.xp, "Rsb" = size.rsb) %>% select(sim_ploidy, sampGen, TajD, ZengsE, FayWuH, Fst, Dxy, XPEHH, Rsb) %>% melt(., id.var = c("sim_ploidy", "sampGen")) %>% mutate(stat = "AUC")
+kkk.med.points = kkk %>% filter(dom == 0.5 & traj_ploidy == sim_ploidy & s == "0.01" & N=="10000" & driftGen == 0 & recomb == 1e-08)  %>% mutate("TajD" = med.d, "FayWuH" = med.h, "ZengsE" = med.e, "Fst" = med.fst, "Dxy" = med.dxy, "XPEHH" = med.xp, "iHS" = med.ihs) %>% select(sim_ploidy, sampGen, TajD, ZengsE, FayWuH, Fst, Dxy, XPEHH, iHS) %>% melt(., id.var = c("sim_ploidy", "sampGen")) %>% mutate(stat = "MaxValue") %>% group_by(sim_ploidy, sampGen, variable) %>% summarize(value = median(value, na.rm=T))
+
+kkk.2 = kkk %>% filter(dom == 0.5 & traj_ploidy == sim_ploidy & s == "0.01" & N=="10000" & driftGen == 0 & recomb == 1e-08)  %>% mutate("TajD" = size.taj, "FayWuH" = size.h, "ZengsE" = size.e, "Fst" = size.fst, "Dxy" = size.dxy, "XPEHH" = size.xp, "iHS" = size.ihs) %>% select(sim_ploidy, sampGen, TajD, ZengsE, FayWuH, Fst, Dxy, XPEHH, iHS) %>% melt(., id.var = c("sim_ploidy", "sampGen")) %>% mutate(stat = "AUC")
 
@@
 
-kkk.3 %>% filter(variable %in% c("sim_ploidy", "sampGen", "TajD", "Fst", "Rsb", "XPEHH") & stat == "AUC") %>% ggplot(., aes(y = value / 100000, fill = as.factor(sampGen), x = as.factor(sim_ploidy))) + geom_boxplot(outlier.shape = NA) + scale_fill_manual(name = "Generations\nsince Fixation", values = wes_palette("Royal2")) + scale_y_continuous(labels=scaleFUN) + ylab("Area Under Curve") + xlab("Ploidy") + facet_wrap(~variable, scales = "free", shrink = T, nrow = 1) + theme_bw() + theme(axis.text.y=element_text(size = 12), axis.title.y=element_text(size=16), axis.text.x=element_blank(), axis.title.x=element_blank(), legend.text = element_text(size=13), legend.title = element_text(size=14), strip.text = element_text(size=14))
+#Combined AUC and MaxValue
+kkk.3 %>% filter(variable %in% c("sim_ploidy", "sampGen", "TajD", "Fst", "iHS", "XPEHH") & stat == "AUC") %>% mutate(variable = factor(variable, levels = c("TajD", "Fst", "iHS", "XPEHH"))) %>% ggplot(., aes(y = value / 100000, fill = as.factor(sampGen), x = as.factor(sim_ploidy))) + geom_boxplot(outlier.shape = NA) + geom_point(data = kkk.med.points[kkk.med.points$variable %in% c("TajD", "Fst", "iHS", "XPEHH"),], aes(y = value), shape = 4, position = position_dodge(width = 0.8)) + scale_fill_manual(name = "Generations\nsince Fixation", values = wes_palette("Royal2")) + scale_y_continuous(labels=scaleFUN) + ylab("Peak Size") + xlab("Ploidy") + facet_wrap(~variable, scales = "free", shrink = T, nrow = 1) + theme_bw() + theme(axis.text.y=element_text(size = 12), axis.title.y=element_text(size=16), axis.text.x=element_text(size=13), axis.title.x=element_text(size = 16), legend.text = element_text(size=13), legend.title = element_text(size=14), strip.text = element_text(size=14))
 
-kkk.3 %>% filter(variable %in% c("sim_ploidy", "sampGen", "TajD", "Fst", "Rsb", "XPEHH") & stat == "MaxValue") %>% ggplot(., aes(y = value, fill = as.factor(sampGen), x = as.factor(sim_ploidy))) + geom_boxplot(outlier.shape = NA) + scale_fill_manual(name = "Generations\nsince Fixation", values = wes_palette("Royal2")) + scale_y_continuous(labels=scaleFUN) + ylab("Max Value") + xlab("Ploidy") + facet_wrap(~variable, scales = "free", shrink = T, nrow = 1) + theme_bw() + theme(axis.text.y=element_text(size = 12), axis.title.y=element_text(size=16), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18), legend.text = element_text(size=13), legend.title = element_text(size=14), strip.background = element_blank(), strip.text.x = element_blank())
+kkk.3 %>% filter(variable %in% c("sim_ploidy", "sampGen", "TajD", "Fst", "iHS", "XPEHH") & stat == "MaxValue") %>% ggplot(., aes(y = value, fill = as.factor(sampGen), x = as.factor(sim_ploidy))) + geom_boxplot(outlier.shape = NA) + scale_fill_manual(name = "Generations\nsince Fixation", values = wes_palette("Royal2")) + scale_y_continuous(labels=scaleFUN) + ylab("Max Value") + xlab("Ploidy") + facet_wrap(~variable, scales = "free", shrink = T, nrow = 1) + theme_bw() + theme(axis.text.y=element_text(size = 12), axis.title.y=element_text(size=16), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18), legend.text = element_text(size=13), legend.title = element_text(size=14), strip.background = element_blank(), strip.text.x = element_blank())
 
 dom.rehh = read.csv("~/Documents/Research/PloidySim/rehh/dom/rehh_dom.csv")
+rehh = read.csv("~/Documents/Research/PloidySim/rehh/rehh_calcs_do0.5_fG1_nDS.csv")
 
-ff = dom.rehh %>% filter(!is.na(xpehh.p) & sampGen!=1000) %>% mutate(mid = POSITION) %>% nest(-c(s, dom, recomb, N, mu, sim_ploidy, traj_ploidy, sampGen, fuseGen, rep)) %>% mutate(size.xp = map(data, ~getDims(., y.metric = "XPEHH")), size.xp.p = map(data, ~getDims(., y.metric = "xpehh.p")), med.xp = map(data, ~getStat(., "XPEHH")), med.xpp = map(data, ~log(getStat(., "xpehh.p"))), size.rsb = map(data, ~getDims(., y.metric = "Rsb")), size.rsb.p = map(data, ~getDims(., y.metric = "rsb.p")), med.rsb = map(data, ~getStat(., "Rsb")), med.rsb.p = map(data, ~log(getStat(., "rsb.p")))) %>% select(-data) %>% unnest()
+ff = rehh %>% filter(!is.na(xpehh.p) & sampGen!=1000) %>% mutate(mid = POSITION) %>% nest(-c(s, dom, recomb, N, mu, sim_ploidy, traj_ploidy, sampGen, fuseGen, driftGen)) %>% mutate(size.xp = map(data, ~getDims(., y.metric = "XPEHH")), size.xp.p = map(data, ~getDims(., y.metric = "xpehh.p")), med.xp = map(data, ~getStat(., "XPEHH")), med.xpp = map(data, ~log(getStat(., "xpehh.p"))), size.ihs = map(data, ~getDims(., y.metric = "iHS")), size.ihs.p = map(data, ~getDims(., y.metric = "ihs.p")), med.ihs = map(data, ~getStat(., "iHS")), med.ihs.p = map(data, ~log(getStat(., "ihs.p"))), rep = driftGen) %>% select(-c(data, driftGen)) %>% unnest()
 

### 2019-12-09 analysis/PaperFigures.Rmd
overdue update

@@
 
-getStat = function(dat, stat, offset = 25000){
-  dat = dat %>% filter(mid > 500000 - offset & mid < 500000 + offset)
-  val = max(abs(unlist(dat[,stat])), na.rm = T)
-  return(val)
-  }
-
 getTraj = function(s, dom, ploidy, start_freq, N = -9, end_freq = 0.99, maxGens = 9999, maxTries = 10){
@@
   # dat = data.frame("mid" = mid, "fst" = febugst)
+  x = 1
+  if(y.metric=="Tajima.D_1"){x = -1}
   peak = tryCatch({
-    auc(dat$mid, unlist(abs(dat[,y.metric])), from = 500000 - offset, to = 500000 + offset)}
+    auc(dat$mid, unlist(x*(dat[,y.metric])), from = 500000 - offset, to = 500000 + offset)}
     , error = function(e){
@@
 getStat = function(dat, stat, offset = 25000){
+  x = 1
+  if(stat=="Tajima.D_1"){x = -1}
   dat = dat %>% filter(mid > 500000 - offset & mid < 500000 + offset)
-  val = max(abs(unlist(dat[,stat])), na.rm = T)
+  val = max(x*(unlist(dat[,stat])), na.rm = T)
   return(val)
@@
     dat = read.csv(files[i])
-    dat.sum = dat %>% mutate(traj_ploidy = as.numeric(str_replace(traj_ploidy, "tp","")), sim_ploidy = as.numeric(str_replace(sim_ploidy, "sp","")), dom = as.numeric(str_replace(dom, "do","")), s = as.numeric(str_replace(s, "se","")), N = as.numeric(str_replace(N, "NN","")), mu = as.numeric(str_replace(mu, "mu","")), recomb = as.numeric(str_replace(recomb, "re","")), sampGen = as.numeric(str_replace(sampGen, "sG","")), fuseGen = as.numeric(str_replace(fuseGen, "fG","")), rep = as.numeric(str_replace(rep, "rep", ""))) %>% filter(!is.na(xpehh.p)) %>% mutate(mid = POSITION) %>% nest(-c(sim_ploidy, dom, rep)) %>% mutate(size.xp = map(data, ~getDims(., y.metric = "XPEHH")), size.xp.p = map(data, ~getDims(., y.metric = "xpehh.p")), med.xp = map(data, ~getStat(., "XPEHH")), med.xpp = map(data, ~log(getStat(., "xpehh.p"))), size.ihs = map(data, ~getDims(., y.metric = "IHS")), size.ihs.p = map(data, ~getDims(., y.metric = "ihs.p")), med.ihs = map(data, ~getStat(., "IHS")), med.ihs.p = map(data, ~log(getStat(., "ihs.p")))) %>% select(-data) %>% unnest()
+    dat.sum = dat %>% mutate(traj_ploidy = as.numeric(str_replace(traj_ploidy, "tp","")), sim_ploidy = as.numeric(str_replace(sim_ploidy, "sp","")), dom = as.numeric(str_replace(dom, "do","")), s = as.numeric(str_replace(s, "se","")), N = as.numeric(str_replace(N, "NN","")), mu = as.numeric(str_replace(mu, "mu","")), recomb = as.numeric(str_replace(recomb, "re","")), sampGen = as.numeric(str_replace(sampGen, "sG","")), fuseGen = as.numeric(str_replace(fuseGen, "fG","")), rep = as.numeric(str_replace(rep, "rep", ""))) %>% filter(!is.na(xpehh.p)) %>% mutate(mid = POSITION) %>% nest(-c(sim_ploidy, dom, rep)) %>% mutate(size.xp = map(data, ~getDims(., y.metric = "XPEHH")), size.xp.p = map(data, ~getDims(., y.metric = "xpehh.p")), med.xp = map(data, ~getStat(., "XPEHH")), med.xpp = map(data, ~log(getStat(., "xpehh.p"))), size.ihs = map(data, ~getDims(., y.metric = "iHS")), size.ihs.p = map(data, ~getDims(., y.metric = "ihs.p")), med.ihs = map(data, ~getStat(., "iHS")), med.ihs.p = map(data, ~log(getStat(., "ihs.p")))) %>% select(-data) %>% unnest()
     all.sum = rbind(all.sum, dat.sum)
@@
 #Figure 1A left
-dat1 %>% filter(ploidy %in% c(2, 4, 8) & dom %in% c(0, 0.5, 1)) %>% ggplot(., aes(x=gen, y=freq, linetype=as.factor(dom), color=as.factor(ploidy))) + geom_line(size = 1.2) + scale_color_manual(name = "Ploidy", values = c("#F8766D", "#00BA38", "#619CFF")) + scale_linetype_manual(name = "Dominance", labels=c("Dominant", "Additive", "Recessive"), values = c("dashed", "solid", "dotted")) + xlim(0,500) + theme_bw() + xlab("Generation") + ylab("Allele Frequency") + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18),axis.text.x=element_text(size=16),axis.title.x=element_text(size=18),legend.text = element_text(size=16), legend.title = element_text(size=18))
+dat1 %>% filter(ploidy %in% c(2, 4, 8) & dom %in% c("recessive", "additive", "dominant")) %>% ggplot(., aes(x=gen, y=freq, linetype=as.factor(dom), color=as.factor(ploidy))) + geom_line(size = 1.2) + scale_color_manual(name = "Ploidy", values = c("#F8766D", "#00BA38", "#619CFF")) + scale_linetype_manual(name = "Dominance", labels=c("Dominant", "Additive", "Recessive"), values = c("dashed", "solid", "dotted")) + xlim(0,500) + theme_bw() + xlab("Generation") + ylab("Allele Frequency") + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18),axis.text.x=element_text(size=16),axis.title.x=element_text(size=18),legend.text = element_text(size=16), legend.title = element_text(size=18))
 
@@
 ```{r}
-ff = rehh %>% filter(!is.na(xpehh.p) & sampGen!=1000) %>% mutate(mid = POSITION) %>% nest(-c(s, dom, recomb, N, mu, sim_ploidy, traj_ploidy, sampGen, fuseGen, rep)) %>% mutate(size.xp = map(data, ~getDims(., y.metric = "XPEHH")), size.xp.p = map(data, ~getDims(., y.metric = "xpehh.p")), med.xp = map(data, ~getStat(., "XPEHH")), med.xpp = map(data, ~log(getStat(., "xpehh.p"))), size.ihs = map(data, ~getDims(., y.metric = "IHS")), size.ihs.p = map(data, ~getDims(., y.metric = "ihs.p")), med.ihs = map(data, ~getStat(., "IHS")), med.ihs.p = map(data, ~log(getStat(., "ihs.p")))) %>% select(-c(data)) %>% unnest()
+ff = rehh %>% filter(!is.na(xpehh.p) & sampGen!=1000) %>% mutate(mid = POSITION) %>% nest(-c(s, dom, recomb, N, mu, sim_ploidy, traj_ploidy, sampGen, fuseGen, rep)) %>% mutate(size.xp = map(data, ~getDims(., y.metric = "XPEHH")), size.xp.p = map(data, ~getDims(., y.metric = "xpehh.p")), med.xp = map(data, ~getStat(., "XPEHH")), med.xpp = map(data, ~log(getStat(., "xpehh.p"))), size.ihs = map(data, ~getDims(., y.metric = "iHS")), size.ihs.p = map(data, ~getDims(., y.metric = "ihs.p")), med.ihs = map(data, ~getStat(., "iHS")), med.ihs.p = map(data, ~log(getStat(., "ihs.p")))) %>% select(-c(data)) %>% unnest()
 
@@
 
-kkk.1 = kkk %>% filter(dom == 0.5 & traj_ploidy == sim_ploidy & s == "0.01" & N=="10000" & driftGen == 0 & recomb == 1e-08)  %>% mutate("TajD" = med.d, "FayWuH" = med.h, "ZengsE" = med.e, "Fst" = med.fst, "Dxy" = med.dxy, "XPEHH" = med.xp, "iHS" = med.ihs) %>% select(sim_ploidy, sampGen, TajD, ZengsE, FayWuH, Fst, Dxy, XPEHH, iHS) %>% melt(., id.var = c("sim_ploidy", "sampGen")) %>% mutate(stat = "MaxValue")
+kkk.1 = kkk %>% filter(dom == 0.5 & traj_ploidy == sim_ploidy & s == "0.01" & N=="10000" & driftGen == 0 & recomb == 1e-08)  %>% mutate("-TajD" = med.d, "FayWuH" = med.h, "ZengsE" = med.e, "Std.Fst" = med.fst, "Dxy" = med.dxy, "XPEHH" = med.xp, "iHS" = med.ihs) %>% select(sim_ploidy, sampGen, `-TajD`, ZengsE, FayWuH, Std.Fst, Dxy, XPEHH, iHS) %>% melt(., id.var = c("sim_ploidy", "sampGen")) %>% mutate(stat = "MaxValue")
 
-kkk.med.points = kkk %>% filter(dom == 0.5 & traj_ploidy == sim_ploidy & s == "0.01" & N=="10000" & driftGen == 0 & recomb == 1e-08)  %>% mutate("TajD" = med.d, "FayWuH" = med.h, "ZengsE" = med.e, "Fst" = med.fst, "Dxy" = med.dxy, "XPEHH" = med.xp, "iHS" = med.ihs) %>% select(sim_ploidy, sampGen, TajD, ZengsE, FayWuH, Fst, Dxy, XPEHH, iHS) %>% melt(., id.var = c("sim_ploidy", "sampGen")) %>% mutate(stat = "MaxValue") %>% group_by(sim_ploidy, sampGen, variable) %>% summarize(value = median(value, na.rm=T))
+kkk.med.points = kkk %>% filter(dom == 0.5 & traj_ploidy == sim_ploidy & s == "0.01" & N=="10000" & driftGen == 0 & recomb == 1e-08)  %>% mutate("-TajD" = med.d, "FayWuH" = med.h, "ZengsE" = med.e, "Std.Fst" = med.fst, "Dxy" = med.dxy, "XPEHH" = med.xp, "iHS" = med.ihs) %>% select(sim_ploidy, sampGen, `-TajD`, ZengsE, FayWuH, Std.Fst, Dxy, XPEHH, iHS) %>% melt(., id.var = c("sim_ploidy", "sampGen")) %>% mutate(stat = "MaxValue") %>% group_by(sim_ploidy, sampGen, variable) %>% summarize(value = median(value, na.rm=T))
 
-kkk.2 = kkk %>% filter(dom == 0.5 & traj_ploidy == sim_ploidy & s == "0.01" & N=="10000" & driftGen == 0 & recomb == 1e-08)  %>% mutate("TajD" = size.taj, "FayWuH" = size.h, "ZengsE" = size.e, "Fst" = size.fst, "Dxy" = size.dxy, "XPEHH" = size.xp, "iHS" = size.ihs) %>% select(sim_ploidy, sampGen, TajD, ZengsE, FayWuH, Fst, Dxy, XPEHH, iHS) %>% melt(., id.var = c("sim_ploidy", "sampGen")) %>% mutate(stat = "AUC")
+kkk.2 = kkk %>% filter(dom == 0.5 & traj_ploidy == sim_ploidy & s == "0.01" & N=="10000" & driftGen == 0 & recomb == 1e-08)  %>% mutate("-TajD" = size.taj, "FayWuH" = size.h, "ZengsE" = size.e, "Std.Fst" = size.fst, "Dxy" = size.dxy, "XPEHH" = size.xp, "iHS" = size.ihs) %>% select(sim_ploidy, sampGen, `-TajD`, ZengsE, FayWuH, Std.Fst, Dxy, XPEHH, iHS) %>% melt(., id.var = c("sim_ploidy", "sampGen")) %>% mutate(stat = "AUC")
 
@@
 #Combined AUC and MaxValue
-kkk.3 %>% filter(variable %in% c("sim_ploidy", "sampGen", "TajD", "Fst", "iHS", "XPEHH") & stat == "AUC") %>% mutate(variable = factor(variable, levels = c("TajD", "Fst", "iHS", "XPEHH"))) %>% ggplot(., aes(y = value / 100000, fill = as.factor(sampGen), x = as.factor(sim_ploidy))) + geom_boxplot(outlier.shape = NA) + geom_point(data = kkk.med.points[kkk.med.points$variable %in% c("TajD", "Fst", "iHS", "XPEHH"),], aes(y = value), shape = 18, color = "blue", position = position_dodge(width = 0.75), show.legend = F, size=2.5)+ scale_fill_manual(name = "Generations\nsince Fixation", values = wes_palette("Royal2")) + scale_y_continuous(labels=scaleFUN) + ylab("Peak Area") + xlab("Ploidy") + facet_wrap(~variable, scales = "free", shrink = T, nrow = 1) + theme_bw() + theme(axis.text.y=element_text(size = 12), axis.title.y=element_text(size=16), axis.text.x=element_text(size=13), axis.title.x=element_text(size = 16), legend.text = element_text(size=13), legend.title = element_text(size=14), strip.text = element_text(size=14))
+kkk.3 %>% filter(variable %in% c("sim_ploidy", "sampGen", "-TajD", "Std.Fst", "iHS", "XPEHH") & stat == "AUC") %>% mutate(variable = factor(variable, levels = c("-TajD", "Std.Fst", "iHS", "XPEHH"))) %>% ggplot(., aes(y = abs(value) / 100000, fill = as.factor(sampGen), x = as.factor(sim_ploidy))) + geom_boxplot(outlier.shape = NA) + geom_point(data = kkk.med.points[kkk.med.points$variable %in% c("-TajD", "Std.Fst", "iHS", "XPEHH"),], aes(y = value, color = as.factor(sampGen)), shape = 18, position = position_dodge(width = 0.75), show.legend = F, size=2.5)+ geom_point(data = kkk.med.points[kkk.med.points$variable %in% c("-TajD", "Std.Fst", "iHS", "XPEHH"),], aes(y = value), shape = 5, color = "black", position = position_dodge(width = 0.75), show.legend = F, size=2)+ scale_fill_manual(name = "Generations\nsince Fixation", values = wes_palette("Royal2"))+scale_color_manual(name = "Generations\nsince Fixation", values = wes_palette("Royal2")) + scale_y_continuous(labels=scaleFUN) + ylab("Peak Area") + xlab("Ploidy") + facet_wrap(~variable, scales = "free", shrink = T, nrow = 1) + theme_bw() + theme(axis.text.y=element_text(size = 12), axis.title.y=element_text(size=16), axis.text.x=element_text(size=13), axis.title.x=element_text(size = 16), legend.text = element_text(size=13), legend.title = element_text(size=14), strip.text = element_text(size=14))
 ```
@@
 ```{r}
-ds = ms2 %>% group_by(sim_ploidy, DS, rep, dom) %>% mutate(Div = mean(Pi.2) - Pi.1, Tajima.D_1 = abs(Tajima.D_1), Fst = scale(fst)) %>% ungroup() %>% nest(-c(sim_ploidy, dom, DS, rep)) %>% mutate(size.div = map(data, ~getDims(., y.metric = "Div")), size.taj = map(data, ~getDims(., y.metric = "Tajima.D_1")), size.h = map(data, ~getDims(., y.metric = "Fay.Wu.H_1")), size.e = map(data, ~getDims(., y.metric = "Zeng.E_1")), size.fst = map(data, ~getDims(., y.metric = "Fst")), size.dxy = map(data, ~getDims(., y.metric = "dxy.1.2")), med.d = map(data, ~getStat(., "Tajima.D_1")), med.e = map(data, ~getStat(., "Zeng.E_1")), med.h = map(data, ~getStat(., "Fay.Wu.H_1")), med.fst = map(data, ~getStat(., "Fst")), med.dxy = map(data, ~getStat(., "dxy.1.2"))) %>% select(-data) %>% unnest()
+ds = ms2 %>% group_by(sim_ploidy, DS, rep, dom) %>% mutate(Div = mean(Pi.2) - Pi.1, Fst = scale(fst)) %>% ungroup() %>% nest(-c(sim_ploidy, dom, DS, rep)) %>% mutate(size.div = map(data, ~getDims(., y.metric = "Div")), size.taj = map(data, ~getDims(., y.metric = "Tajima.D_1")), size.h = map(data, ~getDims(., y.metric = "Fay.Wu.H_1")), size.e = map(data, ~getDims(., y.metric = "Zeng.E_1")), size.fst = map(data, ~getDims(., y.metric = "Fst")), size.dxy = map(data, ~getDims(., y.metric = "dxy.1.2")), med.d = map(data, ~getStat(., "Tajima.D_1")), med.e = map(data, ~getStat(., "Zeng.E_1")), med.h = map(data, ~getStat(., "Fay.Wu.H_1")), med.fst = map(data, ~getStat(., "Fst")), med.dxy = map(data, ~getStat(., "dxy.1.2"))) %>% select(-data) %>% unnest()
 
@@
 
-MS6.1 = ms2b %>% mutate("TajD" = med.d, "FayWuH" = med.h, "ZengsE" = med.e, "Fst" = med.fst, "Dxy" = med.dxy, "XPEHH" = med.xp, "iHS" = med.ihs) %>% select(sim_ploidy, DS, TajD, ZengsE, FayWuH, Fst, Dxy, XPEHH, iHS) %>% group_by(sim_ploidy, DS) %>% summarize_all(c("CV", "lCV", "uCV"))
+MS6.1 = ms2b %>% mutate("-TajD" = med.d, "FayWuH" = med.h, "ZengsE" = med.e, "Std.Fst" = med.fst, "Dxy" = med.dxy, "XPEHH" = med.xp, "iHS" = med.ihs) %>% select(sim_ploidy, DS, `-TajD`, ZengsE, FayWuH, Std.Fst, Dxy, XPEHH, iHS) %>% group_by(sim_ploidy, DS) %>% summarize_all(c("CV", "lCV", "uCV"))
 
-MS6.1 %>% melt(., id.var = c("sim_ploidy", "DS")) %>% separate(variable, c("variable","XX"), "_") %>% spread(XX, value) %>% filter(variable %in% c("TajD", "Fst", "iHS", "XPEHH")) %>% mutate(Variable = factor(variable, levels=c("TajD", "Fst", "iHS", "XPEHH"))) %>% ggplot(., aes(y = CV, fill = as.factor(DS), x = as.factor(sim_ploidy))) + geom_bar(stat="identity", position = position_dodge()) + geom_errorbar(aes(ymin = lCV, ymax = uCV, width = 0.5), position = position_dodge(width = 0.9)) + scale_fill_discrete(name = "Sampling", labels=c("Equal Individuals", "Equal Alleles")) + scale_y_continuous(labels=scaleFUN) + ylab("CV[MaxValue]") + xlab("Ploidy") + facet_wrap(~Variable, scales = "free", shrink = T, nrow = 1) + theme_bw() + theme(axis.text.y=element_blank(), axis.title.y=element_text(size=16), axis.text.x=element_text(size=14), axis.title.x=element_text(size=16), legend.text = element_text(size=13), legend.title = element_text(size=14), strip.text = element_text(size=14))
+MS6.1 %>% melt(., id.var = c("sim_ploidy", "DS")) %>% separate(variable, c("variable","XX"), "_") %>% spread(XX, value) %>% filter(variable %in% c("-TajD", "Std.Fst", "iHS", "XPEHH")) %>% mutate(Variable = factor(variable, levels=c("-TajD", "Std.Fst", "iHS", "XPEHH"))) %>% ggplot(., aes(y = CV, fill = as.factor(DS), x = as.factor(sim_ploidy))) + geom_bar(stat="identity", position = position_dodge()) + geom_errorbar(aes(ymin = lCV, ymax = uCV, width = 0.5), position = position_dodge(width = 0.9)) + scale_fill_discrete(name = "Sampling", labels=c("Equal Individuals", "Equal Alleles")) + scale_y_continuous(labels=scaleFUN) + ylab("CV[MaxValue]") + xlab("Ploidy") + facet_wrap(~Variable, scales = "free", shrink = T, nrow = 1) + theme_bw() + theme(axis.text.y=element_blank(), axis.title.y=element_text(size=16), axis.text.x=element_text(size=14), axis.title.x=element_text(size=16), legend.text = element_text(size=13), legend.title = element_text(size=14), strip.text = element_text(size=14))
 ```
@@
 #Recessive
-kkk.1b = kkk2 %>% filter(dom == 0.1 & traj_ploidy == sim_ploidy & s == "0.01" & N=="10000" & driftGen == 0 & recomb == 1e-08)  %>% mutate("TajD" = med.d, "FayWuH" = med.h, "ZengsE" = med.e, "Fst" = med.fst, "Dxy" = med.dxy, "XPEHH" = med.xp, "iHS" = med.ihs) %>% select(sim_ploidy, sampGen, TajD, ZengsE, FayWuH, Fst, Dxy, XPEHH, iHS) %>% melt(., id.var = c("sim_ploidy", "sampGen")) %>% mutate(stat = "MaxValue")
+kkk.1b = kkk2 %>% filter(dom == 0.1 & traj_ploidy == sim_ploidy & s == "0.01" & N=="10000" & driftGen == 0 & recomb == 1e-08)  %>% mutate("-TajD" = med.d, "FayWuH" = med.h, "ZengsE" = med.e, "Std.Fst" = med.fst, "Dxy" = med.dxy, "XPEHH" = med.xp, "IHS" = med.ihs) %>% select(sim_ploidy, sampGen, `-TajD`, ZengsE, FayWuH, Std.Fst, Dxy, XPEHH, IHS) %>% melt(., id.var = c("sim_ploidy", "sampGen")) %>% mutate(stat = "MaxValue")
 
-kkk.med.points.b = kkk2 %>% filter(dom == 0.1 & traj_ploidy == sim_ploidy & s == "0.01" & N=="10000" & driftGen == 0 & recomb == 1e-08)  %>% mutate("TajD" = med.d, "FayWuH" = med.h, "ZengsE" = med.e, "Fst" = med.fst, "Dxy" = med.dxy, "XPEHH" = med.xp, "iHS" = med.ihs) %>% select(sim_ploidy, sampGen, TajD, ZengsE, FayWuH, Fst, Dxy, XPEHH, iHS) %>% melt(., id.var = c("sim_ploidy", "sampGen")) %>% mutate(stat = "MaxValue") %>% group_by(sim_ploidy, sampGen, variable) %>% summarize(value = median(value, na.rm=T))
+kkk.med.points.b = kkk2 %>% filter(dom == 0.1 & traj_ploidy == sim_ploidy & s == "0.01" & N=="10000" & driftGen == 0 & recomb == 1e-08)  %>% mutate("-TajD" = med.d, "FayWuH" = med.h, "ZengsE" = med.e, "Std.Fst" = med.fst, "Dxy" = med.dxy, "XPEHH" = med.xp, "IHS" = med.ihs) %>% select(sim_ploidy, sampGen, `-TajD`, ZengsE, FayWuH, Std.Fst, Dxy, XPEHH, IHS) %>% melt(., id.var = c("sim_ploidy", "sampGen")) %>% mutate(stat = "MaxValue") %>% group_by(sim_ploidy, sampGen, variable) %>% summarize(value = median(value, na.rm=T))
 
-kkk.2b = kkk2 %>% filter(dom == 0.1 & traj_ploidy == sim_ploidy & s == "0.01" & N=="10000" & driftGen == 0 & recomb == 1e-08)  %>% mutate("TajD" = size.taj, "FayWuH" = size.h, "ZengsE" = size.e, "Fst" = size.fst, "Dxy" = size.dxy, "XPEHH" = size.xp, "iHS" = size.ihs) %>% select(sim_ploidy, sampGen, TajD, ZengsE, FayWuH, Fst, Dxy, XPEHH, iHS) %>% melt(., id.var = c("sim_ploidy", "sampGen")) %>% mutate(stat = "AUC")
+kkk.2b = kkk2 %>% filter(dom == 0.1 & traj_ploidy == sim_ploidy & s == "0.01" & N=="10000" & driftGen == 0 & recomb == 1e-08)  %>% mutate("-TajD" = size.taj, "FayWuH" = size.h, "ZengsE" = size.e, "Std.Fst" = size.fst, "Dxy" = size.dxy, "XPEHH" = size.xp, "IHS" = size.ihs) %>% select(sim_ploidy, sampGen, `-TajD`, ZengsE, FayWuH, Std.Fst, Dxy, XPEHH, IHS) %>% melt(., id.var = c("sim_ploidy", "sampGen")) %>% mutate(stat = "AUC")
 
@@
 #Combined AUC and MaxValue
-kkk.3b %>% filter(variable %in% c("sim_ploidy", "sampGen", "TajD", "Fst", "iHS", "XPEHH") & stat == "AUC") %>% mutate(variable = factor(variable, levels = c("TajD", "Fst", "iHS", "XPEHH"))) %>% ggplot(., aes(y = value / 100000, fill = as.factor(sampGen), x = as.factor(sim_ploidy))) + geom_boxplot(outlier.shape = NA) + geom_point(data = kkk.med.points.b[kkk.med.points.b$variable %in% c("TajD", "Fst", "iHS", "XPEHH"),], aes(y = value), shape = 18, color = "blue", position = position_dodge(width = 0.75), show.legend = F, size=2.5)+ scale_fill_manual(name = "Generations\nsince Fixation", values = wes_palette("Royal2")) + scale_y_continuous(labels=scaleFUN) + ylab("Peak Area") + xlab("Ploidy") + facet_wrap(~variable, scales = "free", shrink = T, nrow = 1) + theme_bw() + theme(axis.text.y=element_text(size = 12), axis.title.y=element_text(size=16), axis.text.x=element_text(size=13), axis.title.x=element_text(size = 16), legend.text = element_text(size=13), legend.title = element_text(size=14), strip.text = element_text(size=14))
+kkk.3b %>% filter(variable %in% c("sim_ploidy", "sampGen", "-TajD", "Std.Fst", "IHS", "XPEHH") & stat == "AUC") %>% mutate(variable = factor(variable, levels = c("-TajD", "Std.Fst", "IHS", "XPEHH"))) %>% ggplot(., aes(y = value / 100000, fill = as.factor(sampGen), x = as.factor(sim_ploidy))) + geom_boxplot(outlier.shape = NA) + geom_point(data = kkk.med.points.b[kkk.med.points.b$variable %in% c("-TajD", "Std.Fst", "IHS", "XPEHH"),], aes(y = value, color = as.factor(sampGen)), shape = 18, position = position_dodge(width = 0.75), show.legend = F, size=2.5)+ geom_point(data = kkk.med.points.b[kkk.med.points.b$variable %in% c("-TajD", "Std.Fst", "IHS", "XPEHH"),], aes(y = value), shape = 5, color = "black", position = position_dodge(width = 0.75), show.legend = F, size=2)+ scale_fill_manual(name = "Generations\nsince Fixation", values = wes_palette("Royal2"))+scale_color_manual(name = "Generations\nsince Fixation", values = wes_palette("Royal2")) + scale_y_continuous(labels=scaleFUN) + ylab("Peak Area") + xlab("Ploidy") + facet_wrap(~variable, scales = "free", shrink = T, nrow = 1) + theme_bw() + theme(axis.text.y=element_text(size = 12), axis.title.y=element_text(size=16), axis.text.x=element_text(size=13), axis.title.x=element_text(size = 16), legend.text = element_text(size=13), legend.title = element_text(size=14), strip.text = element_text(size=14))
 
 #Dominant
-kkk.1c = kkk2 %>% filter(dom == 0.9 & traj_ploidy == sim_ploidy & s == "0.01" & N=="10000" & driftGen == 0 & recomb == 1e-08)  %>% mutate("TajD" = med.d, "FayWuH" = med.h, "ZengsE" = med.e, "Fst" = med.fst, "Dxy" = med.dxy, "XPEHH" = med.xp, "iHS" = med.ihs) %>% select(sim_ploidy, sampGen, TajD, ZengsE, FayWuH, Fst, Dxy, XPEHH, iHS) %>% melt(., id.var = c("sim_ploidy", "sampGen")) %>% mutate(stat = "MaxValue")
+kkk.1c = kkk2 %>% filter(dom == 0.9 & traj_ploidy == sim_ploidy & s == "0.01" & N=="10000" & driftGen == 0 & recomb == 1e-08)  %>% mutate("-TajD" = med.d, "FayWuH" = med.h, "ZengsE" = med.e, "Std.Fst" = med.fst, "Dxy" = med.dxy, "XPEHH" = med.xp, "IHS" = med.ihs) %>% select(sim_ploidy, sampGen, `-TajD`, ZengsE, FayWuH, Std.Fst, Dxy, XPEHH, IHS) %>% melt(., id.var = c("sim_ploidy", "sampGen")) %>% mutate(stat = "MaxValue")
 
-kkk.med.points.c = kkk2 %>% filter(dom == 0.9 & traj_ploidy == sim_ploidy & s == "0.01" & N=="10000" & driftGen == 0 & recomb == 1e-08)  %>% mutate("TajD" = med.d, "FayWuH" = med.h, "ZengsE" = med.e, "Fst" = med.fst, "Dxy" = med.dxy, "XPEHH" = med.xp, "iHS" = med.ihs) %>% select(sim_ploidy, sampGen, TajD, ZengsE, FayWuH, Fst, Dxy, XPEHH, iHS) %>% melt(., id.var = c("sim_ploidy", "sampGen")) %>% mutate(stat = "MaxValue") %>% group_by(sim_ploidy, sampGen, variable) %>% summarize(value = median(value, na.rm=T))
+kkk.med.points.c = kkk2 %>% filter(dom == 0.9 & traj_ploidy == sim_ploidy & s == "0.01" & N=="10000" & driftGen == 0 & recomb == 1e-08)  %>% mutate("-TajD" = med.d, "FayWuH" = med.h, "ZengsE" = med.e, "Std.Fst" = med.fst, "Dxy" = med.dxy, "XPEHH" = med.xp, "IHS" = med.ihs) %>% select(sim_ploidy, sampGen, `-TajD`, ZengsE, FayWuH, Std.Fst, Dxy, XPEHH, IHS) %>% melt(., id.var = c("sim_ploidy", "sampGen")) %>% mutate(stat = "MaxValue") %>% group_by(sim_ploidy, sampGen, variable) %>% summarize(value = median(value, na.rm=T))
 
-kkk.2c = kkk2 %>% filter(dom == 0.9 & traj_ploidy == sim_ploidy & s == "0.01" & N=="10000" & driftGen == 0 & recomb == 1e-08)  %>% mutate("TajD" = size.taj, "FayWuH" = size.h, "ZengsE" = size.e, "Fst" = size.fst, "Dxy" = size.dxy, "XPEHH" = size.xp, "iHS" = size.ihs) %>% select(sim_ploidy, sampGen, TajD, ZengsE, FayWuH, Fst, Dxy, XPEHH, iHS) %>% melt(., id.var = c("sim_ploidy", "sampGen")) %>% mutate(stat = "AUC")
+kkk.2c = kkk2 %>% filter(dom == 0.9 & traj_ploidy == sim_ploidy & s == "0.01" & N=="10000" & driftGen == 0 & recomb == 1e-08)  %>% mutate("-TajD" = size.taj, "FayWuH" = size.h, "ZengsE" = size.e, "Std.Fst" = size.fst, "Dxy" = size.dxy, "XPEHH" = size.xp, "IHS" = size.ihs) %>% select(sim_ploidy, sampGen, `-TajD`, ZengsE, FayWuH, Std.Fst, Dxy, XPEHH, IHS) %>% melt(., id.var = c("sim_ploidy", "sampGen")) %>% mutate(stat = "AUC")
 
@@
 #Combined AUC and MaxValue
-kkk.3c %>% filter(variable %in% c("sim_ploidy", "sampGen", "TajD", "Fst", "iHS", "XPEHH") & stat == "AUC") %>% mutate(variable = factor(variable, levels = c("TajD", "Fst", "iHS", "XPEHH"))) %>% ggplot(., aes(y = value / 100000, fill = as.factor(sampGen), x = as.factor(sim_ploidy))) + geom_boxplot(outlier.shape = NA) + geom_point(data = kkk.med.points.c[kkk.med.points.c$variable %in% c("TajD", "Fst", "iHS", "XPEHH"),], aes(y = value), shape = 18, color = "blue", position = position_dodge(width = 0.75), show.legend = F, size=2.5)+ scale_fill_manual(name = "Generations\nsince Fixation", values = wes_palette("Royal2")) + scale_y_continuous(labels=scaleFUN) + ylab("Peak Area") + xlab("Ploidy") + facet_wrap(~variable, scales = "free", shrink = T, nrow = 1) + theme_bw() + theme(axis.text.y=element_text(size = 12), axis.title.y=element_text(size=16), axis.text.x=element_text(size=13), axis.title.x=element_text(size = 16), legend.text = element_text(size=13), legend.title = element_text(size=14), strip.text = element_text(size=14))
+kkk.3c %>% filter(variable %in% c("sim_ploidy", "sampGen", "-TajD", "Std.Fst", "IHS", "XPEHH") & stat == "AUC") %>% mutate(variable = factor(variable, levels = c("-TajD", "Std.Fst", "IHS", "XPEHH"))) %>% ggplot(., aes(y = value / 100000, fill = as.factor(sampGen), x = as.factor(sim_ploidy))) + geom_boxplot(outlier.shape = NA) + geom_point(data = kkk.med.points.c[kkk.med.points.c$variable %in% c("-TajD", "Std.Fst", "IHS", "XPEHH"),], aes(y = value, color = as.factor(sampGen)), shape = 18, position = position_dodge(width = 0.75), show.legend = F, size=2.5)+ geom_point(data = kkk.med.points.c[kkk.med.points.c$variable %in% c("-TajD", "Std.Fst", "IHS", "XPEHH"),], aes(y = value), shape = 5, color = "black", position = position_dodge(width = 0.75), show.legend = F, size=2)+ scale_fill_manual(name = "Generations\nsince Fixation", values = wes_palette("Royal2"))+scale_color_manual(name = "Generations\nsince Fixation", values = wes_palette("Royal2")) + scale_y_continuous(labels=scaleFUN) + ylab("Peak Area") + xlab("Ploidy") + facet_wrap(~variable, scales = "free", shrink = T, nrow = 1) + theme_bw() + theme(axis.text.y=element_text(size = 12), axis.title.y=element_text(size=16), axis.text.x=element_text(size=13), axis.title.x=element_text(size = 16), legend.text = element_text(size=13), legend.title = element_text(size=14), strip.text = element_text(size=14))
 ```
 
-Supplemental Figure 
+Supp Fig 6
 ```{r}
 
-lCV <- function(data, N = 1000, n = 50){
+lCV <- function(data, N = 1000, n = 20){
     aa = foreach(i = 1:N, .combine = rbind) %do% {
@@
 
-uCV <- function(data, N = 1000, n = 50){
+uCV <- function(data, N = 1000, n = 20){
     aa = foreach(i = 1:N, .combine = rbind) %do% {
@@
 
-pardir = "..." #Set directory housing data for SuppFig6
-ehh = read.csv(paste(pardir, "rehh_calcs_SuppFig6.csv", sep = ""))
+pardir = "~/Documents/Research/PloidySim/data/" #Set directory housing data for SuppFig6
+ehh2 = read.csv(paste(pardir, "rehh_calcs_SuppFig6.csv", sep = ""), head = T)
 
-ds2 = ms2 %>% group_by(sim_ploidy, DS, rep, dom) %>% mutate(Div = mean(Pi.2) - Pi.1, Tajima.D_1 = abs(Tajima.D_1), Fst = scale(fst)) %>% ungroup() %>% nest(-c(sim_ploidy, dom, DS, rep)) %>% mutate(size.div = map(data, ~getDims(., y.metric = "Div")), size.taj = map(data, ~getDims(., y.metric = "Tajima.D_1")), size.h = map(data, ~getDims(., y.metric = "Fay.Wu.H_1")), size.e = map(data, ~getDims(., y.metric = "Zeng.E_1")), size.fst = map(data, ~getDims(., y.metric = "Fst")), size.dxy = map(data, ~getDims(., y.metric = "dxy.1.2")), med.d = map(data, ~getStat(., "Tajima.D_1")), med.e = map(data, ~getStat(., "Zeng.E_1")), med.h = map(data, ~getStat(., "Fay.Wu.H_1")), med.fst = map(data, ~getStat(., "Fst")), med.dxy = map(data, ~getStat(., "dxy.1.2"))) %>% select(-data) %>% unnest()
+ds2 = ms2 %>% group_by(sim_ploidy, DS, rep, dom) %>% mutate(Div = mean(Pi.2) - Pi.1, Fst = scale(fst)) %>% ungroup() %>% nest(-c(sim_ploidy, dom, DS, rep)) %>% mutate(size.div = map(data, ~getDims(., y.metric = "Div")), size.taj = map(data, ~getDims(., y.metric = "Tajima.D_1")), size.h = map(data, ~getDims(., y.metric = "Fay.Wu.H_1")), size.e = map(data, ~getDims(., y.metric = "Zeng.E_1")), size.fst = map(data, ~getDims(., y.metric = "Fst")), size.dxy = map(data, ~getDims(., y.metric = "dxy.1.2")), med.d = map(data, ~getStat(., "Tajima.D_1")), med.e = map(data, ~getStat(., "Zeng.E_1")), med.h = map(data, ~getStat(., "Fay.Wu.H_1")), med.fst = map(data, ~getStat(., "Fst")), med.dxy = map(data, ~getStat(., "dxy.1.2"))) %>% select(-data) %>% unnest()
 
@@
 
-MS6.1b = ms3 %>% filter(dom==0.9) %>%  mutate("TajD" = med.d, "FayWuH" = med.h, "ZengsE" = med.e, "Fst" = med.fst, "Dxy" = med.dxy, "XPEHH" = med.xp, "iHS" = med.ihs) %>% select(sim_ploidy, dom, DS, TajD, ZengsE, FayWuH, Fst, Dxy, XPEHH, iHS) %>% group_by(sim_ploidy, dom, DS) %>% summarize_all(c("CV", "lCV", "uCV"))
+# MS6.1b = ms3 %>% filter(dom==0.9) %>%  mutate("-TajD" = med.d, "FayWuH" = med.h, "ZengsE" = med.e, "Std.Fst" = med.fst, "Dxy" = med.dxy, "XPEHH" = med.xp, "iHS" = med.ihs) %>% select(sim_ploidy, dom, DS, `-TajD`, ZengsE, FayWuH, Std.Fst, Dxy, XPEHH, iHS) %>% group_by(sim_ploidy, dom, DS) %>% summarize_all(c("CV", "lCV", "uCV"))
 
-MS6.1b = ms3 %>% mutate("TajD" = med.d, "FayWuH" = med.h, "ZengsE" = med.e, "Fst" = med.fst, "Dxy" = med.dxy, "XPEHH" = med.xp, "iHS" = med.ihs) %>% select(sim_ploidy, dom, DS, TajD, ZengsE, FayWuH, Fst, Dxy, XPEHH, iHS) %>% group_by(sim_ploidy, dom, DS) %>% summarize_all(c("CV", "lCV", "uCV"))
+MS6.1b = ms3 %>% mutate("-TajD" = med.d, "FayWuH" = med.h, "ZengsE" = med.e, "Std.Fst" = med.fst, "Dxy" = med.dxy, "XPEHH" = med.xp, "iHS" = med.ihs) %>% select(sim_ploidy, dom, DS, `-TajD`, ZengsE, FayWuH, Std.Fst, Dxy, XPEHH, iHS) %>% group_by(sim_ploidy, dom, DS) %>% summarize_all(c("CV", "lCV", "uCV"))
 
-MS6.1b %>% filter(dom==0.1) %>% melt(., id.var = c("sim_ploidy", "DS")) %>% separate(variable, c("variable","XX"), "_") %>% spread(XX, value) %>% filter(variable %in% c("TajD", "Fst", "iHS", "XPEHH")) %>% mutate(Variable = factor(variable, levels=c("TajD", "Fst", "iHS", "XPEHH"))) %>% ggplot(., aes(y = CV, fill = as.factor(DS), x = as.factor(sim_ploidy))) + geom_bar(stat="identity", position = position_dodge()) + geom_errorbar(aes(ymin = lCV, ymax = uCV, width = 0.5), position = position_dodge(width = 0.9)) + scale_fill_discrete(name = "Sampling", labels=c("Equal Individuals", "Equal Alleles")) + scale_y_continuous(labels=scaleFUN) + ylab("CV[MaxValue]") + xlab("Ploidy") + facet_wrap(~Variable, scales = "free", shrink = T, nrow = 1) + theme_bw() + theme(axis.text.y=element_blank(), axis.title.y=element_text(size=16), axis.text.x=element_text(size=14), axis.title.x=element_text(size=16), legend.text = element_text(size=13), legend.title = element_text(size=14), strip.text = element_text(size=14))
-MS6.1b %>% filter(dom==0.9) %>% melt(., id.var = c("sim_ploidy", "DS")) %>% separate(variable, c("variable","XX"), "_") %>% spread(XX, value) %>% filter(variable %in% c("TajD", "Fst", "iHS", "XPEHH")) %>% mutate(Variable = factor(variable, levels=c("TajD", "Fst", "iHS", "XPEHH"))) %>% ggplot(., aes(y = CV, fill = as.factor(DS), x = as.factor(sim_ploidy))) + geom_bar(stat="identity", position = position_dodge()) + geom_errorbar(aes(ymin = lCV, ymax = uCV, width = 0.5), position = position_dodge(width = 0.9)) + scale_fill_discrete(name = "Sampling", labels=c("Equal Individuals", "Equal Alleles")) + scale_y_continuous(labels=scaleFUN) + ylab("CV[MaxValue]") + xlab("Ploidy") + facet_wrap(~Variable, scales = "free", shrink = T, nrow = 1) + theme_bw() + theme(axis.text.y=element_blank(), axis.title.y=element_text(size=16), axis.text.x=element_text(size=14), axis.title.x=element_text(size=16), legend.text = element_text(size=13), legend.title = element_text(size=14), strip.text = element_text(size=14))
+MS6.1b %>% filter(dom==0.1) %>% melt(., id.var = c("sim_ploidy", "DS")) %>% separate(variable, c("variable","XX"), "_") %>% spread(XX, value) %>% filter(variable %in% c("-TajD", "Std.Fst", "iHS", "XPEHH")) %>% mutate(Variable = factor(variable, levels=c("-TajD", "Std.Fst", "iHS", "XPEHH"))) %>% ggplot(., aes(y = CV, fill = as.factor(DS), x = as.factor(sim_ploidy))) + geom_bar(stat="identity", position = position_dodge()) + geom_errorbar(aes(ymin = lCV, ymax = uCV, width = 0.5), position = position_dodge(width = 0.9)) + scale_fill_discrete(name = "Sampling", labels=c("Equal Individuals", "Equal Alleles")) + scale_y_continuous(labels=scaleFUN) + ylab("CV[MaxValue]") + xlab("Ploidy") + facet_wrap(~Variable, scales = "free", shrink = T, nrow = 1) + theme_bw() + theme(axis.text.y=element_blank(), axis.title.y=element_text(size=16), axis.text.x=element_text(size=14), axis.title.x=element_text(size=16), legend.text = element_text(size=13), legend.title = element_text(size=14), strip.text = element_text(size=14))
+MS6.1b %>% filter(dom==0.9) %>% melt(., id.var = c("sim_ploidy", "DS")) %>% separate(variable, c("variable","XX"), "_") %>% spread(XX, value) %>% filter(variable %in% c("-TajD", "Std.Fst", "iHS", "XPEHH")) %>% mutate(Variable = factor(variable, levels=c("-TajD", "Std.Fst", "iHS", "XPEHH"))) %>% ggplot(., aes(y = CV, fill = as.factor(DS), x = as.factor(sim_ploidy))) + geom_bar(stat="identity", position = position_dodge()) + geom_errorbar(aes(ymin = lCV, ymax = uCV, width = 0.5), position = position_dodge(width = 0.9)) + scale_fill_discrete(name = "Sampling", labels=c("Equal Individuals", "Equal Alleles")) + scale_y_continuous(labels=scaleFUN) + ylab("CV[MaxValue]") + xlab("Ploidy") + facet_wrap(~Variable, scales = "free", shrink = T, nrow = 1) + theme_bw() + theme(axis.text.y=element_blank(), axis.title.y=element_text(size=16), axis.text.x=element_text(size=14), axis.title.x=element_text(size=16), legend.text = element_text(size=13), legend.title = element_text(size=14), strip.text = element_text(size=14))
 ```

### 2019-12-09 scripts/ms_accessories.Rmd
overdue update

@@
 knitr::opts_chunk$set(echo = TRUE)
-msr = read.table("~/Documents/Research/PloidySim/mssel_out_R3.txt",head=T)
-msr$s = as.factor(msr$s)
-msr %<>% mutate(Alt=ifelse(str_detect(substr(subrep,2,9), "Alt"), "Alt", "Org"))
-msr['ALTPloidy'] = paste(msr$ploidy, msr$Alt)
-msr$ALTPloidy = as.factor(msr$ALTPloidy)
-
-msr["REP"] = paste(msr$s, msr$dom, msr$rep, msr$Alt)
+#Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
+library(assertthat)
+library(ggplot2)
+library(dplyr)
+library(tidyr)
+library(PopGenome)
+library(stringr)
+library(data.table)
 
@@
 
-## R Markdown
-
-This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.
-
-When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.
-You can embed an R code chunk like this:
-
+HW Genotype frequencies for diploids and tetraploids
 ```{r}
-
-ggplot(msr, aes(x=bp.end, y = div2, color = as.factor(ploidy), linetype=as.factor(sel))) + geom_smooth() + facet_grid(~dom)
-
-ggplot(msr[msr$dom=="additive" & msr$s!=0.001,], aes(x=bp.end, y = div2, color = as.factor(ALTPloidy), linetype = s)) + geom_smooth(method="loess",span=0.2, size=1, se=F) + xlab("Position") + scale_color_brewer(limits=c("2 Org", "2 Alt","4 Alt","4 Org"), labels = c("Dip/Dip", "Tet/Dip", "Dip/Tet","Tet/Tet"),palette = "RdBu") + guides(linetype=guide_legend(title="Sel.
-Coeff."), color = guide_legend(title="Traj/Params"))
-
-ggplot(msr[msr$s!=0.001,], aes(x=bp.end, y = div2, color = as.factor(ALTPloidy), linetype = s)) + geom_smooth(method="loess",span=0.2, size=1, se=F) + xlab("Position") + scale_color_brewer(limits=c("2 Org", "2 Alt","4 Alt","4 Org"), labels = c("Dip/Dip", "Tet/Dip", "Dip/Tet","Tet/Tet"),palette = "RdBu") + facet_grid(~dom) + guides(linetype=guide_legend(title="Sel.
-Coeff."), color = guide_legend(title="Traj/Params")) + theme_bw() + ylab("Diversity")
-
-```
-
-Functions to generate allele frequency trajectory of beneficial alleles
-```{r}
-
+# Generate HW genotype frequencies for dips and tets
 genoFreqs = function(freqs){
@@
 
+# Calculate diploid/tetraploid genotype frequencies across entire range of allele frequency values
 freqs = genoFreqs(seq(0,1,0.01))
 
-ggplot(freqs, aes(x = p, y = value, color = as.factor(Ploidy), group = variable)) + geom_line() + scale_color_manual(name="Ploidy", values = c('red','blue')) + annotate("text", x = 0.25, y = 0.625, label="aa", color = "red") + annotate("text", x = 0.5, y = 0.55, label="Aa", color = "red") + annotate("text", x = 0.75, y = 0.625, label="AA", color = "red") + annotate("text", x = 0.085, y = 0.6, label="aaaa", color = "blue") + annotate("text", x = 0.085, y = 0.365, label="Aaaa", color = "blue") + annotate("text", x = 0.5, y = 0.395, label="AAaa", color = "blue") + annotate("text", x = 0.915, y = 0.365, label="AAAa", color = "blue") + annotate("text", x = 0.915, y = 0.6, label="AAAA", color = "blue") + ylab("Genotype Frequency") + xlab("Allele Frequency") + theme_bw()
+# Plot HW genotype frequencies
+ggplot(freqs, aes(x = p, y = value, color = as.factor(Ploidy), group = variable)) + geom_line() + scale_color_manual(name="Ploidy", values = c("#F8766D", "#00BA38")) + annotate("text", x = 0.28, y = 0.625, label="aa", color = "#F8766D", size = 6) + annotate("text", x = 0.5, y = 0.55, label="Aa", color = "#F8766D", size = 6) + annotate("text", x = 0.72, y = 0.625, label="AA", color = "#F8766D", size = 6) + annotate("text", x = 0.055, y = 0.6, label="aaaa", color = "#00BA38", size = 6) + annotate("text", x = 0.055, y = 0.365, label="Aaaa", color = "#00BA38", size = 6) + annotate("text", x = 0.5, y = 0.415, label="AAaa", color = "#00BA38", size = 6) + annotate("text", x = 0.955, y = 0.365, label="AAAa", color = "#00BA38", size = 6) + annotate("text", x = 0.955, y = 0.6, label="AAAA", color = "#00BA38", size = 6) + ylab("Genotype Frequency") + xlab("Allele Frequency") + theme_bw() + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18),axis.text.x=element_text(size=16),axis.title.x=element_text(size=18),legend.text = element_text(size=16), legend.title = element_text(size=18))
 
-dipTraj = function(s, h, start_freq, end_freq, max_gens){
-  df = data.frame("s" = s, "h1" = h, "gen" = 0, "freq" = start_freq, "dp1" = 0, "dp2" = 0, "w.bar" = 0, "var.w" = 0, "w.bar.p" = 0, "h0" = NA, "h2" = NA, "ploidy" = as.factor(2))
+freqs %>% filter(Ploidy == 2) %>% ggplot(., aes(x = p, y = value, color = "#F8766D", group = variable)) + geom_line() + scale_color_manual(name="Ploidy", values = c("#F8766D"), label = "2") + annotate("text", x = 0.28, y = 0.625, label="aa", color = "#F8766D", size = 6) + annotate("text", x = 0.5, y = 0.55, label="Aa", color = "#F8766D", size = 6) + annotate("text", x = 0.72, y = 0.625, label="AA", color = "#F8766D", size = 6) + ylab("Genotype Frequency") + xlab("Allele Frequency") + theme_bw() + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18),axis.text.x=element_text(size=16),axis.title.x=element_text(size=18),legend.text = element_text(size=16), legend.title = element_text(size=18))
+
+ggplot(freqs, aes(x = p, y = value, color = as.factor(Ploidy), group = variable)) + geom_line() + scale_color_manual(name="Ploidy", values = c("#F8766D", "#00BA38")) + annotate("text", x = 0.28, y = 0.625, label="aa", color = "#F8766D", size = 6) + annotate("text", x = 0.5, y = 0.55, label="Aa", color = "#F8766D", size = 6) + annotate("text", x = 0.72, y = 0.625, label="AA", color = "#F8766D", size = 6) + annotate("text", x = 0.055, y = 0.6, label="aaaa", color = "#00BA38", size = 6) + annotate("text", x = 0.055, y = 0.365, label="Aaaa", color = "#00BA38", size = 6) + annotate("text", x = 0.5, y = 0.415, label="AAaa", color = "#00BA38", size = 6) + annotate("text", x = 0.955, y = 0.365, label="AAAa", color = "#00BA38", size = 6) + annotate("text", x = 0.955, y = 0.6, label="AAAA", color = "#00BA38", size = 6) + ylab("Genotype Frequency") + xlab("Allele Frequency") + theme_bw() + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18),axis.text.x=element_text(size=16),axis.title.x=element_text(size=18),legend.text = element_text(size=16), legend.title = element_text(size=18))
+```
+
+Allele frequency trajectories plot (dips and tets)
+```{r}
+# Generate allele frequency trajectory based on deterministic recursion equations   
+getTraj = function(s, dom, ploidy, start_freq, N = -9, end_freq = 0.99, maxGens = 9999, maxTries = 10){
+  dom_coeffs = getDomCoefs(dom, ploidy)
+  attempts = 0
   p = start_freq
+  k = ploidy
   gen = 0
-  fits = c(1 + s, 1 + (s * h), 1) / (1 + s)
-  while (p < end_freq & gen < max_gens){
+  while (attempts <= maxTries & p < end_freq & gen <= maxGens){
+    df = data.frame("s" = s, "dom" = dom, "gen" = 0, "freq" = start_freq, "dp1" = 0, "w.bar" = 0, "ploidy" = ploidy)
+    p = start_freq
+    dp1 = 0
+    gen = 0
+    het_fits = 1 + dom_coeffs * s
+    fits = c(1, het_fits, 1 + s) / (1 + s)
+    while (p < end_freq & p > 0 & gen <= maxGens){
       q = 1 - p
-    Gfreqs = c(p ^ 2, 2 * p * q, q ^ 2)
-    num = (Gfreqs[1] * fits[1]) + (p * q * fits[2])
-    w.bar.p = (p * fits[1]) + (q * fits[2])
-    w.bar = sum(Gfreqs * fits)
-    p_prime = num / w.bar
+      i = seq(0, k)
+      Num = sum(choose(k, i) * ((k - i) / k) * (p ^ (k - i)) * (q ^ i) * rev(fits))
+      Den = sum(choose(k, i) * (p ^ (k - i)) * (q ^ i) * rev(fits))
+      p_prime = Num / Den
+      if (N != -9){
+        p_prime = sum(rbinom(N, k, p_prime)) / (k * N) 
+      }
+      df = rbind(df, c(s, dom, gen, p, dp1, Den, k))
       dp1 = p_prime - p
-    dp2 = (p * (w.bar.p - w.bar)) / w.bar
       p = p_prime
-    var.w = sum((Gfreqs * (fits - w.bar) ^ 2) / length(Gfreqs))
       gen = gen + 1
-
-    df = rbind(df, c(s, h, gen, p, dp1, dp2, w.bar, var.w, w.bar.p, NA, NA, 2))
+    }
+    df = rbind(df, c(s, dom, gen, p, dp1, Den, k))
+    attempts = attempts + 1
+  }
+  if (attempts > maxTries & nrow(df) <= maxGens){
+    print(paste("Beneficial allele was lost due to drift for", maxTries, "consecutive attempts"))
+  }
+  if (nrow(df) > maxGens){
+    print(paste("Beneficial allele did not fix before the maximum number of generations (", maxGens, ")."))
   }
@@
 
-tetTraj = function(s, h2, h1, h0, start_freq, end_freq, max_gens){
-  df = data.frame("s" = s, "h1" = h1, "gen" = 0, "freq" = start_freq, "dp1" = 0, "dp2" = 0, "w.bar" = 0, "var.w" = 0, "w.bar.p" = 0, "h0" = h0, "h2" = h2, "ploidy" = as.factor(4))
-  p = start_freq
-  gen = 0
-  freq = c(p)
-  fits = c(1 + s, 1 + (s * h0), 1 + (s * h1), 1 + (s * h2), 1) / (1 + s)
-  while (p < end_freq & gen < max_gens){
+#E.g
+traj = rbind(getTraj(0.1, 0, 2, 0.05), getTraj(0.1, 0, 4, 0.05))
+traj = rbind(traj, getTraj(0.1, 0.5, 2, 0.05))
+traj = rbind(traj, getTraj(0.1, 0.5, 4, 0.05))
+traj = rbind(traj, getTraj(0.1, 1, 2, 0.05))
+traj = rbind(traj, getTraj(0.1, 1, 4, 0.05))
+
+ggplot(traj, aes(x=gen, y=freq, linetype=as.factor(dom), color=as.factor(ploidy))) + geom_line() + scale_color_manual(name="Ploidy",values=c('red','blue')) + scale_linetype_discrete(name="Dominance", labels=c("Recessive","Additive","Dominant")) + xlim(0,300) + theme_bw() + xlab("Generation") + ylab("Allele Frequency")
+
+```
+
+Allele frequency trajectories for additive allele with arbitrary ploidy
+```{r}
+params = data.frame("s" = rep(0.1,9), "dom" = c(rep(0.5,3), rep(0.1,3), rep(0.9,3)), "ploidy" = rep(c(2,4,8),3), "start" = rep(0.05, 9))
+
+dat = foreach(i = 1:nrow(params), .combine=rbind) %do% {
+  getTraj(params[i,]$s, params[i,]$dom, params[i,]$ploidy, params[i,]$start)
+}
+
+ggplot(traj, aes(x=gen, y=freq, linetype=as.factor(dom), color=as.factor(ploidy))) + geom_line() + scale_color_manual(name="Ploidy",values=c('red','blue')) + scale_linetype_discrete(name="Dominance", labels=c("Recessive","Additive","Dominant")) + xlim(0,300) + theme_bw() + xlab("Generation") + ylab("Allele Frequency")
+```
+
+Dominance functions
+```{r}
+getDomCoefs = function(dominance, ploidy = 100){
+  if (dominance == 0){
+    coeffs = rep(0, ploidy - 1)
+  }
+  else if (dominance == 1){
+    coeffs = rep(1, ploidy - 1)
+  }
+  else {
+    dom = (1 - dominance) - 0.5
+    dom = abs((dom * 10 + sign(dom)) ^ sign(dom))
+    coeffs = (seq(1, ploidy - 1) / ploidy) ^ dom
+  }
+  return(coeffs)
+}
+
+doms = c(seq(0,1, 0.1))
+Doms = as.data.frame(sapply(doms, getDomCoefs))
+Doms = rbind(c(0,0,0,0,0,0,0), Doms, c(1,1,1,1,1,1,1))
+colnames(Doms) = doms
+Doms = cbind(Doms, data.frame("i/k"=seq(0,100) / 100))
+mDoms = melt(Doms, id.var = "i.k")
+ggplot(mDoms, aes(x = i.k, y = value, color = variable)) + geom_line() + scale_color_discrete(name = "Dominance\nScalar") + theme_bw() + xlab("i / k") + ylab("Dominance Coefficient")
+```
+
+```{r}
+#Fixation probs of diploids as function of N
+getFix = function(p, s, N){
+  num = 1 - exp(-4*N*s*p)
+  den = 1 - exp(-4*N*s)
+  return(num / den)
+}
+
+# Generate fitness stats as a function of allele frequency
+getFits = function(freqs, s, h1, h, h3){
+  df = data.frame("s" = s, "h" = h, "freq" = s, "w.bar" = 0, "var.w" = 0, "w.bar.p" = 0, "h1" = NA, "h3" = NA, "ploidy" = 2)
+  assert_that(length(h1) == length(h))
+  assert_that(length(h) == length(h3))
+  for (j in 1:length(s)){
+    for(k in 1:length(h)){
+    for (i in 1:length(freqs)){
+      p = freqs[i]
       q = 1 - p
-    Gfreqs = c(p ^ 4, 4 * p^3 * q, 6 * p^2 * q^2, 4 * p * q^3, q ^ 4)
-    num = (Gfreqs[1] * fits[1]) + (3 * p ^ 3 * q * fits[2]) + (3 * p ^ 2 * q ^ 2 * fits[3]) + (p * q ^ 3 * fits[4])
-    w.bar.p = ((p ^ 3) * fits[1]) + (3 * (p ^ 2) * q * fits[2]) + (3 * p * (q ^ 2) * fits[3]) + ((q ^ 3) * fits[4])
-    w.bar = sum(Gfreqs * fits)
-    p_prime = num / w.bar
-    dp1 = p_prime - p
-    dp2 = (p * (w.bar.p - w.bar)) / w.bar
-    p = p_prime
-    var.w = sum((Gfreqs * (fits - w.bar) ^ 2) / length(Gfreqs))
-    gen = gen + 1
-    df = rbind(df, c(s, h1, gen, p, dp1, dp2, w.bar, var.w, w.bar.p, h0, h2, 4))
+      Tfits = c(1 + s[j], 1 + (s[j] * h3[k]), 1 + (s[j] * h[k]), 1 + (s[j] * h1[k]), 1) / (1 + s[j])
+      TGfreqs = c(p ^ 4, 4 * p^3 * q, 6 * p^2 * q^2, 4 * p * q^3, q ^ 4)
+      Tw.bar = sum(TGfreqs * Tfits)
+      Dfits = c(1 + s[j], 1 + (s[j] * h[k]), 1) / (1 + s[j])
+      DGfreqs = c(p ^ 2, 2 * p * q, q ^ 2)
+      Dw.bar = sum(DGfreqs * Dfits)
+      Tvar.w = sum((TGfreqs * (Tfits - Tw.bar) ^ 2) / length(TGfreqs))
+      Dvar.w = sum((DGfreqs * (Dfits - Dw.bar) ^ 2) / length(DGfreqs))
+      Dw.bar.p = (p * Dfits[1]) + (q * Dfits[2])
+      Tw.bar.p = ((p ^ 3) * Tfits[1]) + (3 * (p ^ 2) * q * Tfits[2]) + (3 * p * (q ^ 2) * Tfits[3]) + ((q ^ 3) * Tfits[4])
+      df = rbind(df, c(s[j], h[k], p, Dw.bar, Dvar.w, Dw.bar.p, NA, NA, 2))
+      df = rbind(df, c(s[j], h[k], p, Tw.bar, Tvar.w, Tw.bar.p, h1[k], h3[k], 4))
+    }
+    }
   }
@@
 
+# Function to loop over all possible combinations of s and h.
+simTraj = function(s = c(0.1, 0.01, 0.001), h2 = c(0.25, 0, 1), h1 = c(0.5, 0, 1), h0 = c(0.75, 0, 1), start_freq =  0.05, end_freq = 1.0, maxGen = 9999){
+  traj = data.frame()
+  for (i in 1:length(s)){
+    for (j in 1:length(h1)){
+      print(paste("Starting; s =", s[i], ", h =", h1[j]))
+      jj = dipTraj(s[i], h1[j], start_freq, end_freq, maxGen)
+      kk = tetTraj(s[i], h2[j], h1[j], h0[j], start_freq, end_freq, maxGen)
+      traj = rbind(traj, jj)
+      traj = rbind(traj, kk)
+    }
+  }
+  return(traj)
+}
+
+# Other plots
+
+ggplot(traj, aes(x=gen, y=freq, linetype=as.factor(s), color=ploidy)) + geom_line()+facet_grid(~h1,scales="free_x") + scale_color_discrete()
+
+ggplot(traj[traj$s==0.1,], aes(x=gen, y=var.w, linetype=as.factor(h1), color=ploidy)) + geom_line() + scale_color_manual(name="Ploidy",values=c("red","blue")) + scale_linetype_discrete(name="Dominance", labels=c("Recessive","Additive","Dominant")) + xlab("Generation") + ylab("Variance in Fitness") + theme_bw() + scale_x_log10()
+
+ggplot(traj[traj$s==0.1,], aes(x=gen, y=w.bar, linetype=as.factor(h1), color=ploidy)) + geom_line() + scale_color_manual(name="Ploidy",values=c("red","blue")) + scale_linetype_discrete(name="Dominance", labels=c("Recessive","Additive","Dominant")) + xlab("Generation") + ylab("Mean Fitness") + theme_bw() + scale_x_log10()
+
+ggplot(traj[traj$s==0.1,], aes(x=gen, y=freq, linetype=as.factor(s), color=ploidy)) + geom_line() + scale_color_manual(name="Ploidy",values=c("red","blue")) + scale_linetype_discrete(name="Dominance", labels=c("Recessive","Additive","Dominant")) + ylab("Allele Frequency") + xlab("Generation") + theme_bw()
+
+fits = getFits(seq(0,1,0.01), 0.1, 0.25, 0.5, 0.75)
+fits = rbind(fits, getFits(seq(0,1,0.01), 0.1, 1, 1, 1))
+fits = rbind(fits, getFits(seq(0,1,0.01), 0.1, 0, 0, 0))
+
+ggplot(fits[fits$s==0.1,], aes(x=freq, y=var.w, color = as.factor(ploidy), linetype=as.factor(h1))) + geom_line() + scale_color_manual(name="Ploidy",values=c("red","blue")) + scale_linetype_discrete(name="Dominance", labels=c("Recessive","Additive","Dominant")) + xlab("Allele Frequency") + ylab("Variance in Fitness") + theme_bw()
+
+ggplot(fits[fits$s==0.1,], aes(x=freq, y=w.bar, color = as.factor(ploidy), linetype=as.factor(h1))) + geom_line() + scale_color_manual(name="Ploidy",values=c("red","blue")) + scale_linetype_discrete(name="Dominance", labels=c("Recessive","Additive","Dominant")) + xlab("Allele Frequency") + ylab("Mean Fitness") + theme_bw()
+
+```
+
+OLD or incomplete ideas
+```{r}
+
+# Attempting to implement the diffusion approximations for dips and tets...currently not working
 difTraj = function(s, start_freq, end_freq, N, ploidy, max_gens = 10000){
@@
 
-getFits = function(freqs, s, h0, h1, h2){
-  df = data.frame("s" = s, "h1" = h1, "freq" = s, "w.bar" = 0, "var.w" = 0, "w.bar.p" = 0, "h0" = NA, "h2" = NA, "ploidy" = 2)
-  for (i in 1:length(freqs)){
-    p = freqs[i]
-    q = 1 - p
-    Tfits = c(1 + s, 1 + (s * h0), 1 + (s * h1), 1 + (s * h2), 1) / (1 + s)
-    TGfreqs = c(p ^ 4, 4 * p^3 * q, 6 * p^2 * q^2, 4 * p * q^3, q ^ 4)
-    Tw.bar = sum(TGfreqs * Tfits)
-    Dfits = c(1 + s, 1 + (s * h1), 1) / (1 + s)
-    DGfreqs = c(p ^ 2, 2 * p * q, q ^ 2)
-    Dw.bar = sum(DGfreqs * Dfits)
-    Tvar.w = sum((TGfreqs * (Tfits - Tw.bar) ^ 2) / length(TGfreqs))
-    Dvar.w = sum((DGfreqs * (Dfits - Dw.bar) ^ 2) / length(DGfreqs))
-    Dw.bar.p = (p * Dfits[1]) + (q * Dfits[2])
-    Tw.bar.p = ((p ^ 3) * Tfits[1]) + (3 * (p ^ 2) * q * Tfits[2]) + (3 * p * (q ^ 2) * Tfits[3]) + ((q ^ 3) * Tfits[4])
-    df = rbind(df, c(s, h1, p, Dw.bar, Dvar.w, Dw.bar.p, NA, NA, 2))
-    df = rbind(df, c(s, h1, p, Tw.bar, Tvar.w, Tw.bar.p, h0, h2, 4))
-  }
-  return(df[-1,])
-}
-
-s = c(0.1, 0.01, 0.001)
-h1 = c(0.5, 0, 1)
-h0 = c(0.75, 0, 1)
-h2 = c(0.25, 0, 1)
-
-simTraj = function(s, h0, h1, h2, start_freq, end_freq, maxGen){
-  traj = data.frame()
-  for (i in 1:length(s)){
-    for (j in 1:length(h1)){
-      print(paste("Starting; s =", s[i], ", h =", h1[j]))
-      jj = dipTraj(s[i], h1[j], start_freq, end_freq, maxGen)
-      kk = tetTraj(s[i], h2[j], h1[j], h0[j], start_freq, end_freq, maxGen)
-      traj = rbind(traj, jj)
-      traj = rbind(traj, kk)
-    }
-  }
-  return(traj)
-}
-
-traj = simTraj(s, h0, h1, h2, 0.05, 1.0, 9999)
-
-ggplot(traj, aes(x=gen, y=freq, linetype=as.factor(s), color=ploidy)) + geom_line()+facet_grid(~h1,scales="free_x") + scale_color_discrete()
-
-ggplot(traj[traj$s==0.1,], aes(x=gen, y=freq, linetype=as.factor(s), color=ploidy)) + geom_line() + scale_color_discrete()
-
-ggplot(fits[fits$s==0.1,], aes(x=freq, y=var.w, color = as.factor(ploidy), linetype=as.factor(h1))) + geom_line() + scale_color_manual(name="Ploidy",values=c("red","blue")) + scale_linetype_discrete(name="Dominance", labels=c("Recessive","Additive","Dominant")) + xlab("Allele Frequency") + ylab("Variance in Fitness") + theme_bw()
-
-ggplot(fits[fits$s==0.1,], aes(x=freq, y=w.bar, color = as.factor(ploidy), linetype=as.factor(h1))) + geom_line() + scale_color_manual(name="Ploidy",values=c("red","blue")) + scale_linetype_discrete(name="Dominance", labels=c("Recessive","Additive","Dominant")) + xlab("Allele Frequency") + ylab("Mean Fitness") + theme_bw()
-
-```
-
-```{r}
-
+#Functions to run mssell
 traj_file = "/Users/pmonnahan/Documents/Research/PloidySim/mssel_output/mssel_input/traj_p4_s0.001_N10000_recessive_rep4-4Alt.txt"
+traj_file = "/Users/pmonnahan/Documents/Research/PloidySim/testing.txt"
 
 msselRun = function(N, n, traj_file, L = 1000000, mu = 1e-8, r = 1e-8, ploidy = 2, numWindows = 200, slideRate = 0.5, selPos = 0.5, selPop = 2, ms = "/Users/pmonnahan/Documents/Research/code/dmc/mssel_modified/mssel", ms_summarize = "/Users/pmonnahan/Documents/Research/PloidySim/scripts/ms_summarize.R"){
-
+  options(scipen=999)
   p = ploidy
@@
   args2 = paste(out1, out2, L, numWindows, slideRate, Npops, selPop, n * p, n * p)
-
+  print(args1)
+  print(args2)
   system2(ms, args1, stdout = out1)
@@
 dat = rbind(dat, new_dat)
+
+## Stochastic simulation of selection for a beneficial allele
+PloidyForSim = function(ploidy,  N, s, h, start_freq, end_freq, maxGen, maxTries){
+
+  assert_that(ploidy - length(h) == 1)
+  attempts = 0
+
+  #Sample individuals to reproduce
+  # taken from https://stats.stackexchange.com/questions/67911/how-to-sample-from-a-discrete-distribution
+  sampleDist = function(PLOIDY, n, genoFreqs) { 
+    sample(x = seq(0, PLOIDY), n, replace = T, prob = genoFreqs)
+  }
+
+  #Initalize population
+  fits = sort( c(1, 1 + h * s, 1 + s) / (1 + s))
+  Pop = rbinom(n = N, size = ploidy, prob = start_freq)
+  p = sum(Pop) / (ploidy * N)
+  freqs = c(p)
+
+  while(p < end_freq & length(freqs) < maxGen & attempts < maxTries){
+    #Retry if stochastic loss of beneficial allele in previous generation
+    if ( p == 0 ){
+      Pop = rbinom(n = N, size = ploidy, prob = start_freq)
+      p = sum(Pop) / (ploidy * N)
+      freqs = c(p)
+      attempts = attempts + 1
+    }
+
+    geno_freq = c( table(factor(Pop, levels = as.character(seq(0, ploidy)))) / N )
+    g_prime = ( fits * geno_freq ) / sum(fits * geno_freq) 
+    # Make individuals for next generation
+    p1 = sampleDist(length(g_prime) - 1, N, g_prime)
+    p2 = sampleDist(length(g_prime) - 1, N, g_prime)
+    Pop = c()
+    for (i in 1:N){
+      g1 = sample(c(rep(0, ploidy - p1[i]), rep(1, p1[i])), ploidy / 2, replace = F)
+      g2 = sample(c(rep(0, ploidy - p2[i]), rep(1, p2[i])), ploidy / 2, replace = F)
+      Pop = c(Pop, sum(g1) + sum(g2))
+    }
+    p = sum(Pop) / (ploidy * N)
+    print(p)
+    freqs = c(freqs, p)
+  }
+  return(freqs)
+}
+
+writeTraj = function(file, traj, numPops, selPops, timeScale, trajName = "rep1"){
+  gen = seq(1, length(traj) + 1) / timeScale
+  traj = rev(traj)
+  traj = c(traj, 0)
+  anc_traj = rep(0, length(traj))
+  fileConn = file(file)
+  # writeLines(c(paste("ntraj:", "1"), paste("npop:", numPops), "", paste("n:", length(traj), trajName), paste(gen, traj, anc_traj), sep="\t"), fileConn)
+  writeLines(c(paste("ntraj:", "1"), paste("npop:", numPops), paste("n:", length(traj), trajName)), con = fileConn)
+
+  dat = data.frame("gen"=gen, "traj"=traj, "anc"=anc_traj)
+  print(dat)
+  write.table(dat, file, quote=F, col.names = F, row.names = F, sep="\t", append=T)
+  close(fileConn)
+}
 ```
-
-Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

### 2019-12-09 Ploidy_Forward_Sim.py

@@ -1,128 +1,0 @@
-import collections
-import numpy as np
-import argparse
-
-
-def simulate(ploidy, starting_freq, pop_size, s, dom):
-
-    pop = np.random.binomial(ploidy, starting_freq, pop_size)
-
-    # Makes a dictionary with keys equal to allele count and value equal to number of individuals with this allele count
-    counter = collections.Counter(pop)
-
-    geno_freq = [0.0 for x in range(0, ploidy + 1)]
-    # can we replace g_prime with p_prime?  
-    counts = list(counter.values())
-    indexes = list(counter.keys())
-    for x in indexes:
-        geno_freq[x] = counts[x] / pop_size
-
-    af = sum(pop) / (ploidy * pop_size)
-    gen = 1
-    Ngen = gen / (2 * ploidy * pop_size)
-
-    fitness = [0 for x in range(0, ploidy + 1)]
-    fitness[ploidy] = 1
-    fitness[0] = 1 - s
-
-    for f in range(1, ploidy):
-        if dom == "additive":
-            h = s / ploidy
-            fitness[f] = (1 - s) + (f * h) #Is this valid?
-        elif dom == "recessive":
-            fitness[f] = (1 - s)    
-        elif dom == "dominant":
-            fitness[f] = 1
-
-    af_list = [af]
-    Ngen_list = [Ngen]
-    while af < 0.99:
-        counter = collections.Counter(pop)
-
-        geno_freq = [0.0 for x in range(0, ploidy + 1)]
-        # can we replace g_prime with p_prime?  
-        counts = list(counter.values())
-        indexes = list(counter.keys())
-        # print(counts,indexes)
-        # print(geno_freq)
-
-        Counts = [0 for i in range(0, ploidy + 1)]
-        for j, i in enumerate(indexes):
-            Counts[i] = counts[j]
-        geno_freq = [x / pop_size for x in Counts]
-
-        tot_fitness = sum([a * b for a, b in zip(geno_freq, fitness)])
-        g_prime = [a * b / tot_fitness for a, b in zip(geno_freq, fitness)] 
-        # print(af)
-        # print(geno_freq)
-        # print(g_prime)
-        if af == 0.0:
-            break
-        # Make individuals for next generation
-        new_pop = []
-        for n in range(0, pop_size):
-
-            rx1 = np.random.random()
-            rx2 = np.random.random()
-            thresh = 0
-            p1 = -9
-            p2 = -9
-            # Draw parents
[…]

### 2019-12-09 cosi2_wrapper.py

@@ -1,230 +1,0 @@
-import pandas as pd
-import sys
-import os
-import argparse
-import subprocess
-
-# Specify arguments to be read from the command line
-parser = argparse.ArgumentParser(description='This script will take a trajectory file produced from Ploidy_Forward_Sim.py, run mssel, and parse the output')
-parser.add_argument('-t', type=str, metavar='trajectory_file', required=True, help='Full path to results from Ploidy_Forward_Sim.py')
-parser.add_argument('-o', type=str, metavar='output_directory', required=True, help='Full path to output directory.')
-parser.add_argument('-mu', type=str, metavar='mutation_rate', default="0.000000015", required=False, help='specified as decimal.')
-parser.add_argument('-r', type=str, metavar='recombination_file', default="/Users/pmonnahan/Documents/Research/PloidySim/cosi2_input/model.test", required=False, help='Recombination map file')
-parser.add_argument('-reps', type=str, metavar='number_of_reps', default="1", required=False, help='Number of cosi2 reps for a single trajectory')
-parser.add_argument('-n', type=str, metavar='sample_sizes', default="10,10", required=False, help='sample size of each population specified as comma separated list.')
-parser.add_argument('-N', type=str, metavar='population_sizes', default="-9", required=False, help='size of each population')
-parser.add_argument('-L', type=str, metavar='sequence_length', default="200000", required=False, help='Total number of sites')
[…]

### 2019-12-09 ms_summarize.R

@@ -1,173 +1,0 @@
-#!/usr/bin/env Rscript
-
-require("PopGenome")
-require("stringr")
-require("data.table")
-require("dplyr")
-
-
-args = commandArgs(trailingOnly=TRUE)
-
-# test if there is at least one argument: if not, return an error
-if (length(args)==0) {
-  stop("At least one argument must be supplied (input file).n", call.=FALSE)
-} else if (length(args)==1) {
-  # default output file
-  args[2] = "out.txt"
-  # default window size
-  args[3] = 50
-}
-  
-
-# HARDCODED ARGS TO BE RELAXED LATER
-Nanc=5 #Number of ancestral samples
-Nder=5 #Number of derived/sweep samples
-Nsites=50000 #Number of sites
-winSize=50 #In terms of number of snps
-slideRate = 0.5 # Proportion of winSize that we want to slide the window
-
-# Necessary Functions
-read.ms.output <- function( txt=NA, file.ms.output=NA,MSMS=FALSE) {
-  
-  if( !is.na(file.ms.output) ) txt <- scan(file=file.ms.output,
-                                           what=character(0), sep="\n", quiet=TRUE)
-  if( is.na(txt[1]) ){
-    print("Usage: read.ms.output(txt), or read.ms.output(file=filename)")
-    return()
-  }
-  
-  
-  if(MSMS[1]==FALSE){
-    nsam   <- as.integer(strsplit(txt[1], split=" ")[[1]][2] )
-    ndraws <- as.integer(strsplit(txt[1], split=" ")[[1]][3] )
-  }
-  
-  #print(strsplit(txt[1], split=" "))
-  
-  h         <- numeric()
-  result    <- list()
-  gamlist   <- list()
-  positions <- list()
-  
-  #marker <- grep("prob",txt)
-  #probs <- sapply(strsplit(txt[marker], split=":"), function(vec) as.numeric(vec[2]))
-  #marker <- grep("time",txt)
-  #times <- sapply(strsplit(txt[marker], split="\t"), function(vec){ as.numeric(vec[2:3])} )
-  times <- NaN
-  probs <- NaN
-  
-  ## THE OUTPUT TEXT FOR EACH DRAW SHOULD CONTAIN THE WORD "segsites"
-  
-  
-  marker <- grep("segsites", txt)
-  
[…]

### 2019-12-09 mssel_wrapper.py

@@ -1,92 +1,0 @@
-import pandas as pd
-import sys
-import os
-import argparse
-import subprocess
-
-# Specify arguments to be read from the command line
-parser = argparse.ArgumentParser(description='This script will take a trajectory file produced from Ploidy_Forward_Sim.py, run mssel, and parse the output')
-parser.add_argument('-t', type=str, metavar='trajectory_file', required=True, help='Full path to results from Ploidy_Forward_Sim.py')
-parser.add_argument('-o', type=str, metavar='output_directory', required=True, help='Full path to output directory.')
-parser.add_argument('-ms', type=str, metavar='mssel_path', default="/Users/pmonnahan/Documents/Research/code/dmc/mssel_modified/mssel", required=False, help='Full path to mssel executable')
-args = parser.parse_args()
-
-args.o += "/"
-if os.path.exists(args.o) is False: os.mkdir(args.o)
-if os.path.exists(args.o + "mssel_input") is False: os.mkdir(args.o + "mssel_input")
-if os.path.exists(args.o + "mssel_output") is False: os.mkdir(args.o + "mssel_output")
-
-mu = 10**(-8)
-r = 10**(-8)
-num_reps = 10
-n_anc = 0 # number of alleles sampled from ancestral population
-n_der = 10 # number of alleles sampled from selected population
-n_sites = 200000 #number of sites
-selection_spot = 25000
-segsites=1000
-
-#Is Pandas the way to go on this? Takes a long time to read data into memory
-traj = pd.read_table(args.t,sep=r"\s*",header=0)
-
-dipTraj = traj.loc[traj['ploidy'] == 2,]
-tetTraj = traj.loc[traj['ploidy'] == 4,]
-
-# Loop over
-jobList=[] 
-for s in dipTraj.s.unique():
-	for N in dipTraj.N.unique():
-		for dom in dipTraj.dom.unique():
-			df=dipTraj.loc[(dipTraj.s == s) & (dipTraj.N == N) & (dipTraj.dom == dom),]
-			for rep in df.rep.unique():
-				traj_file = args.o + "mssel_input/traj_p2_s" + str(s) + "_N" + str(N) + "_" + dom.strip() + "_rep" + str(rep) + ".txt "
-				traj_File=open(traj_file,'w')
[…]

### 2019-12-09 scripts/PloidyHitch.R

@@ -29,11 +29,11 @@ outdir = args[1]
 outfile = args[2]
 path_to_mssel = args[3]
 dom_idx = as.numeric(args[4])
-num_tries = as.numeric(args[5])
+num_tries = as.numeric(args[5]) # Number of attempts to simulate the allele frequency trajectory.  If end_freq is not reached within max_gens, then another 'try' is made.
 current_df = args[6] # file containing data of most current df of results.  used to keep track of how many reps we've done of each param set
 recomb_rate = as.numeric(args[7]) # per-base recombination rate; r
 num_reps = as.numeric(args[8])
-num_drift_tries = as.numeric(args[9])
+num_drift_tries = 10000
 num_cores = detectCores() - 1
 
 #make tmpdir
@@ -44,17 +44,11 @@ setwd(tmpdir)
 # cl <- makeCluster(num_cores) # Do we need to leave one core to handle the results that are being returned??
 # registerDoParallel(cl)
 
-
-
-#####
-#WRITE OUT DATA PERIODICALLY SO YOU DON'T KEEP LOSING ALL DATA FROM TIMEOUTS
-#Also add a percent complete to output to see how far you are getting.
-
 ##### BEGIN: Set parameter values to explore #####
 Ploidy = c(2, 4, 8)
-pop_size = c(10000) # Keep this value above 100 and below 1000000 (computation time will increase with increasing pop_size)
+pop_size = c(1000, 10000) # Keep this value above 100 and below 1000000 (computation time will increase with increasing pop_size)
 # selection_coeff = c(0.1, 0.01) # Keep this between 0 and 1
-selection_coeff = c(0.01) # Keep this between 0 and 1
+selection_coeff = c(0.1, 0.01) # Keep this between 0 and 1
 
 # drift_gen = c(0, 1000, 10000)
 drift_gen = c(0)
@@ -64,12 +58,11 @@ dominance = dominance[dom_idx]
 
 seq_len = 1000000 # Length of sequence that we will simulate with mssel.  Increasing this value will increase computation time.
 mutation_rate = c(1e-8) # per-base mutation rate; mu
-# sampGen = c(1, 10000)
-sampGen = c(1)
-fuseTime = c(1)
-samp_num = -9 # number of individuals to sample
+sampGen = c(1, 1000, 10000)
+fuseTime = c(1, 1000, 10000)
[…]

### 2019-12-09 scripts/calcREHH.R

@@ -14,7 +14,7 @@ args = commandArgs(trailingOnly=TRUE)
 
 ms_outdir_path = args[1]
 outfile = args[2]
-downsample = 20
+downsample = -9
 files <- list.files(path = ms_outdir_path, pattern = "*.out", full.names=TRUE, recursive=FALSE)
 
 num_cores=4
@@ -229,6 +229,7 @@ RE.input = function(ms_file, num_chrom, jit_amt = 1){
   bb = read_lines(ms_file)
   aa = bb %>% parse_ms()
   haps = as.numeric(str_split(bb[1]," ")[[1]][2])
+  if (num_chrom==-9){num_chrom = haps/2}
   # L = as.numeric(str_split(bb[1]," ")[[1]][10])
   L=1000000
   hap_file1 = str_replace(ms_file,"[.]out",".hap1") #hap_file population 1
@@ -243,15 +244,17 @@ RE.input = function(ms_file, num_chrom, jit_amt = 1){
 }
 
 calcHAP = function(HapPaths){
-  invisible(capture.output(hh1 <- data2haplohh(HapPaths[1], HapPaths[3]))) #Import data
-  invisible(capture.output(hh2 <- data2haplohh(HapPaths[2], HapPaths[3])))
+  invisible(capture.output(hh1 <- data2haplohh(HapPaths[1], HapPaths[3], remove_multiple_markers = T))) #Import data
+  invisible(capture.output(hh2 <- data2haplohh(HapPaths[2], HapPaths[3], remove_multiple_markers = T)))
   ss1 = scan_hh(hh1) #Calc iHH and iES
   ss2 = scan_hh(hh2)
   
-  rsb = ies2rsb(ss1,ss2) #These are cross population haplotype estimates of selective sweep
+  rsb = ihh2ihs(ss1, freqbin = 0.1, min_maf = 0)
+  rsb = rsb$ihs
+  # rsb = ies2rsb(ss1,ss2) #These are cross population haplotype estimates of selective sweep
   xp.ehh = ies2xpehh(ss1,ss2)
   
-  colnames(rsb)[4] = "rsb.p"
+  colnames(rsb)[4] = "ihs.p"
   colnames(xp.ehh)[4] = "xpehh.p"
   HAP = merge(rsb, xp.ehh, by=c("CHR","POSITION"))
   return(HAP)
@@ -350,7 +353,7 @@ dat = foreach(i = 1:(length(files)), .combine=rbind,
             },
             error = function(e){
               message("Error: calcHAP")
[…]

### 2019-12-09 scripts/drift.py

@@ -4,12 +4,12 @@ import argparse
 import numpy
 import copy
 
-def initialize(size, ploidy, freq):
-    pop = [[] for x in range(0, size)]
+def initialize(size, ploidy, freq): 
+    pop = [[] for x in range(0, size)] #Each individual is a list of alleles (0 or 1) and the population is a list of lists.
     for i, ind in enumerate(pop):
         for k in range(0,ploidy):
             rx = random.random()
-            if rx < freq:
+            if rx < freq: # Draw alleles for each individual based on starting frequency
                 pop[i].append(1)
             else:
                 pop[i].append(0)
@@ -19,18 +19,18 @@ def drift(pop, numGens):
     popSize = len(pop)
     p = calcFreq(pop) 
     F = []
-    for i in range(0,numGens):
+    for i in range(0,numGens): #Simulate drift for specified number of generations
         if p > 0 and p < 1:
-            newpop = []
+            newpop = [] #Store individuals for next generation's population as they are created
             for j in range(0, popSize):
-                p1 = copy.deepcopy(random.choice(pop))
-                p2 = copy.deepcopy(random.choice(pop))
+                p1 = copy.deepcopy(random.choice(pop)) #Parent 1 is a random individual drawn from population
+                p2 = copy.deepcopy(random.choice(pop)) #Parent 2
 
-                g1 = [p1.pop() for x in range(0, int(len(p1)/2))]
-                g2 = [p2.pop() for x in range(0, int(len(p2)/2))]
+                g1 = [p1.pop() for x in range(0, int(len(p1)/2))] #Gamete1. Randomly sample alleles without replacement from Parent1
+                g2 = [p2.pop() for x in range(0, int(len(p2)/2))] #Gamete2
 
-                o1 = g1 + g2
-                newpop.append(o1)
+                o1 = g1 + g2 #New individual is sum of gamete lists
+                newpop.append(o1) #Add new individual to next generations' population
             p = calcFreq(newpop)
             F.append(p)
 
@@ -43,8 +43,8 @@ def calcFreq(pop):
     M = 0
     T = 0
     for ind in pop:
-        M += sum(ind)
-        T += len(ind)
+        M += sum(ind) #Tracks number of mutant (1) alleles in the population
+        T += len(ind) #Tracks total alleles
     if T != 0: p = M / T
     else: p = 0
     return(p)
@@ -69,7 +69,7 @@ if __name__ == "__main__":
 
[…]

### 2019-12-21 analysis/PaperFigures.Rmd
Figure mods

@@
 dat1 = foreach(i = 1:nrow(params), .combine=rbind) %do% {
-  getTraj(params[i,]$s, params[i,]$dom, params[i,]$ploidy, params[i,]$start, maxGens = 99999, maxTries = 1)
+  getTraj(params[i,]$s, params[i,]$dom, params[i,]$ploidy, params[i,]$start, maxGens = 600, maxTries = 1)
 }
@@
 #Figure 1A left
-dat1 %>% filter(ploidy %in% c(2, 4, 8) & dom %in% c("recessive", "additive", "dominant")) %>% ggplot(., aes(x=gen, y=freq, linetype=as.factor(dom), color=as.factor(ploidy))) + geom_line(size = 1.2) + scale_color_manual(name = "Ploidy", values = c("#F8766D", "#00BA38", "#619CFF")) + scale_linetype_manual(name = "Dominance", labels=c("Dominant", "Additive", "Recessive"), values = c("dashed", "solid", "dotted")) + xlim(0,500) + theme_bw() + xlab("Generation") + ylab("Allele Frequency") + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18),axis.text.x=element_text(size=16),axis.title.x=element_text(size=18),legend.text = element_text(size=16), legend.title = element_text(size=18))
+dat1 %>% ggplot(., aes(x=gen, y=freq, linetype=as.factor(dom), color=as.factor(ploidy))) + geom_line(size = 1.2) + scale_color_manual(name = "Ploidy", values = c("#F8766D", "#00BA38", "#619CFF")) + scale_linetype_manual(name = "Dominance", labels=c("Dominant", "Additive", "Recessive"), values = c("dashed", "solid", "dotted")) + xlim(0,500) + theme_bw() + xlab("Generation") + ylab("Allele Frequency") + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18),axis.text.x=element_text(size=16),axis.title.x=element_text(size=18),legend.text = element_text(size=16), legend.title = element_text(size=18))
 
